### 2018-10-02 paper/paper.tex
First version of manuscript

\documentclass[manuscript=letter, email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
% \usepackage{lineno}
% \linenumbers

\author{Roman M. Wyss} \affiliation{Institute of Soft Materials
  Department of Material Sciences, Eidgenössische Technische
  Hochschule (ETH) Zürich, Vladimir-Prelog-Weg 1-5, Zürich CH-8093,
  Switzerland.  }
\altaffiliation{R. M. S. and T. T. contributed equally to this work}
\author{Tian Tian} \affiliation{Institute for
  Chemical and Bioengineering Department of Chemistry and Applied
  Biosciences, Eidgenössische Technische Hochschule (ETH) Zürich,
  Vladimir-Prelog-Weg 1-5, Zürich CH-8093, Switzerland.}
\altaffiliation{R. M. S. and T. T. contributed equally to this work}

\author{Khadija Yazda} \affiliation{Nanoscience for Energy Technology and Sustainability,
Department of Mechanical and Process Engineering,
Eidgenössische Technische Hochschule (ETH) Zürich,
Tannenstrasse 3, Zürich CH-8092, Switzerland.}

\author{Hyung Gyu Park} \affiliation{Nanoscience for Energy Technology and Sustainability,
Department of Mechanical and Process Engineering,
Eidgenössische Technische Hochschule (ETH) Zürich,
Tannenstrasse 3, Zürich CH-8092, Switzerland.}

\author{Chih-Jen Shih}  \affiliation{Institute for
  Chemical and Bioengineering Department of Chemistry and Applied
  Biosciences, Eidgenössische Technische Hochschule (ETH) Zürich,
  Vladimir-Prelog-Weg 1-5, Zürich CH-8093, Switzerland.}
\email{chih-jen.shih@chem.ethz.ch}

\title{Macroscopic Salt Rejection through Electrostatically Gated Monolayer Porous Graphene}

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  Atomically thin graphene nanopores is emerging as one of the most
  promising candidates for next-generation membrane technology owing
  to the ultrahigh permeability. However, the size-exclusive mechanism
  limits its scalability as it remains technically challenging to
  drill subnanometer pores over a large area. Here we report
  macroscopic salt rejection through monolayer porous graphene with
  the pore sizes of 20$\pm$10 nanometers, overcoming the pore size
  limitation set by the hydrated radii. By electrostatically gating a
  sheet of porous graphene, we report a considerable reduction of salt
  flux by up to 55\% with the gate voltage. We systematically
  investigate the effects of salt concentration and species, including
  developing a theory to model the electrolyte diffusion through a
  nanopore in a sheet of gated monolayer graphene. The interplay
  between graphene quantum capacitance and electrical double layer is
  identified to be the main mechanism responsible for the observed
  salt rejection, when the pore size is comparable to the Debye
  screening length. Our findings reveal a new degree of freedom
  controlling the membrane potential and electrolyte permeation
  through porous two-dimensional monolayers.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage{}

\section{Introduction}
\label{sec:intro}
In the emerging field of nanofluidics, a central objective is to
manipulate transport phenomena at nanometer scale to enable new
technological opportunities for sensing and energy applications. The
reduction of characteristic dimensions in nanofluidics gives rise to
substantially different transport properties compared to their bulk
counterparts \cite{Schoch_2008}. In nanopores, for example, the effect
of surface-mediated transport becomes dominant when the pore size is
comparable to the solute diffusion length, enabling new applications,
including ionic diodes \cite{Karnik_2007}, field-effect transistors
\cite{Nam_2009}, desalination \todo[inline]{cite}, and nanopore-based DNA
sequencing \cite{Heerema_2016,Garaj_2013}, Atomically thin
two-dimensional (2D) materials, such as graphene, represent an ideal
category of membrane materials due to their ultimate permeability
\cite{Cohen_Tanugi_2012}. In electrolyte systems, specifically for the
aqueous media, early research has suggested that the separation of
ions by the pore size differentiating the hydrated radii of
$\sim{}$1-3 nm enables excellent salt rejection \todo[inline]{(cite
  Refs. [1-7] in
  https://www.nature.com/articles/ncomms11408.pdf)}. Nevertheless, the
fabrication of sub-5 nanometer porous 2D membranes over a large area
with atomic precision is technically challenging \cite{Suk_2014}
\todo[inline]{also Refs [8], [9] in the nature comm paper, as well as the
  nature comm paper itself}. Moreover, a small portion of large pores
can significantly diminish salt rejection. To address these issues,
recent research efforts have been focused on control over the surface
charges by chemical functionalization \todo[inline]{cite 7-13}. However, it
remains controversial that if the surface charges can result in a
degree of salt rejection, as the membrane potential is sensitive to
the surroundings and chemical treatment \todo[inline]{onecite}. The difficulty
in turn hinders fundamental understanding of the interactions between
the atomically thin 2D membrane and electrolyte solution. Here, we
demonstrate macroscopic salt rejection through a sheet of large-area
porous monolayer graphene using electrostatic gating.

\section{Results and discussions}
\label{sec:res}

\subsection{Free diffusion through porous graphene}
\label{sec:res-1}

Figure \ref{fig:1}a presents the experimental setup characterizing
ionic diffusion through a sheet of monolayer porous graphene (PG). Two
reservoirs, namely the high-concentration reservoir (HCR) containing
electrolyte solution with molar concentration $c_0$, and the
low-concentration reservoir (LCR) containing de-ionized (DI) water,
are separated by a PG membrane supported by polycarbonate track-etched
(PCTE) film. Magnetic stirrers are used to minimize the mass transfer
resistance in both reservoirs, and a conductivity probe is placed in
the LCR to monitor the ionic concentration as a function of time. The
membrane is attached to a piece of copper tape connected to a voltage
source applying an electrical bias VG, with the LCR grounded (Figure
\ref{fig:1}a inset). We fabricated the PCTE-supported PG using the
protocol developed by our group \todo[inline]{cite}, as schematically shown in
Figure \ref{fig:1}b. By optimizing the process, a high surface
coverage (> 98\%) of graphene on PCTE was reached (Figure
\ref{fig:1}c), allowing us to reliably characterize the ion transport
behavior (details see Supplementary Information Section S1). The
circular pores with pore diameters of 20$\pm$10 nm (Figure
\ref{fig:1}c inset) over a large area were drilled on monolayer
graphene. The system presented here allows us to systematically
investigate the diffusive flux across a sheet of porous graphene,
$\boldsymbol{J}$, driven by the gradient of electrochemical potential in
the electrolyte medium.

First, the control experiments were carried out by measuring the ionic
diffusion of seven salt species, including KCl, NaCl, LiCl,
K$_{2}$SO$_{4}$, MgSO4$_{4}$, CaCl$_{2}$ and K$_{3}$Fe(CN)$_{6}$,
through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
flux is comparably small, the conductivity versus time profile
(e.g. Figure \ref{fig:2}a) remains linear within the measurement
duration ($\sim{}$1 h), suggesting the concentration change in
individual reservoirs is negligible \todo[inline]{really?}. The diffusive
fluxes correspond to different salts were obtained by converting the
conductivity-time profiles with the calibration curves (blue bars in
Figure \ref{fig:2}b and Supplementary Figure S2). On the other hand,
for comparison purposes, based on the assumption that the membrane is
composed of cylindrical pores with uniform diameter and a low
tortuosity $\tau$ of $\sim{}$1.2 \todo[inline]{cite 14}, the molar diffusive
flux through the bare PCTE membrane,
$\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
  \begin{equation}
    \label{eq:j-pcte}
    \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi a^{2} N_{\mathrm{p}} D \Delta c}{\delta \tau}
  \end{equation}
where $a$ is the PCTE pore radius, $N_{\mathrm{p}}$ is numbers of pore
per area, $D$ is the salt diffusivity, and $\Delta c$ is the bulk
concentration difference between two reservoirs, i.e.,
$\Delta c \sim c_{0}$, $\delta$ is the thickness of the PCTE membrane,
and $\tau$ is the tortuosity. By using the salt diffusivity values
provided by the PTCE vendor (Supplementary Table SXX \todo[inline]{ref}), the
calculated diffusive fluxes (red bars in Figure \ref{fig:2}b) show
reasonable agreement with the experimental values.

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
Figure \ref{fig:2}b), remain at the same order of magnitude compared
to those of bare PCTE membrane, suggesting that the mass transfer
resistance of PG is not significant, as the permeability is high. We
observed a more pronounced decrease of diffusive flux in KCl, K$_{2}$SO$_{4}$
and K$_{3}$Fe(CN)$_{6}$ systems but not for the rest of the salts. We
hypothesized that the strong cation-$\pi$ interactions between K$^{+}$ cations
and graphene \todo[inline]{15} slow down the migration of cations along the
surface-mediated transport pathway, which has been proven as a strong
contributor at low concentration \todo[inline]{cite}.

\subsection{Salt rejection induced by electrostatic gating}
\label{sec:res-2}

We next discuss the effects of electrostatic gating on graphene. In
order to avoid any interference from the conductivity probe to the
membrane potential, the “three-interval” method, which had been used
in controlling the membrane potential in mesoporous carbon membranes
\todo[inline]{8}, is adopted here. Figure \ref{fig:2}a presents a
representative data of the measured conductivity with respect to
time. Specifically, in the first interval, the gate voltage source is
turned off and the conductivity probe is on, allowing us to obtain the
conductivity-time profile corresponding to the diffusive flux through
the PG-PCTE membrane, giving the average slope $s_{1}$. In the second
interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane after
turning off the conductivity probe, followed by the third interval, in
which the conductivity probe is turned on again to give the
corresponding slope, $s_{3}$. The slope corresponding to the second
interval, $s_{2}$, as the conductivity probe is off, is determined by
linearly interpolating the conductivities from the endpoint of
interval 1 to the starting point of interval 3. Accordingly, we define
the salt rejection factor, $\xi$, which is effectively equivalent to
the relative degree of diffusive flux decrease as follows:
\begin{equation}
  \label{eq:rejection}
  \xi = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
    - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
\end{equation}
where $\bar{s}$ is the average slope of $s_{1}$ and $s_{2}$, namely
$(s_{1} + s_{2})/2$ \todo[inline]{Should this be $(s_{1}+s_{3})/2$?},
and $\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive
flux across the PTCE-supported PG double layer as a function of
$V_{\mathrm{G}}$. Note that a positive $\xi$ between 0 and 1
represents a decrease of the diffusive flux. The factor $\xi$ enables a
reliable and stable measurement of salt rejection, as the salt species
and initial conditions may induce a degree of measurement uncertainty
between different samples. A control experiment was performed to
ensure the copper tape was not in direct contact with the ionic
solution (Supplementary Section 3).

Using 0.1 mM KCl solution in HCR, we measured $\xi$ as a function of
$V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
electrochemical reactions (Figure \ref{fig:2}c). We observe an
asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
a higher degree of salt rejection for $V_{\mathrm{G}}>0$. where
positive carriers (holes) are induced in graphene. We notice that an
increase $\xi$, or a decrease of $\boldsymbol{J}_{\mathrm{PG}}$ with
$V_{\mathrm{G}}$, showing an inverse trend compared to those observed
in ionic field effect transistors (IFETs) \todo{cite}, in which the
diffusive flux increases with the gate voltage \todo{cite 3, 23}. A
further increase of the KCl concentration $c_{0}$ influences the
attainable degree of salt rejection. $\xi$ values measured at
$V_{\mathrm{G}}$=1.25 V, $\xi_{\mathrm{max}}$, as a function of
$c_{0}$ from 10$^{-4}$ to 10$^{-2}$ M KCl (see Supplementary Section
S4) exhibit a power law dependency (Figure \ref{fig:2}d). The
$\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
law function following
$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{Const}$. As the Debye
screening length in solution, $\lambda_{\mathrm{D}}$, is inversely
proportional to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced
salt rejection originates from the modulation of the electrical double
layer (EDL), as will be discussed later.

\subsection{Self-consistent ion transport theory}
\label{sec:theory}

In order to quantitatively understand the observed $V_{\mathrm{G}}$
dependence, we develop a theory to model the coupling of graphene’s
elementary transport properties and EDL, in order to quantify the
ionic transport through a graphene nanopore. Under the assumption that
the time scale for the bulk concentration change is significantly
longer than that of ionic diffusion, the pseudo-steady state
approximation holds. Accordingly, the steady-state Nernst-Planck equation
describing the ionic transport in an electrolyte solution is given by \todo{cite}:
\begin{equation}
  \label{eq:pnp}
  \nabla \cdot \boldsymbol{J}_{i} = -\Delta \cdot (\frac{D_{i}}{k_{\mathrm{B}}T} c_{i} N_{\mathrm{A}} \nabla \mu_{i}) = 0
\end{equation}
where $\boldsymbol{J}$ is the mass flux, subscript \textit{i}
corresponds to the species (anion or cation), $D$ is the diffusivity,
$k_{\mathrm{B}}$ is the Boltzmann constant, $T$ is temperature, $c$ is
the molar concentration, $N_{\mathrm{A}}$ is the Avogadro constant,
and $\mu_{i}$ is the electrochemical potential. Under the assumption
of ideal solution, it follows \todo{cite}:
\begin{equation}
  \label{eq:mu}
  \nabla \mu_{i} = k_{\mathrm{B}} T \nabla \ln x_{i} + z_{i} e \nabla \psi
\end{equation}
where $x$ is the molar fraction, $z$ is the ionic valence, $e$ is the
unit charge, and $\psi$ is the electric potential. On the other hand,
the Poisson equation describing the electric potential distribution is
given by:
\begin{equation}
  \label{eq:poisson}
  \nabla \cdot (\varepsilon_{\mathrm{m}} \varepsilon_{0} \nabla \psi)
  =
  - N_{\mathrm{A}} e \sum_{i} c_{i} z_{i}
\end{equation}
where $\varepsilon_{\mathrm{m}}$ is the relative permittivity of
individual materials in the system. Including water and the internal
Stern layer \todo{for graphene?}, and $\varepsilon_{0}$ is the vacuum
permittivity. When applying $V_{\mathrm{G}}$ to graphene adjacent to
the electrolyte solution, charges (electrons or holes) are induced in
graphene; the electroneutrality of the entire system suggests:
\begin{equation}
  \label{eq:electro-neutral}
  \sigma_{\mathrm{G}} S_{\mathrm{G}} + \sum_{i} \int_{\Omega} z_{i} c_{i} N_{\mathrm{A}} e \mathrm{d}^{3} \Omega= 0
\end{equation}
where $\sigma_{\mathrm{G}}$ is the charge density in graphene,
$S_{\mathrm{G}}$ is the total area of graphene, and $\Omega$
corresponds to the entire volumetric domain of electrolyte
solution. Note that the graphene surface potential,
$\psi_{\mathrm{G}}$, is not equivalent to $V_{\mathrm{G}}$ due to the
graphene quantum capacitance effect \todo{cite-24} (Figure
\ref{fig:3}a) following:
\begin{equation}
  \label{eq:Vg}
  V_{\mathrm{G}} = \Delta \phi_{\mathrm{G}} + \psi_{\mathrm{G}}
\end{equation}
where $\Delta \phi_{\mathrm{G}}$ is the change of graphene’s work
function. Under the assumption that the charge neutrality point of
graphene coincides with the Dirac point at $V_{\mathrm{G}}=0$, the elementary
electronic properties of graphene give:
\begin{equation}
  \label{eq:delta-phiG}
  \Delta \phi_{\mathrm{G}} = \mathrm{sign}(\sigma_{\mathrm{G}}) \frac{\hbar v_{\mathrm{F}}}{e}
  \sqrt{\frac{\pi |\sigma_{\mathrm{G}}|}{e}}
\end{equation}
where $\hbar$ is the reduced Planck constant, and
$v_{\mathrm{F}}=1.1\times10^{6}$ m$\cdot$s$^{-1}$ is the Fermi
velocity of graphene (more details find Supplementary Section SXX
\todo{ref}). Note that the PG film fabricated experimentally is
double-layer turbostratic graphene, in which we assume the
$\Delta \phi_{\mathrm{G}} - \sigma_{\mathrm{G}}$ dependence follows
Eq. \ref{eq:delta-phiG}. The theory proposed here was solved
self-consistently by discretizing Eqs. \ref{eq:pnp}-\ref{eq:poisson}
using the finite-element method, in which the graphene surface
potential is coupled with
Eqs. \ref{eq:electro-neutral}-\ref{eq:delta-phiG} that were solved
simultaneously to reach convergent numerical solutions of
$\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ for a given
$V_{\mathrm{G}}$. Clearly, the above model yields symmetric
characteristics for $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ with
respect to $V_{\mathrm{G}}$ due to the symmetric band structure of
graphene (Eq. \ref{eq:delta-phiG}). However, for chemical vapor
deposition- (CVD) synthesized graphene used in our experiments, it is
well-recognized that the electron traps are inherently introduced
during synthesis and patterning \todo{25}, effectively increasing the
graphene quantum capacitance for $V_{\mathrm{G}}<0$ (Supplementary
Figure SXX \todo{ref}). With the nonideality in mind, hereafter, we
compare the calculations and experiments in the regime of
$V_{\mathrm{G}}>0$. For example, Figure \ref{fig:3}c presents the
calculated $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ as a function
of $V_{\mathrm{G}}$ considering the ionic diffusion through a single
20 nm-diameter nanopore drilled on a sheet of semi-infinite double
layer graphene that separates HCR containing KCl solution at
$c_{0}=0.1$ mM, and LCR at $c_{0}/10$ in axisymmetric coordinates
(details see Supplementary Section SXX \todo{cite}). Indeed, the
interplay between graphene quantum capacitance and the EDL
significantly reduces the graphene surface potential
$\psi_{\mathrm{G}}$ tp $\sim{}$0.3 V at $V_{\mathrm{G}}=1.25$ V,
corresponding a surface charge density $\sigma_{\mathrm{G}}$ of
$\sim{}$0.08 C$\cdot$m$^{-2}$. Note that as we mentioned earlier, an
important merit of the system here is that the surface charge density
can be precisely determined and controlled, rather than being treated
as a fitting parameter as in most of the 2D nanopore studies,
\todo{cite 18}.

\subsection{Salt rejection mechanism}
\label{sec:mechanism}
The numerical procedure described above allows us to resolve the
concentration and electric potential profiles near to a graphene
nanopore for a given $V_{\mathrm{G}}$. Since the ionic flux is driven
by both $\psi$ and $c$ fields (see Eq. \ref{eq:pnp} and \ref{eq:mu}),
we focus on the electrochemical potential $\mu_{i}$, which represents
the combined driving force, to reveal its dependence on the applied
$V_{\mathrm{G}}$. Following the same system considered in Figure
\ref{fig:3}b, the calculated axisymmetric electric potential $\psi$
and the relative electrochemical potentials,
$\Delta \mu_{\mathrm{K^{+}}}$ and $\Delta \mu_{\mathrm{Cl^{-}}}$, for
$V_{\mathrm{G}}=0.75$ V are shown in Figure \ref{fig:4}a and
\ref{fig:4}b, respectively. \todo[inline]{say somthing} The reference point of the electrochemical
potentials is set at the bulk phase in the HCR. As expected, the
electric potential reaches the maximum at the graphene surface (with
$\psi_{\mathrm{G}}$ of $\sim{}$100 mV) and decays towards the bulk
solution phase, forming an EDL surrounding the graphene surface. Since
the Debye screening length $\lambda_{\mathrm{D}}$ is comparable to the
pore radius $R_{\mathrm{G}}$, the electric potential at the nanopore
center remains at $\sim{}$25 mV, comparable to the thermal energy at
room temperature ($k_{\mathrm{B}}T=$26 meV). Consequently, it is
evident that the potential barrier is sufficient to modulate the
diffusive flux.

We further reveal the cation and anion transport pathways by looking
into their electrochemical potentials (Figure \ref{fig:4}b). By
increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
graphene surface reduces the cation concentration at the pore edge due
to the electrostatic interactions, thereby increasing its
concentration gradient at the pore center. On the other hand, the
anion concentration near the pore edge increases exponentially, such
that the concentration gradient at the pore center becomes small. The
observation confirms the distinct ionic transport pathways upon
applying a positive $V_{\mathrm{G}}$: pore center for cations and pore
edge for anions. Figure \ref{fig:4}c presents the calculated
z-component of the cation and anion fluxes through the pore at the
graphene plane (z = 0), $\boldsymbol{J}_{z}$ ,as a function of the
normalized radius, $r/R_{\mathrm{G}}$ , where $r$ is the radial
coordinate and $R_{\mathrm{G}}$ is the pore radius, at different
$V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$ is negative
because the LCR is placed at z < 0 in the simulations. At
$V_{\mathrm{G}}=$0 (pure diffusion), the anion and cation flux
profiles are identical, with a higher flux near the pore edge, which
is expected, as the concentration gradient is higher. By gradually
increasing $V_{\mathrm{G}}$, both fluxes are reduced throughout the
pore, while the degree of reduction is more pronounced at the pore
edge for the cation, and at the pore center for the anion, following
the scenarios we discussed above. Accordingly, the integrated fluxes
across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
$V_{\mathrm{G}}$ (Figure \ref{fig:4}d). A total flux reduction of up
to 80\% is predicted. Another interesting finding here is that, by
increasing $V_{\mathrm{G}}$, the nanopore transport preferentially
allows cations over anions, or in other words, the anion flux is more
reduced with $V_{\mathrm{G}}$ (see Figure \ref{fig:4}c), known as the
ion selectivity of graphene nanopore \todo{cite 18}.

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \todo{3,26,27}. To this end, we further increased the
graphene surface potential $\psi_{\mathrm{G}}$ considering the same
system (Supplementary Section 6 \todo{confirm}). Intriguingly, by
increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
starts to increase, reversing the trend observed at the low
$\psi_{\mathrm{G}}$ regime, because of an increase of cation diffusion
\todo{note!}. This level of $\psi_{\mathrm{G}}$ cannot be reached
experimentally in graphene membrane, as this requires a
$V_{\mathrm{G}}$ larger than 2.0 V \todo{confirm}, which triggers the
electrochemical reactions. On the other hand, in an IFET, the electric
potential on the pore wall is considerably higher, equivalent to
$V_{\mathrm{G}}$ due to the metallic nature of gate electrode (having
an infinitely-large quantum capacitance). We therefore conclude that
the quantum capacitance-induced nonlinear damping in the surface
potential results in the observed salt rejection.  Following the above
discussions, we further investigate the physical limits for the biased
graphene nanopores. Specifically, the salt rejection characteristics
are controlled by: (i) the overlap of EDL inside the nanopore,
essentially controlled by two length scales of $\lambda_{\mathrm{D}}$
and $R_{\mathrm{G}}$, and (ii) the graphene surface potential
$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
Eq. \ref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
function of $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
$V_{\mathrm{G}}$ (Figure \ref{fig:5}a). Clearly, when the bulk
concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
revealed in Figure \ref{fig:5}b, the calculated salt rejection factor
$\xi$ increases with both $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
$V_{\mathrm{G}}$, in line with the experimentally observed
$\xi - c_{0}$ dependence. We also find the overall trends for
$\psi_{\mathrm{G}}$ and $\xi$ with respect to
$\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$=1.25 V and
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$=1.0, a high value of $\xi$ of
$>$0.85 can be achieved.

\subsection{Effects of salt species}
\label{sec:salts}

Finally, we examine other salt species and compare the degree of salt
rejection between experiments and simulations. Figure \ref{fig:6}a
presents the measured salt rejection $\xi$ as a function of
$V_{\mathrm{G}}$ from at $c_{0}$=0.1 mM, for the seven salt species
considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
K$_{2}$SO$_{4}$, and K$_{3}$Fe(CN)$_{6}$ (details see Supplementary
Section S7 \todo{confirm}). Similar to the KCl system discussed
earlier, the salt rejection was only observed in the positive
$V_{\mathrm{G}}$ regime. The degree of salt rejection deceases with
the salt valance; for example, the measured $\xi$ values at
$V_{\mathrm{G}}$=1.25 V decreases from $>$0.5 for monovalent NaCl to
-0.04 for multivalent K$_{3}$Fe(CN)$_{6}$. This observation is
endorsed by our simulations, in which we calculate $\xi$ as a function
of $V_{\mathrm{g}}$ using the same setups in simulations (Figure
\ref{fig:6}b; details see Supplementary Section SXX
\todo{confirm}). The calculated $\xi_{\mathrm{max}}$ values are
quantitatively compared with experiments (Figure \ref{fig:6}c), and
the same trend is observed. Indeed, because the Debye screening length
$\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
surface potential appears to decrease in the multivalent salt systems,
thereby reducing $\xi$ (see Figure \ref{fig:5}b). The calculated and
experimental $\xi_{\mathrm{max}}$ as a function of
$\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
species considered here (Figure \ref{fig:6}d). We notice that without
any fitting parameters, our theory can predict the experimental values
reasonably well. In addition, the
$\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$ dependence is approximately
linear, suggesting that the effect of salt diffusivity is
negligible. This finding also explains the concentration dependence of
$\xi_{\mathrm{max}}$ observed in Figure \ref{fig:2}d, as
$\delta_{\mathrm{D}} \propto c_{0}^{-0.5}$.

\section{Conclusion}
\label{sec:consl}

In summary, we have
presented a comparative experimental and modeling study on macroscopic
salt rejection through a sheet of large-area porous graphene under
electrostatic gating. We show that due to a small quantum capacitance
of double layer graphene, the graphene surface potential is
considerably lower than the applied gate voltage. As a result, the
subtle redistribution of the electrochemical potentials create new
pathways for ionic transport, which in turn lead to a considerably
degree of salt rejection. We report a high degree of salt rejection at
$V_{\mathrm{G}}$=1.25 V of up to 55\% and 80\%, based on our
experiments and theoretical predictions, respectively. We demonstrate
that the observed salt rejection positively correlates with the Debye
screening length that nonlinearly modulates the graphene surface
potential and charge density. The experimental results and fundamental
principles presented here open an avenue towards realization of
atomically thin 2D porous membranes for advanced separation process in
electrolyte solutions.

\section{Methods}
\label{sec:methods}

\section*{}
\label{sec:ref}
\bibliography{ref}

\clearpage
\section{Figures}
\label{sec:figs}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.85\linewidth]{img/fig1.pdf}
  \caption{a}
  \label{fig:1}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.85\linewidth]{img/fig2.pdf}
  \caption{a}
  \label{fig:2}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig3.pdf}
  \caption{a}
  \label{fig:3}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.85\linewidth]{img/fig4.pdf}
  \caption{a}
  \label{fig:4}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.9\linewidth]{img/fig5.pdf}
  \caption{a}
  \label{fig:5}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.9\linewidth]{img/fig6.pdf}
  \caption{a}
  \label{fig:6}
\end{figure}

\end{document}

### 2018-10-02 correction/phi_G.py

@@ -1,0 +1,35 @@
+import numpy
+from scipy.constants import pi, hbar, e
+vf = 1.1e6
+
+# Use C/m^2
+def delta_phi_gr(sigma):
+    fac = hbar * vf / e * numpy.sqrt(pi * numpy.abs(sigma) / e)
+    return fac * numpy.sign(sigma)
+
+if __name__ == "__main__":
+    import matplotlib.pyplot as plt
+    data = numpy.genfromtxt("../result/radius/10/1D/sigma_0.001.txt", comments="%")
+    phi_surf = data[:, 0]
+    sigma_gr = -data[:, 1]
+    d_phi  = delta_phi_gr(sigma_gr)
+    V_b = phi_surf + d_phi
+    fig = plt.figure(figsize=(2.8, 2.1))
+    plt.style.use("science")
+    ax1 = fig.add_subplot(111)
+    ax2 = ax1.twinx()
+    ax1.plot(V_b, sigma_gr, "s-", markersize=4)
+    ax2.plot(V_b, phi_surf, "o-", color="r", markersize=4)
+    
+    ax2.set_ylabel(r"$\phi_{\rm{0}}$ (V)")
+    ax1.set_ylabel(r"$\sigma_{\rm{G}}$ (C/m$^{2}$)")
+
+    ax1.set_xlabel("$V_{\\mathrm{G}}$ (V)")
+    plt.xlim(0, 1.25)
+    ax1.set_ylim(0, 0.1)
+    ax2.set_ylim(0, 0.3)
+    # plt.axhline(y=1.25, color="red", alpha=0.6, ls="--")
+
+    plt.tight_layout()
+    
+    plt.savefig("two_panels.svg")

### 2018-10-02 paper/img/convert.sh

@@ -1,0 +1,10 @@
+inkscape -T --file=fig1.svg --export-png=fig1.png --without-gui --export-dpi=600
+inkscape -T --file=fig2.svg --export-png=fig2.png --without-gui --export-dpi=600
+inkscape -T --file=fig3.svg --export-png=fig3.png --without-gui --export-dpi=600
+inkscape -T --file=fig4.svg --export-png=fig4.png --without-gui --export-dpi=600
+inkscape -T --file=fig5.svg --export-png=fig5.png --without-gui --export-dpi=600
+inkscape -T --file=fig6.svg --export-png=fig6.png --without-gui --export-dpi=600
+inkscape -T --file=SI-numerical-1.svg --export-png=SI-numerical-1.png --without-gui --export-dpi=600
+inkscape -T --file=SI-flux-larger.svg --export-png=SI-flux-larger.png --without-gui --export-dpi=600
+inkscape -T --file=SI-flux.svg --export-png=SI-flux.png --without-gui --export-dpi=600
+inkscape -T --file=SI-concentration.svg --export-png=SI-concentration.png --without-gui --export-dpi=600

### 2018-10-02 paper/src/plot_pore_diameter.py

@@ -1,0 +1,15 @@
+import numpy
+import matplotlib.pyplot as plt
+
+file_name = "../data/pore-dist.csv"
+data = numpy.genfromtxt(file_name, delimiter=",")
+
+fig = plt.style.use("science")
+plt.figure(figsize=(2.5, 2.5), facecolor="w")
+repeat = [d for d, n in data for _ in range(int(n))]
+plt.hist(repeat, numpy.arange(5,66,5), density=True)
+plt.ylim(0, 0.04)
+plt.yticks([0, 0.02, 0.04])
+plt.xlabel("Pore Radius (nm)")
+plt.ylabel("Frequencies")
+plt.savefig("../img/radius_dist.svg")

### 2018-10-02 paper/src/plot_ratio.py

@@ -1,0 +1,29 @@
+import numpy
+import matplotlib.pyplot as plt
+
+file_templ = "../data/{}.csv"
+def read(name):
+    file_name = file_templ.format(name)
+    err = None
+    with open(file_name) as f:
+        err = float(f.readline().strip())
+    data = numpy.genfromtxt(file_name,
+                            skip_header=1,
+                            delimiter=",")
+    return data, err
+
+import sys
+try:
+    name = sys.argv[1]
+except IndexError:
+    name = "KCl"
+
+fig = plt.style.use("science")
+plt.figure(figsize=(2.8, 2.1), facecolor="w")
+plt.axvline(x=0, ls="--", color="#00ffee")
+data, err = read(name)
+plt.errorbar(data[:, 0], data[:, 1], yerr=err / 2, fmt="o")
+plt.xlim(-1.3, 1.3)
+plt.xlabel("$V_{\mathrm{G}}$ (V)")
+plt.ylabel("Rectification")
+plt.savefig("../img/rect_{}.svg".format(name))

### 2018-10-02 paper/src/plot_rec_all.py

@@ -1,0 +1,37 @@
+import numpy
+import matplotlib.pyplot as plt
+
+file_templ = "../data/{}.csv"
+def read(name):
+    file_name = file_templ.format(name)
+    err = None
+    with open(file_name) as f:
+        err = float(f.readline().strip())
+    data = numpy.genfromtxt(file_name,
+                            skip_header=1,
+                            delimiter=",")
+    return data, err
+
+fig = plt.style.use("science")
+plt.figure(figsize=(2.8, 2.8), facecolor="w")
+plt.axvline(x=0, ls="--", color="#00ffee")
+plt.axhline(y=0, ls="--", color="#00ffee")
+
+for name in ["KCl", "NaCl", "LiCl",
+             "MgSO4", "K2SO4", "CaCl2",
+             "K3FeCN"]:
+
+    data, err = read(name)
+    plt.errorbar(data[:, 0], data[:, 1], yerr=err / 2,
+                 fmt="o-", alpha=0.5, label=name,
+                 markersize=4)
+    # plt.fill_between(data[:, 0], data[:, 1] - err / 2,
+                     # data[:, 1] + err / 2,
+                     # fmt="o",
+                     # alpha=0.5, label=name)
+plt.ylim(-0.1, 0.7)
+plt.xlim(-1.25, 1.25)
+plt.xlabel("$V_{\\mathrm{G}}$ (V)")
+plt.ylabel("Rectification")
+plt.legend()
+plt.savefig("../img/rect_all.svg".format(name))

### 2018-10-02 paper/src/plot_rect_conc.py

@@ -1,0 +1,32 @@
+import numpy
+import matplotlib.pyplot as plt
+
+file_templ = "../data/rect_{}_conc.csv"
+def read(name):
+    file_name = file_templ.format(name)
+    err = None
+    with open(file_name) as f:
+        err = float(f.readline().strip())
+    data = numpy.genfromtxt(file_name,
+                            skip_header=1,
+                            delimiter=",")
+    return data, err
+
+import sys
+try:
+    name = sys.argv[1]
+except IndexError:
+    name = "KCl"
+
+fig = plt.style.use("science")
+plt.figure(figsize=(2.8, 2.1), facecolor="w")
+# plt.axvline(x=0, ls="--", color="#00ffee")
+data, err = read(name)
+plt.errorbar(data[:, 0], data[:, 1], yerr=err / 2, fmt="o")
+xx = numpy.logspace(-4.2, -1)
+yy = 0.0014 * xx ** -0.587
+plt.plot(xx, yy, "--")
+plt.xscale("log")
+plt.xlabel("KCl concentration (mol/L)")
+plt.ylabel("Rectification")
+plt.savefig("../img/rect_{}_conc.svg".format(name))

### 2018-10-03 paper/paper.tex
Drafted version done

@@
 \label{sec:intro}
-In the emerging field of nanofluidics, a central objective is to
+A central objective in the emerging field of nanofluidics is to
 manipulate transport phenomena at nanometer scale to enable new
@@
 including ionic diodes \cite{Karnik_2007}, field-effect transistors
-\cite{Nam_2009}, desalination \todo[inline]{cite}, and nanopore-based DNA
-sequencing \cite{Heerema_2016,Garaj_2013}, Atomically thin
-two-dimensional (2D) materials, such as graphene, represent an ideal
-category of membrane materials due to their ultimate permeability
-\cite{Cohen_Tanugi_2012}. In electrolyte systems, specifically for the
-aqueous media, early research has suggested that the separation of
-ions by the pore size differentiating the hydrated radii of
-$\sim{}$1-3 nm enables excellent salt rejection \todo[inline]{(cite
-  Refs. [1-7] in
-  https://www.nature.com/articles/ncomms11408.pdf)}. Nevertheless, the
-fabrication of sub-5 nanometer porous 2D membranes over a large area
-with atomic precision is technically challenging \cite{Suk_2014}
-\todo[inline]{also Refs [8], [9] in the nature comm paper, as well as the
-  nature comm paper itself}. Moreover, a small portion of large pores
-can significantly diminish salt rejection. To address these issues,
-recent research efforts have been focused on control over the surface
-charges by chemical functionalization \todo[inline]{cite 7-13}. However, it
+\cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
+nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}, Porous,
+atomically thin two-dimensional (2D) materials, such as graphene,
+embody an ideal membrane materials due to their ultimate permeability
+\cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
+research has suggested that using nanoporous graphene as the
+desalination membrane enables excellent salt rejection by preventing
+the permeation of the hydrated ions the (1 nm - 3 nm) with
+simultaneous high water permeation
+\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2015,Surwade_2015}. Nevertheless,
+the fabrication of sub-5 nanometer porous 2D membranes over a large
+area with atomic precision is technically challenging
+\cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
+portion of large pores can significantly diminish salt rejection.
+Accordingly, recent research efforts have explored the effect of
+surface charges on the selectivity of ion transport, as a consequence
+of coulombic repulsion of the solvated ion and the charged functional
+groups on graphene \cite{Rollings_2016,Surwade_2014}. However, it
 remains controversial that if the surface charges can result in a
 degree of salt rejection, as the membrane potential is sensitive to
-the surroundings and chemical treatment \todo[inline]{onecite}. The difficulty
-in turn hinders fundamental understanding of the interactions between
-the atomically thin 2D membrane and electrolyte solution. Here, we
-demonstrate macroscopic salt rejection through a sheet of large-area
-porous monolayer graphene using electrostatic gating.
+the surroundings and chemical treatment \cite{Li_2008}. The
+difficulty in turn hinders fundamental understanding of the
+interactions between the atomically thin 2D membrane and electrolyte
+solution. Here, we demonstrate macroscopic salt rejection through a
+sheet of large-area porous graphene using electrostatic gating,
+thereby deepening the understanding of ion-graphene interaction and
+its implications on nanoporous graphene-based desalination
+applications.
 
@@
 
-Figure \ref{fig:1}a presents the experimental setup characterizing
+Figure \ref{fig:1}a depicts the experimental setup characterizing
 ionic diffusion through a sheet of monolayer porous graphene (PG). Two
@@
 are separated by a PG membrane supported by polycarbonate track-etched
-(PCTE) film. Magnetic stirrers are used to minimize the mass transfer
-resistance in both reservoirs, and a conductivity probe is placed in
-the LCR to monitor the ionic concentration as a function of time. The
-membrane is attached to a piece of copper tape connected to a voltage
-source applying an electrical bias VG, with the LCR grounded (Figure
-\ref{fig:1}a inset). We fabricated the PCTE-supported PG using the
-protocol developed by our group \todo[inline]{cite}, as schematically shown in
-Figure \ref{fig:1}b. By optimizing the process, a high surface
-coverage (> 98\%) of graphene on PCTE was reached (Figure
-\ref{fig:1}c), allowing us to reliably characterize the ion transport
+(PCTE) film. Magnetic stirrers are used to minimize the effects of
+external concentration polarization, and a conductivity probe is
+placed in the LCR to monitor the ionic concentration as a function of
+time. The membrane is attached to a piece of copper tape connected to
+a voltage source applying an electrical bias $V_{\mathrm{G}}$, with
+the LCR grounded (Figure \ref{fig:1}a inset). We fabricated the
+PCTE-supported PG using the protocol developed by our group
+\cite{Choi_2018}, as schematically shown in Figure \ref{fig:1}b. The
+normally distributed, circular pores with pore diameters of 20$\pm$10
+nm (Figure \ref{fig:1}c inset) over a large area were drilled on
+graphene.  By optimizing the subsequent transfer process, a high
+surface coverage (> 98\%) of graphene on PCTE was reached (Figure
+\ref{fig:1}c), allowing to reliably characterize the ion transport
 behavior (details see Supplementary Information Section S1).  The
-circular pores with pore diameters of 20$\pm$10 nm (Figure
-\ref{fig:1}c inset) over a large area were drilled on monolayer
-graphene. The system presented here allows us to systematically
-investigate the diffusive flux across a sheet of porous graphene,
-$\boldsymbol{J}$, driven by the gradient of electrochemical potential in
-the electrolyte medium.
+system presented here allows us to systematically investigate the
+diffusive flux across a sheet of porous graphene, $\boldsymbol{J}$,
+driven by the gradient of electrochemical potential in the electrolyte
+medium.
 
@@
 (e.g. Figure \ref{fig:2}a) remains linear within the measurement
-duration ($\sim{}$1 h), suggesting the concentration change in
-individual reservoirs is negligible \todo[inline]{really?}. The diffusive
-fluxes correspond to different salts were obtained by converting the
+duration (1 h), suggesting the concentration change in individual
+reservoirs is negligible \todo[inline]{really?}. The diffusive fluxes
+correspond to different salts were obtained by converting the
 conductivity-time profiles with the calibration curves (blue bars in
-Figure \ref{fig:2}b and Supplementary Figure S2). On the other hand,
-for comparison purposes, based on the assumption that the membrane is
-composed of cylindrical pores with uniform diameter and a low
-tortuosity $\tau$ of $\sim{}$1.2 \todo[inline]{cite 14}, the molar diffusive
-flux through the bare PCTE membrane,
-$\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
+Figure \ref{fig:2}b and Supplementary Figure S2). For comparison
+purposes, based on the assumption that the membrane consists
+cylindrical pores with uniform diameter and a low tortuosity $\tau$ of
+$\sim{}$1.2 \cite{O_Hern_2012}, the molar diffusive flux through
+the bare PCTE membrane, $\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
   \begin{equation}
@@
 and $\tau$ is the tortuosity. By using the salt diffusivity values
-provided by the PTCE vendor (Supplementary Table SXX \todo[inline]{ref}), the
+provided by the PTCE vendor (Supplementary Table S1), the
 calculated diffusive fluxes (red bars in Figure \ref{fig:2}b) show
@@
 resistance of PG is not significant, as the permeability is high. We
-observed a more pronounced decrease of diffusive flux in KCl, K$_{2}$SO$_{4}$
-and K$_{3}$Fe(CN)$_{6}$ systems but not for the rest of the salts. We
-hypothesized that the strong cation-$\pi$ interactions between K$^{+}$ cations
-and graphene \todo[inline]{15} slow down the migration of cations along the
-surface-mediated transport pathway, which has been proven as a strong
-contributor at low concentration \todo[inline]{cite}.
+observed a more pronounced decrease of diffusive flux in KCl,
+K$_{2}$SO$_{4}$ and K$_{3}$Fe(CN)$_{6}$ systems but not for the rest
+of the salts. We hypothesized that the strong cation-$\pi$ interactions
+between K$^{+}$ cations and graphene slow down the migration of cations
+along the surface-mediated transport pathway \cite{Sun_2014}.
 
@@
 in controlling the membrane potential in mesoporous carbon membranes
-\todo[inline]{8}, is adopted here. Figure \ref{fig:2}a presents a
+\cite{Surwade_2014}, is adopted here. Figure \ref{fig:2}a presents the
 representative data of the measured conductivity with respect to
@@
 \end{equation}
-where $\bar{s}$ is the average slope of $s_{1}$ and $s_{2}$, namely
-$(s_{1} + s_{2})/2$ \todo[inline]{Should this be $(s_{1}+s_{3})/2$?},
-and $\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive
-flux across the PTCE-supported PG double layer as a function of
+where $\bar{s}$ is the average slope of $s_{1}$ and $s_{3}$, namely
+$(s_{1} + s_{3})/2$, and
+$\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive flux
+across the PTCE-supported PG double layer as a function of
 $V_{\mathrm{G}}$. Note that a positive $\xi$ between 0 and 1
-represents a decrease of the diffusive flux. The factor $\xi$ enables a
-reliable and stable measurement of salt rejection, as the salt species
-and initial conditions may induce a degree of measurement uncertainty
-between different samples. A control experiment was performed to
-ensure the copper tape was not in direct contact with the ionic
-solution (Supplementary Section 3).
+represents a decrease of the diffusive flux. The factor $\xi$ enables
+a reliable and stable measurement of salt rejection, as the salt
+species and initial conditions may induce a degree of measurement
+uncertainty between different samples. A control experiment was
+performed to ensure the copper tape was not in direct contact with the
+ionic solution (Supplementary Section 3).
 
@@
 $V_{\mathrm{G}}$, showing an inverse trend compared to those observed
-in ionic field effect transistors (IFETs) \todo{cite}, in which the
-diffusive flux increases with the gate voltage \todo{cite 3, 23}. A
-further increase of the KCl concentration $c_{0}$ influences the
-attainable degree of salt rejection. $\xi$ values measured at
+in ionic field effect transistors (IFETs), in which the diffusive flux
+increases with the gate voltage \cite{Nam_2009,Cheng_2018}. A further
+increase of the KCl concentration $c_{0}$ influences the attainable
+degree of salt rejection. $\xi$ values measured at
 $V_{\mathrm{G}}$=1.25 V, $\xi_{\mathrm{max}}$, as a function of
@@
 law function following
-$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{Const}$. As the Debye
+$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{Constant}$. As the Debye
 screening length in solution, $\lambda_{\mathrm{D}}$, is inversely
@@
 longer than that of ionic diffusion, the pseudo-steady state
-approximation holds. Accordingly, the steady-state Nernst-Planck equation
-describing the ionic transport in an electrolyte solution is given by \todo{cite}:
+approximation holds. Accordingly, the steady-state Nernst-Planck
+equation describing the ionic transport in an electrolyte solution is
+given by \cite{MacGillivray_1968}:
 \begin{equation}
@@
 and $\mu_{i}$ is the electrochemical potential. Under the assumption
-of ideal solution, it follows \todo{cite}:
+of ideal solution, it follows \cite{Kilic_2007}:
 \begin{equation}
@@
 individual materials in the system. Including water and the internal
-Stern layer \todo{for graphene?}, and $\varepsilon_{0}$ is the vacuum
-permittivity. When applying $V_{\mathrm{G}}$ to graphene adjacent to
-the electrolyte solution, charges (electrons or holes) are induced in
-graphene; the electroneutrality of the entire system suggests:
+Stern layer\cite{Tian_2017}, and
+$\varepsilon_{0}$ is the vacuum permittivity. When applying
+$V_{\mathrm{G}}$ to graphene adjacent to the electrolyte solution,
+charges (electrons or holes) are induced in graphene; the
+electroneutrality of the entire system suggests:
 \begin{equation}
@@
 $\psi_{\mathrm{G}}$, is not equivalent to $V_{\mathrm{G}}$ due to the
-graphene quantum capacitance effect \todo{cite-24} (Figure
+graphene quantum capacitance effect\cite{Xia_2009} (Figure
 \ref{fig:3}a) following:
@@
 self-consistently by discretizing Eqs. \ref{eq:pnp}-\ref{eq:poisson}
-using the finite-element method, in which the graphene surface
+using the finite-element method (FEM), in which the graphene surface
 potential is coupled with
@@
 well-recognized that the electron traps are inherently introduced
-during synthesis and patterning \todo{25}, effectively increasing the
-graphene quantum capacitance for $V_{\mathrm{G}}<0$ (Supplementary
-Figure SXX \todo{ref}). With the nonideality in mind, hereafter, we
-compare the calculations and experiments in the regime of
-$V_{\mathrm{G}}>0$. For example, Figure \ref{fig:3}c presents the
+during synthesis and patterning \cite{Dean_2010}, effectively
+increasing the graphene quantum capacitance for $V_{\mathrm{G}}<0$
+(Supplementary Figure SXX \todo{ref}). With the nonideality in mind,
+hereafter, we compare the calculations and experiments in the regime
+of $V_{\mathrm{G}}>0$. For example, Figure \ref{fig:3}c presents the
 calculated $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ as a function
@@
 significantly reduces the graphene surface potential
-$\psi_{\mathrm{G}}$ tp $\sim{}$0.3 V at $V_{\mathrm{G}}=1.25$ V,
+$\psi_{\mathrm{G}}$ tp $\sim$0.3 V at $V_{\mathrm{G}}$=1.25 V,
 corresponding a surface charge density $\sigma_{\mathrm{G}}$ of
-$\sim{}$0.08 C$\cdot$m$^{-2}$. Note that as we mentioned earlier, an
+$\sim$0.08 C$\cdot$m$^{-2}$. Note that as we mentioned earlier, an
 important merit of the system here is that the surface charge density
 can be precisely determined and controlled, rather than being treated
-as a fitting parameter as in most of the 2D nanopore studies,
-\todo{cite 18}.
+as a fitting parameter as in most of the 2D nanopore studies
+\cite{Rollings_2016}.
 
@@
 $\Delta \mu_{\mathrm{K^{+}}}$ and $\Delta \mu_{\mathrm{Cl^{-}}}$, for
-$V_{\mathrm{G}}=0.75$ V are shown in Figure \ref{fig:4}a and
-\ref{fig:4}b, respectively. \todo[inline]{say somthing} The reference point of the electrochemical
+$V_{\mathrm{G}}$=0.75 V are shown in Figure \ref{fig:4}a and
+\ref{fig:4}b, respectively. The reference point of the electrochemical
 potentials is set at the bulk phase in the HCR. As expected, the
 electric potential reaches the maximum at the graphene surface (with
-$\psi_{\mathrm{G}}$ of $\sim{}$100 mV) and decays towards the bulk
+$\psi_{\mathrm{G}}$ of $\sim$100 mV) and decays towards the bulk
 solution phase, forming an EDL surrounding the graphene surface. Since
@@
 pore radius $R_{\mathrm{G}}$, the electric potential at the nanopore
-center remains at $\sim{}$25 mV, comparable to the thermal energy at
+center remains at $\sim$25 mV, comparable to the thermal energy at
 room temperature ($k_{\mathrm{B}}T=$26 meV). Consequently, it is
@@
 anion concentration near the pore edge increases exponentially, such
-that the concentration gradient at the pore center becomes small. The
-observation confirms the distinct ionic transport pathways upon
-applying a positive $V_{\mathrm{G}}$: pore center for cations and pore
-edge for anions. Figure \ref{fig:4}c presents the calculated
-z-component of the cation and anion fluxes through the pore at the
-graphene plane (z = 0), $\boldsymbol{J}_{z}$ ,as a function of the
-normalized radius, $r/R_{\mathrm{G}}$ , where $r$ is the radial
-coordinate and $R_{\mathrm{G}}$ is the pore radius, at different
-$V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$ is negative
-because the LCR is placed at z < 0 in the simulations. At
+that the concentration gradient at the pore center becomes
+small. (also see Supplementary Figures SXX \todo{note}). We also
+observe that $\Delta \mu_{+}$ is dominated by the concentration, while
+$\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
+between the diffusion and drift potentials (see Supplementary Figure
+SXX \todo{note}). The observations confirm the distinct ionic
+transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
+center for cations and pore edge for anions. Figure \ref{fig:4}c
+presents the calculated z-component of the cation and anion fluxes
+through the pore at the graphene plane (z = 0), $\boldsymbol{J}_{z}$
+,as a function of the normalized radius, $r/R_{\mathrm{G}}$ , where
+$r$ is the radial coordinate and $R_{\mathrm{G}}$ is the pore radius,
+at different $V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$
+is negative because the LCR is placed at z < 0 in the simulations. At
 $V_{\mathrm{G}}=$0 (pure diffusion), the anion and cation flux
@@
 reduced with $V_{\mathrm{G}}$ (see Figure \ref{fig:4}c), known as the
-ion selectivity of graphene nanopore \todo{cite 18}.
+ion selectivity of graphene nanopore \cite{Rollings_2016}.
 
@@
 the nanopore center usually results in an increase of ionic
-conductivity \todo{3,26,27}. To this end, we further increased the
-graphene surface potential $\psi_{\mathrm{G}}$ considering the same
-system (Supplementary Section 6 \todo{confirm}). Intriguingly, by
-increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
-starts to increase, reversing the trend observed at the low
-$\psi_{\mathrm{G}}$ regime, because of an increase of cation diffusion
-\todo{note!}. This level of $\psi_{\mathrm{G}}$ cannot be reached
-experimentally in graphene membrane, as this requires a
-$V_{\mathrm{G}}$ larger than 2.0 V \todo{confirm}, which triggers the
-electrochemical reactions. On the other hand, in an IFET, the electric
-potential on the pore wall is considerably higher, equivalent to
-$V_{\mathrm{G}}$ due to the metallic nature of gate electrode (having
-an infinitely-large quantum capacitance). We therefore conclude that
-the quantum capacitance-induced nonlinear damping in the surface
-potential results in the observed salt rejection.  Following the above
-discussions, we further investigate the physical limits for the biased
-graphene nanopores. Specifically, the salt rejection characteristics
-are controlled by: (i) the overlap of EDL inside the nanopore,
-essentially controlled by two length scales of $\lambda_{\mathrm{D}}$
-and $R_{\mathrm{G}}$, and (ii) the graphene surface potential
+conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
+further increased the graphene surface potential $\psi_{\mathrm{G}}$
+considering the same system (Supplementary Section 6
+\todo{confirm}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
+larger than 400 mV, the ionic flux starts to increase, reversing the
+trend observed at the low $\psi_{\mathrm{G}}$ regime, because of an
+increase of cation diffusion \todo{note!}. This level of
+$\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
+membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V
+\todo{confirm}, which triggers the electrochemical reactions. On the
+other hand, in an IFET, the electric potential on the pore wall is
+considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
+metallic nature of gate electrode (having an infinitely-large quantum
+capacitance). We therefore conclude that the quantum
+capacitance-induced nonlinear damping in the surface potential results
+in the observed salt rejection.  Following the above discussions, we
+further investigate the physical limits for the biased graphene
+nanopores. Specifically, the salt rejection characteristics are
+controlled by: (i) the overlap of EDL inside the nanopore, essentially
+controlled by two length scales of $\lambda_{\mathrm{D}}$ and
+$R_{\mathrm{G}}$, and (ii) the graphene surface potential
 $\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
@@
 
+\textbf{Graphene synthesis}: Graphene was grown in a cold-wall,
+low-pressure chemical vapor deposition system (BM 4 inch, Aixtron SE)
+on surface-pretreated copper foil (Alfa Aesar N$^{o}$ 46986). Synthesis was
+carried out at 950 $^{\circ}$C for 3 min using ethylene after 30 min of
+hydrogen/argon annealing. A first graphene layer was subsequently
+transferred to a second one to yield double layer graphene using a
+PMMA transfer method. A glass slide was used as the support for
+subsequent patterning of the graphene, PMMA was removed using acetone
+ultrasonication and subsequent isopropanol (IPA) rinsing. The entire
+process is described in detail in Ref. \citenum{Choi_2018}.
+
+\vspace{1em}
+\noindent
+\textbf{Graphene patterning and transfer to PCTE}: Spherical block copolymer
+(s-BCP) based patterning has enabled the manufacturing of perforated
+graphene membranes having pores in the range of 10 nm to 50 nm on
+average up to wafer-scale\cite{Choi_2018}. In brief, s-BCP
+(polystyrene-block-polymethylmethacrylate, PS-b-PMMA, 195-b-20,
+Polymer Source Inc, Canada, 1 weight\% in anhydrous toluene) is spun
+from solution and thermally annealed at 220 $^{\circ}$C for 6 h in
+vacuum. Microphase separation of s-BCP leads to distinct phases: the
+minor phase will form spheres (PMMA) and the major phase will form the
+matrix (PS). Oxygen plasma (8 , 100 W, 25 mTorr, Oxford Instruments
+plc) removes the top layer PS from the PMMA spheres, which are
+subsequentially etched in glacial acetic acid to form a porous etch
+mask directly on top of the double layer graphene. Anisotropic etching
+using oxygen beam milling (10 s, 100 mA, 600 V acceleration voltage,
+Oxford IonFab 600) leads to perforation of the underlying graphene
+through the porous PS mask. Polymer residues are removed by thermal
+annealing in hydrogen:argon (9:1) at 400 $^{\circ}$C. The patterned
+graphene is transferred to PCTE membranes (hydrophobic, 400 nm pores,
+from Sterlitech) by baking the PCTE briefly to the perforated graphene
+at 180 $^{\circ}$C followed by a lift-off etch in buffered
+hydrofluoric acid (BHF) as described by\cite{Choi_2018}. A schematic
+of the process is shown in Figure S1.
+
+\vspace{1em}
+\noindent
+\textbf{Membrane preparation}: The ion-diffusion and gating experiments are
+performed in a custom-made diffusion cell. An initial dip-wetting
+procedure using ethanol/water 1:1 is performed to wet the membrane,
+followed by extensive washing and inserting the membrane. The
+diffusion cell is filled immediately after mounting the membrane with
+DI water to prevent drying. The ion solution is placed on the HCR
+side, distilled water on the LCR side, with a volume of 7.33 mL for
+each cell. Bar-stirrers close to the membrane ensure well-mixed
+solutions avoiding potential external concentration polarization
+effects. Water channels in the fixture ensure stable measurement
+temperatures using a chiller. The temperature for all measurements is
+kept at 25 $^{\circ}$C. A conductivity probe (eDAQ, Pty Ltd.,
+Australia), inserted on the LCR side measures the conductivity, which
+is recorded with time steps of 2 s. The membrane is kept wet for the
+entire series of experiments, multiple rinsing steps with DI water are
+performed after each experiment and change to a different salt
+solution. The salt solutions were prepared immediately before the
+experiments using MilliQ water that was additionally distilled to
+increase purity level. The distilled water, has a conductivity of
+0.0012 mS/cm with a pH of 6.3, no buffer has been used in these
+experiments. 7 salts were used: KCl, NaCl, LiCl, K$_{2}$SO$_{4}$,
+CaCl$_{2}$, MgSO$_{4}$ and K$_{3}$Fe(CN)$_{6}$. The salts were
+purchased from Sigma Aldrich and used without further purification,
+salt solutions were prepared by subsequent dilution of a base solution
+(1 M) to the final concentrations.
+
+\vspace{1em}
+\noindent
+\textbf{Ion diffusion experiments}: Baseline measurements were
+performed using bare PCTE (b-PCTE) by extracting the diffusion rates
+of 3 measurements and averaging the resulting values (see
+Supplementary Section 2). For the measurement, DI water was filled on
+the LCR side, where a 0.1 mM salt solution is placed on the HCR side
+of the fixture. The conductivity increase was recorded over 1 h before
+rinsing and replacing both sides with fresh solutions.
+
+\vspace{1em}
+\noindent
+\textbf{Ion gating experiments}: The salt rejection behavior of the graphene
+was characterized using patterned graphene on PCTE (PG-PCTE) in a
+3-interval-type measurement based on salt diffusion: 1h per interval
+with (i) no bias (ii) bias and (iii) no bias, ruling out possible
+electrochemical effects at the membrane that might mislead
+interpretation of the conductivity reading. The voltage is applied via
+copper tape so that the membrane acts as a working electrode (WE). A
+platinum wire (length 3cm, diameter 0.6 mm) placed in the low
+concentration side of the diffusion cell with a distance of $\sim$3.5 cm
+from the PG-PCTE membrane is counter- (CE) and reference electrode
+(RE) simultaneously, forming effectively a two-electrode setup. An
+electrochemical workstation (PGSTAT204, Metrohm Autolab S.V.) is used
+to apply the selected voltage.
+
+\vspace{1em}
+\noindent
+\textbf{Numerical Simulations}: Numerical simulations using finite
+element method (FEM) were carried out using COMSOL Multiphysics
+5.3a. A single pore in graphene is simulated, with the horizontal
+length of the simulation box set to 20 times of the nanopore size. The
+transport of ionic species was solved by the Nernst-Planck equation,
+with the electrostatic potential further given by the Poisson
+equation. Since the surface on graphene cannot be predetermined, we
+performed all calculations by setting the values of
+$\psi_{\mathrm{G}}$. The surface charge of graphene is further
+extracted and used to reconstruct the value of actual $V_{\mathrm{G}}$
+applied to graphene. We examined the convergence of the solutions by
+performing simulations with varied mesh sizes. For further details
+about the simulation setup please refer to Supplementary Section 5.
+
+\section{Acknowledgements}
+\label{sec:ack}
+\todo[inline]{TBD} R.M.W. and H.G.P. acknowledge the support from
+XXX. T.T. and C.J.S. are grateful for the financial support from the
+ETH startup funding.
+
+\section{Author Contributions}
+\label{sec:author}
+
+H.G.P and C.J.S conceived the experiments. R.M.W measured the ion diffusion
+and gating experiments. T.T performed numerical simulations. All authors
+contributed to writing and discussion.
+
 \section*{}
@@
   \centering
-  \includegraphics[width=0.85\linewidth]{img/fig1.pdf}
-  \caption{a}
+  \includegraphics[width=0.95\linewidth]{img/fig1.pdf}
+  \caption{\textbf{Experimental setup and nanopore characterization}.
+    \textbf{a}. 3D schematic diagram showing the experimental
+    setup. Inset: photograph of the PG-PCTE membrane supported by
+    Kapton and copper tapes, scale bar: 1 cm. \textbf{b}. 3D schematic
+    of the nanoscale cross-sectional structure of the PG-PCTE
+    membrane. \textbf{c}. SEM image of the PG-PCTE membrane, showing
+    excellent coverage of graphene over the PCTE substrate, scale bar:
+    20 $\mathrm{\mu}$m.  Upper right inset: high-resolution SEM image
+    of individual nanopores on PG fabricated by the patterning
+    technique, scale bar: 500 nm. Bottom right inset: histogram of the
+    pore diameter distribution revealed by the SEM
+    image. \textbf{d}. Schematic of the nanoscale ionic transport
+    through a gated graphene nanopore.}
   \label{fig:1}
@@
   \centering
-  \includegraphics[width=0.85\linewidth]{img/fig2.pdf}
-  \caption{a}
+  \includegraphics[width=0.95\linewidth]{img/fig2.pdf}
+  \caption{\textbf{The experimental evidence of salt rejection.}
+    \textbf{a}. Measured conductivity of LCR as a function of
+    time. The slope of conductivity-time curve when $V_{\mathrm{G}}>0$
+    is added, is smaller than that without gating. \textbf{b}. Molar
+    diffusive flux through bare PCTE (blue bars: experimental; red
+    bars: theoretical values) and PG+PCTE (green bars) membranes for
+    different salts. \textbf{c}. Experimentally measured salt
+    rejection factor $\xi$ as a function of $V_{\mathrm{G}}$ for 0.1
+    mM KCl solution in HCR, showing an asymmetric response, with a
+    higher degree of salt rejection for
+    $V_{\mathrm{G}}$>0. \textbf{d}. $\xi_{\mathrm{max}}$ as a function
+    of KCL concentration, fitted by a power law relation, suggesting
+    the effect of Debye length on the observed salt rejection. }
   \label{fig:2} 
@@
   \includegraphics[width=0.95\linewidth]{img/fig3.pdf}
-  \caption{a}
+  \caption{\textbf{Interplay between graphene quantum capacitance and
+      EDL.} \textbf{a}. Schematic diagram of the electrostatic
+    potential at the graphene-electrolyte interface considering the
+    quantum capacitance of graphene. The interfacial potential of the
+    electrolyte solution, $\psi_{0}$, is smaller than the bias
+    $V_{\mathrm{G}}$ applied, as a result of the change of graphene’s
+    Fermi level $\Delta \phi_{\mathrm{G}}$ and the potential drop in
+    the Stern layer $\Delta \psi$. \textbf{b}. Calculated surface
+    charge $\sigma_{\mathrm{G}}$ and surface potential
+    $\psi_{\mathrm{G}}$ of graphene as a function of $V_{\mathrm{G}}$
+    in a 1 mM KCl solution. }
   \label{fig:3}
@@
   \centering
-  \includegraphics[width=0.85\linewidth]{img/fig4.pdf}
-  \caption{a}
+  \includegraphics[width=0.95\linewidth]{img/fig4.pdf}
+  \caption{\textbf{Self-consistent theoretical
+      calculations}. \textbf{a}. Calculated cross-sectional contour
+    plot of electrostatic potential $\psi$ near the center of the
+    graphene nanopore at $V_{\mathrm{G}}$=0.75 V. \textbf{b}. The
+    corresponding electrochemical potential change for cation
+    $\Delta \mu_{+}$ (left) and anion $\Delta \mu_{-}$ (right). The
+    reference of electrochemical potential is set in the HCR far from
+    the graphene layer. The diffusive pathways for both ions are
+    indicated by arrows. \textbf{c}. Calculated z-component of
+    diffusive fluxes $\boldsymbol{J}_{z}$ for cation (left) and anion
+    (right) through the pore as functions of the relative position
+    inside the pore, considering different levels of $V_{\mathrm{G}}$
+    applied. \textbf{d}. Calculated z-components of cation, anion, and
+    total fluxes through the graphene nanopore as functions of
+    $V_{\mathrm{G}}$, showing salt rejection for all fluxes.}
   \label{fig:4}
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{img/fig5.pdf}
-  \caption{a}
+  \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
+  \caption{\textbf{The Debye length effect}. \textbf{a}. Contour plot
+    of the surface potential of graphene $\psi_{\mathrm{G}}$ as a
+    function of $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and
+    $V_{\mathrm{G}}$. When the Debye length reduces, a higher
+    $V_{\mathrm{G}}$ is required to maintain the same surface
+    $\psi_{\mathrm{G}}$ level. \textbf{b}. 2D contour plot of
+    theoretically predicted $\xi$ as a function of
+    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and
+    $V_{\mathrm{G}}$. Clearly, a higher degree of salt rejection can
+    be achieved by having a higher $V_{\mathrm{G}}$ and
+    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ ratio.}
   \label{fig:5}
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{img/fig6.pdf}
-  \caption{a}
+  \includegraphics[width=0.95\linewidth]{img/fig6.pdf}
+  \caption{\textbf{Comparison between experiments and simulations
+      considering different salt species}. \textbf{a}. Experimentally
+    measured $\xi$ as a function of $V_{\mathrm{G}}$ for various salts
+    at 0.1 mM. The error bar indicates the standard
+    error. \textbf{b}. Simulated $\xi-V_{\mathrm{G}}$ relations for
+    the salt species considered here. \textbf{c}. Comparison between
+    the experimental and calculated $\xi_{\mathrm{max}}$ values for
+    different salt species, decreasing with the salt
+    valence. \textbf{d}. $\xi_{\mathrm{max}}$ as a function of
+    $\lambda_{\mathrm{D}}$ for the experimental (circle) and model
+    (diamond) values, with a linear correlation.}
   \label{fig:6}

### 2018-10-03 paper/src/plot_pore_diameter.py

@@ -7,9 +7,9 @@ data = numpy.genfromtxt(file_name, delimiter=",")
 fig = plt.style.use("science")
 plt.figure(figsize=(2.5, 2.5), facecolor="w")
 repeat = [d for d, n in data for _ in range(int(n))]
-plt.hist(repeat, numpy.arange(5,66,5), density=True)
-plt.ylim(0, 0.04)
-plt.yticks([0, 0.02, 0.04])
+plt.hist(repeat, numpy.arange(5,66,5))
+# plt.ylim(0, 0.04)
+ # plt.yticks([0, 0.02, 0.04])
 plt.xlabel("Pore Radius (nm)")
 plt.ylabel("Frequencies")
 plt.savefig("../img/radius_dist.svg")

### 2018-10-03 paper/paper.tex
Complete refs in main

@@
-\documentclass[manuscript=letter, email=true, hyperref=true, keywords=false]{achemso}
+\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{todonotes}
+\newcommand{\Fig}{Fig.}
 % \usepackage{lineno}
@@
 
-Figure \ref{fig:1}a depicts the experimental setup characterizing
+\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
 ionic diffusion through a sheet of monolayer porous graphene (PG). Two
@@
 a voltage source applying an electrical bias $V_{\mathrm{G}}$, with
-the LCR grounded (Figure \ref{fig:1}a inset). We fabricated the
+the LCR grounded (\Fig{} \ref{fig:1}a inset). We fabricated the
 PCTE-supported PG using the protocol developed by our group
-\cite{Choi_2018}, as schematically shown in Figure \ref{fig:1}b. The
+\cite{Choi_2018}, as schematically shown in \Fig{} \ref{fig:1}b. The
 normally distributed, circular pores with pore diameters of 20$\pm$10
-nm (Figure \ref{fig:1}c inset) over a large area were drilled on
+nm (\Fig{} \ref{fig:1}c inset) over a large area were drilled on
 graphene.  By optimizing the subsequent transfer process, a high
-surface coverage (> 98\%) of graphene on PCTE was reached (Figure
+surface coverage ($>$ 98\%) of graphene on PCTE was reached (\Fig{}
 \ref{fig:1}c), allowing to reliably characterize the ion transport
@@
 flux is comparably small, the conductivity versus time profile
-(e.g. Figure \ref{fig:2}a) remains linear within the measurement
+(e.g. \Fig{} \ref{fig:2}a) remains linear within the measurement
 duration (1 h), suggesting the concentration change in individual
-reservoirs is negligible \todo[inline]{really?}. The diffusive fluxes
+reservoirs is negligible \todo[inline]{Isn't the increasing of
+  conductivity a measure of the diffusion of ions?}. The diffusive fluxes
 correspond to different salts were obtained by converting the
 conductivity-time profiles with the calibration curves (blue bars in
-Figure \ref{fig:2}b and Supplementary Figure S2). For comparison
+\Fig{} \ref{fig:2}b and Supplementary \Fig{} S2). For comparison
 purposes, based on the assumption that the membrane consists
 cylindrical pores with uniform diameter and a low tortuosity $\tau$ of
-$\sim{}$1.2 \cite{O_Hern_2012}, the molar diffusive flux through
-the bare PCTE membrane, $\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
+$\sim{}$1.2 \cite{O_Hern_2012}, the molar diffusive flux through the
+bare PCTE membrane, $\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
   \begin{equation}
@@
 provided by the PTCE vendor (Supplementary Table S1), the
-calculated diffusive fluxes (red bars in Figure \ref{fig:2}b) show
+calculated diffusive fluxes (red bars in \Fig{} \ref{fig:2}b) show
 reasonable agreement with the experimental values.
@@
 diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
-Figure \ref{fig:2}b), remain at the same order of magnitude compared
+\Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
 to those of bare PCTE membrane, suggesting that the mass transfer
@@
 in controlling the membrane potential in mesoporous carbon membranes
-\cite{Surwade_2014}, is adopted here. Figure \ref{fig:2}a presents the
+\cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a presents the
 representative data of the measured conductivity with respect to
@@
 $V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
-electrochemical reactions (Figure \ref{fig:2}c). We observe an
+electrochemical reactions (\Fig{} \ref{fig:2}c). We observe an
 asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
@@
 degree of salt rejection. $\xi$ values measured at
-$V_{\mathrm{G}}$=1.25 V, $\xi_{\mathrm{max}}$, as a function of
+$V_{\mathrm{G}}$ = 1.25 V, $\xi_{\mathrm{max}}$, as a function of
 $c_{0}$ from 10$^{-4}$ to 10$^{-2}$ M KCl (see Supplementary Section
-S4) exhibit a power law dependency (Figure \ref{fig:2}d). The
+S4) exhibit a power law dependency (\Fig{} \ref{fig:2}d). The
 $\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
@@
   \label{eq:pnp}
-  \nabla \cdot \boldsymbol{J}_{i} = -\Delta \cdot (\frac{D_{i}}{k_{\mathrm{B}}T} c_{i} N_{\mathrm{A}} \nabla \mu_{i}) = 0
+  \nabla \cdot \boldsymbol{J}_{i} = -\nabla \cdot (\frac{D_{i}}{k_{\mathrm{B}}T} c_{i} N_{\mathrm{A}} \nabla \mu_{i}) = 0
 \end{equation}
@@
 $\psi_{\mathrm{G}}$, is not equivalent to $V_{\mathrm{G}}$ due to the
-graphene quantum capacitance effect\cite{Xia_2009} (Figure
+graphene quantum capacitance effect\cite{Xia_2009} (\Fig{}
 \ref{fig:3}a) following:
@@
 function. Under the assumption that the charge neutrality point of
-graphene coincides with the Dirac point at $V_{\mathrm{G}}=0$, the elementary
+graphene coincides with the Dirac point at $V_{\mathrm{G}}$ = 0, the elementary
 electronic properties of graphene give:
@@
 $v_{\mathrm{F}}=1.1\times10^{6}$ m$\cdot$s$^{-1}$ is the Fermi
-velocity of graphene (more details find Supplementary Section SXX
-\todo{ref}). Note that the PG film fabricated experimentally is
-double-layer turbostratic graphene, in which we assume the
+velocity of graphene (more details find Supplementary Section
+S5). Note that the PG film fabricated experimentally is double-layer
+turbostratic graphene, in which we assume the
 $\Delta \phi_{\mathrm{G}} - \sigma_{\mathrm{G}}$ dependence follows
@@
 respect to $V_{\mathrm{G}}$ due to the symmetric band structure of
-graphene (Eq. \ref{eq:delta-phiG}). However, for chemical vapor
-deposition- (CVD) synthesized graphene used in our experiments, it is
+graphene (Eq. \ref{eq:delta-phiG}). However, for graphene synthesized
+by chemical vapor deposition (CVD) used in our experiments, it is
 well-recognized that the electron traps are inherently introduced
-during synthesis and patterning \cite{Dean_2010}, effectively
-increasing the graphene quantum capacitance for $V_{\mathrm{G}}<0$
-(Supplementary Figure SXX \todo{ref}). With the nonideality in mind,
-hereafter, we compare the calculations and experiments in the regime
-of $V_{\mathrm{G}}>0$. For example, Figure \ref{fig:3}c presents the
-calculated $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ as a function
-of $V_{\mathrm{G}}$ considering the ionic diffusion through a single
-20 nm-diameter nanopore drilled on a sheet of semi-infinite double
-layer graphene that separates HCR containing KCl solution at
-$c_{0}=0.1$ mM, and LCR at $c_{0}/10$ in axisymmetric coordinates
-(details see Supplementary Section SXX \todo{cite}). Indeed, the
+during synthesis and patterning \cite{Dean_2010}, effectively reducing
+the charge density and surface potential on graphene
+$V_{\mathrm{G}}<0$ (Supplementary \Fig{} S3). With the nonideality in
+mind, hereafter, we compare the calculations and experiments in the
+regime of $V_{\mathrm{G}}>0$. For example, \Fig{} \ref{fig:3}c
+presents the calculated $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$
+as a function of $V_{\mathrm{G}}$ considering the ionic diffusion
+through a single 20 nm-diameter nanopore drilled on a sheet of
+semi-infinite double layer graphene that separates HCR containing KCl
+solution at $c_{0}$ = 0.1 mM, and LCR at $c_{0}/10$ in axisymmetric
+coordinates (details see Supplementary Section S5). Indeed, the
 interplay between graphene quantum capacitance and the EDL
 significantly reduces the graphene surface potential
-$\psi_{\mathrm{G}}$ tp $\sim$0.3 V at $V_{\mathrm{G}}$=1.25 V,
+$\psi_{\mathrm{G}}$ tp $\sim$0.3 V at $V_{\mathrm{G}}$ = 1.25 V,
 corresponding a surface charge density $\sigma_{\mathrm{G}}$ of
@@
 the combined driving force, to reveal its dependence on the applied
-$V_{\mathrm{G}}$. Following the same system considered in Figure
+$V_{\mathrm{G}}$. Following the same system considered in \Fig{}
 \ref{fig:3}b, the calculated axisymmetric electric potential $\psi$
@@
 $\Delta \mu_{\mathrm{K^{+}}}$ and $\Delta \mu_{\mathrm{Cl^{-}}}$, for
-$V_{\mathrm{G}}$=0.75 V are shown in Figure \ref{fig:4}a and
+$V_{\mathrm{G}}$ = 0.75 V are shown in \Fig{} \ref{fig:4}a and
 \ref{fig:4}b, respectively. The reference point of the electrochemical
@@
 center remains at $\sim$25 mV, comparable to the thermal energy at
-room temperature ($k_{\mathrm{B}}T=$26 meV). Consequently, it is
+room temperature ($k_{\mathrm{B}}T$ = 26 meV). Consequently, it is
 evident that the potential barrier is sufficient to modulate the
@@
 We further reveal the cation and anion transport pathways by looking
-into their electrochemical potentials (Figure \ref{fig:4}b). By
+into their electrochemical potentials (\Fig{} \ref{fig:4}b). By
 increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
@@
 that the concentration gradient at the pore center becomes
-small. (also see Supplementary Figures SXX \todo{note}). We also
+small. (also see Supplementary \Fig{}s S4). We also
 observe that $\Delta \mu_{+}$ is dominated by the concentration, while
 $\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
-between the diffusion and drift potentials (see Supplementary Figure
-SXX \todo{note}). The observations confirm the distinct ionic
+between the diffusion and drift potentials (see Supplementary \Fig{}
+S5). The observations confirm the distinct ionic
 transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
-center for cations and pore edge for anions. Figure \ref{fig:4}c
+center for cations and pore edge for anions. \Fig{} \ref{fig:4}c
 presents the calculated z-component of the cation and anion fluxes
@@
 is negative because the LCR is placed at z < 0 in the simulations. At
-$V_{\mathrm{G}}=$0 (pure diffusion), the anion and cation flux
+$V_{\mathrm{G}}$ = 0 (pure diffusion), the anion and cation flux
 profiles are identical, with a higher flux near the pore edge, which
@@
 across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
-$V_{\mathrm{G}}$ (Figure \ref{fig:4}d). A total flux reduction of up
+$V_{\mathrm{G}}$ (\Fig{} \ref{fig:4}d). A total flux reduction of up
 to 80\% is predicted. Another interesting finding here is that, by
@@
 allows cations over anions, or in other words, the anion flux is more
-reduced with $V_{\mathrm{G}}$ (see Figure \ref{fig:4}c), known as the
+reduced with $V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the
 ion selectivity of graphene nanopore \cite{Rollings_2016}.
@@
 further increased the graphene surface potential $\psi_{\mathrm{G}}$
-considering the same system (Supplementary Section 6
-\todo{confirm}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
-larger than 400 mV, the ionic flux starts to increase, reversing the
-trend observed at the low $\psi_{\mathrm{G}}$ regime, because of an
-increase of cation diffusion \todo{note!}. This level of
-$\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
-membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V
-\todo{confirm}, which triggers the electrochemical reactions. On the
-other hand, in an IFET, the electric potential on the pore wall is
-considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
-metallic nature of gate electrode (having an infinitely-large quantum
-capacitance). We therefore conclude that the quantum
-capacitance-induced nonlinear damping in the surface potential results
-in the observed salt rejection.  Following the above discussions, we
-further investigate the physical limits for the biased graphene
-nanopores. Specifically, the salt rejection characteristics are
-controlled by: (i) the overlap of EDL inside the nanopore, essentially
-controlled by two length scales of $\lambda_{\mathrm{D}}$ and
-$R_{\mathrm{G}}$, and (ii) the graphene surface potential
-$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
-Eq. \ref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
-function of $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
-$V_{\mathrm{G}}$ (Figure \ref{fig:5}a). Clearly, when the bulk
-concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
-to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
-revealed in Figure \ref{fig:5}b, the calculated salt rejection factor
-$\xi$ increases with both $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
-$V_{\mathrm{G}}$, in line with the experimentally observed
-$\xi - c_{0}$ dependence. We also find the overall trends for
-$\psi_{\mathrm{G}}$ and $\xi$ with respect to
-$\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
+considering the same system (Supplementary Section 6). Intriguingly,
+by increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
+starts to increase, reversing the trend observed at the low
+$\psi_{\mathrm{G}}$ regime, due to (i) the drift flux become dominant
+over diffusion flux and (ii) the concentration near the pore edge
+(prefered path) greatly increases. This level of $\psi_{\mathrm{G}}$
+cannot be reached experimentally in graphene membrane, as this
+requires a $V_{\mathrm{G}}$ larger than 2.0 V, which triggers the
+electrochemical reactions \cite{Toh_2011}. On the other hand, in an
+IFET, the electric potential on the pore wall is considerably higher,
+equivalent to $V_{\mathrm{G}}$ due to the metallic nature of gate
+electrode (having an infinitely-large quantum capacitance). We
+therefore conclude that the quantum capacitance-induced nonlinear
+damping in the surface potential results in the observed salt
+rejection.  Following the above discussions, we further investigate
+the physical limits for the biased graphene nanopores. Specifically,
+the salt rejection characteristics are controlled by: (i) the overlap
+of EDL inside the nanopore, essentially controlled by two length
+scales of $\lambda_{\mathrm{D}}$ and $R_{\mathrm{G}}$, and (ii) the
+graphene surface potential $\psi_{\mathrm{G}}$ controlled by
+$V_{\mathrm{G}}$ following Eq. \ref{eq:Vg}. To this end, we calculate
+$\psi_{\mathrm{G}}$ as a function of
+$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (\Fig{}
+\ref{fig:5}a). Clearly, when the bulk concentration $c_{0}$ increases,
+a higher $V_{\mathrm{G}}$ is required to reach the same level of
+$\psi_{\mathrm{G}}$. Consequently, as revealed in \Fig{} \ref{fig:5}b,
+the calculated salt rejection factor $\xi$ increases with both
+$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$, in line
+with the experimentally observed $\xi - c_{0}$ dependence. We also
+find the overall trends for $\psi_{\mathrm{G}}$ and $\xi$ with respect
+to $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
 similar. More importantly, based on our theoretical prediction, with
-$V_{\mathrm{G}}$=1.25 V and
-$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$=1.0, a high value of $\xi$ of
-$>$0.85 can be achieved.
+$V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$
+= 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.
 
@@
 Finally, we examine other salt species and compare the degree of salt
-rejection between experiments and simulations. Figure \ref{fig:6}a
+rejection between experiments and simulations. \Fig{} \ref{fig:6}a
 presents the measured salt rejection $\xi$ as a function of
-$V_{\mathrm{G}}$ from at $c_{0}$=0.1 mM, for the seven salt species
+$V_{\mathrm{G}}$ from at $c_{0}$ = 0.1 mM, for the seven salt species
 considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
 K$_{2}$SO$_{4}$, and K$_{3}$Fe(CN)$_{6}$ (details see Supplementary
-Section S7 \todo{confirm}). Similar to the KCl system discussed
-earlier, the salt rejection was only observed in the positive
-$V_{\mathrm{G}}$ regime. The degree of salt rejection deceases with
-the salt valance; for example, the measured $\xi$ values at
-$V_{\mathrm{G}}$=1.25 V decreases from $>$0.5 for monovalent NaCl to
--0.04 for multivalent K$_{3}$Fe(CN)$_{6}$. This observation is
-endorsed by our simulations, in which we calculate $\xi$ as a function
-of $V_{\mathrm{g}}$ using the same setups in simulations (Figure
-\ref{fig:6}b; details see Supplementary Section SXX
-\todo{confirm}). The calculated $\xi_{\mathrm{max}}$ values are
-quantitatively compared with experiments (Figure \ref{fig:6}c), and
-the same trend is observed. Indeed, because the Debye screening length
+Section S7 \todo[inline]{Roman, could you check the value of Debye
+  length K$3$(Fe(CN)$_{6}$ in Table S3? I calculated 12.4
+  nm}). Similar to the KCl system discussed earlier, the salt
+rejection was only observed in the positive $V_{\mathrm{G}}$
+regime. The degree of salt rejection deceases with the salt valance;
+for example, the measured $\xi$ values at $V_{\mathrm{G}}$ = 1.25 V
+decreases from $>$ 0.5 for monovalent NaCl to -0.04 for multivalent
+K$_{3}$Fe(CN)$_{6}$. This observation is endorsed by our simulations,
+in which we calculate $\xi$ as a function of $V_{\mathrm{g}}$ using
+the same setups in simulations (\Fig{} \ref{fig:6}b). The calculated
+$\xi_{\mathrm{max}}$ values are quantitatively compared with
+experiments (\Fig{} \ref{fig:6}c), and the same trend is
+observed. Indeed, because the Debye screening length
 $\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
 surface potential appears to decrease in the multivalent salt systems,
-thereby reducing $\xi$ (see Figure \ref{fig:5}b). The calculated and
+thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b). The calculated and
 experimental $\xi_{\mathrm{max}}$ as a function of
 $\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
-species considered here (Figure \ref{fig:6}d). We notice that without
+species considered here (\Fig{} \ref{fig:6}d). We notice that without
 any fitting parameters, our theory can predict the experimental values
@@
 negligible. This finding also explains the concentration dependence of
-$\xi_{\mathrm{max}}$ observed in Figure \ref{fig:2}d, as
+$\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
 $\delta_{\mathrm{D}} \propto c_{0}^{-0.5}$.
@@
 degree of salt rejection. We report a high degree of salt rejection at
-$V_{\mathrm{G}}$=1.25 V of up to 55\% and 80\%, based on our
+$V_{\mathrm{G}}$ = 1.25 V of up to 55\% and 80\%, based on our
 experiments and theoretical predictions, respectively. We demonstrate
@@
 hydrofluoric acid (BHF) as described by\cite{Choi_2018}. A schematic
-of the process is shown in Figure S1.
+of the process is shown in \Fig{} S1.
 
@@
 copper tape so that the membrane acts as a working electrode (WE). A
-platinum wire (length 3cm, diameter 0.6 mm) placed in the low
+platinum wire (length 3 cm, diameter 0.6 mm) placed in the low
 concentration side of the diffusion cell with a distance of $\sim$3.5 cm
@@
 
-\section{Acknowledgements}
-\label{sec:ack}
+\begin{acknowledgement}
 \todo[inline]{TBD} R.M.W. and H.G.P. acknowledge the support from
@@
 ETH startup funding.
+\end{acknowledgement}
 
@@
 
-H.G.P and C.J.S conceived the experiments. R.M.W measured the ion diffusion
-and gating experiments. T.T performed numerical simulations. All authors
-contributed to writing and discussion.
+H.G.P and C.J.S conceived the experiments. R.M.W and K.Y. measured the ion
+diffusion and gating experiments. T.T performed numerical
+simulations. All authors contributed to writing and discussion.
 
@@
     higher degree of salt rejection for
-    $V_{\mathrm{G}}$>0. \textbf{d}. $\xi_{\mathrm{max}}$ as a function
+    $V_{\mathrm{G}}>0$. \textbf{d}. $\xi_{\mathrm{max}}$ as a function
     of KCL concentration, fitted by a power law relation, suggesting
@@
     plot of electrostatic potential $\psi$ near the center of the
-    graphene nanopore at $V_{\mathrm{G}}$=0.75 V. \textbf{b}. The
+    graphene nanopore at $V_{\mathrm{G}}$ = 0.75 V. \textbf{b}. The
     corresponding electrochemical potential change for cation

### 2018-10-03 paper/src/plot_diffusion_slope.py

@@ -1,0 +1,21 @@
+import numpy
+import matplotlib.pyplot as plt
+
+def get_time(string):
+    string = string.decode("ascii")
+    h, m, s = map(float, string.split(":"))
+    return 3600 * h + 60 * m + 1 * s
+    
+data = numpy.genfromtxt("../data/diffusion-slope.csv",
+                        converters={1: get_time},
+                        delimiter=",")
+
+plt.figure(figsize=(3, 3 * 0.8))
+plt.style.use("science")
+cond = numpy.where(data[:, 1] < 3600)
+# plt.plot(data[:, 1][cond] / 3600, data[:, 2][cond] / 1e-3)
+# plt.plot(data[:, 1][data[:, 1] > 7200] / 3600, data[:, 2][data[:, 1] > 7200] / 1e-3)
+plt.plot(data[:, 1] / 3600, data[:, 2] / 1e-3)
+plt.xlabel("t (h)")
+plt.ylabel("Conductivity")
+plt.savefig("../img/diffusion-slope.svg")

### 2018-10-03 paper/src/plt_bar_diffuse.py

@@ -1,0 +1,44 @@
+import numpy
+import matplotlib.pyplot as plt
+
+
+salts = ["KCl", "NaCl", "LiCl", "CaCl2", "MgSO4", "K2SO4", "KFeCN"]
+data = numpy.genfromtxt("../data/diffuse-pcte-salt.csv",
+                        delimiter=",",
+                        skip_header=2)
+
+plt.figure(figsize=(3, 3 * 0.8))
+plt.style.use("science")
+
+# for i in range(len(salts)):
+    # name = salts[i]
+    # Measured
+data = data / 1e-6
+print(data.shape)
+x = numpy.arange(len(salts))
+w = 1.0 /6
+#bare pcte measure
+plt.bar(x - w * 3 / 2 , data[:, 6], width=w,
+        yerr=data[:, 7], color="blue",
+        label="raw")
+
+# Simulate
+plt.bar(x - w / 2, data[:, 3], width=w, color="red",
+        label="simu")
+
+# Bare
+plt.bar(x + 1 / 2 * w, data[:, 1], width=w,
+        yerr=data[:, 2], color="green",
+        label="gr")
+
+
+
+    # 
+# plt.plot(data[:, 1] / 3600, data[:, 2] / 1e-3)
+# plt.xlabel("t (h)")
+# plt.ylabel("Conductivity")
+plt.xticks(range(0, 7))
+plt.xlim(-0.5, 6.5)
+
+plt.legend()
+plt.savefig("../img/diffusion-salts.svg")

### 2018-10-03 paper/SI.tex
Added SI

\documentclass[manuscript=suppinfo,email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
\newcommand{\Fig}{Fig.}
\renewcommand{\thesection}{S\arabic{section}}
\SectionNumbersOn
% \usepackage{lineno}
% \linenumbers

\author{Roman M. Wyss} \affiliation{Institute of Soft Materials
  Department of Material Sciences, Eidgenössische Technische
  Hochschule (ETH) Zürich, Vladimir-Prelog-Weg 1-5, Zürich CH-8093,
  Switzerland.  }
\altaffiliation{R. M. S. and T. T. contributed equally to this work}
\author{Tian Tian} \affiliation{Institute for
  Chemical and Bioengineering Department of Chemistry and Applied
  Biosciences, Eidgenössische Technische Hochschule (ETH) Zürich,
  Vladimir-Prelog-Weg 1-5, Zürich CH-8093, Switzerland.}
\altaffiliation{R. M. S. and T. T. contributed equally to this work}

\author{Khadija Yazda} \affiliation{Nanoscience for Energy Technology and Sustainability,
Department of Mechanical and Process Engineering,
Eidgenössische Technische Hochschule (ETH) Zürich,
Tannenstrasse 3, Zürich CH-8092, Switzerland.}

\author{Hyung Gyu Park} \affiliation{Nanoscience for Energy Technology and Sustainability,
Department of Mechanical and Process Engineering,
Eidgenössische Technische Hochschule (ETH) Zürich,
Tannenstrasse 3, Zürich CH-8092, Switzerland.}

\author{Chih-Jen Shih}  \affiliation{Institute for
  Chemical and Bioengineering Department of Chemistry and Applied
  Biosciences, Eidgenössische Technische Hochschule (ETH) Zürich,
  Vladimir-Prelog-Weg 1-5, Zürich CH-8093, Switzerland.}
\email{chih-jen.shih@chem.ethz.ch}

\title{Macroscopic Salt Rejection through Electrostatically Gated Monolayer Porous Graphene}

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage{}

\section{Supplementary Section 1.	Graphene membrane manufacturing and 
results.}
\label{sec:exp}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-1.png}
  \caption{\textbf{a}. Schematic of manufacturing process for
    patterning of double layer graphene. Graphene is synthesized and
    transferred to a substrate (glass slide) to yield a double
    layer. BCP is spun and annealed in vacuum to undergo microphase
    separation, followed by plasma etch and wet etching yielding a
    porous polystyrene (PS) mask. Anisotropic etching of the mask
    leads to patterning the underlying graphene, PS is removed by
    thermal annealing. The porous graphene is then transferred to a
    substrate (e.g. PCTE). \textbf{b}. Raman spectra of graphene
    before (unpatterned, orange curve) and after (patterned, blue
    curve). An increase of the D-peak at 1350 cm$^{-1}$ indicates the
    formation of defects and edges. The spectra have been normalized
    to the G-peak intensity and offset for better
    clarity. \textbf{c}. SEM graph of patterned graphene on PCTE at
    lower (top) and higher (bottom) magnifications. Note that tears in
    graphene appear bright white with a black center.}
  \label{fig:exp}
\end{figure}

\section{Supplementary Section 2.	Ion diffusion measurement and calculation}
\label{sec:measure}

\begin{table}[htbp]
  \centering
  \begin{tabular}{lc}
    \hline
    Salt & $D$ (10$^{9}$ m$^{2}\cdot$s$^{-1}$) \\
    \hline
    K$^{+}$	& 1.95 \\
    Na$^{+}$	& 1.33 \\
    Li$^{+}$	& 1.03 \\
    SO$_{4}^{2-}$	& 1.06 \\
    Ca$^{2+}$	& 0.79\\
    Mg$^{2+}$ &	0.7\\
    Fe(CN)$_{6}^{3-}$	& 0.90\\
    Cl$^{-}$ &	2.03 \\
               \hline
  \end{tabular}
  \caption{Different diffusivities for the anions and cations of the
    salts used in this work \todo[inline]{do you need any
      reference?}. The theoretical diffusion through PCTE can be
    calculated using Eq. 1 in the main text and the diffusivities of
    the respective anion and cation.}
  \label{tab:diff}
\end{table}

The ion diffusion through b-PCTE has been performed using a sample
sandwiched between two layers of Aluminum tape where the edges have
been sealed using water-resistant epoxy (ACS Marine Epoxy) to avoid
interlayer leakage pathways \cite{Choi_2018}.  The sample was inserted in
the fixture following the same wetting procedure described in the main
text and was kept wet for the entire series of experiments.

The conductivity increases $s$ (mS$\cdot$cm$^{-1}\cdot$d$^{-1}$) is
converted into ion permeation rates $\boldsymbol{J}_{\mathrm{PCTE}}$
(mol$\cdot$m$^{-2}\cdot$s$^{-1}$) by use of a calibration factor
$c_{\mathrm{f}}$, the volume of LCR ($V_{\mathrm{LCR}}$) , the area of
the membrane $A$ and the time $t$ as:
\begin{equation}
  \label{eq:JPCTE}
  \boldsymbol{J}_{\mathrm{PCTE}} = \frac{s V_{\mathrm{LCR}}}{c_{\mathrm{f}} A t}
\end{equation}
The calibration factors for all salts have been obtained by a linear
fit of conductivity versus concentration for 4 solutions with
concentrations from 10$^{-4}$ M to 10$^{-2}$ M and extracting the
resulting slope. The rest of the factors are $V_{\mathrm{LCR}}$ = 7.33
mL, $A$ = 9$\times$10$^{-6}$ m$^{-2}$. Table \ref{tab:exp-2} shows the
averaged conductivity increase s, the extracted calibration factors
$c_{\mathrm{f}}$ and the resulting ion permeation rates using
Eq. \ref{eq:JPCTE}. The values from this table are shown in main text \Fig 2b
(blue bars).
\begin{table}[htbp]
  \centering
  \begin{tabular}{lccc}
    \hline
    Salt & $s$ (mS$\cdot$cm$^{-1}$d$^{-1}$) & $c_{\mathrm{f}}$ (mS$\cdot$cm$^{-1}\cdot$mol$^{-1}\cdot$ml) &
                                                                                                            $\boldsymbol{J}_{\mathrm{PCTE}}$ (10$^{6}$ mol$\cdot$m$^{-2}\cdot$s$^{-1}$)\\
    \hline
    KCl	& 0.0151 $\pm$ 0.00265	& 106	& 1.34 $\pm$ 0.235\\
    NaCl	& 0.0099 $\pm$ 0.000173	& 91	& 1.02 $\pm$ 0.0179\\
    LiCl	& 0.00603 $\pm$ 0.000802	& 83	& 0.679 $\pm$ 0.0903\\
    CaCl$_{2}$	& 0.0125 $\pm$ 0.001	& 149	& 0.789 $\pm$ 0.0631\\
    MgSO$_{4}$	& 0.0088 $\pm$ 0.0012	& 130	& 0.633 $\pm$ 0.084\\
    K$_{3}$Fe(CN)$_{6}$	& 0.024 $\pm$ 0.00275	& 395	& 0.575 $\pm$ 0.0633\\
    K$_{2}$SO4$_{4}$	& 0.0198 $\pm$ 0.00199	& 258	& 0.722 $\pm$ 0.0726\\
    \hline
  \end{tabular}
  \caption{Extracted slope $s$ as an averaged result from 3 consecutive
    measurements, the calibration factors $c_{\mathrm{f}}$ and the resulting ion
    permeation $\boldsymbol{J}_{\mathrm{PCTE}}$ through b-PCTE membranes for all salts.}
  \label{tab:exp-2}
\end{table}

\section{Control experiment with copper tape}
\label{sec:copper}
We make sure that the applied voltage is effectively applied via the
graphene membrane and not through leakage directly coupling the
coppertape to the ionic solution. For this, we use a device as in
\Fig 1c \todo[inline]{which figure?}, omitting the graphene and
measuring the current through the membrane with the Autolab
electrochemical workstation using the membrane as working electrode
and a platinum wire as counter/reference electrode 3.5 cm apart in 0.1
mM KCl. When no graphene is inserted in the device, a current in the
baseline range ($\sim$ 0.1 nA) is observed, indicating no current
passing from the membrane. However, if graphene is inserted, a current
in the range of $\sim$ 10 - 100 nA is measured. If the copper tape is
in contact with the solution when omitting the Kapton tape, the
current increases to $\sim$ 1 - 10 $\mathrm{\mu}$A, independent of the
exposed area of the copper tape to the solution.

\section{KCl Debye length and conductivity}
\label{sec:debye}
Table \ref{tab:debye} gives an overview about the measured
conductivities and their calculated Debye lengths for KCl. The
information is used to plot the rectification versus concentration.

\begin{table}[htbp]
  \centering
  \begin{tabular}{lccc}
    \hline
    $c_{0}$ (mM) & Conductivity (mS$\cdot$cm$^{-1}$) & $\lambda_{\mathrm{D}}$ (nm)\\
    \hline
    0.1&	0.01903&	30.4\\
    0.33&	0.0541&	16\\
    1	&0.1329	&10\\
    3.3KCl&	0.513&	6\\
    10KCl&	1.08	&3.3\\
    \hline
  \end{tabular}
  \caption{Conductivity and calculated Debye lengths of various KCl
    concentrations in order to obtain rectification versus
    concentration curves. }
  \label{tab:debye}
\end{table}

\section{Further details of the numerical simulation }
\label{sec:numer}

The numerical simulations were carried out using COMSOL Multiphysics
5.3a. The simulation domain is shown in \Fig \ref{fig:scheme}. To
simplify the geometry, we use axial symmetric coordinate system. The
radius \textit{L} and height \textit{H} of both HCR and LCR are set to
20 $R_{\mathrm{G}}$, the radius of the nanopore. The potential at the
bottom of the LCR and the center of the graphene domains are set to be
0 and $\psi_{\mathrm{G}}$, respectively. The potential at the end of
HCR is not set explicitly, but rather determined through the Poisson
equation with no flux boundary condition
$\boldsymbol{D}^{\mathrm{norm}}=0$. The relative permittivity in the
HCR and LCR is set as $\varepsilon_{\mathrm{}}=78$. The relative
permittivity of the Stern layer is set to
$\varepsilon_{\mathrm{H}}=20$\cite{Conway_1951} and for the graphene
domain we set the relative permittivity as a large number
(e.g. $10^{5}$) for a better convergence of the solver.  For the
transport of diluted ionic species, we use the PNP equations to
describe the diffusion and drift of the ions, which can be further
unified by the gradient of electrochemical potential, as described in
the main text. The initial values of the electrolyte is set to $c_{0}$
in HCR and 0.1 $c_{0}$ in LCR. At the ends of the cells in the
z-direction, we use the inlet boundaries conditions for the
concentration of electrolytes, that the concentration on these
boundaries remains the same with the initial value, due to the
effective mixing in the experimental setup.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-numerical-1.png}
  \caption{Scheme of the simulation domain used. Left: geometry of the
    whole simulation domain. Right: configuration near the graphene
    nanopore, corresponding to the red rectangle on the left side.}
  \label{fig:scheme}
\end{figure}

The transport of ionic species is described by the steady-state
Nernst-Planck equation:
\begin{eqnarray}
  \label{eq:pnp}
  \nabla \cdot \boldsymbol{J}_{i} = -\nabla \cdot \left( \frac{D_{i}}{k_{\mathrm{B}}T} c_{i} N_{\mathrm{A}} \nabla \mu_{i}\right)
  = -\nabla \cdot \left( \frac{D_{i}}{k_{\mathrm{B}} T} c_{i} N_{\mathrm{A}}
  [k_{\mathrm{B}}T \nabla \ln x_{i} + z_{i} e \nabla \psi]\right) = 0\\
  x_{i} = \frac{c_{i}}{\sum_{i} c_{i} + c_{\mathrm{H_{2}O}}}
\end{eqnarray}
The potential distribution within the whole simulation domain is
described by the Poisson equation:
\begin{equation}
  \label{eq:poisson}
  \nabla \cdot (\varepsilon_{\mathrm{m}} \varepsilon_{0} \nabla \psi) = -N_{\mathrm{A}} e \sum_{i} c_{i}z_{i}
\end{equation}
Where $\varepsilon_{\mathrm{m}}$ is the relative permittivity of
domain m. The contribution of mobile charges is only valid in the
solution domain. The use of a large $\varepsilon_{\mathrm{G}}$ ensures
that the potential in the whole simulation domain can be solved
continuously.

To simulate the applied external bias $V_{\mathrm{G}}$, we set the
value of $\psi_{\mathrm{G}}$ explicitly and extract the charge
$\sigma_{\mathrm{G}}$ by:
\begin{equation}
  \label{eq:sigma-G}
  \sigma_{\mathrm{G}} = - {\displaystyle \frac{\int_{\mathrm{\Omega}} z_{i} c_{i} N_{\mathrm{A}} e \mathrm{d}^{3} \Omega}{S_{\mathrm{G}}}}
\end{equation}
and $V_{\mathrm{G}}$ is then calculated by:
\begin{eqnarray}
  \label{eq:VG}
  V_{\mathrm{G}} = \Delta \phi_{\mathrm{G}} + \psi_{\mathrm{G}}\\
  \sigma_{\mathrm{G}} = \int_{0}^{\Delta \phi_{\mathrm{G}}} \frac{1}{C_{\mathrm{Q}}(\phi_{\mathrm{G}})} \mathrm{d} \phi_{\mathrm{G}}
\end{eqnarray}
where the quantum capacitance
$C_{\mathrm{Q}}=\partial \sigma_{\mathrm{G}}/\partial
\phi_{\mathrm{G}}$ is calculated by Eq. 8 in main text.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{img/SI-trap.png}
  \caption{Schematic illustration of the origin of the asymmetric
    rectification with respect to $V_{\mathrm{G}}$. Due to the
    existence of surface charge traps at negative $V_{\mathrm{G}}$,
    the graphene is less charged compared to the positive
    $V_{\mathrm{G}}$.}
  \label{fig:trap}
\end{figure}

Note that due
to the existence of electron traps on graphene due to fabrication
process, the induced charge traps on graphene effectively reduce the
charge density on graphene and greatly attenuate the surface potential
on graphene, as illustrated in \Fig. \ref{fig:trap}. This effect is
universally observed in CVD-graphene-based field effect transistors in
air, while the mechanism is fully understood yet. In view of this, we
only simulate the situation where $V_{\mathrm{G}}>$ 0 for the salt
rejection mechanism. The trend that $\xi$ is almost independent of
$V_{\mathrm{G}}$ when $V_{\mathrm{G}}<$ 0 can be qualitatively
explained by the existence of surface charge traps as stated above.

\section{Further numerical simulation results}
\label{sec:simu-res}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-concentration.png}
  \caption{Cation concentration $c_{+}$ (\textbf{a}.) and anion
    concentration $c_{-}$ (\textbf{b}.) near the graphene nanopore for
    KCl solution at 0.1 mM. Depletion of cation and accumulation of
    anion can be observed near the graphene surface.}
  \label{fig:conc}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-electrochemical-decomposite.pdf}
  \caption{Decomposition of electrochemical potential near a nanopore
    corresponding to \Fig 4 in main text. \textbf{a}. The electrostatic
    (drift) contribution to the electrochemical potential for cation
    (left) and anion (right) and \textbf{b}. The concentration (diffusion)
    contribution to the electrochemical potential for cation (left)
    and anion (right). The relative small order of magnitude for anion
    electrochemical potential is caused by the balance between the
    diffusion and drift for anion.}
  \label{fig:potential}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-flux.png}
  \caption{z-component flux $\boldsymbol{J}_{z}$ of cation
    (\textbf{a}.)  and anion (\textbf{b}.) near the graphene nanopore
    corresponding to Figure 4b in main text. The pathways for the
    different ions can be spatially distinguished: the flux of cation
    passes mostly through the center of the graphene nanopore while
    the anion passes mainly through the edge. The analysis is in
    consistent with the gradient of chemical potential as shown in the
    main text \Fig 4b.}
  \label{fig:flux}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{img/SI-rect-reverse.pdf}
  \caption{Average total flux $\boldsymbol{J}_{z}$ in the nanopore as
    a function of $\psi_{\mathrm{G}}$ at different concentrations. The
    range of $\psi_{\mathrm{G}}$ is larger than the experimentally
    achievable value. The rectification of flux becomes weaker after a
    certain level of $\psi_{\mathrm{G}}$ is reached. Further
    increasing the surface potential of graphene may even enhance the
    transportation of ions, which is similar to the cases of ionic
    transistors.}
  \label{fig:reverse}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-flux-larger.png}
  \caption{Spatial distribution of $\boldsymbol{J}_{z}$ as a function
    of $r$ in a 20 nm nanopore at different levels of
    $\psi_{\mathrm{G}}$ (larger than experimentally achievable values)
    for cation (\textbf{a}.) and anion (\textbf{b}.). The cation flux
    becomes nearly saturated with increasing $\psi_{\mathrm{G}}$,
    while the flow of anion near the pore edge becomes much
    larger. The drastic increase of pore-bounded anion flux is caused
    by the accumulation of anions near the graphene surface, and in
    turn causes the increasing of total flux as seen in \Fig
    \ref{fig:reverse}.}
  \label{fig:large-V}
\end{figure}
\clearpage{}

\section{Conductivities and Debye length for all salts}
\label{sec:salts}
In Table \ref{tab:debye}, the conductivities and calculated Debye
lengths for 6 salts are shown. At the same concentration, the higher
ionic strength of the multivalent salts leads to a reduction of the
respective Debye lengths.

\begin{table}[htbp]
  \centering
  \begin{tabular}{lcc}
    \hline
    Solution & Conductivity (mS$\cdot$cm$^{-1}$) & $\lambda_{\mathrm{D}}$ (nm) \\
    \hline
    0.1 mM NaCl	&0.018	&30.4\\
    0.1 mM LiCl	&0.0158	&30.4\\
    0.1 mM CaCl$_{2}$&	0.02187	&17.2\\
    0.1 mM MgSO$_{4}$	&0.0327	&15.2\\
    0.1 mM K$_{2}$SO$_{4}$	&0.0416	&17.2\\
    0.1 mM K$_{3}$(Fe(CN)$_{6}$)&	0.0595	&9.6\\
    \hline
  \end{tabular}
  \caption{conductivity}
  \label{tab:conductivity}
\end{table}

\section*{}
\label{sec:ref}
\bibliography{ref}

\end{document}

### 2018-10-04 paper/SI.tex
Add Makefiles

@@
 
-\section{Supplementary Section 1.	Graphene membrane manufacturing and 
+\section{Graphene membrane manufacturing and 
 results.}
@@
 
-\section{Supplementary Section 2.	Ion diffusion measurement and calculation}
+\section{Ion diffusion measurement and calculation}
 \label{sec:measure}
@@
     Mg$^{2+}$ & 0.7\\
-    Fe(CN)$_{6}^{3-}$	& 0.90\\
+    {[Fe(CN)$_{6}$]$^{3-}$}   & 0.90\\
     Cl$^{-}$ &  2.03 \\
@@
   \caption{Different diffusivities for the anions and cations of the
-    salts used in this work \todo[inline]{do you need any
-      reference?}. The theoretical diffusion through PCTE can be
+    salts used in this work \cite{vanysek_2000}. The theoretical diffusion through PCTE can be
     calculated using Eq. 1 in the main text and the diffusivities of
@@
     MgSO$_{4}$  & 0.0088 $\pm$ 0.0012   & 130   & 0.633 $\pm$ 0.084\\
-    K$_{3}$Fe(CN)$_{6}$	& 0.024 $\pm$ 0.00275	& 395	& 0.575 $\pm$ 0.0633\\
+    K$_{3}$[Fe(CN)$_{6}$] & 0.024 $\pm$ 0.00275   & 395   & 0.575 $\pm$ 0.0633\\
     K$_{2}$SO4$_{4}$    & 0.0198 $\pm$ 0.00199  & 258   & 0.722 $\pm$ 0.0726\\
@@
     1   &0.1329 &10\\
-    3.3KCl&	0.513&	6\\
-    10KCl&	1.08	&3.3\\
+    3.3&     0.513&  6\\
+    10&      1.08    &3.3\\
     \hline
@@
     0.1 mM K$_{2}$SO$_{4}$      &0.0416 &17.2\\
-    0.1 mM K$_{3}$(Fe(CN)$_{6}$)&	0.0595	&9.6\\
+    0.1 mM K$_{3}${[Fe(CN)$_{6}$]}&       0.0595  &9.6\\
     \hline
   \end{tabular}
-  \caption{conductivity}
+  \caption{Conductivities and Debye lengths for the 6 different salts
+    under investigation.}
   \label{tab:conductivity}

### 2018-10-04 paper/paper.tex
Add Makefiles

@@
 diffusion of seven salt species, including KCl, NaCl, LiCl,
-K$_{2}$SO$_{4}$, MgSO4$_{4}$, CaCl$_{2}$ and K$_{3}$Fe(CN)$_{6}$,
+K$_{2}$SO$_{4}$, MgSO4$_{4}$, CaCl$_{2}$ and K$_{3}$[Fe(CN)$_{6}$],
 through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
@@
 observed a more pronounced decrease of diffusive flux in KCl,
-K$_{2}$SO$_{4}$ and K$_{3}$Fe(CN)$_{6}$ systems but not for the rest
+K$_{2}$SO$_{4}$ and K$_{3}$[Fe(CN)$_{6}$] systems but not for the rest
 of the salts. We hypothesized that the strong cation-$\pi$ interactions
@@
 considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
-K$_{2}$SO$_{4}$, and K$_{3}$Fe(CN)$_{6}$ (details see Supplementary
-Section S7 \todo[inline]{Roman, could you check the value of Debye
-  length K$3$(Fe(CN)$_{6}$ in Table S3? I calculated 12.4
-  nm}). Similar to the KCl system discussed earlier, the salt
+K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (details see Supplementary
+Section S7). Similar to the KCl system discussed earlier, the salt
 rejection was only observed in the positive $V_{\mathrm{G}}$
@@
 decreases from $>$ 0.5 for monovalent NaCl to -0.04 for multivalent
-K$_{3}$Fe(CN)$_{6}$. This observation is endorsed by our simulations,
+K$_{3}$[Fe(CN)$_{6}$]. This observation is endorsed by our simulations,
 in which we calculate $\xi$ as a function of $V_{\mathrm{g}}$ using
@@
 $\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
-$\delta_{\mathrm{D}} \propto c_{0}^{-0.5}$.
+$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$.
 
@@
 experiments. 7 salts were used: KCl, NaCl, LiCl, K$_{2}$SO$_{4}$,
-CaCl$_{2}$, MgSO$_{4}$ and K$_{3}$Fe(CN)$_{6}$. The salts were
+CaCl$_{2}$, MgSO$_{4}$ and K$_{3}$[Fe(CN)$_{6}$]. The salts were
 purchased from Sigma Aldrich and used without further purification,

### 2018-10-04 paper/SI.tex
Minor revision in main and SI

--- 2018-10-03 paper/SI.tex
@@
     0.1 mM K$_{2}$SO$_{4}$	&0.0416	&17.2\\
-    0.1 mM K$_{3}$(Fe(CN)$_{6}$)&	0.0595	&9.6\\
+    0.1 mM K$_{3}$(Fe(CN)$_{6}$)&	0.0595	&12.4\\
     \hline

### 2018-10-04 paper/paper.tex
Minor revision in main and SI

@@
 \newcommand{\Fig}{Fig.}
+\newcommand{\hide}[1]{}
 % \usepackage{lineno}
@@
 
-\title{Macroscopic Salt Rejection through Electrostatically Gated Monolayer Porous Graphene}
+\title{Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene}
 
@@
   drill subnanometer pores over a large area. Here we report
-  macroscopic salt rejection through monolayer porous graphene with
+  macroscopic salt rejection through  porous graphene with
   the pore sizes of 20$\pm$10 nanometers, overcoming the pore size
@@
   developing a theory to model the electrolyte diffusion through a
-  nanopore in a sheet of gated monolayer graphene. The interplay
+  nanopore in a sheet of gated  graphene. The interplay
   between graphene quantum capacitance and electrical double layer is
@@
   controlling the membrane potential and electrolyte permeation
-  through porous two-dimensional monolayers.
+  through porous two-dimensional materials.
 \end{abstract}
@@
 \Fig{} \ref{fig:1}a depicts the experimental setup characterizing
-ionic diffusion through a sheet of monolayer porous graphene (PG). Two
+ionic diffusion through a sheet of porous graphene (PG). Two
 reservoirs, namely the high-concentration reservoir (HCR) containing
@@
 (e.g. \Fig{} \ref{fig:2}a) remains linear within the measurement
-duration (1 h), suggesting the concentration change in individual
-reservoirs is negligible \todo[inline]{Isn't the increasing of
-  conductivity a measure of the diffusion of ions?}. The diffusive fluxes
+duration (1 h), indicating the cross-membrane concentration gradient
+is almost constant during the experiment. The diffusive fluxes
 correspond to different salts were obtained by converting the

### 2018-10-04 paper/SI.tex
Minor changes to main and SI

--- 2018-10-04 paper/SI.tex
@@
 
-\section{Graphene membrane manufacturing and 
-results.}
+\section{Graphene membrane manufacturing and results.}
 \label{sec:exp}
@@
 
-\section{Ion diffusion measurement and calculation}
+\section{Supplementary Section 2.       Ion diffusion measurement and calculation}
 \label{sec:measure}
@@
     Mg$^{2+}$ & 0.7\\
-    {[Fe(CN)$_{6}$]$^{3-}$}   & 0.90\\
+    Fe{[(CN)$_{6}$]}$^{3-}$   & 0.90\\
     Cl$^{-}$ &  2.03 \\
@@
   \caption{Different diffusivities for the anions and cations of the
-    salts used in this work \cite{vanysek_2000}. The theoretical diffusion through PCTE can be
-    calculated using Eq. 1 in the main text and the diffusivities of
-    the respective anion and cation.}
+    salts used in this work \cite{vanysek_2000}. The theoretical
+    diffusion through PCTE can be calculated using Eq. 1 in the main
+    text and the diffusivities of the respective anion and cation.}
   \label{tab:diff}
@@
     MgSO$_{4}$  & 0.0088 $\pm$ 0.0012   & 130   & 0.633 $\pm$ 0.084\\
-    K$_{3}$[Fe(CN)$_{6}$] & 0.024 $\pm$ 0.00275   & 395   & 0.575 $\pm$ 0.0633\\
+    K$_{3}$[Fe(CN)$_{6}]$ & 0.024 $\pm$ 0.00275   & 395   & 0.575 $\pm$ 0.0633\\
     K$_{2}$SO4$_{4}$    & 0.0198 $\pm$ 0.00199  & 258   & 0.722 $\pm$ 0.0726\\
@@
 graphene membrane and not through leakage directly coupling the
-coppertape to the ionic solution. For this, we use a device as in
-\Fig 1c \todo[inline]{which figure?}, omitting the graphene and
-measuring the current through the membrane with the Autolab
-electrochemical workstation using the membrane as working electrode
-and a platinum wire as counter/reference electrode 3.5 cm apart in 0.1
-mM KCl. When no graphene is inserted in the device, a current in the
-baseline range ($\sim$ 0.1 nA) is observed, indicating no current
-passing from the membrane. However, if graphene is inserted, a current
-in the range of $\sim$ 10 - 100 nA is measured. If the copper tape is
-in contact with the solution when omitting the Kapton tape, the
-current increases to $\sim$ 1 - 10 $\mathrm{\mu}$A, independent of the
-exposed area of the copper tape to the solution.
+coppertape to the ionic solution. For this, we use a device as in \Fig
+1a, omitting the graphene and measuring the current through the
+membrane with the Autolab electrochemical workstation using the
+membrane as working electrode and a platinum wire as counter/reference
+electrode 3.5 cm apart in 0.1 mM KCl. When no graphene is inserted in
+the device, a current in the baseline range ($\sim$ 0.1 nA) is
+observed, indicating no current passing from the membrane. However, if
+graphene is inserted, a current in the range of $\sim$ 10 - 100 nA is
+measured. If the copper tape is in contact with the solution when
+omitting the Kapton tape, the current increases to $\sim$ 1 - 10
+$\mathrm{\mu}$A, independent of the exposed area of the copper tape to
+the solution.
 
@@
     0.1 mM K$_{2}$SO$_{4}$      &0.0416 &17.2\\
-    0.1 mM K$_{3}${[Fe(CN)$_{6}$]}&       0.0595  &9.6\\
+    0.1 mM K$_{3}$[Fe(CN)$_{6}$]&       0.0595  &12.4\\
     \hline
   \end{tabular}
-  \caption{Conductivities and Debye lengths for the 6 different salts
-    under investigation.}
+  \caption{conductivity}
   \label{tab:conductivity}

### 2018-10-21 paper/paper.tex
Minor changes to main and SI
Change abstract 20181021

@@
 \newcommand{\Fig}{Fig.}
-\newcommand{\hide}[1]{}
 % \usepackage{lineno}
@@
 \begin{abstract}
+  {\normalsize
   Atomically thin graphene nanopores is emerging as one of the most
@@
   to the ultrahigh permeability. However, the size-exclusive mechanism
-  limits its scalability as it remains technically challenging to
-  drill subnanometer pores over a large area. Here we report
-  macroscopic salt rejection through  porous graphene with
-  the pore sizes of 20$\pm$10 nanometers, overcoming the pore size
-  limitation set by the hydrated radii. By electrostatically gating a
-  sheet of porous graphene, we report a considerable reduction of salt
-  flux by up to 55\% with the gate voltage. We systematically
-  investigate the effects of salt concentration and species, including
-  developing a theory to model the electrolyte diffusion through a
-  nanopore in a sheet of gated  graphene. The interplay
-  between graphene quantum capacitance and electrical double layer is
-  identified to be the main mechanism responsible for the observed
-  salt rejection, when the pore size is comparable to the Debye
-  screening length. Our findings reveal a new degree of freedom
-  controlling the membrane potential and electrolyte permeation
-  through porous two-dimensional materials.
+  of selectivity limits its scalability as it remains technically
+  challenging to drill subnanometer pores over a large area. Here we
+  report macroscopic salt rejection through atomically-thin porous
+  graphene with the pore sizes of 20$\pm$10 nanometers, overcoming the
+  pore size limitation set by the hydrated radii. By electrostatically
+  gating a sheet of porous graphene, we report a considerable
+  reduction of salt flux by up to 55\% and 85\% with the gate voltage,
+  based on our experiments and theoretical predictions,
+  respectively. We systematically investigate the effects of salt
+  concentration and species, including developing a theory to model
+  the electrolyte diffusion through a nanopore in a sheet of gated
+  graphene. The interplay between graphene quantum capacitance and
+  electrical double layer is identified to be the main mechanism
+  responsible for the observed salt rejection, when the pore size is
+  comparable to the Debye screening length. Our findings reveal a new
+  degree of freedom controlling the membrane potential and electrolyte
+  permeation through porous two-dimensional materials.
+  }
 \end{abstract}

### 2018-10-21 paper/paper.tex
Change Intro part

@@
 manipulate transport phenomena at nanometer scale to enable new
-technological opportunities for sensing and energy applications. The
-reduction of characteristic dimensions in nanofluidics gives rise to
-substantially different transport properties compared to their bulk
-counterparts \cite{Schoch_2008}. In nanopores, for example, the effect
-of surface-mediated transport becomes dominant when the pore size is
+technological opportunities. The reduction of characteristic
+dimensions in nanofluidics gives rise to substantially different
+transport properties compared to their bulk counterparts
+\cite{Schoch_2008}. In nanopores, for example, the effect of
+surface-mediated transport becomes dominant when the pore size is
 comparable to the solute diffusion length, enabling new applications,
@@
 nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}, Porous,
-atomically thin two-dimensional (2D) materials, such as graphene,
-embody an ideal membrane materials due to their ultimate permeability
+atomically thin two-dimensional (2D) materials, such as graphene, are
+emerging as ideal membrane materials due to their ultimate
+permeability
 \cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
@@
 desalination membrane enables excellent salt rejection by preventing
-the permeation of the hydrated ions the (1 nm - 3 nm) with
-simultaneous high water permeation
+the permeation of hydrated ions with a high water permeability
+simultaneous
 \cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2015,Surwade_2015}. Nevertheless,
-the fabrication of sub-5 nanometer porous 2D membranes over a large
-area with atomic precision is technically challenging
+the fabrication of subnanometer porous 2D membranes over a large area
+with atomic precision remains technically challenging
 \cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
 portion of large pores can significantly diminish salt rejection.
-Accordingly, recent research efforts have explored the effect of
-surface charges on the selectivity of ion transport, as a consequence
-of coulombic repulsion of the solvated ion and the charged functional
-groups on graphene \cite{Rollings_2016,Surwade_2014}. However, it
-remains controversial that if the surface charges can result in a
-degree of salt rejection, as the membrane potential is sensitive to
-the surroundings and chemical treatment \cite{Li_2008}. The
-difficulty in turn hinders fundamental understanding of the
-interactions between the atomically thin 2D membrane and electrolyte
-solution. Here, we demonstrate macroscopic salt rejection through a
-sheet of large-area porous graphene using electrostatic gating,
-thereby deepening the understanding of ion-graphene interaction and
-its implications on nanoporous graphene-based desalination
-applications.
+Very recently, a number of reports have explored the effect of surface
+charges on the selectivity of ion transport through graphene
+nanopores, as a consequence of the electrostatic interactions between
+solvated ions and the charged functional groups attached on graphene
+\cite{Rollings_2016,Surwade_2014}. However, it remains controversial
+that if the surface charges can result in a degree of salt rejection,
+as the membrane charge and potential cannot be precisely quantified
+and are sensitive to the surroundings and chemical treatment
+\cite{Li_2008}. The difficulty in turn hinders fundamental
+understanding of the interactions between the atomically thin 2D
+membrane and electrolyte solution. Here, we demonstrate macroscopic
+salt rejection through a sheet of large-area porous graphene using
+electrostatic gating, thereby deepening the understanding of
+ion-graphene interaction and its implications on nanoporous
+graphene-based desalination applications.
 

### 2018-10-21 paper/paper.tex
Change exp part

@@
 \Fig{} \ref{fig:1}a depicts the experimental setup characterizing
-ionic diffusion through a sheet of porous graphene (PG). Two
-reservoirs, namely the high-concentration reservoir (HCR) containing
-electrolyte solution with molar concentration $c_0$, and the
-low-concentration reservoir (LCR) containing de-ionized (DI) water,
-are separated by a PG membrane supported by polycarbonate track-etched
-(PCTE) film. Magnetic stirrers are used to minimize the effects of
-external concentration polarization, and a conductivity probe is
-placed in the LCR to monitor the ionic concentration as a function of
-time. The membrane is attached to a piece of copper tape connected to
-a voltage source applying an electrical bias $V_{\mathrm{G}}$, with
-the LCR grounded (\Fig{} \ref{fig:1}a inset). We fabricated the
-PCTE-supported PG using the protocol developed by our group
-\cite{Choi_2018}, as schematically shown in \Fig{} \ref{fig:1}b. The
-normally distributed, circular pores with pore diameters of 20$\pm$10
-nm (\Fig{} \ref{fig:1}c inset) over a large area were drilled on
-graphene.  By optimizing the subsequent transfer process, a high
-surface coverage ($>$ 98\%) of graphene on PCTE was reached (\Fig{}
-\ref{fig:1}c), allowing to reliably characterize the ion transport
-behavior (details see Supplementary Information Section S1).  The
-system presented here allows us to systematically investigate the
-diffusive flux across a sheet of porous graphene, $\boldsymbol{J}$,
-driven by the gradient of electrochemical potential in the electrolyte
-medium.
+ionic diffusion through a sheet of double layer porous graphene
+(PG). Two reservoirs, namely the high-concentration reservoir (HCR)
+containing electrolyte solution with molar concentration $c_0$, and
+the low-concentration reservoir (LCR) containing de-ionized (DI)
+water, are separated by a PG membrane supported by polycarbonate
+track-etched (PCTE) film. Magnetic stirrers are used to minimize the
+effects of external concentration polarization, and a conductivity
+probe is placed in the LCR to monitor the ionic concentration as a
+function of time. The membrane is attached to a piece of copper tape
+connected to a voltage source applying an electrical bias
+$V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
+inset). We fabricated the PCTE-supported PG using the protocol
+developed by our group \cite{Choi_2018}, as schematically shown in
+\Fig{} \ref{fig:1}b. The normally distributed, circular pores with
+pore diameters of 20$\pm$10 nm (\Fig{} \ref{fig:1}c inset) over a
+large area were drilled on graphene.  By optimizing the subsequent
+transfer process, a high surface coverage ($>$ 98\%) of graphene on
+PCTE was reached (\Fig{} \ref{fig:1}c), allowing to reliably
+characterize the ion transport behavior (details see Supplementary
+Information Section S1).  The system presented here allows us to
+systematically investigate the diffusive flux across a sheet of porous
+graphene, $\boldsymbol{J}$, driven by the gradient of electrochemical
+potential in the electrolyte medium.
 
@@
 (e.g. \Fig{} \ref{fig:2}a) remains linear within the measurement
-duration (1 h), indicating the cross-membrane concentration gradient
-is almost constant during the experiment. The diffusive fluxes
+duration (1 h), suggesting the concentration gradient across the
+membrane remains constant. The diffusive fluxes
 correspond to different salts were obtained by converting the
@@
 where $\boldsymbol{J}$ is the mass flux, subscript \textit{i}
-corresponds to the species (anion or cation), $D$ is the diffusivity,
+corresponds to the ionic species (anion or cation), $D$ is the diffusivity,
 $k_{\mathrm{B}}$ is the Boltzmann constant, $T$ is temperature, $c$ is
@@
 \end{equation}
-where $x$ is the molar fraction, $z$ is the ionic valence, $e$ is the
-unit charge, and $\psi$ is the electric potential. On the other hand,
-the Poisson equation describing the electric potential distribution is
-given by:
+where $x$ is the molar fraction in solution, $z$ is the ionic valence,
+$e$ is the unit charge, and $\psi$ is the electric potential. On the
+other hand, the Poisson equation describing the electric potential
+distribution is given by:
 \begin{equation}
@@
 where $\varepsilon_{\mathrm{m}}$ is the relative permittivity of
-individual materials in the system. Including water and the internal
+individual materials in the system, including water and the internal
 Stern layer\cite{Tian_2017}, and
@@
 $\Delta \phi_{\mathrm{G}} - \sigma_{\mathrm{G}}$ dependence follows
-Eq. \ref{eq:delta-phiG}. The theory proposed here was solved
-self-consistently by discretizing Eqs. \ref{eq:pnp}-\ref{eq:poisson}
+Eq. \eqref{eq:delta-phiG}. The theory proposed here was solved
+self-consistently by discretizing Eqs. \eqref{eq:pnp}-\eqref{eq:poisson}
 using the finite-element method (FEM), in which the graphene surface
 potential is coupled with
-Eqs. \ref{eq:electro-neutral}-\ref{eq:delta-phiG} that were solved
+Eqs. \eqref{eq:electro-neutral}-\eqref{eq:delta-phiG} that were solved
 simultaneously to reach convergent numerical solutions of
@@
 respect to $V_{\mathrm{G}}$ due to the symmetric band structure of
-graphene (Eq. \ref{eq:delta-phiG}). However, for graphene synthesized
+graphene (Eq. \eqref{eq:delta-phiG}). However, for graphene synthesized
 by chemical vapor deposition (CVD) used in our experiments, it is
@@
 nanopore for a given $V_{\mathrm{G}}$. Since the ionic flux is driven
-by both $\psi$ and $c$ fields (see Eq. \ref{eq:pnp} and \ref{eq:mu}),
+by both $\psi$ and $c$ fields (see Eq. \eqref{eq:pnp} and \eqref{eq:mu}),
 we focus on the electrochemical potential $\mu_{i}$, which represents
@@
 that the concentration gradient at the pore center becomes
-small. (also see Supplementary \Fig{}s S4). We also
+small. (also see Supplementary \Fig{} S4). We also
 observe that $\Delta \mu_{+}$ is dominated by the concentration, while
@@
 center for cations and pore edge for anions. \Fig{} \ref{fig:4}c
-presents the calculated z-component of the cation and anion fluxes
+presents the calculated \textit{z}-component of the cation and anion fluxes
 through the pore at the graphene plane (z = 0), $\boldsymbol{J}_{z}$
@@
 at different $V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$
-is negative because the LCR is placed at z < 0 in the simulations. At
+is negative because the LCR is placed at z$<$0 in the simulation box. At
 $V_{\mathrm{G}}$ = 0 (pure diffusion), the anion and cation flux
@@
 over diffusion flux and (ii) the concentration near the pore edge
-(prefered path) greatly increases. This level of $\psi_{\mathrm{G}}$
-cannot be reached experimentally in graphene membrane, as this
-requires a $V_{\mathrm{G}}$ larger than 2.0 V, which triggers the
-electrochemical reactions \cite{Toh_2011}. On the other hand, in an
-IFET, the electric potential on the pore wall is considerably higher,
-equivalent to $V_{\mathrm{G}}$ due to the metallic nature of gate
-electrode (having an infinitely-large quantum capacitance). We
-therefore conclude that the quantum capacitance-induced nonlinear
-damping in the surface potential results in the observed salt
-rejection.  Following the above discussions, we further investigate
-the physical limits for the biased graphene nanopores. Specifically,
-the salt rejection characteristics are controlled by: (i) the overlap
-of EDL inside the nanopore, essentially controlled by two length
-scales of $\lambda_{\mathrm{D}}$ and $R_{\mathrm{G}}$, and (ii) the
-graphene surface potential $\psi_{\mathrm{G}}$ controlled by
-$V_{\mathrm{G}}$ following Eq. \ref{eq:Vg}. To this end, we calculate
-$\psi_{\mathrm{G}}$ as a function of
-$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (\Fig{}
-\ref{fig:5}a). Clearly, when the bulk concentration $c_{0}$ increases,
-a higher $V_{\mathrm{G}}$ is required to reach the same level of
-$\psi_{\mathrm{G}}$. Consequently, as revealed in \Fig{} \ref{fig:5}b,
-the calculated salt rejection factor $\xi$ increases with both
-$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$, in line
-with the experimentally observed $\xi - c_{0}$ dependence. We also
-find the overall trends for $\psi_{\mathrm{G}}$ and $\xi$ with respect
-to $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
+(prefered path) greatly increases (details see Supplementary Section
+SXX \todo{markr}). This level of $\psi_{\mathrm{G}}$ cannot be reached
+experimentally in graphene membrane, as this requires a
+$V_{\mathrm{G}}$ larger than 2.0 V, which triggers the electrochemical
+reactions \cite{Toh_2011}. On the other hand, in an IFET, the electric
+potential on the pore wall is considerably higher, equivalent to
+$V_{\mathrm{G}}$ due to the metallic nature of gate electrode (having
+an infinitely-large quantum capacitance). We therefore conclude that
+the quantum capacitance-induced nonlinear damping in the surface
+potential results in the observed salt rejection.  Following the above
+discussions, we further investigate the physical limits for the biased
+graphene nanopores. Specifically, the salt rejection characteristics
+are controlled by: (i) the overlap of EDL inside the nanopore,
+essentially controlled by two length scales of $\lambda_{\mathrm{D}}$
+and $R_{\mathrm{G}}$, and (ii) the graphene surface potential
+$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
+Eq. \eqref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
+function of $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
+$V_{\mathrm{G}}$ (\Fig{} \ref{fig:5}a). Clearly, when the bulk
+concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
+to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
+revealed in \Fig{} \ref{fig:5}b, the calculated salt rejection factor
+$\xi$ increases with both $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
+$V_{\mathrm{G}}$, in line with the experimentally observed
+$\xi - c_{0}$ dependence. We also find the overall trends for
+$\psi_{\mathrm{G}}$ and $\xi$ with respect to
+$\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
 similar. More importantly, based on our theoretical prediction, with

### 2018-10-21 paper/paper.tex
minor change to simu part

@@
 presents the measured salt rejection $\xi$ as a function of
-$V_{\mathrm{G}}$ from at $c_{0}$ = 0.1 mM, for the seven salt species
+$V_{\mathrm{G}}$ at $c_{0}$ = 0.1 mM, for the seven salt species
 considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
-K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (details see Supplementary
+K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (Supplementary
 Section S7). Similar to the KCl system discussed earlier, the salt
-rejection was only observed in the positive $V_{\mathrm{G}}$
+rejection is more pronounced in the positive $V_{\mathrm{G}}$
 regime. The degree of salt rejection deceases with the salt valance;
@@
 in which we calculate $\xi$ as a function of $V_{\mathrm{g}}$ using
-the same setups in simulations (\Fig{} \ref{fig:6}b). The calculated
+the same simulation setups(\Fig{} \ref{fig:6}b). The calculated
 $\xi_{\mathrm{max}}$ values are quantitatively compared with
@@
 
-\section{Conclusion}
-\label{sec:consl}
-
-In summary, we have
-presented a comparative experimental and modeling study on macroscopic
-salt rejection through a sheet of large-area porous graphene under
-electrostatic gating. We show that due to a small quantum capacitance
-of double layer graphene, the graphene surface potential is
-considerably lower than the applied gate voltage. As a result, the
-subtle redistribution of the electrochemical potentials create new
-pathways for ionic transport, which in turn lead to a considerably
-degree of salt rejection. We report a high degree of salt rejection at
-$V_{\mathrm{G}}$ = 1.25 V of up to 55\% and 80\%, based on our
-experiments and theoretical predictions, respectively. We demonstrate
-that the observed salt rejection positively correlates with the Debye
-screening length that nonlinearly modulates the graphene surface
-potential and charge density. The experimental results and fundamental
-principles presented here open an avenue towards realization of
-atomically thin 2D porous membranes for advanced separation process in
-electrolyte solutions.
+In summary, we have presented a comparative experimental and modeling
+study on macroscopic salt rejection through a sheet of large-area
+porous graphene under electrostatic gating. We show that due to a
+small quantum capacitance of atomically-thin graphene, the graphene
+surface potential is considerably lower than the applied gate
+voltage. As a result, the subtle redistribution of the electrochemical
+potentials create new pathways for ionic transport, which in turn lead
+to a considerably degree of salt rejection. We report a high degree of
+salt rejection at $V_{\mathrm{G}}$ = 1.25 V of up to 55\% and 85\%,
+based on our experiments and theoretical predictions, respectively. We
+demonstrate that the observed salt rejection positively correlates
+with the Debye screening length that nonlinearly modulates the
+graphene surface potential and charge density. The experimental
+results and fundamental principles presented here open an avenue
+towards realization of atomically thin 2D porous membranes for
+advanced separation process in electrolyte solutions.
 
@@
 low-pressure chemical vapor deposition system (BM 4 inch, Aixtron SE)
-on surface-pretreated copper foil (Alfa Aesar N$^{o}$ 46986). Synthesis was
+on surface-pretreated copper foil (Alfa Aesar No. 46986). Synthesis was
 carried out at 950 $^{\circ}$C for 3 min using ethylene after 30 min of
@@
 \noindent
-\textbf{Graphene patterning and transfer to PCTE}: Spherical block copolymer
-(s-BCP) based patterning has enabled the manufacturing of perforated
-graphene membranes having pores in the range of 10 nm to 50 nm on
-average up to wafer-scale\cite{Choi_2018}. In brief, s-BCP
+\textbf{Graphene patterning and transfer to PCTE}: Spherical block
+copolymer (s-BCP) based patterning has enabled the manufacturing of
+perforated graphene membranes having pores in the range of 10 nm to 50
+nm on average up to wafer-scale\cite{Choi_2018}. In brief, s-BCP
 (polystyrene-block-polymethylmethacrylate, PS-b-PMMA, 195-b-20,
-Polymer Source Inc, Canada, 1 weight\% in anhydrous toluene) is spun
-from solution and thermally annealed at 220 $^{\circ}$C for 6 h in
-vacuum. Microphase separation of s-BCP leads to distinct phases: the
-minor phase will form spheres (PMMA) and the major phase will form the
-matrix (PS). Oxygen plasma (8 , 100 W, 25 mTorr, Oxford Instruments
-plc) removes the top layer PS from the PMMA spheres, which are
-subsequentially etched in glacial acetic acid to form a porous etch
-mask directly on top of the double layer graphene. Anisotropic etching
-using oxygen beam milling (10 s, 100 mA, 600 V acceleration voltage,
-Oxford IonFab 600) leads to perforation of the underlying graphene
-through the porous PS mask. Polymer residues are removed by thermal
-annealing in hydrogen:argon (9:1) at 400 $^{\circ}$C. The patterned
-graphene is transferred to PCTE membranes (hydrophobic, 400 nm pores,
-from Sterlitech) by baking the PCTE briefly to the perforated graphene
-at 180 $^{\circ}$C followed by a lift-off etch in buffered
-hydrofluoric acid (BHF) as described by\cite{Choi_2018}. A schematic
-of the process is shown in \Fig{} S1.
+Polymer Source Inc, Canada, 1 weight\% in anhydrous toluene) is
+spin-coated from solution and thermally annealed at 220 $^{\circ}$C
+for 6 h in vacuum. Microphase separation of s-BCP leads to distinct
+phases: the minor phase will form spheres (PMMA) and the major phase
+will form the matrix (PS). Oxygen plasma (8 , 100 W, 25 mTorr, Oxford
+Instruments plc) removes the top layer PS from the PMMA spheres, which
+are subsequentially etched in glacial acetic acid to form a porous
+etch mask directly on top of the double layer graphene. Anisotropic
+etching using oxygen beam milling (10 s, 100 mA, 600 V acceleration
+voltage, Oxford IonFab 600) leads to perforation of the underlying
+graphene through the porous PS mask. Polymer residues are removed by
+thermal annealing in hydrogen:argon (9:1) at 400 $^{\circ}$C. The
+patterned graphene is transferred to PCTE membranes (hydrophobic, 400
+nm pores, from Sterlitech) by baking the PCTE briefly to the
+perforated graphene at 180 $^{\circ}$C followed by a lift-off etch in
+buffered hydrofluoric acid (BHF) as described by\cite{Choi_2018}. A
+schematic of the process is shown in \Fig{} S1.
 

### 2018-10-21 paper/paper.tex
Change figure captions of main

@@
 \usepackage{todonotes}
+\DeclareCaptionLabelSeparator{bar}{  \textbar\quad}
+\usepackage[labelsep=bar, labelfont=bf]{caption}
 \newcommand{\Fig}{Fig.}
@@
 % \linenumbers
+
+% \makeatletter
+% \renewcommand*{\fnum@figure}{{\normalfont\bfseries \figurename~\thefigure}}
+% \renewcommand*{\@caption@fignum@sep}{\textbf{ \textbar }}
+% \makeatother
 
@@
     setup. Inset: photograph of the PG-PCTE membrane supported by
-    Kapton and copper tapes, scale bar: 1 cm. \textbf{b}. 3D schematic
+    Kapton and copper tapes. (Scale bar: 1 cm.) \textbf{b}. 3D schematic
     of the nanoscale cross-sectional structure of the PG-PCTE
-    membrane. \textbf{c}. SEM image of the PG-PCTE membrane, showing
+    membrane. \textbf{c}. SEM image of the PG-PCTE membrane, showingan
     excellent coverage of graphene over the PCTE substrate, scale bar:
@@
     of individual nanopores on PG fabricated by the patterning
-    technique, scale bar: 500 nm. Bottom right inset: histogram of the
+    technique. (Scale bar: 500 nm.) Bottom right inset: histogram of the
     pore diameter distribution revealed by the SEM
@@
   \caption{\textbf{The experimental evidence of salt rejection.}
-    \textbf{a}. Measured conductivity of LCR as a function of
-    time. The slope of conductivity-time curve when $V_{\mathrm{G}}>0$
-    is added, is smaller than that without gating. \textbf{b}. Molar
-    diffusive flux through bare PCTE (blue bars: experimental; red
-    bars: theoretical values) and PG+PCTE (green bars) membranes for
-    different salts. \textbf{c}. Experimentally measured salt
-    rejection factor $\xi$ as a function of $V_{\mathrm{G}}$ for 0.1
-    mM KCl solution in HCR, showing an asymmetric response, with a
-    higher degree of salt rejection for
+    \textbf{a}.An example of measured conductivity in LCR as a
+    function of time. The slope of conductivity-time curve when
+    $V_{\mathrm{G}}>0$ is interpolated, is smaller than that without
+    gating. \textbf{b}. Molar diffusive flux through bare PCTE (blue
+    bars: experimental; red bars: model values) and PG+PCTE (green
+    bars) membranes for different salts. \textbf{c}. Experimentally
+    measured salt rejection factor $\xi$ as a function of
+    $V_{\mathrm{G}}$ for 0.1 mM KCl solution in HCR, showing an
+    asymmetric response, with a higher degree of salt rejection for
     $V_{\mathrm{G}}>0$. \textbf{d}. $\xi_{\mathrm{max}}$ as a function
-    of KCL concentration, fitted by a power law relation, suggesting
-    the effect of Debye length on the observed salt rejection. }
+    of KCl concentration, fitted by a power law relation, suggesting
+    the effect of Debye length on the observed salt rejection, since
+    $\lambda_{\mathrm{D}} \propto c_{0}^{-\frac{1}{2}}$.}
   \label{fig:2} 
@@
   \caption{\textbf{Interplay between graphene quantum capacitance and
-      EDL.} \textbf{a}. Schematic diagram of the electrostatic
+      EDL.} \textbf{a}. Schematic diagram of the electric
     potential at the graphene-electrolyte interface considering the
@@
   \includegraphics[width=0.95\linewidth]{img/fig4.pdf}
-  \caption{\textbf{Self-consistent theoretical
-      calculations}. \textbf{a}. Calculated cross-sectional contour
-    plot of electrostatic potential $\psi$ near the center of the
-    graphene nanopore at $V_{\mathrm{G}}$ = 0.75 V. \textbf{b}. The
+  \caption{\textbf{Calculations using the proposed self-consistent
+      theory}. \textbf{a}. Calculated cross-sectional contour plot of
+    electric potential $\psi$ near the center of the graphene
+    nanopore at $V_{\mathrm{G}}$ = 0.75 V. \textbf{b}. The
     corresponding electrochemical potential change for cation
@@
     the graphene layer. The diffusive pathways for both ions are
-    indicated by arrows. \textbf{c}. Calculated z-component of
+    indicated by the arrows. \textbf{c}. Calculated z-component of
     diffusive fluxes $\boldsymbol{J}_{z}$ for cation (left) and anion
@@
   \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
-  \caption{\textbf{The Debye length effect}. \textbf{a}. Contour plot
-    of the surface potential of graphene $\psi_{\mathrm{G}}$ as a
-    function of $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and
-    $V_{\mathrm{G}}$. When the Debye length reduces, a higher
-    $V_{\mathrm{G}}$ is required to maintain the same surface
-    $\psi_{\mathrm{G}}$ level. \textbf{b}. 2D contour plot of
-    theoretically predicted $\xi$ as a function of
+  \caption{\textbf{The Debye length effect on the degree of salt
+      rejection}. \textbf{a}. Calculated contour plot of the surface
+    potential of graphene $\psi_{\mathrm{G}}$ as a function of
+    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$. When
+    the Debye length reduces, a higher $V_{\mathrm{G}}$ is required to
+    maintain the same surface $\psi_{\mathrm{G}}$
+    level. \textbf{b}. Calculated 2D contour plot of theoretically
+    predicted $\xi$ as a function of
     $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and
@@
     be achieved by having a higher $V_{\mathrm{G}}$ and
-    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ ratio.}
+    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$}
   \label{fig:5}
@@
   \includegraphics[width=0.95\linewidth]{img/fig6.pdf}
-  \caption{\textbf{Comparison between experiments and simulations
-      considering different salt species}. \textbf{a}. Experimentally
-    measured $\xi$ as a function of $V_{\mathrm{G}}$ for various salts
-    at 0.1 mM. The error bar indicates the standard
-    error. \textbf{b}. Simulated $\xi-V_{\mathrm{G}}$ relations for
-    the salt species considered here. \textbf{c}. Comparison between
-    the experimental and calculated $\xi_{\mathrm{max}}$ values for
-    different salt species, decreasing with the salt
+  \caption{\textbf{Comparison between experimental and theoretical
+      salt rejection considering different salt
+      species}. \textbf{a}. Experimentally measured $\xi$ as a
+    function of $V_{\mathrm{G}}$ for various salts at 0.1 mM. The
+    error bar represents the standard error. \textbf{b}. Theoretically
+    calculated $\xi-V_{\mathrm{G}}$ relations for the salt species
+    considered here. \textbf{c}. Comparison between the experimental
+    and calculated $\xi_{\mathrm{max}}$ values for different salt
+    species, decreasing with the salt
     valence. \textbf{d}. $\xi_{\mathrm{max}}$ as a function of
     $\lambda_{\mathrm{D}}$ for the experimental (circle) and model
-    (diamond) values, with a linear correlation.}
+    (diamonds) values, showing a linear correlation.}
   \label{fig:6}

### 2018-10-23 paper/SI.tex
Minor change to SI

@@
     transferred to a substrate (glass slide) to yield a double
-    layer. BCP is spun and annealed in vacuum to undergo microphase
+    layer. s-BCP is spin-coated and annealed in vacuum to undergo microphase
     separation, followed by plasma etch and wet etching yielding a
@@
     substrate (e.g. PCTE). \textbf{b}. Raman spectra of graphene
-    before (unpatterned, orange curve) and after (patterned, blue
-    curve). An increase of the D-peak at 1350 cm$^{-1}$ indicates the
+    before (orange curve) and after (blue
+    curve) patterning. An increase of the D-peak at 1350 cm$^{-1}$ indicates the
     formation of defects and edges. The spectra have been normalized
     to the G-peak intensity and offset for better
-    clarity. \textbf{c}. SEM graph of patterned graphene on PCTE at
-    lower (top) and higher (bottom) magnifications. Note that tears in
-    graphene appear bright white with a black center.}
+    comparison. \textbf{c}. SEM graph of patterned graphene on PCTE at
+    lower (top) and higher (bottom) magnifications.
+    % Note that tears in
+    % graphene appear bright white with a black center.
+  }
   \label{fig:exp}
@@
 the fixture following the same wetting procedure described in the main
-text and was kept wet for the entire series of experiments.
+text Methods and was kept wet for the entire series of experiments.
 
@@
 Table \ref{tab:debye} gives an overview about the measured
-conductivities and their calculated Debye lengths for KCl. The
-information is used to plot the rectification versus concentration.
+conductivities and their calculated Debye length values for KCl. The
+information is used to plot the $\xi$ versus $c_{0}$ curve.
 
@@
     \hline
-    0.1&        0.01903&        30.4\\
-    0.33&       0.0541& 16\\
-    1   &0.1329 &10\\
-    3.3&     0.513&  6\\
+    0.1&        1.90$\times$10$^{-2}$ &        30.4\\
+    0.33&       5.41$\times$10$^{-2}$ & 16.0\\
+    1   &1.33$\times$10$^{-1}$ & 10.0\\
+    3.3&     5.13$\times$10$^{-1}$ &  6.0\\
     10&      1.08    &3.3\\
@@
 
-Note that due
-to the existence of electron traps on graphene due to fabrication
-process, the induced charge traps on graphene effectively reduce the
-charge density on graphene and greatly attenuate the surface potential
-on graphene, as illustrated in \Fig. \ref{fig:trap}. This effect is
-universally observed in CVD-graphene-based field effect transistors in
-air, while the mechanism is fully understood yet. In view of this, we
-only simulate the situation where $V_{\mathrm{G}}>$ 0 for the salt
-rejection mechanism. The trend that $\xi$ is almost independent of
+Note that due to the existence of electron traps on graphene due to
+fabrication process, the induced charge traps on graphene effectively
+reduce the charge density on graphene and greatly attenuate the
+surface potential on graphene, as illustrated in \Fig
+\ref{fig:trap}. This effect is universally observed in
+CVD-graphene-based field effect transistors in air, while the
+mechanism is fully understood yet. In view of this, we only simulate
+the situation where $V_{\mathrm{G}}>$ 0 for the salt rejection
+mechanism. The trend that $\xi$ is almost independent of
 $V_{\mathrm{G}}$ when $V_{\mathrm{G}}<$ 0 can be qualitatively
 explained by the existence of surface charge traps as stated above.
+We have also tested the mesh-independency of our solutions. As show in
+in \Fig \ref{fig:mesh}a, we use two parameters to control the
+refinement of the mesh entities: (i) the smallest triangle mesh size
+$\delta_{\mathrm{G}} / N_{\mathrm{div}}$, where $\delta_{\mathrm{G}}$
+is the thickness of graphene, and (ii) division of mesh on the
+boundary $0<r<R_{\mathrm{G}};z=0$ $N_{\mathrm{b}}$. The solution
+convergence is evaluated by the mean absolute error (MAE) of anion
+flux $\boldsymbol{J}_{z}$ on the boundary
+$\delta_{\mathrm{G}} / N_{\mathrm{div}}$, as shown in \Fig
+\ref{fig:mesh}b. The solution of the PNP model is sensitive to the
+value $N_{\mathrm{b}}$, and can be regarded numerically converged when
+$N_{\mathrm{b}}>100$. Combining the calculation effort and numerical
+precision, we adapt the value $N_{\mathrm{div}}=5$ and
+$N_{\mathrm{b}}=100$ in our simulations.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-mesh.pdf}
+  \caption{Mesh independence of the solution. \textbf{a}. Scheme of
+    the mesh refinement near the graphene pore. The values
+    $N_{\mathrm{div}}$ and $N_{\mathrm{b}}$ controls the size of mesh
+    along the boundary $z=0, 0<r<R_{\mathrm{G}}$ (shown in
+    red). \textbf{b}. Mean absolute error (MAE) of the anion flux
+    $\boldsymbol{J}_{z}$ along the boundary $z=0,
+    0<r<R_{\mathrm{G}}$. The error is more sensitive to
+    $N_{\mathrm{b}}$ than $N_{\mathrm{div}}$.}
+  \label{fig:mesh}
+\end{figure}
 
@@
   \end{tabular}
-  \caption{conductivity}
+  \caption{Conductivity and $\lambda_{\mathrm{D}}$ of various salts.}
   \label{tab:conductivity}

### 2018-10-23 paper/paper.tex
small chengs to paper.tex

@@
 (prefered path) greatly increases (details see Supplementary Section
-SXX \todo{markr}). This level of $\psi_{\mathrm{G}}$ cannot be reached
-experimentally in graphene membrane, as this requires a
-$V_{\mathrm{G}}$ larger than 2.0 V, which triggers the electrochemical
-reactions \cite{Toh_2011}. On the other hand, in an IFET, the electric
-potential on the pore wall is considerably higher, equivalent to
-$V_{\mathrm{G}}$ due to the metallic nature of gate electrode (having
-an infinitely-large quantum capacitance). We therefore conclude that
-the quantum capacitance-induced nonlinear damping in the surface
-potential results in the observed salt rejection.  Following the above
-discussions, we further investigate the physical limits for the biased
-graphene nanopores. Specifically, the salt rejection characteristics
-are controlled by: (i) the overlap of EDL inside the nanopore,
-essentially controlled by two length scales of $\lambda_{\mathrm{D}}$
-and $R_{\mathrm{G}}$, and (ii) the graphene surface potential
-$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
-Eq. \eqref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
-function of $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
-$V_{\mathrm{G}}$ (\Fig{} \ref{fig:5}a). Clearly, when the bulk
-concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
-to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
-revealed in \Fig{} \ref{fig:5}b, the calculated salt rejection factor
-$\xi$ increases with both $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
-$V_{\mathrm{G}}$, in line with the experimentally observed
-$\xi - c_{0}$ dependence. We also find the overall trends for
-$\psi_{\mathrm{G}}$ and $\xi$ with respect to
-$\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
+S6, Supplementary Figs. S8 and S9). This level of $\psi_{\mathrm{G}}$
+cannot be reached experimentally in graphene membrane, as this
+requires a $V_{\mathrm{G}}$ larger than 2.0 V, which triggers the
+electrochemical reactions \cite{Toh_2011}. On the other hand, in an
+IFET, the electric potential on the pore wall is considerably higher,
+equivalent to $V_{\mathrm{G}}$ due to the metallic nature of gate
+electrode (having an infinitely-large quantum capacitance). We
+therefore conclude that the quantum capacitance-induced nonlinear
+damping in the surface potential results in the observed salt
+rejection.  Following the above discussions, we further investigate
+the physical limits for the biased graphene nanopores. Specifically,
+the salt rejection characteristics are controlled by: (i) the overlap
+of EDL inside the nanopore, essentially controlled by two length
+scales of $\lambda_{\mathrm{D}}$ and $R_{\mathrm{G}}$, and (ii) the
+graphene surface potential $\psi_{\mathrm{G}}$ controlled by
+$V_{\mathrm{G}}$ following Eq. \eqref{eq:Vg}. To this end, we
+calculate $\psi_{\mathrm{G}}$ as a function of
+$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (\Fig{}
+\ref{fig:5}a). Clearly, when the bulk concentration $c_{0}$ increases,
+a higher $V_{\mathrm{G}}$ is required to reach the same level of
+$\psi_{\mathrm{G}}$. Consequently, as revealed in \Fig{} \ref{fig:5}b,
+the calculated salt rejection factor $\xi$ increases with both
+$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$, in line
+with the experimentally observed $\xi - c_{0}$ dependence. We also
+find the overall trends for $\psi_{\mathrm{G}}$ and $\xi$ with respect
+to $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
 similar. More importantly, based on our theoretical prediction, with

### 2018-10-25 paper/SI.tex
Apply changes by Park

@@
 Tannenstrasse 3, Zürich CH-8092, Switzerland.}
+\affiliation{Mechanical Engineering, Pohang University of Science and
+  Technology (POSTECH), 77 Cheongam-ro, Nam-gu, Pohang, Gyeongbuk,
+  Republic of Korea.}
+\email{iduserpark@gmail.com}
 
@@
 We have also tested the mesh-independency of our solutions. As show in
-in \Fig \ref{fig:mesh}a, we use two parameters to control the
-refinement of the mesh entities: (i) the smallest triangle mesh size
+in \Fig{} \ref{fig:mesh}a, we use two parameters to control the
+refinement of the mesh entities: (i) trangle mesh division
+$N_{\mathrm{div}}$, giving the smallest triangle mesh size
 $\delta_{\mathrm{G}} / N_{\mathrm{div}}$, where $\delta_{\mathrm{G}}$
-is the thickness of graphene, and (ii) division of mesh on the
-boundary $0<r<R_{\mathrm{G}};z=0$ $N_{\mathrm{b}}$. The solution
-convergence is evaluated by the mean absolute error (MAE) of anion
-flux $\boldsymbol{J}_{z}$ on the boundary
-$\delta_{\mathrm{G}} / N_{\mathrm{div}}$, as shown in \Fig
+is the thickness of graphene, and (ii) division of mesh
+$N_{\mathrm{b}}$, on the boundary $0<r<R_{\mathrm{G}};z=0$. The
+solution convergence is evaluated by the mean absolute error (MAE) of
+anion flux $\boldsymbol{J}_{z}$ on the boundary
+$0<r<R_{\mathrm{G}};z=0$, as shown in \Fig{}
 \ref{fig:mesh}b. The solution of the PNP model is sensitive to the

### 2018-10-25 paper/paper.tex
Apply changes by Park

@@
 % \linenumbers
-
-% \makeatletter
-% \renewcommand*{\fnum@figure}{{\normalfont\bfseries \figurename~\thefigure}}
-% \renewcommand*{\@caption@fignum@sep}{\textbf{ \textbar }}
-% \makeatother
 
@@
 
-\author{Hyung Gyu Park} \affiliation{Nanoscience for Energy Technology and Sustainability,
-Department of Mechanical and Process Engineering,
-Eidgenössische Technische Hochschule (ETH) Zürich,
+\author{Hyung Gyu Park} \affiliation{Nanoscience for Energy Technology
+  and Sustainability, Department of Mechanical and Process
+  Engineering, Eidgenössische Technische Hochschule (ETH) Zürich,
   Tannenstrasse 3, Zürich CH-8092, Switzerland.}
+\affiliation{Mechanical Engineering, Pohang University of Science and
+  Technology (POSTECH), 77 Cheongam-ro, Nam-gu, Pohang, Gyeongbuk,
+  Republic of Korea.}
+\email{iduserpark@gmail.com}
 
@@
 \begin{abstract}
-  {\normalsize
-  Atomically thin graphene nanopores is emerging as one of the most
-  promising candidates for next-generation membrane technology owing
-  to the ultrahigh permeability. However, the size-exclusive mechanism
-  of selectivity limits its scalability as it remains technically
-  challenging to drill subnanometer pores over a large area. Here we
-  report macroscopic salt rejection through atomically-thin porous
-  graphene with the pore sizes of 20$\pm$10 nanometers, overcoming the
-  pore size limitation set by the hydrated radii. By electrostatically
-  gating a sheet of porous graphene, we report a considerable
-  reduction of salt flux by up to 55\% and 85\% with the gate voltage,
-  based on our experiments and theoretical predictions,
-  respectively. We systematically investigate the effects of salt
-  concentration and species, including developing a theory to model
-  the electrolyte diffusion through a nanopore in a sheet of gated
-  graphene. The interplay between graphene quantum capacitance and
-  electrical double layer is identified to be the main mechanism
-  responsible for the observed salt rejection, when the pore size is
-  comparable to the Debye screening length. Our findings reveal a new
-  degree of freedom controlling the membrane potential and electrolyte
-  permeation through porous two-dimensional materials.
-  }
+  {\normalsize Atomically thin graphene nanopores is emerging as one
+    of the most promising candidates for next-generation membrane
+    technology owing to the ultrahigh permeability. However, the
+    size-exclusive mechanism of selectivity limits its scalability as
+    it remains technically challenging to drill subnanometer pores
+    over a large area. Here we report macroscopic salt rejection
+    through atomically-thin porous graphene with the pore sizes of
+    20$\pm$10 nanometers, and a pore density of 1.25$\times$10$^{10}$
+    cm$^{-2}$, overcoming the pore size limitation set by the hydrated
+    radii. By electrostatically gating a sheet of porous graphene, we
+    report a considerable reduction of salt flux by up to 55\% and
+    85\% with the gate voltage, based on our experiments and
+    theoretical predictions, respectively. We systematically
+    investigate the effects of salt concentration and species,
+    including developing a theory to model the electrolyte diffusion
+    through a nanopore in a sheet of gated graphene. The interplay
+    between graphene quantum capacitance and electrical double layer
+    is identified to be the main mechanism responsible for the
+    observed salt rejection, when the pore size is comparable to the
+    Debye length. Our findings reveal a new degree of
+    freedom controlling the membrane potential and electrolyte
+    permeation through porous two-dimensional materials.  }
 \end{abstract}
@@
 dimensions in nanofluidics gives rise to substantially different
-transport properties compared to their bulk counterparts
+transport properties in comparison to their bulk counterparts
 \cite{Schoch_2008}. In nanopores, for example, the effect of
 surface-mediated transport becomes dominant when the pore size is
-comparable to the solute diffusion length, enabling new applications,
-including ionic diodes \cite{Karnik_2007}, field-effect transistors
-\cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
+comparable to the characteristic length of diffusion, enabling new
+applications such as ionic diodes \cite{Karnik_2007}, field-effect
+transistors \cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
 nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}, Porous,
 atomically thin two-dimensional (2D) materials, such as graphene, are
-emerging as ideal membrane materials due to their ultimate
-permeability
+emerging as ideal membrane materials due to their ultimate permeation
 \cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
@@
 simultaneous
-\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2015,Surwade_2015}. Nevertheless,
+\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}. Nevertheless,
 the fabrication of subnanometer porous 2D membranes over a large area
@@
 \cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
-portion of large pores can significantly diminish salt rejection.
-Very recently, a number of reports have explored the effect of surface
-charges on the selectivity of ion transport through graphene
-nanopores, as a consequence of the electrostatic interactions between
-solvated ions and the charged functional groups attached on graphene
-\cite{Rollings_2016,Surwade_2014}. However, it remains controversial
-that if the surface charges can result in a degree of salt rejection,
-as the membrane charge and potential cannot be precisely quantified
-and are sensitive to the surroundings and chemical treatment
-\cite{Li_2008}. The difficulty in turn hinders fundamental
-understanding of the interactions between the atomically thin 2D
-membrane and electrolyte solution. Here, we demonstrate macroscopic
-salt rejection through a sheet of large-area porous graphene using
-electrostatic gating, thereby deepening the understanding of
-ion-graphene interaction and its implications on nanoporous
-graphene-based desalination applications.
+portion of excessively large pores can significantly diminish salt
+rejection.  Very recently, a number of reports have explored the
+effect of surface charges on the selectivity of ion transport through
+graphene nanopores, as a consequence of the electrostatic interactions
+between solvated ions and the charged functional groups attached on
+graphene \cite{Rollings_2016,Surwade_2014}. However, it remains
+controversial that if the surface charges can result in a degree of
+salt rejection, as the membrane charge and potential cannot be
+precisely quantified and are sensitive to the surroundings and
+chemical treatment \cite{Li_2008}. The difficulty in turn hinders a
+fundamental understanding of the interactions between the atomically
+thin 2D membrane and the electrolyte solution. Here, we demonstrate
+macroscopic salt rejection through a sheet of large-area porous
+graphene using electrostatic gating, thereby deepening the
+understanding of ion-graphene interaction and its implications on
+nanoporous graphene-based desalination applications.
 
@@
 pore diameters of 20$\pm$10 nm (\Fig{} \ref{fig:1}c inset) over a
-large area were drilled on graphene.  By optimizing the subsequent
-transfer process, a high surface coverage ($>$ 98\%) of graphene on
-PCTE was reached (\Fig{} \ref{fig:1}c), allowing to reliably
-characterize the ion transport behavior (details see Supplementary
-Information Section S1).  The system presented here allows us to
-systematically investigate the diffusive flux across a sheet of porous
-graphene, $\boldsymbol{J}$, driven by the gradient of electrochemical
-potential in the electrolyte medium.
+large area were perforated on graphene.  By optimizing the subsequent
+transfer process, a high surface coverage ($>$ 98\%) of PG on PCTE was
+obtained (\Fig{} \ref{fig:1}c), allowing reliable characterization of
+the ion transport behavior (details see Supplementary Information
+Section S1).  The system presented here allows us to systematically
+investigate the diffusive flux of ions across a sheet of PG,
+$\boldsymbol{J}$, driven by the gradient of electrochemical potential
+in the electrolyte medium.
 
@@
 through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
-flux is comparably small, the conductivity versus time profile
-(e.g. \Fig{} \ref{fig:2}a) remains linear within the measurement
-duration (1 h), suggesting the concentration gradient across the
-membrane remains constant. The diffusive fluxes
-correspond to different salts were obtained by converting the
-conductivity-time profiles with the calibration curves (blue bars in
-\Fig{} \ref{fig:2}b and Supplementary \Fig{} S2). For comparison
-purposes, based on the assumption that the membrane consists
-cylindrical pores with uniform diameter and a low tortuosity $\tau$ of
-$\sim{}$1.2 \cite{O_Hern_2012}, the molar diffusive flux through the
-bare PCTE membrane, $\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
+flux is comparably small, the conductivity varies linearly with time
+(e.g. \Fig{} \ref{fig:2}a) within the measurement duration (1 h),
+suggesting the concentration gradient across the membrane remains
+constant. The diffusive fluxes of different salts were
+obtained by converting the conductivity-time profiles with the
+calibration curves (blue bars in \Fig{} \ref{fig:2}b and Supplementary
+\Fig{} S2). For comparison purposes, based on the assumption that the
+membrane consists cylindrical pores with uniform diameter and a low
+tortuosity $\tau$ of $\sim{}$1.2 \cite{O_Hern_2012}, the molar
+diffusive flux through the bare PCTE membrane,
+$\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
   \begin{equation}
@@
 $\Delta c \sim c_{0}$, $\delta$ is the thickness of the PCTE membrane,
-and $\tau$ is the tortuosity. By using the salt diffusivity values
+and $\tau$ is the tortuosity of the PCTE membrane. By using the salt diffusivity values
 provided by the PTCE vendor (Supplementary Table S1), the
@@
 \Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
-to those of bare PCTE membrane, suggesting that the mass transfer
+with those of bare PCTE membrane, suggesting that the mass transfer
 resistance of PG is not significant, as the permeability is high. We
@@
 order to avoid any interference from the conductivity probe to the
-membrane potential, the “three-interval” method, which had been used
+membrane potential, the “three-interval” method, which has been used
 in controlling the membrane potential in mesoporous carbon membranes
-\cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a presents the
-representative data of the measured conductivity with respect to
+\cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a
+illustratively represents how the measured conductivity evolves with
 time. Specifically, in the first interval, the gate voltage source is
 turned off and the conductivity probe is on, allowing us to obtain the
-conductivity-time profile corresponding to the diffusive flux through
-the PG-PCTE membrane, giving the average slope $s_{1}$. In the second
-interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane after
-turning off the conductivity probe, followed by the third interval, in
-which the conductivity probe is turned on again to give the
-corresponding slope, $s_{3}$. The slope corresponding to the second
-interval, $s_{2}$, as the conductivity probe is off, is determined by
-linearly interpolating the conductivities from the endpoint of
-interval 1 to the starting point of interval 3. Accordingly, we define
-the salt rejection factor, $\xi$, which is effectively equivalent to
-the relative degree of diffusive flux decrease as follows:
+conductivity-time profile with an average slope $s_{1}$ that
+corresponds to the diffusive flux across the PG-PCTE membrane, . In
+the second interval, a voltage $V_{\mathrm{G}}$ is applied to the
+membrane after turning off the conductivity probe, followed by the
+third interval $s_{3}$, in which the conductivity probe is turned on
+again to give the corresponding slope. The slope corresponding to the
+second interval $s_{2}$, as the conductivity probe is off, is
+determined by linear interpolation of the conductivities from the
+endpoint of interval 1 to the starting point of interval
+3. Accordingly, we define the salt rejection factor, $\xi$, which is
+effectively equivalent to the relative degree of diffusive flux
+decrease as follows:
 \begin{equation}
@@
 positive carriers (holes) are induced in graphene. We notice that an
-increase $\xi$, or a decrease of $\boldsymbol{J}_{\mathrm{PG}}$ with
-$V_{\mathrm{G}}$, showing an inverse trend compared to those observed
-in ionic field effect transistors (IFETs), in which the diffusive flux
-increases with the gate voltage \cite{Nam_2009,Cheng_2018}. A further
-increase of the KCl concentration $c_{0}$ influences the attainable
-degree of salt rejection. $\xi$ values measured at
-$V_{\mathrm{G}}$ = 1.25 V, $\xi_{\mathrm{max}}$, as a function of
-$c_{0}$ from 10$^{-4}$ to 10$^{-2}$ M KCl (see Supplementary Section
-S4) exhibit a power law dependency (\Fig{} \ref{fig:2}d). The
-$\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
-law function following
-$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{Constant}$. As the Debye
-screening length in solution, $\lambda_{\mathrm{D}}$, is inversely
-proportional to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced
-salt rejection originates from the modulation of the electrical double
+increase of $\xi$, or a decrease of $\boldsymbol{J}_{\mathrm{PG}}$
+with $V_{\mathrm{G}}$, showing an inverse trend compared with those
+observed in ionic field effect transistors (IFETs) in which the
+diffusive flux increases with the gate voltage
+\cite{Nam_2009,Cheng_2018}. A further increase of the KCl
+concentration $c_{0}$ influences the attainable degree of salt
+rejection. $\xi$ values measured at $V_{\mathrm{G}}$ = 1.25 V,
+$\xi_{\mathrm{max}}$, as a function of $c_{0}$ from 10$^{-4}$ to
+10$^{-2}$ M KCl (see Supplementary Section S4) exhibit a power law
+dependency (\Fig{} \ref{fig:2}d). The $\xi_{\mathrm{max}}-c_{0}$
+relation can be nicely fitted by a power law function following
+$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{constant}$. As the Debye
+length in solution, $\lambda_{\mathrm{D}}$, is inversely proportional
+to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced salt
+rejection originates from the modulation of the electrical double
 layer (EDL), as will be discussed later.
@@
 significantly reduces the graphene surface potential
-$\psi_{\mathrm{G}}$ tp $\sim$0.3 V at $V_{\mathrm{G}}$ = 1.25 V,
+$\psi_{\mathrm{G}}$ to $\sim$0.3 V at $V_{\mathrm{G}}$ = 1.25 V,
 corresponding a surface charge density $\sigma_{\mathrm{G}}$ of
@@
 The numerical procedure described above allows us to resolve the
-concentration and electric potential profiles near to a graphene
+concentration and electric potential profiles near a graphene
 nanopore for a given $V_{\mathrm{G}}$. Since the ionic flux is driven
@@
 solution phase, forming an EDL surrounding the graphene surface. Since
-the Debye screening length $\lambda_{\mathrm{D}}$ is comparable to the
+the Debye length $\lambda_{\mathrm{D}}$ is comparable to the
 pore radius $R_{\mathrm{G}}$, the electric potential at the nanopore
@@
 experiments (\Fig{} \ref{fig:6}c), and the same trend is
-observed. Indeed, because the Debye screening length
+observed. Indeed, because the Debye length
 $\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
@@
 potentials create new pathways for ionic transport, which in turn lead
-to a considerably degree of salt rejection. We report a high degree of
+to a considerable degree of salt rejection. We report a high degree of
 salt rejection at $V_{\mathrm{G}}$ = 1.25 V of up to 55\% and 85\%,
@@
 demonstrate that the observed salt rejection positively correlates
-with the Debye screening length that nonlinearly modulates the
-graphene surface potential and charge density. The experimental
-results and fundamental principles presented here open an avenue
-towards realization of atomically thin 2D porous membranes for
-advanced separation process in electrolyte solutions.
+with the Debye length that nonlinearly modulates the graphene surface
+potential and charge density. The experimental results and fundamental
+principles presented here open an avenue towards realization of
+atomically thin 2D porous membranes for advanced separation process in
+electrolyte solutions.
 
@@
 \begin{acknowledgement}
-\todo[inline]{TBD} R.M.W. and H.G.P. acknowledge the support from
-XXX. T.T. and C.J.S. are grateful for the financial support from the
-ETH startup funding.
+  R.M.W. acknowledges support from the Binnig and Rohrer
+  Nanotechnology Center of ETH Zurich and IBM Zurich. T.T. and
+  C.J.S. are grateful for the financial support from the ETH startup
+  funding.
 \end{acknowledgement}

### 2018-10-25 paper/SI.tex
Makefile more flexible

@@
 Tannenstrasse 3, Zürich CH-8092, Switzerland.}
-\affiliation{Mechanical Engineering, Pohang University of Science and
+\alsoaffiliation{Mechanical Engineering, Pohang University of Science and
   Technology (POSTECH), 77 Cheongam-ro, Nam-gu, Pohang, Gyeongbuk,

### 2018-10-25 paper/paper.tex
Makefile more flexible

@@
   Tannenstrasse 3, Zürich CH-8092, Switzerland.}
-\affiliation{Mechanical Engineering, Pohang University of Science and
+\alsoaffiliation{Mechanical Engineering, Pohang University of Science and
   Technology (POSTECH), 77 Cheongam-ro, Nam-gu, Pohang, Gyeongbuk,

### 2018-10-25 paper/SI.tex
Minor changes to paper and SI

@@
     \hline
-    KCl & 0.0151 $\pm$ 0.00265  & 106   & 1.34 $\pm$ 0.235\\
-    NaCl        & 0.0099 $\pm$ 0.000173 & 91    & 1.02 $\pm$ 0.0179\\
-    LiCl        & 0.00603 $\pm$ 0.000802        & 83    & 0.679 $\pm$ 0.0903\\
-    CaCl$_{2}$  & 0.0125 $\pm$ 0.001    & 149   & 0.789 $\pm$ 0.0631\\
-    MgSO$_{4}$  & 0.0088 $\pm$ 0.0012   & 130   & 0.633 $\pm$ 0.084\\
-    K$_{3}$[Fe(CN)$_{6}]$ & 0.024 $\pm$ 0.00275   & 395   & 0.575 $\pm$ 0.0633\\
-    K$_{2}$SO4$_{4}$    & 0.0198 $\pm$ 0.00199  & 258   & 0.722 $\pm$ 0.0726\\
+    KCl & 1.51$\pm$0.27$\times$10$^{-2}$  & 106   & 1.34 $\pm$ 0.24\\
+    NaCl        & 9.90$\pm$0.17$\times$10$^{-3}$ & 91    & 1.02 $\pm$ 0.02\\
+    LiCl        & 6.03 $\pm$0.80$\times$10$^{-3}$        & 83    & 0.682 $\pm$ 0.090\\
+    CaCl$_{2}$  & 1.25$\pm$0.1$\times$10$^{-2}$    & 149   & 0.789 $\pm$ 0.063\\
+    MgSO$_{4}$  & 8.80$\pm$1.2$\times$10$^{-2}$   & 130   & 0.633 $\pm$ 0.084\\
+    K$_{3}$[Fe(CN)$_{6}]$ & 2.40$\pm$0.28$\times$10$^{-2}$   & 395   & 0.575 $\pm$ 0.063\\
+    K$_{2}$SO4$_{4}$    & 1.98$\pm$0.20$\times$10$^{-2}$  & 258   & 0.722 $\pm$ 0.073\\
     \hline
@@
     \hline
-    0.1 mM NaCl &0.018  &30.4\\
-    0.1 mM LiCl &0.0158 &30.4\\
-    0.1 mM CaCl$_{2}$&  0.02187 &17.2\\
-    0.1 mM MgSO$_{4}$   &0.0327 &15.2\\
-    0.1 mM K$_{2}$SO$_{4}$      &0.0416 &17.2\\
-    0.1 mM K$_{3}$[Fe(CN)$_{6}$]&       0.0595  &12.4\\
+    0.1 mM NaCl &1.80$\times$10$^{-2}$  &30.4\\
+    0.1 mM LiCl &1.58$\times$10$^{-2}$ &30.4\\
+    0.1 mM CaCl$_{2}$&  2.19$\times$10$^{-2}$ &17.2\\
+    0.1 mM MgSO$_{4}$   &3.27$\times$10$^{-2}$ &15.2\\
+    0.1 mM K$_{2}$SO$_{4}$      &4.16$\times$10$^{-2}$ &17.2\\
+    0.1 mM K$_{3}$[Fe(CN)$_{6}$]&       5.95$\times$10$^{-2}$  &12.4\\
     \hline

### 2018-10-25 paper/paper.tex
Minor changes to paper and SI

@@
 \Fig{} \ref{fig:1}b. The normally distributed, circular pores with
-pore diameters of 20$\pm$10 nm (\Fig{} \ref{fig:1}c inset) over a
+pore diameters of 20$\pm$10 nm and a pore density of
+1.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset) over a
 large area were perforated on graphene.  By optimizing the subsequent

### 2018-10-25 paper/SI.tex
Change SI

@@
     CaCl$_{2}$  & 1.25$\pm$0.1$\times$10$^{-2}$    & 149   & 0.789 $\pm$ 0.063\\
-    MgSO$_{4}$  & 8.80$\pm$1.2$\times$10$^{-2}$   & 130   & 0.633 $\pm$ 0.084\\
+    MgSO$_{4}$  & 8.80$\pm$1.2$\times$10$^{-3}$   & 130   & 0.633 $\pm$ 0.084\\
     K$_{3}$[Fe(CN)$_{6}]$ & 2.40$\pm$0.28$\times$10$^{-2}$   & 395   & 0.575 $\pm$ 0.063\\

### 2018-10-25 paper/paper.tex
Change pore density

--- 2018-10-25 paper/paper.tex
@@
     through atomically-thin porous graphene with the pore sizes of
-    20$\pm$10 nanometers, and a pore density of 1.25$\times$10$^{10}$
+    20$\pm$10 nanometers, and a pore density of 1.25$\pm$0.25$\times$10$^{10}$
     cm$^{-2}$, overcoming the pore size limitation set by the hydrated
@@
 \Fig{} \ref{fig:1}b. The normally distributed, circular pores with
-pore diameters of 20$\pm$10 nm (\Fig{} \ref{fig:1}c inset) over a
+pore diameters of 20$\pm$10 nm and a pore density of
+1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset) over a
 large area were perforated on graphene.  By optimizing the subsequent

### 2018-12-22 paper/paper.tex
Implement changes 20181212

@@
 \newcommand{\Fig}{Fig.}
-% \usepackage{lineno}
-% \linenumbers
+\usepackage{lineno}
 
@@
 \clearpage{}
-
+\linenumbers
 \section{Introduction}
@@
 \end{equation}
-where $x$ is the molar fraction in solution, $z$ is the ionic valence,
+ $x$ is the molar fraction in solution, $z$ is the ionic valence,
 $e$ is the unit charge, and $\psi$ is the electric potential. On the
@@
 solution. Note that the graphene surface potential,
-$\psi_{\mathrm{G}}$, is not equivalent to $V_{\mathrm{G}}$ due to the
+$\psi_{\mathrm{G}}$, is not equivalent to $V_{\mathrm{G}}$ due to
+change of graphene's work function upon charging, known as the
 graphene quantum capacitance effect\cite{Xia_2009} (\Fig{}
@@
 \end{equation}
-where $\Delta \phi_{\mathrm{G}}$ is the change of graphene’s work
-function. Under the assumption that the charge neutrality point of
-graphene coincides with the Dirac point at $V_{\mathrm{G}}$ = 0, the elementary
+where
+$\Delta \phi_{\mathrm{G}} = \phi_{\mathrm{G}}(V_{\mathrm{g}}) -
+\phi_{\mathrm{G}}(V_{\mathrm{g}}=0)$ is the change of graphene’s work
+function. The properties of the PG samples fabricated is close to
+intrinsic graphene, with charge density at $V_{\mathrm{G}}=0$ measured
+to be XXX $e \cdot$cm$^{-2}$, corresponding to a work function
+difference of XXX meV from graphene's Dirac point (details see
+Supplementary Section SXX), much smaller than the
+$\Delta \phi_{\mathrm{G}}$ induced by gating.  Therefore we adapt the
+simplification that the charge neutrality point of graphene coincides
+with the Dirac point at $V_{\mathrm{G}}$ = 0. The elementary
 electronic properties of graphene give:
@@
 $v_{\mathrm{F}}=1.1\times10^{6}$ m$\cdot$s$^{-1}$ is the Fermi
-velocity of graphene (more details find Supplementary Section
-S5). Note that the PG film fabricated experimentally is double-layer
-turbostratic graphene, in which we assume the
+velocity of graphene (more details find Supplementary Section S5).
+Note that the PG film fabricated experimentally is double-layer
+turbostratic (randomly aligned) graphene, in which we assume the
 $\Delta \phi_{\mathrm{G}} - \sigma_{\mathrm{G}}$ dependence follows
 Eq. \eqref{eq:delta-phiG}. The theory proposed here was solved
-self-consistently by discretizing Eqs. \eqref{eq:pnp}-\eqref{eq:poisson}
-using the finite-element method (FEM), in which the graphene surface
-potential is coupled with
+self-consistently by discretizing
+Eqs. \eqref{eq:pnp}-\eqref{eq:poisson} using the finite-element method
+(FEM), in which the graphene surface potential is coupled with
 Eqs. \eqref{eq:electro-neutral}-\eqref{eq:delta-phiG} that were solved
@@
 respect to $V_{\mathrm{G}}$ due to the symmetric band structure of
-graphene (Eq. \eqref{eq:delta-phiG}). However, for graphene synthesized
-by chemical vapor deposition (CVD) used in our experiments, it is
-well-recognized that the electron traps are inherently introduced
-during synthesis and patterning \cite{Dean_2010}, effectively reducing
-the charge density and surface potential on graphene
-$V_{\mathrm{G}}<0$ (Supplementary \Fig{} S3). With the nonideality in
-mind, hereafter, we compare the calculations and experiments in the
-regime of $V_{\mathrm{G}}>0$. For example, \Fig{} \ref{fig:3}c
-presents the calculated $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$
-as a function of $V_{\mathrm{G}}$ considering the ionic diffusion
-through a single 20 nm-diameter nanopore drilled on a sheet of
-semi-infinite double layer graphene that separates HCR containing KCl
-solution at $c_{0}$ = 0.1 mM, and LCR at $c_{0}/10$ in axisymmetric
-coordinates (details see Supplementary Section S5). Indeed, the
-interplay between graphene quantum capacitance and the EDL
-significantly reduces the graphene surface potential
+graphene (Eq. \eqref{eq:delta-phiG}). However, for graphene
+synthesized by chemical vapor deposition (CVD) used in our
+experiments, it is well-recognized that the electron traps are
+inherently introduced during synthesis and patterning
+\cite{Dean_2010}, effectively reducing the charge density and surface
+potential on graphene $V_{\mathrm{G}}<0$ (Supplementary \Fig{} S3),
+which is related to the fact that observed $\xi$ is much lower within
+the $V_{\mathrm{G}}<0$ regime in \Fig{} \ref{fig:2}c. With the
+nonideality in mind, hereafter, we compare the calculations and
+experiments in the regime of $V_{\mathrm{G}}>0$. For example, \Fig{}
+\ref{fig:3}c presents the calculated $\sigma_{\mathrm{G}}$ and
+$\psi_{\mathrm{G}}$ as a function of $V_{\mathrm{G}}$ considering the
+ionic diffusion through a single 20 nm-diameter nanopore drilled on a
+sheet of semi-infinite double layer graphene that separates HCR
+containing KCl solution at $c_{0}$ = 0.1 mM, and LCR at $c_{0}/10$ in
+axisymmetric coordinates (details see Supplementary Section
+S5). Indeed, the interplay between graphene quantum capacitance and
+the EDL significantly reduces the graphene surface potential
 $\psi_{\mathrm{G}}$ to $\sim$0.3 V at $V_{\mathrm{G}}$ = 1.25 V,
@@
 that the concentration gradient at the pore center becomes
-small. (also see Supplementary \Fig{} S4). We also
-observe that $\Delta \mu_{+}$ is dominated by the concentration, while
+small. (also see Supplementary \Fig{} S4). We also observe that
+$\Delta \mu_{+}$ is dominated by the concentration, while
 $\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
 between the diffusion and drift potentials (see Supplementary \Fig{}
-S5). The observations confirm the distinct ionic
-transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
-center for cations and pore edge for anions. \Fig{} \ref{fig:4}c
-presents the calculated \textit{z}-component of the cation and anion fluxes
-through the pore at the graphene plane (z = 0), $\boldsymbol{J}_{z}$
-,as a function of the normalized radius, $r/R_{\mathrm{G}}$ , where
-$r$ is the radial coordinate and $R_{\mathrm{G}}$ is the pore radius,
-at different $V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$
-is negative because the LCR is placed at z$<$0 in the simulation box. At
+S5). The observations confirm the distinct ionic transport pathways
+upon applying a positive $V_{\mathrm{G}}$: pore center for cations and
+pore edge for anions. \Fig{} \ref{fig:4}c presents the calculated
+\textit{z}-component of the cation and anion fluxes through the pore
+at the graphene plane (z = 0), $\boldsymbol{J}_{z}$ ,as a function of
+the normalized radius, $r/R_{\mathrm{G}}$ , where $r$ is the radial
+coordinate and $R_{\mathrm{G}}$ is the pore radius, at different
+$V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$ is negative
+because the LCR is placed at z$<$0 in the simulation box. At
 $V_{\mathrm{G}}$ = 0 (pure diffusion), the anion and cation flux
@@
 reduced with $V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the
-ion selectivity of graphene nanopore \cite{Rollings_2016}.
+ion selectivity of graphene nanopore \cite{Rollings_2016}. In our setup, the imbalance between cation and anion
+fluxes near the graphene nanopore is compensated by the EDL formation
+at the counter-electrode in LCR, which maintains the electroneutrality
+of the system. Notably, since atomically thin graphene samples are
+used, the mechanism of salt rejection is clearly distinct from that in
+capacitive deionization \cite{Li_2010}, where electrodes with large
+surface area are required.
 
@@
 = 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.
+\todo[inline]{Some comments for large $\xi$ values after considering
+  the transport resistance can be shown here.}
 
@@
 considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
-K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (Supplementary
-Section S7). Similar to the KCl system discussed earlier, the salt
-rejection is more pronounced in the positive $V_{\mathrm{G}}$
-regime. The degree of salt rejection deceases with the salt valance;
-for example, the measured $\xi$ values at $V_{\mathrm{G}}$ = 1.25 V
-decreases from $>$ 0.5 for monovalent NaCl to -0.04 for multivalent
-K$_{3}$[Fe(CN)$_{6}$]. This observation is endorsed by our simulations,
-in which we calculate $\xi$ as a function of $V_{\mathrm{g}}$ using
-the same simulation setups(\Fig{} \ref{fig:6}b). The calculated
-$\xi_{\mathrm{max}}$ values are quantitatively compared with
-experiments (\Fig{} \ref{fig:6}c), and the same trend is
-observed. Indeed, because the Debye length
+K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (Supplementary Section
+S7). Similar to the KCl system discussed earlier, the salt rejection
+is more pronounced in the positive $V_{\mathrm{G}}$ regime. The degree
+of salt rejection deceases with the salt valance; for example, the
+measured $\xi$ values at $V_{\mathrm{G}}$ = 1.25 V decreases from $>$
+0.5 for monovalent NaCl to -0.04 for multivalent
+K$_{3}$[Fe(CN)$_{6}$]. This observation is endorsed by our
+simulations, in which we calculate $\xi$ as a function of
+$V_{\mathrm{g}}$ using the same simulation setups(\Fig{}
+\ref{fig:6}b). The calculated $\xi_{\mathrm{max}}$ values are
+quantitatively compared with experiments (\Fig{} \ref{fig:6}c), and
+the same trend is observed. Indeed, because the Debye length
 $\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
@@
 $\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
-species considered here (\Fig{} \ref{fig:6}d). We notice that without
-any fitting parameters, our theory can predict the experimental values
-reasonably well. In addition, the
+species considered here (\Fig{} \ref{fig:6}d). Similar to the
+experimenal observations, small difference between the $\xi$ of salts
+with same valence (e.g. LiCl, NaCl and KCl) is also predicted from the
+simulations due to the variation in ionic mobilities. We notice that
+without any fitting parameters, our theory can predict the
+experimental values reasonably well.  In addition, the
 $\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$ dependence is approximately
-linear, suggesting that the effect of salt diffusivity is
-negligible. This finding also explains the concentration dependence of
-$\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
-$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$.
+linear, suggesting that the effect of Debye length is dominant over
+the salt diffusivity. This finding also explains the concentration
+dependence of $\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
+$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$. Further including the
+specific interaction of ionic species with the graphene membrane
+\cite{Ghosh_2018} may give even better agreement with experimental
+results.
 

### 2018-12-22 paper/paper.tex
Implement manuscript changes with Roman

@@
 
-\author{Roman M. Wyss} \affiliation{Institute of Soft Materials
-  Department of Material Sciences, Eidgenössische Technische
+\author{Roman M. Wyss} \affiliation{Soft Materials,
+  Department of Materials, Eidgenössische Technische
   Hochschule (ETH) Zürich, Vladimir-Prelog-Weg 1-5, Zürich CH-8093,
@@
 \begin{abstract}
-  {\normalsize Atomically thin graphene nanopores is emerging as one
-    of the most promising candidates for next-generation membrane
-    technology owing to the ultrahigh permeability. However, the
-    size-exclusive mechanism of selectivity limits its scalability as
-    it remains technically challenging to drill subnanometer pores
-    over a large area. Here we report macroscopic salt rejection
-    through atomically-thin porous graphene with the pore sizes of
+  {\normalsize Atomically thin porous graphene membranes are emerging as one
+    of the most promising candidates as next-generation membrane
+    technology owing to their unique transport physics and high permeation. Among the current challenges of 2D membranes
+    is the understanding of fundamental ion transport as well as its control towards applications in ion rectification, ionic transistors or desalination. 
+    Here we report the study of tailoring the ion transport 
+    through atomically-thin porous graphene with pore sizes of
     20$\pm$10 nanometers, and a pore density of 1.25$\pm$0.25$\times$10$^{10}$
-    cm$^{-2}$, overcoming the pore size limitation set by the hydrated
-    radii. By electrostatically gating a sheet of porous graphene, we
-    report a considerable reduction of salt flux by up to 55\% and
-    85\% with the gate voltage, based on our experiments and
+    cm$^{-2}$. By electrostatically gating a sheet of porous graphene, we demonstrate
+    a considerable reduction of salt flux by up to 55\% and
+    85\% using a gate voltage, based on our experiments and
     theoretical predictions, respectively. We systematically
     investigate the effects of salt concentration and species,
-    including developing a theory to model the electrolyte diffusion
+    including the development of a theory to model the electrolyte diffusion
     through a nanopore in a sheet of gated graphene. The interplay
@@
     is identified to be the main mechanism responsible for the
-    observed salt rejection, when the pore size is comparable to the
+    observed salt flux reduction, when the pore size is comparable to the
     Debye length. Our findings reveal a new degree of
@@
 A central objective in the emerging field of nanofluidics is to
-manipulate transport phenomena at nanometer scale to enable new
-technological opportunities. The reduction of characteristic
+control transport phenomena at nanometer scale to enable and study novel
+devices and systems. The reduction of characteristic
 dimensions in nanofluidics gives rise to substantially different
@@
 transistors \cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
-nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}, Porous,
+nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}. Porous,
 atomically thin two-dimensional (2D) materials, such as graphene, are
@@
 \cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
-research has suggested that using nanoporous graphene as the
+research has suggested that using nanoporous graphene as a
 desalination membrane enables excellent salt rejection by preventing
-the permeation of hydrated ions with a high water permeability
-simultaneous
+the passage of ions, maintaining a high water permeability
+simultaneously.
 \cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}. Nevertheless,
@@
 between solvated ions and the charged functional groups attached on
-graphene \cite{Rollings_2016,Surwade_2014}. However, it remains
-controversial that if the surface charges can result in a degree of
-salt rejection, as the membrane charge and potential cannot be
+graphene, indicating that even large pores ($>$ 30nm) can be ion selective \cite{Rollings_2016,Surwade_2014}. However, it remains
+controversial if surface charges effectively allow controlled salt -transport 
+or -rejection, as the membrane charge and potential cannot be
 precisely quantified and are sensitive to the surroundings and
-chemical treatment \cite{Li_2008}. The difficulty in turn hinders a
+chemical treatment \cite{Li_2008}. Therefore, there is a lack of 
 fundamental understanding of the interactions between the atomically
-thin 2D membrane and the electrolyte solution. Here, we demonstrate
-macroscopic salt rejection through a sheet of large-area porous
+thin 2D membrane, its surface charge and the electrolyte solution. Here, we study 
+macroscopic salt rectification through a sheet of large-area porous
 graphene using electrostatic gating, thereby deepening the
-understanding of ion-graphene interaction and its implications on
-nanoporous graphene-based desalination applications.
+understanding of ion-graphene interaction and sheding light on applications of
+nanoporous graphene for tailored ion transport.
 
@@
 obtained (\Fig{} \ref{fig:1}c), allowing reliable characterization of
-the ion transport behavior (details see Supplementary Information
+the ion transport behavior (details see Supplementary 
 Section S1).  The system presented here allows us to systematically
@@
 diffusion of seven salt species, including KCl, NaCl, LiCl,
-K$_{2}$SO$_{4}$, MgSO4$_{4}$, CaCl$_{2}$ and K$_{3}$[Fe(CN)$_{6}$],
+K$_{2}$SO$_{4}$, MgSO$_{4}$, CaCl$_{2}$ and K$_{3}$[Fe(CN)$_{6}$],
 through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
-flux is comparably small, the conductivity varies linearly with time
+flux is comparably small, the conductivity increases linearly with time in the LCR
 (e.g. \Fig{} \ref{fig:2}a) within the measurement duration (1 h),
 suggesting the concentration gradient across the membrane remains 
-constant. The diffusive fluxes of different salts were
-obtained by converting the conductivity-time profiles with the
-calibration curves (blue bars in \Fig{} \ref{fig:2}b and Supplementary
-\Fig{} S2). For comparison purposes, based on the assumption that the
-membrane consists cylindrical pores with uniform diameter and a low
-tortuosity $\tau$ of $\sim{}$1.2 \cite{O_Hern_2012}, the molar
-diffusive flux through the bare PCTE membrane,
-$\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
+constant. The diffusive fluxes (blue bars in \Fig{} \ref{fig:2}b) of different salts were
+obtained by converting the conductivity-time profiles using
+calibration curves (Supplementary Section S2). The theoretical diffusive fluxes through PCTE are obtained based on the assumption that the
+membrane consists of cylindrical pores with uniform diameter and a low
+tortuosity $\tau$ of $\sim{}$1.2 \cite{O_Hern_2012}:
+
   \begin{equation}
@@
   \end{equation}
+
 where $a$ is the PCTE pore radius, $N_{\mathrm{p}}$ is numbers of pore
-per area, $D$ is the salt diffusivity, and $\Delta c$ is the bulk
+per area, $D$ is the salt diffusivity (average of cation and anion diffusivity), $\Delta c$ is the bulk
 concentration difference between two reservoirs, i.e.,
-$\Delta c \sim c_{0}$, $\delta$ is the thickness of the PCTE membrane,
-and $\tau$ is the tortuosity of the PCTE membrane. By using the salt diffusivity values
-provided by the PTCE vendor (Supplementary Table S1), the
+$\Delta c \sim c_{0}$ and $\delta$ is the thickness of the PCTE membrane.
+ By using the salt diffusivity values (Supplementary Table S1), the
 calculated diffusive fluxes (red bars in \Fig{} \ref{fig:2}b) show
@@
 with those of bare PCTE membrane, suggesting that the mass transfer
-resistance of PG is not significant, as the permeability is high. We
-observed a more pronounced decrease of diffusive flux in KCl,
-K$_{2}$SO$_{4}$ and K$_{3}$[Fe(CN)$_{6}$] systems but not for the rest
-of the salts. We hypothesized that the strong cation-$\pi$ interactions
-between K$^{+}$ cations and graphene slow down the migration of cations
-along the surface-mediated transport pathway \cite{Sun_2014}.
+resistance of PG is not significant, as the permeability is high. 
+The diffusive transport resistance through graphene pores scales with $\sim$ 1/D while
+for a PCTE pore, the scaling follows $\sim$ L/D$^2$ \cite{O_Hern_2014},
+ D being the respective diameter and L the channel length. 
+Taking into account that there are 10 graphene pores
+per PCTE pore on average, the transport resistance ratio of R$_{graphene}$/R$_{PCTE}$ is roughly 1/30,
+ indicating that the PCTE dominates the overall ion transport, which is in line 
+ with the observed behavior.
+
+%Interestingly, we observed a pronounced decrease of diffusive flux in KCl,
+%K$_{2}$SO$_{4}$ and K$_{3}$[Fe(CN)$_{6}$] systems but not for the rest
+%of the salts. We hypothesized that the strong cation-$\pi$ interactions
+%between K$^{+}$ cations and graphene slow down the migration of cations
+%along the surface-mediated transport pathway \cite{Sun_2014}.
 
@@
 conductivity-time profile with an average slope $s_{1}$ that
-corresponds to the diffusive flux across the PG-PCTE membrane, . In
+corresponds to the diffusive flux across the PG-PCTE membrane. In
 the second interval, a voltage $V_{\mathrm{G}}$ is applied to the
@@
 distribution is given by:
+
 \begin{equation}
@@
 \end{equation}
+
 where $\varepsilon_{\mathrm{m}}$ is the relative permittivity of
@@
 \ref{fig:3}a) following:
+
 \begin{equation}
@@
 \end{equation}
+
 where
+
 $\Delta \phi_{\mathrm{G}} = \phi_{\mathrm{G}}(V_{\mathrm{g}}) -
@@
 difference of XXX meV from graphene's Dirac point (details see
-Supplementary Section SXX), much smaller than the
+Supplementary Section S5), much smaller than the
 $\Delta \phi_{\mathrm{G}}$ induced by gating.  Therefore we adapt the
@@
 electronic properties of graphene give:
+
 \begin{equation}
@@
 \end{equation}
+
 where $\hbar$ is the reduced Planck constant, and
 $v_{\mathrm{F}}=1.1\times10^{6}$ m$\cdot$s$^{-1}$ is the Fermi
-velocity of graphene (more details find Supplementary Section S5).
+velocity of graphene (more details find Supplementary Section S6).
 Note that the PG film fabricated experimentally is double-layer
@@
 \label{sec:mechanism}
+
 The numerical procedure described above allows us to resolve the
@@
 (prefered path) greatly increases (details see Supplementary Section
-S6, Supplementary Figs. S8 and S9). This level of $\psi_{\mathrm{G}}$
+S7, Supplementary Figs. S8 and S9). This level of $\psi_{\mathrm{G}}$
 cannot be reached experimentally in graphene membrane, as this
@@
 = 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.
-\todo[inline]{Some comments for large $\xi$ values after considering
-  the transport resistance can be shown here.}
+
+As seen in the introduction, the diffusive transport resistance of ungated patterned graphene 
+is much smaller than that of the PCTE. When gating the graphene membrane,
+the overall flux, however, reduces to $\sim$ 55 $\%$
+of the ungated flux. This indicates, that R$_{graphene}$ $\approx$ R$_{PCTE}$, 
+a 26 fold increase of the resistance with respect to the ungated case. 
+This finding indicates, that the experimentally observed $\xi$ for graphene alone 
+is indeed higher than the 55$\%$, which is observed for the PG-PCTE combined.
 
@@
 K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (Supplementary Section
-S7). Similar to the KCl system discussed earlier, the salt rejection
+S8). Similar to the KCl system discussed earlier, the salt rejection
 is more pronounced in the positive $V_{\mathrm{G}}$ regime. The degree
@@
 \begin{acknowledgement}
-  R.M.W. acknowledges support from the Binnig and Rohrer
+  R.M.W. acknowledges Dr. Kyoungjun Choi from ETH Zurich for the measurement of the electron mobility 
+  of patterned graphene and is grateful for the support from the Binnig and Rohrer
   Nanotechnology Center of ETH Zurich and IBM Zurich. T.T. and

### 2018-12-22 paper/SI.tex
Implement changes SI with Roman

@@
 
-\section{Supplementary Section 2.       Ion diffusion measurement and calculation}
+\section{Ion diffusion measurement and calculation}
 \label{sec:measure}
@@
 \end{table}
+
+\section{Measurement of charge carrier density of patterned graphene}
+\label{sec:charge-dens}
+The intrinsic charge carrier density of graphene was measured using a 
+field electron transistor (FET) in air with a 300nm SiO$_2$ as a gate.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/charge-dens.png}
+  \caption{The I$_{SD}$ as a function of V$_G$. The electron mobility of xyz is extracted from the graph, which very similar to the 
+  intrinsic charge carrier density of unpatterned graphene (See Main Text).}
+  \label{fig:charge-dens}
+\end{figure}
 

### 2019-01-07 paper/SI.tex
Add results for the charge density calculations

@@
 The intrinsic charge carrier density of graphene was measured using a
-field electron transistor (FET) in air with a 300nm SiO$_2$ as a gate.
+field electron transistor (FET) in air with a 300nm SiO$_2$ as a
+gate. The device setup is shown in \Fig{} \ref{fig:charge-dens}a,
+where the source and drain electrodes were deposited onto the PG
+sample transfered onto 300nm SiO$_2$ on doped Silicon. The
+characteristic drain-source current $I_{\mathrm{DS}}$ as a function of
+$V_{\mathrm{G}}$ is shown in \Fig{} \ref{fig:charge-dens}. The
+charge-neutral point gate voltage $V_{\mathrm{CNP}}$ is measured to be 2.8 V.
+Using the capacitance of the SiO$_{2}$ dielectric, we an intrinsic
+charge density of $\sim{}$1.4$\times$10$^{11}$
+\textit{e}$\cdot$cm$^{-2}$, and a shift in the PG's Fermi level by
+$\sim{}$48 meV, which is negligible compared with the gate-induced
+charge density in our experiments. Therefore, the assumption that the
+PG sample is intrinsic without gating, is justified.
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{img/charge-dens.png}
-  \caption{The I$_{SD}$ as a function of V$_G$. The electron mobility of xyz is extracted from the graph, which very similar to the 
-  intrinsic charge carrier density of unpatterned graphene (See Main Text).}
+  \includegraphics[width=0.8\linewidth]{img/SI-gr-transistor.pdf}
+  \caption{Characterization of the intrinsic charge density of the PG
+    sample using field effect transistor. \textbf{a}. The setup of the
+    PG-FET. \textbf{b}. The I$_{\mathrm{DS}}$ as a function of
+    $V_{\mathrm{G}}$. The charge neutral point gate voltage is
+    determined as $\sim{}$2.8 V, corresponding to an intrinsic charge
+    density of $\sim{}$1.4$\times$10$^{11}$
+    \textit{e}$\cdot$cm$^{-2}$, which is negligible compared with the
+    gate-induced charges.}
   \label{fig:charge-dens}

### 2019-01-07 paper/paper.tex
Add results for the charge density calculations

@@
 intrinsic graphene, with charge density at $V_{\mathrm{G}}=0$ measured
-to be XXX $e \cdot$cm$^{-2}$, corresponding to a work function
-difference of XXX meV from graphene's Dirac point (details see
-Supplementary Section S5), much smaller than the
+to be 1.4$\times$10$^{11}$ \textit{e}$\cdot$cm$^{-2}$, corresponding
+to a work function difference of 48 meV from graphene's Dirac point
+(details see Supplementary Section S5), much smaller than the
 $\Delta \phi_{\mathrm{G}}$ induced by gating.  Therefore we adapt the

### 2019-01-07 paper/src/plt_bar_diffuse.py
Add revised data for PCTE diffusion

@@ -24,6 +24,7 @@ plt.bar(x - w * 3 / 2 , data[:, 6], width=w,
 
 # Simulate
 plt.bar(x - w / 2, data[:, 3], width=w, color="red",
+        yerr=data[:, 5 : 3 : -1].T,
         label="simu")
 
 # Bare

### 2019-01-07 paper/src/plot_gr_transistor.py
Add correction for graphene resistance

@@ -1,0 +1,40 @@
+import numpy
+from scipy.interpolate import interp1d
+import matplotlib.pyplot as plt
+from scipy.constants import epsilon_0
+from scipy.constants import elementary_charge as e
+from scipy.constants import hbar, pi
+
+file_name = "../data/gr_sample.csv"
+data = numpy.genfromtxt(file_name, delimiter=",")
+# print(data)
+VG = data[:, 0]
+IDS = data[:, -1]
+vv = numpy.linspace(VG.min(), VG.max(), 128)
+ii = interp1d(VG, IDS, kind="linear")(vv)
+p = numpy.polyfit(vv[(vv < 4) & (vv > 0)], ii[(vv < 4) & (vv > 0)], 2)
+print(-p[1]/(2*p[0]))
+
+v_min = -p[1]/(2*p[0])
+print("Dirac point", v_min)
+
+plt.figure(figsize=(3.2, 2.5))
+plt.style.use("science")
+
+plt.plot(VG, IDS / 1e-6, "o", markersize=3)
+plt.xlabel("$V_{\\rm{G}}$ (V)")
+plt.ylabel("$I_{\\rm{DS}}$ ($\\rm{\\mu}$)A")
+plt.axvline(x=v_min, ls="--")
+plt.xlim(-80, 80)
+plt.tight_layout()
+plt.savefig("../img/pg-transistor.svg")
+
+epsilon_sio2 = 2.8
+d = 300e-9
+c = epsilon_0 * epsilon_sio2 / d
+sigma = v_min * c
+sigma_e = sigma / e / 1e4 / 1e12
+print(sigma, sigma_e)
+vf = 1.1e6
+del_v = hbar * vf / e * numpy.sqrt(pi * abs(sigma) / e)
+print(del_v)

### 2019-01-07 paper/src/plot_rect_conc_gg.py

@@ -1,0 +1,52 @@
+import numpy
+import matplotlib.pyplot as plt
+from scipy.stats import linregress
+
+file_templ = "../data/rect_{}_conc.csv"
+def read(name):
+    file_name = file_templ.format(name)
+    err = None
+    with open(file_name) as f:
+        err = float(f.readline().strip())
+    data = numpy.genfromtxt(file_name,
+                            skip_header=1,
+                            delimiter=",")
+    return data, err
+
+def convert(delta, eta):
+    assert delta > 0
+    xi_inv = (1 - eta) / (delta * eta + 1)
+    return 1 - xi_inv
+
+import sys
+try:
+    name = sys.argv[1]
+except IndexError:
+    name = "KCl"
+
+fig = plt.style.use("science")
+plt.figure(figsize=(4, 4), facecolor="w")
+# plt.axvline(x=0, ls="--", color="#00ffee")
+data, err = read(name)
+# data[-1, -1] *= 1.5
+# plt.errorbar(data[:, 0], data[:, 1], yerr=err / 2, fmt="o")
+conc = data[:, 0]
+eta = data[:, 1]
+for delta in (0.2, 0.5, 1, 2, 5, 10, 20, 30):
+    xx = conc
+    yy = convert(delta, eta)
+    log_x = numpy.log(xx)
+    log_y = numpy.log(yy)
+    p = linregress(log_x, log_y)
+    s = p.slope
+    plt.plot(conc, convert(delta, eta),
+             "o",
+             label="$\\delta={{{0}}}, p={{{1:.2f}}}$".format(delta, s))
+# plt.plot(xx, yy, "--")
+# plt.xscale("log")
+plt.xlabel("KCl concentration (mol/L)")
+plt.ylabel("Rectification")
+plt.xscale("log")
+plt.yscale("log")
+plt.legend(loc=0)
+plt.savefig("../img/rect_{}_conc_gg.svg".format(name))

### 2019-01-07 postprocessing/plot_salt_gg.py

@@ -1,0 +1,156 @@
+from utils import *
+import numpy
+import matplotlib.pyplot as plt
+import os, os.path
+from scipy.constants import pi, hbar, e, N_A, k, epsilon_0
+
+vf = 1.1e6
+
+# Use C/m^2
+def delta_phi_gr(sigma):
+    fac = hbar * vf / e * numpy.sqrt(pi * numpy.abs(sigma) / e)
+    return fac * numpy.sign(sigma)
+
+pixels = (512, 512)
+
+quantities = ("V", "c_p", "c_n", "zflux_cp", "zflux_cn")
+units = ("V", "mol/m$^{3}$", "mol/m$^{3}$", "mol/(m$^{2}$*s)", "mol/(m$^{2}$*s)")
+
+# Vg_all = [0.001, 0.025, 0.05, 0.1, 0.15, 0.2] + list(numpy.arange(0.25, 0.651, 0.1))
+Vg_all = [0.001] + list(numpy.arange(0.025, 0.301, 0.025))
+Vg_true = []
+
+file_template = "{0}.npy"
+sigma_file_template = "sigma_{0}.txt"
+
+salts = ["NaCl", "LiCl", "KCl", "CaCl2",
+         "MgSO4", "K2SO4", "K3FeCN"]
+
+ratio_conc = 10**3
+
+# out_path = "../result/salt/"
+out_path = "../result/salt/20/"
+plot_path = "../plot/salt"
+plt.style.use("science")
+"""
+# get the index of column in the new matrix
+def get_col_index(Vg, quantity):
+    idx_V = Vg_all.index(Vg)
+    idx_quant = quantities.index(quantity)
+    len_quant = len(quantities)
+    return 1 + len_quant * idx_V + idx_quant
+
+
+avg_tflux = []
+
+quant_flux = ("zflux_cp", "zflux_cn")
+
+fig = plt.figure(figsize=(4, 4))
+for salt in salts:
+    tflux = []
+    file_name = os.path.join(out_path, file_template.format(salt))
+    print(file_name)
+    data = numpy.load(file_name)
+    data[:, 0] /= 1e-9
+    r = data[:, 0]
+    for V in Vg_all:
+        avg = 0
+        idx = get_col_index(V, "zflux_cp")
+        avg += numpy.abs(numpy.mean(data[:, idx]))
[…]

### 2019-01-09 paper/paper.tex
Change equation 1

@@
 tortuosity $\tau$ of $\sim{}$1.2 \cite{O_Hern_2012}:
-
 \begin{equation}
   \label{eq:j-pcte}
-    \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi a^{2} N_{\mathrm{p}} D \Delta c}{\delta \tau}
+  \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi r_{\mathrm{PCTE}}^{2} N_{\mathrm{p}} D_{\mathrm{\pm}} \Delta c}{L \tau}
 \end{equation}
 
-where $a$ is the PCTE pore radius, $N_{\mathrm{p}}$ is numbers of pore
-per area, $D$ is the salt diffusivity (average of cation and anion diffusivity), $\Delta c$ is the bulk
+where $r_{\mathrm{PCTE}}$ is the PCTE pore radius, $N_{\mathrm{p}}$ is
+numbers of pore per area, $D_{\mathrm{\pm}}$ is the salt diffusivity
+(average of cation and anion diffusivity), $\Delta c$ is the bulk
 concentration difference between two reservoirs, i.e.,
-$\Delta c \sim c_{0}$ and $\delta$ is the thickness of the PCTE membrane.
+$\Delta c \sim c_{0}$ and $L$ is the thickness of the PCTE membrane.
 By using the salt diffusivity values (Supplementary Table S1), the

### 2019-01-09 paper/paper.tex
Add comment for delta definition

@@
 \Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
-with those of bare PCTE membrane, suggesting that the mass transfer
-resistance of PG is not significant, as the permeability is high. 
-The diffusive transport resistance through graphene pores scales with $\sim$ 1/D while
-for a PCTE pore, the scaling follows $\sim$ L/D$^2$ \cite{O_Hern_2014},
- D being the respective diameter and L the channel length. 
-Taking into account that there are 10 graphene pores
-per PCTE pore on average, the transport resistance ratio of R$_{graphene}$/R$_{PCTE}$ is roughly 1/30,
- indicating that the PCTE dominates the overall ion transport, which is in line 
- with the observed behavior.
+with those of bare PCTE membrane, suggesting the transport resistance
+of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG,
+$R_{\mathrm{G}}^{0}$. Using a simple circuit model, we estimate the
+ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and $R_{\mathrm{PG}}$,
+such that $\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be ~2,
+which is in good agreement with the value derived from the
+experimental data in \Fig{} \ref{fig:2}b (details see Supplementary Section SXX).
+\todo[inline]{Make sure that the values used are correct.}
+
+% The diffusive transport resistance through graphene pores scales with $\sim$ 1/D while
+% for a PCTE pore, the scaling follows $\sim$ L/D$^2$ \cite{O_Hern_2014},
+ % D being the respective diameter and L the channel length. 
+% Taking into account that there are 10 graphene pores
+% per PCTE pore on average, the transport resistance ratio of R$_{graphene}$/R$_{PCTE}$ is roughly 1/30,
+ % indicating that the PCTE dominates the overall ion transport, which is in line 
+ % with the observed behavior.
 
@@
 used, the mechanism of salt rejection is clearly distinct from that in
-capacitive deionization \cite{Li_2010}, where electrodes with large
+capacitive deionization \cite{Biesheuvel_2010}, where electrodes with large
 surface area are required.

### 2019-01-09 paper/paper.tex
change symbol for graphene radius

@@
 \Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
-with those of bare PCTE membrane, suggesting the transport resistance
-of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG,
+with those of bare PCTE membrane, suggesting that the transport resistance
+of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG without gating,
 $R_{\mathrm{G}}^{0}$. Using a simple circuit model, we estimate the
-ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and $R_{\mathrm{PG}}$,
+ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and $R_{\mathrm{PCTE}}$,
 such that $\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be ~2,
@@
 the Debye length $\lambda_{\mathrm{D}}$ is comparable to the
-pore radius $R_{\mathrm{G}}$, the electric potential at the nanopore
+pore radius $r_{\mathrm{G}}$, the electric potential at the nanopore
 center remains at $\sim$25 mV, comparable to the thermal energy at
@@
 at the graphene plane (z = 0), $\boldsymbol{J}_{z}$ ,as a function of
-the normalized radius, $r/R_{\mathrm{G}}$ , where $r$ is the radial
-coordinate and $R_{\mathrm{G}}$ is the pore radius, at different
+the normalized radius, $r/r_{\mathrm{G}}$ , where $r$ is the radial
+coordinate and $r_{\mathrm{G}}$ is the pore radius, at different
 $V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$ is negative
@@
 of EDL inside the nanopore, essentially controlled by two length
-scales of $\lambda_{\mathrm{D}}$ and $R_{\mathrm{G}}$, and (ii) the
+scales of $\lambda_{\mathrm{D}}$ and $r_{\mathrm{G}}$, and (ii) the
 graphene surface potential $\psi_{\mathrm{G}}$ controlled by
@@
 calculate $\psi_{\mathrm{G}}$ as a function of
-$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (\Fig{}
+$\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (\Fig{}
 \ref{fig:5}a). Clearly, when the bulk concentration $c_{0}$ increases,
@@
 the calculated salt rejection factor $\xi$ increases with both
-$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$, in line
+$\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$, in line
 with the experimentally observed $\xi - c_{0}$ dependence. We also
 find the overall trends for $\psi_{\mathrm{G}}$ and $\xi$ with respect
-to $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
+to $\lambda_{\mathrm{D}}/r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
 similar. More importantly, based on our theoretical prediction, with
-$V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$
+$V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
 = 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.
@@
     potential of graphene $\psi_{\mathrm{G}}$ as a function of
-    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$. When
+    $\lambda_{\mathrm{D}}/r_{\mathrm{G}}$ and $V_{\mathrm{G}}$. When
     the Debye length reduces, a higher $V_{\mathrm{G}}$ is required to
@@
     predicted $\xi$ as a function of
-    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and
+    $\lambda_{\mathrm{D}}/r_{\mathrm{G}}$ and
     $V_{\mathrm{G}}$. Clearly, a higher degree of salt rejection can
     be achieved by having a higher $V_{\mathrm{G}}$ and
-    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$}
+    $\lambda_{\mathrm{D}}/r_{\mathrm{G}}$}
   \label{fig:5}

### 2019-01-09 paper/paper.tex
Change symbols in paper for reduction mechanism

@@
 \begin{abstract}
-  {\normalsize Atomically thin porous graphene membranes are emerging as one
-    of the most promising candidates as next-generation membrane
-    technology owing to their unique transport physics and high permeation. Among the current challenges of 2D membranes
-    is the understanding of fundamental ion transport as well as its control towards applications in ion rectification, ionic transistors or desalination. 
-    Here we report the study of tailoring the ion transport 
-    through atomically-thin porous graphene with pore sizes of
-    20$\pm$10 nanometers, and a pore density of 1.25$\pm$0.25$\times$10$^{10}$
-    cm$^{-2}$. By electrostatically gating a sheet of porous graphene, we demonstrate
-    a considerable reduction of salt flux by up to 55\% and
-    85\% using a gate voltage, based on our experiments and
+  {\normalsize Atomically thin porous graphene membranes are emerging
+    as one of the most promising candidates as next-generation
+    membrane technology owing to their unique transport physics and
+    high permeation. Among the current challenges of 2D membranes is
+    the understanding of fundamental ion transport as well as its
+    control towards applications in ion rectification, ionic
+    transistors or desalination.  Here we report the study of
+    tailoring the ion transport through atomically-thin porous
+    graphene with pore sizes of 20$\pm$10 nanometers, and a pore
+    density of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$. By
+    electrostatically gating a sheet of porous graphene, we
+    demonstrate a considerable reduction of salt flux by up to 55\%
+    and 85\% using a gate voltage, based on our experiments and
     theoretical predictions, respectively. We systematically
     investigate the effects of salt concentration and species,
-    including the development of a theory to model the electrolyte diffusion
-    through a nanopore in a sheet of gated graphene. The interplay
-    between graphene quantum capacitance and electrical double layer
-    is identified to be the main mechanism responsible for the
-    observed salt flux reduction, when the pore size is comparable to the
-    Debye length. Our findings reveal a new degree of
-    freedom controlling the membrane potential and electrolyte
+    including the development of a theory to model the electrolyte
+    diffusion through a nanopore in a sheet of gated graphene. The
+    interplay between graphene quantum capacitance and electrical
+    double layer is identified to be the main mechanism responsible
+    for the observed salt flux reduction, when the pore size is
+    comparable to the Debye length. Our findings reveal a new degree
+    of freedom controlling the membrane potential and electrolyte
     permeation through porous two-dimensional materials.  }
@@
 A central objective in the emerging field of nanofluidics is to
-control transport phenomena at nanometer scale to enable and study novel
-devices and systems. The reduction of characteristic
-dimensions in nanofluidics gives rise to substantially different
-transport properties in comparison to their bulk counterparts
+control transport phenomena at nanometer scale to enable and study
+novel devices and systems. The reduction of characteristic dimensions
+in nanofluidics gives rise to substantially different transport
+properties in comparison to their bulk counterparts
 \cite{Schoch_2008}. In nanopores, for example, the effect of
@@
 between solvated ions and the charged functional groups attached on
-graphene, indicating that even large pores ($>$ 30nm) can be ion selective \cite{Rollings_2016,Surwade_2014}. However, it remains
-controversial if surface charges effectively allow controlled salt -transport 
-or -rejection, as the membrane charge and potential cannot be
-precisely quantified and are sensitive to the surroundings and
+graphene, indicating that even large pores ($>$ 30nm) can be ion
+selective \cite{Rollings_2016,Surwade_2014}. However, it remains
+controversial if surface charges effectively allow controlled salt
+-transport or -rejection, as the membrane charge and potential cannot
+be precisely quantified and are sensitive to the surroundings and
 chemical treatment \cite{Li_2008}. Therefore, there is a lack of
 fundamental understanding of the interactions between the atomically
-thin 2D membrane, its surface charge and the electrolyte solution. Here, we study 
-macroscopic salt rectification through a sheet of large-area porous
-graphene using electrostatic gating, thereby deepening the
-understanding of ion-graphene interaction and sheding light on applications of
-nanoporous graphene for tailored ion transport.
+thin 2D membrane, its surface charge and the electrolyte
+solution. Here, we study macroscopic salt rectification through a
+sheet of large-area porous graphene using electrostatic gating,
+thereby deepening the understanding of ion-graphene interaction and
+sheding light on applications of nanoporous graphene for tailored ion
+transport.
 
@@
 conductivity-time profile with an average slope $s_{1}$ that
-corresponds to the diffusive flux across the PG-PCTE membrane. In
-the second interval, a voltage $V_{\mathrm{G}}$ is applied to the
-membrane after turning off the conductivity probe, followed by the
-third interval $s_{3}$, in which the conductivity probe is turned on
-again to give the corresponding slope. The slope corresponding to the
+corresponds to the diffusive flux across the PG-PCTE membrane. In the
+second interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane
+after turning off the conductivity probe, followed by the third
+interval $s_{3}$, in which the conductivity probe is turned on again
+to give the corresponding slope. A control experiment was performed to
+ensure the copper tape was not in direct contact with the ionic
+solution (Supplementary Section 3). The slope corresponding to the
 second interval $s_{2}$, as the conductivity probe is off, is
 determined by linear interpolation of the conductivities from the
-endpoint of interval 1 to the starting point of interval
-3. Accordingly, we define the salt rejection factor, $\xi$, which is
-effectively equivalent to the relative degree of diffusive flux
-decrease as follows:
+endpoint of interval 1 to the starting point of interval 3. A decrease
+of slope observed in interval 2 indicates that the total flux through
+PCTE+PG is reduced upon gating (i.e. salt penetration through the PG
+pores is partially rejected). We define such experimentally measured
+reduction rate as $\eta$, which is equivalent to the decrease of total
+diffusive flux through PCTE+PG as follows:
 \begin{equation}
   \label{eq:rejection}
-  \xi = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
+  \eta = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
     - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
@@
 across the PTCE-supported PG double layer as a function of
-$V_{\mathrm{G}}$. Note that a positive $\xi$ between 0 and 1
-represents a decrease of the diffusive flux. The factor $\xi$ enables
-a reliable and stable measurement of salt rejection, as the salt
-species and initial conditions may induce a degree of measurement
-uncertainty between different samples. A control experiment was
-performed to ensure the copper tape was not in direct contact with the
-ionic solution (Supplementary Section 3).
+$V_{\mathrm{G}}$. PG and PCTE membranes effectively form a transport
+system with series resistance $R_{\mathrm{PG}}$ (tunable by
+$V_{\mathrm{G}}$) and $R_{\mathrm{PCTE}}$ (independent of
+$V_{\mathrm{G}}$), respectively. Due to the dominance of
+$R_{\mathrm{PCTE}}$ in the ionic transport, significant reduction of
+total ionic flux can only be achieved, when
+$R_{\mathrm{\mathrm{G}}}(V_{\mathrm{G}} \neq 0) \gg
+R_{\mathrm{\mathrm{G}}}^{0}$. Using the circuit analog model, we can
+extract the effective salt rejection ratio of PG $\xi$ from the
+observable flux reduction ratio $\eta$, as a function of
+$V_{\mathrm{G}}$ as (details see Supplementary Section S4):
+\begin{equation}
+\label{eq:xi-def}
+\xi = \frac{(\delta+1) \eta}{\delta \eta + 1}
+\end{equation}
+The factor $\xi$ enables a reliable and stable measurement of salt
+rejection through the PG membrane, as the salt species and initial
+conditions may induce a degree of measurement uncertainty between
+different samples.
 

### 2019-01-10 paper/paper.tex
Use hyper-xr to figure crossref

@@
 \usepackage{lineno}
+\usepackage{xr-hyper}
+\externaldocument[SI-]{SI}
 
@@
 the ion transport behavior (details see Supplementary 
-Section S1).  The system presented here allows us to systematically
+Section \ref{SI-sec:exp}).  The system presented here allows us to systematically
 investigate the diffusive flux of ions across a sheet of PG,
@@
 through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
-flux is comparably small, the conductivity increases linearly with time in the LCR
-(e.g. \Fig{} \ref{fig:2}a) within the measurement duration (1 h),
-suggesting the concentration gradient across the membrane remains 
-constant. The diffusive fluxes (blue bars in \Fig{} \ref{fig:2}b) of different salts were
-obtained by converting the conductivity-time profiles using
-calibration curves (Supplementary Section S2). The theoretical diffusive fluxes through PCTE are obtained based on the assumption that the
-membrane consists of cylindrical pores with uniform diameter and a low
+flux is comparably small, the conductivity increases linearly with
+time in the LCR (e.g. \Fig{} \ref{fig:2}a) within the measurement
+duration (1 h), suggesting the concentration gradient across the
+membrane remains constant. The diffusive fluxes (blue bars in \Fig{}
+\ref{fig:2}b) of different salts were obtained by converting the
+conductivity-time profiles using calibration curves (Supplementary
+Section \ref{SI-sec:measure}). The theoretical diffusive fluxes
+through PCTE are obtained based on the assumption that the membrane
+consists of cylindrical pores with uniform diameter and a low
 tortuosity $\tau$ of $\sim{}$1.2 \cite{O_Hern_2012}:
@@
 $\Delta c \sim c_{0}$ and $L$ is the thickness of the PCTE membrane.
-By using the salt diffusivity values (Supplementary Table S1), the
-calculated diffusive fluxes (red bars in \Fig{} \ref{fig:2}b) show
-reasonable agreement with the experimental values.
+By using the salt diffusivity values (Supplementary Table
+\ref{SI-tab:diff}), the calculated diffusive fluxes (red bars in
+\Fig{} \ref{fig:2}b) show reasonable agreement with the experimental
+values.
 
@@
 \Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
-with those of bare PCTE membrane, suggesting that the transport resistance
-of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG without gating,
-$R_{\mathrm{G}}^{0}$. Using a simple circuit model, we estimate the
-ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and $R_{\mathrm{PCTE}}$,
-such that $\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be ~2,
-which is in good agreement with the value derived from the
-experimental data in \Fig{} \ref{fig:2}b (details see Supplementary Section SXX).
-\todo[inline]{Make sure that the values used are correct.}
+with those of bare PCTE membrane, suggesting that the transport
+resistance of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG
+without gating, $R_{\mathrm{G}}^{0}$. Using a simple circuit model, we
+estimate the ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and
+$R_{\mathrm{PCTE}}$, such that
+$\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be ~2, which is in
+good agreement with the value derived from the experimental data in
+\Fig{} \ref{fig:2}b (details see Supplementary Section
+\ref{SI-sec:R-model}).
+\todo[inline]{Make sure that the values used
+  are correct.}
 
@@
 ensure the copper tape was not in direct contact with the ionic
-solution (Supplementary Section 3). The slope corresponding to the
+solution (Supplementary Section \ref{SI-sec:copper}). The slope corresponding to the
 second interval $s_{2}$, as the conductivity probe is off, is
@@
 observable flux reduction ratio $\eta$, as a function of
-$V_{\mathrm{G}}$ as (details see Supplementary Section S4):
+$V_{\mathrm{G}}$ as (details see Supplementary Section
+\ref{SI-sec:R-model}):
 \begin{equation}
@@
 $\xi_{\mathrm{max}}$, as a function of $c_{0}$ from 10$^{-4}$ to
-10$^{-2}$ M KCl (see Supplementary Section S4) exhibit a power law
+10$^{-2}$ M KCl (see Supplementary Section \ref{SI-sec:debye}) exhibit a power law
 dependency (\Fig{} \ref{fig:2}d). The $\xi_{\mathrm{max}}-c_{0}$
@@
 to a work function difference of 48 meV from graphene's Dirac point
-(details see Supplementary Section S5), much smaller than the
-$\Delta \phi_{\mathrm{G}}$ induced by gating.  Therefore we adapt the
-simplification that the charge neutrality point of graphene coincides
-with the Dirac point at $V_{\mathrm{G}}$ = 0. The elementary
-electronic properties of graphene give:
+(details see Supplementary Section \ref{SI-sec:charge-dens}), much
+smaller than the $\Delta \phi_{\mathrm{G}}$ induced by gating.
+Therefore we adapt the simplification that the charge neutrality point
+of graphene coincides with the Dirac point at $V_{\mathrm{G}}$ =
+0. The elementary electronic properties of graphene give:
 
@@
 $v_{\mathrm{F}}=1.1\times10^{6}$ m$\cdot$s$^{-1}$ is the Fermi
-velocity of graphene (more details find Supplementary Section S6).
-Note that the PG film fabricated experimentally is double-layer
-turbostratic (randomly aligned) graphene, in which we assume the
+velocity of graphene (more details find Supplementary Section
+\ref{SI-sec:charge-dens}).  Note that the PG film fabricated
+experimentally is double-layer turbostratic (randomly aligned)
+graphene, in which we assume the
 $\Delta \phi_{\mathrm{G}} - \sigma_{\mathrm{G}}$ dependence follows
@@
 \cite{Dean_2010}, effectively reducing the charge density and surface
-potential on graphene $V_{\mathrm{G}}<0$ (Supplementary \Fig{} S3),
-which is related to the fact that observed $\xi$ is much lower within
-the $V_{\mathrm{G}}<0$ regime in \Fig{} \ref{fig:2}c. With the
-nonideality in mind, hereafter, we compare the calculations and
-experiments in the regime of $V_{\mathrm{G}}>0$. For example, \Fig{}
-\ref{fig:3}c presents the calculated $\sigma_{\mathrm{G}}$ and
-$\psi_{\mathrm{G}}$ as a function of $V_{\mathrm{G}}$ considering the
-ionic diffusion through a single 20 nm-diameter nanopore drilled on a
-sheet of semi-infinite double layer graphene that separates HCR
-containing KCl solution at $c_{0}$ = 0.1 mM, and LCR at $c_{0}/10$ in
-axisymmetric coordinates (details see Supplementary Section
-S5). Indeed, the interplay between graphene quantum capacitance and
-the EDL significantly reduces the graphene surface potential
-$\psi_{\mathrm{G}}$ to $\sim$0.3 V at $V_{\mathrm{G}}$ = 1.25 V,
-corresponding a surface charge density $\sigma_{\mathrm{G}}$ of
-$\sim$0.08 C$\cdot$m$^{-2}$. Note that as we mentioned earlier, an
-important merit of the system here is that the surface charge density
-can be precisely determined and controlled, rather than being treated
-as a fitting parameter as in most of the 2D nanopore studies
-\cite{Rollings_2016}.
+potential on graphene $V_{\mathrm{G}}<0$ (Supplementary \Fig{}
+\ref{SI-fig:trap}), which is related to the fact that observed $\xi$
+is much lower within the $V_{\mathrm{G}}<0$ regime in \Fig{}
+\ref{fig:2}c. With the nonideality in mind, hereafter, we compare the
+calculations and experiments in the regime of $V_{\mathrm{G}}>0$. For
+example, \Fig{} \ref{fig:3}c presents the calculated
+$\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ as a function of
+$V_{\mathrm{G}}$ considering the ionic diffusion through a single 20
+nm-diameter nanopore drilled on a sheet of semi-infinite double layer
+graphene that separates HCR containing KCl solution at $c_{0}$ = 0.1
+mM, and LCR at $c_{0}/10$ in axisymmetric coordinates (details see
+Supplementary Section \ref{SI-fig:scheme}). Indeed, the interplay between graphene
+quantum capacitance and the EDL significantly reduces the graphene
+surface potential $\psi_{\mathrm{G}}$ to $\sim$0.3 V at
+$V_{\mathrm{G}}$ = 1.25 V, corresponding a surface charge density
+$\sigma_{\mathrm{G}}$ of $\sim$0.08 C$\cdot$m$^{-2}$. Note that as we
+mentioned earlier, an important merit of the system here is that the
+surface charge density can be precisely determined and controlled,
+rather than being treated as a fitting parameter as in most of the 2D
+nanopore studies \cite{Rollings_2016}.
 
@@
 anion concentration near the pore edge increases exponentially, such
-that the concentration gradient at the pore center becomes
-small. (also see Supplementary \Fig{} S4). We also observe that
+that the concentration gradient at the pore center becomes small (see
+Supplementary \Fig{} \ref{SI-fig:conc}). We also observe that
 $\Delta \mu_{+}$ is dominated by the concentration, while
@@
 between the diffusion and drift potentials (see Supplementary \Fig{}
-S5). The observations confirm the distinct ionic transport pathways
-upon applying a positive $V_{\mathrm{G}}$: pore center for cations and
-pore edge for anions. \Fig{} \ref{fig:4}c presents the calculated
-\textit{z}-component of the cation and anion fluxes through the pore
-at the graphene plane (z = 0), $\boldsymbol{J}_{z}$ ,as a function of
-the normalized radius, $r/r_{\mathrm{G}}$ , where $r$ is the radial
-coordinate and $r_{\mathrm{G}}$ is the pore radius, at different
-$V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$ is negative
-because the LCR is placed at z$<$0 in the simulation box. At
-$V_{\mathrm{G}}$ = 0 (pure diffusion), the anion and cation flux
-profiles are identical, with a higher flux near the pore edge, which
-is expected, as the concentration gradient is higher. By gradually
-increasing $V_{\mathrm{G}}$, both fluxes are reduced throughout the
-pore, while the degree of reduction is more pronounced at the pore
-edge for the cation, and at the pore center for the anion, following
-the scenarios we discussed above. Accordingly, the integrated fluxes
-across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
-$V_{\mathrm{G}}$ (\Fig{} \ref{fig:4}d). A total flux reduction of up
-to 80\% is predicted. Another interesting finding here is that, by
-increasing $V_{\mathrm{G}}$, the nanopore transport preferentially
-allows cations over anions, or in other words, the anion flux is more
-reduced with $V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the
-ion selectivity of graphene nanopore \cite{Rollings_2016}. In our setup, the imbalance between cation and anion
-fluxes near the graphene nanopore is compensated by the EDL formation
-at the counter-electrode in LCR, which maintains the electroneutrality
-of the system. Notably, since atomically thin graphene samples are
-used, the mechanism of salt rejection is clearly distinct from that in
-capacitive deionization \cite{Biesheuvel_2010}, where electrodes with large
-surface area are required.
+\ref{SI-fig:potential}). The observations confirm the distinct ionic
+transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
+center for cations and pore edge for anions. \Fig{} \ref{fig:4}c
+presents the calculated \textit{z}-component of the cation and anion
+fluxes through the pore at the graphene plane (z = 0),
+$\boldsymbol{J}_{z}$ ,as a function of the normalized radius,
+$r/r_{\mathrm{G}}$ , where $r$ is the radial coordinate and
+$r_{\mathrm{G}}$ is the pore radius, at different $V_{\mathrm{G}}$
+values. Note that $\boldsymbol{J}_{z}$ is negative because the LCR is
+placed at z$<$0 in the simulation box. At $V_{\mathrm{G}}$ = 0 (pure
+diffusion), the anion and cation flux profiles are identical, with a
+higher flux near the pore edge, which is expected, as the
+concentration gradient is higher. By gradually increasing
+$V_{\mathrm{G}}$, both fluxes are reduced throughout the pore, while
+the degree of reduction is more pronounced at the pore edge for the
+cation, and at the pore center for the anion, following the scenarios
+we discussed above. Accordingly, the integrated fluxes across the
+pore, $|\boldsymbol{J}_{z}|$, are reduced with $V_{\mathrm{G}}$
+(\Fig{} \ref{fig:4}d). A total flux reduction of up to 80\% is
+predicted. Another interesting finding here is that, by increasing
+$V_{\mathrm{G}}$, the nanopore transport preferentially allows cations
+over anions, or in other words, the anion flux is more reduced with
+$V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the ion
+selectivity of graphene nanopore \cite{Rollings_2016}. In our setup,
+the imbalance between cation and anion fluxes near the graphene
+nanopore is compensated by the EDL formation at the counter-electrode
+in LCR, which maintains the electroneutrality of the system. Notably,
+since atomically thin graphene samples are used, the mechanism of salt
+rejection is clearly distinct from that in capacitive deionization
+\cite{Biesheuvel_2010}, where electrodes with large surface area are
+required.
 
@@
 further increased the graphene surface potential $\psi_{\mathrm{G}}$
-considering the same system (Supplementary Section 6). Intriguingly,
-by increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
-starts to increase, reversing the trend observed at the low
-$\psi_{\mathrm{G}}$ regime, due to (i) the drift flux become dominant
-over diffusion flux and (ii) the concentration near the pore edge
-(prefered path) greatly increases (details see Supplementary Section
-S7, Supplementary Figs. S8 and S9). This level of $\psi_{\mathrm{G}}$
-cannot be reached experimentally in graphene membrane, as this
-requires a $V_{\mathrm{G}}$ larger than 2.0 V, which triggers the
-electrochemical reactions \cite{Toh_2011}. On the other hand, in an
-IFET, the electric potential on the pore wall is considerably higher,
-equivalent to $V_{\mathrm{G}}$ due to the metallic nature of gate
-electrode (having an infinitely-large quantum capacitance). We
-therefore conclude that the quantum capacitance-induced nonlinear
-damping in the surface potential results in the observed salt
-rejection.  Following the above discussions, we further investigate
-the physical limits for the biased graphene nanopores. Specifically,
-the salt rejection characteristics are controlled by: (i) the overlap
-of EDL inside the nanopore, essentially controlled by two length
-scales of $\lambda_{\mathrm{D}}$ and $r_{\mathrm{G}}$, and (ii) the
-graphene surface potential $\psi_{\mathrm{G}}$ controlled by
-$V_{\mathrm{G}}$ following Eq. \eqref{eq:Vg}. To this end, we
-calculate $\psi_{\mathrm{G}}$ as a function of
-$\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (\Fig{}
-\ref{fig:5}a). Clearly, when the bulk concentration $c_{0}$ increases,
-a higher $V_{\mathrm{G}}$ is required to reach the same level of
-$\psi_{\mathrm{G}}$. Consequently, as revealed in \Fig{} \ref{fig:5}b,
-the calculated salt rejection factor $\xi$ increases with both
-$\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$, in line
-with the experimentally observed $\xi - c_{0}$ dependence. We also
-find the overall trends for $\psi_{\mathrm{G}}$ and $\xi$ with respect
-to $\lambda_{\mathrm{D}}/r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
+considering the same system (details see Supplementary Section
+\ref{SI-sec:simu-res}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
+larger than 400 mV, the ionic flux starts to increase, reversing the
+trend observed at the low $\psi_{\mathrm{G}}$ regime, due to (i) the
+drift flux become dominant over diffusion flux and (ii) the
+concentration near the pore edge (prefered path) greatly increases
+(details see Supplementary Section \ref{SI-sec:simu-res}, Supplementary
+Figs. \ref{SI-fig:reverse} and \ref{SI-fig:large-V}). This level of
+$\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
+membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V, which
+triggers the electrochemical reactions \cite{Toh_2011}. On the other
+hand, in an IFET, the electric potential on the pore wall is
+considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
+metallic nature of gate electrode (having an infinitely-large quantum
+capacitance). We therefore conclude that the quantum
+capacitance-induced nonlinear damping in the surface potential results
+in the observed salt rejection.  Following the above discussions, we
+further investigate the physical limits for the biased graphene
+nanopores. Specifically, the salt rejection characteristics are
+controlled by: (i) the overlap of EDL inside the nanopore, essentially
+controlled by two length scales of $\lambda_{\mathrm{D}}$ and
+$r_{\mathrm{G}}$, and (ii) the graphene surface potential
+$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
+Eq. \eqref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
+function of $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and
+$V_{\mathrm{G}}$ (\Fig{} \ref{fig:5}a). Clearly, when the bulk
+concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
+to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
+revealed in \Fig{} \ref{fig:5}b, the calculated salt rejection factor
+$\xi$ increases with both $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and
+$V_{\mathrm{G}}$, in line with the experimentally observed
+$\xi - c_{0}$ dependence. We also find the overall trends for
+$\psi_{\mathrm{G}}$ and $\xi$ with respect to
+$\lambda_{\mathrm{D}}/r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
 similar. More importantly, based on our theoretical prediction, with
@@
 considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
-K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (Supplementary Section
-S8). Similar to the KCl system discussed earlier, the salt rejection
-is more pronounced in the positive $V_{\mathrm{G}}$ regime. The degree
-of salt rejection deceases with the salt valance; for example, the
-measured $\xi$ values at $V_{\mathrm{G}}$ = 1.25 V decreases from $>$
-0.5 for monovalent NaCl to -0.04 for multivalent
-K$_{3}$[Fe(CN)$_{6}$]. This observation is endorsed by our
-simulations, in which we calculate $\xi$ as a function of
-$V_{\mathrm{g}}$ using the same simulation setups(\Fig{}
+K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (details see Supplementary
+Section \ref{SI-sec:simu-res}). Similar to the KCl system discussed
+earlier, the salt rejection is more pronounced in the positive
+$V_{\mathrm{G}}$ regime. The degree of salt rejection deceases with
+the salt valance; for example, the measured $\xi$ values at
+$V_{\mathrm{G}}$ = 1.25 V decreases from $>$ 0.5 for monovalent NaCl
+to -0.04 for multivalent K$_{3}$[Fe(CN)$_{6}$]. This observation is
+endorsed by our simulations, in which we calculate $\xi$ as a function
+of $V_{\mathrm{g}}$ using the same simulation setups(\Fig{}
 \ref{fig:6}b). The calculated $\xi_{\mathrm{max}}$ values are
@@
 of 3 measurements and averaging the resulting values (see
-Supplementary Section 2). For the measurement, DI water was filled on
+Supplementary Section \ref{SI-sec:measure}). For the measurement, DI water was filled on
 the LCR side, where a 0.1 mM salt solution is placed on the HCR side
@@
 performing simulations with varied mesh sizes. For further details
-about the simulation setup please refer to Supplementary Section 5.
+about the simulation setup please refer to Supplementary Section
+\ref{SI-sec:numer}.
 

### 2019-01-10 paper/SI.tex
Use hyper-xr to figure crossref
Change SI for delta value part

@@
 \SectionNumbersOn
+\usepackage{xr-hyper}
+\externaldocument[main-]{paper}
+
 % \usepackage{lineno}
@@
 the solution.
+
+\section{Circuit analog model of transport through PG-PCTE}
+\label{sec:R-model}
+The ionic transport through the PG-PCTE membrane is the concerted
+effect the transport resistance through PG and PCTE membranes,
+respectively. As schematically shown in \Fig{} \ref{fig:R-model}, the
+overall transport resistance of the system is composed of the series
+resistance $R_{\mathrm{G}}$ and $R_{\mathrm{PCTE}}$, respectively. We
+further treat $R_{\mathrm{G}}$ as the effective resistance of $\gamma$
+parallel resistors with individual resistance $R_{\mathrm{g}}$, where
+$\gamma$ is the average numbers of PG pores per PCTE channel, and
+$R_{\mathrm{g}}$ is the average transport resistance per PG pore. 
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-resistance-rectification.pdf}
+  \caption{Simple circuit analog model for the transport through
+    PG-PCTE membrane. \textbf{a}. Schematic of PG-PCTE membrane in
+    cross-section view. \textbf{b}. Model for transport resistance in
+    analogy to an electric circuit. This schematic depicts a cut
+    through a PG-PCTE membrane showing a single PCTE pore and multiple
+    graphene pores.}
+  \label{fig:R-model}
+\end{figure}
+We then estimate the value of $\gamma$ from geometric analysis of both
+membranes. Given the pore number density of PG
+($\sim$1.25$\times$10$^{14}$ m$^{-2}$), the pore number density of
+PCTE ($\sim$1.50$\times$10$^{12}$ m$^{-2}$), and the percentage of
+PCTE pores with PG on top ($\sim$0.13), $\gamma$ is determined to be
+$\sim$10.83.
+
+Next we seek the value between $R_{\mathrm{PCTE}}$ and
+$R_{\mathrm{G}}^{0}$ (ungated resistance of PG), $\delta$ (as defined
+in main text Section \ref{main-sec:res-1}). It is pointed out that the
+scaling law for $R_{\mathrm{PCTE}}$ and $R_{\mathrm{G}}^{0}$
+differs. For a long channel like PCTE, the resistance is derived from
+Fick's law as\cite{O_Hern_2014}:
+\begin{equation}
+\label{eq:R-PCTE}
+ R_{\mathrm{PCTE}} = \frac{1}{D} \frac{L}{\pi r_{\mathrm{PCTE}}^{2}}
+\end{equation}
+whereas $D$ is the diffusivity of the specie, $L$ is the length of
+channel ($\sim$24 $\mathrm{\mu}$m), and $r_{\mathrm{PCTE}}$ is the
+average radius of the PCTE channels ($\sim$400 nm). On the other hand,
+the transport through 2D pore with high radius/thickness ratio falls
+into the regime of the Sampson formula \cite{Roscoe_1949}, where the
+entrance resistance dominates over the bulk resistance, with the
+formula as \cite{Roscoe_1949,Celebi_2014}:
+\begin{equation}
+  \label{eq:sampson}
+  R_{\mathrm{g}}^{0} = \frac{1}{D} \frac{3 \pi}{r_{\mathrm{G}}}
+\end{equation}
+We therefore estimate the value of $\delta$ as:
+\begin{equation}
+  \label{eq:delta-resistance}
+  \delta = {\displaystyle
+    \frac{{\displaystyle \frac{L}
+        {\pi r_{\mathrm{PCTE}}^{2}}}}
+    {{\displaystyle \frac{3 \pi}{r_{\mathrm{G}}} \frac{1}{\gamma}}}}
+  \approx 2.20
+\end{equation}
 

### 2019-01-10 paper/paper.tex
Fix PG+PTCE name in paper

@@
 of slope observed in interval 2 indicates that the total flux through
-PCTE+PG is reduced upon gating (i.e. salt penetration through the PG
+PG-PCTE is reduced upon gating (i.e. salt penetration through the PG
 pores is partially rejected). We define such experimentally measured
 reduction rate as $\eta$, which is equivalent to the decrease of total
-diffusive flux through PCTE+PG as follows:
+diffusive flux through PG-PCTE as follows:
 \begin{equation}

### 2019-01-10 paper/src/plot_delta.py
Add plot for estimating delta

@@ -1,0 +1,37 @@
+import numpy
+import matplotlib.pyplot as plt
+
+# def get_time(string):
+    # string = string.decode("ascii")
+    # h, m, s = map(float, string.split(":"))
+    # return 3600 * h + 60 * m + 1 * s
+
+salts = ["KCl", "NaCl", "LiCl", "CaCl2",
+         "MgSO4", "K3FeCN6", "K2SO4"]
+data = numpy.genfromtxt("../data/diffuse-pcte-salt-delta.csv",
+                        skip_header=2,
+                        delimiter=",")
+exclude = ["LiCl", "MgSO4"]
+
+cond = [i for i, s in enumerate(salts) if s not in exclude]
+cond_salts = [s for i, s in enumerate(salts) if s not in exclude]
+c = data[cond, -3]
+low = data[cond, -2]
+up = data[cond, -1]
+delta = 2.20
+
+plt.figure(figsize=(3, 3 * 0.8))
+plt.style.use("science")
+plt.errorbar(range(len(cond)), y=c, yerr=[c - low, up - c],
+             fmt="s", label="Experiment")
+plt.axhline(y=delta, ls="--", label="Model")
+# plt.plot(data[:, 1][cond] / 3600, data[:, 2][cond] / 1e-3)
+# plt.plot(data[:, 1][data[:, 1] > 7200] / 3600, data[:, 2][data[:, 1] > 7200] / 1e-3)
+plt.xticks(range(len(cond)))
+plt.legend(loc=0)
+plt.gca().set_xticklabels(cond_salts, rotation=-45, ha="left")
+plt.xlim(-0.5, 5.5)
+# plt.xlabel("t (h)")
+plt.ylabel("$\\delta$")
+plt.ylim(0, 10)
+plt.savefig("../img/delta-estimate.svg")

### 2019-01-10 paper/SI.tex
Complete SI analysis of delta

@@
   \label{eq:delta-resistance}
-  \delta = {\displaystyle
+  \delta
+  = \frac{R_{\mathrm{PCTE}}}{R_{\mathrm{G}}^{0}}
+  = {\displaystyle
     \frac{{\displaystyle \frac{L}
@@
 \end{equation}
+Alternatively, we may also estimate the range of $\delta$ from
+experimental data in main text \Fig{} \ref{main-fig:2}b using the
+relation:
+\begin{equation}
+  \label{eq:exp-delta}
+  \delta = \left(\frac{\boldsymbol{J}_{\mathrm{PCTE}}}{\boldsymbol{J}_{\mathrm{PG}}^{0}} -1 \right)^{-1}
+\end{equation}
+by assuming the validity of the circuit analog model for all salt
+systems. We find that the $\delta$ value estimated from the simple
+geometric model agrees well with the experimental results. As shown in
+\Fig{}, the theoretical estimated value of $\delta$ (organe line) lies
+within the margin of the majority of experimental data, which is
+exceptionally good given the simplicity of the model used.
+
+Next we show how the effective salt rejection ratio through PG, $\xi$,
+is extracted from the experimental $\eta$ values. Using the circuit
+analog model, the definition of $\eta$ from main text
+Eq. \ref{main-eq:rejection} can be rewritted using transport
+resistances as:
+\begin{equation}
+  \begin{aligned}[t]
+      \label{eq:eta-R}
+  \eta &= 1 - {\displaystyle
+    \frac{(R_{\mathrm{PCTE}} + R_{\mathrm{G}})^{-1}}
+    {(R_{\mathrm{PCTE}} + R_{\mathrm{G}}^{0})}} \\
+    &= 1 - \frac{\delta + 1}{\delta + R_{\mathrm{G}}/R_{\mathrm{G}}^{0}} \\
+    &= 1 - \frac{\delta + 1}{\delta + \chi}
+  \end{aligned}
+\end{equation}
+where we define $\chi = R_{\mathrm{G}}/R_{\mathrm{G}}^{0}$ which
+represents the change of the transport resistance through PG upon
+gating. Consequentially, the salt rejection ratio $\xi$, is associated
+with $\chi$ by $\xi = 1 - \chi^{-1}$. Reformatting Eq. \ref{eq:eta-R}
+gives:
+\begin{equation}
+  \label{eq:xi-deriv}
+  \begin{aligned}[t]
+    \xi &= 1 - \chi^{-1} \\
+    &= \frac{(\delta + 1) \eta}{\delta\eta + 1}
+  \end{aligned}
+\end{equation}
+which is main text Eq. \ref{main-eq:xi-def}. When $0<\eta<1$ (salt
+rejection regime) and $\delta>0$, Eq. \ref{eq:xi-deriv} always
+guarantees $\xi>\eta$, since $\delta + 1$ is always larger than
+$\delta\eta + 1$. In other words, due to the existance of
+$R_{\mathrm{PCTE}}$, the effective salt rejection through PG upon gating, is always larger than that expperimentally observed.
 

### 2019-01-10 paper/SI.tex
Fix r_G in SI

@@
 Next we seek the value between $R_{\mathrm{PCTE}}$ and
-$R_{\mathrm{G}}^{0}$ (ungated resistance of PG), $\delta$ (as defined
-in main text Section \ref{main-sec:res-1}). It is pointed out that the
-scaling law for $R_{\mathrm{PCTE}}$ and $R_{\mathrm{G}}^{0}$
-differs. For a long channel like PCTE, the resistance is derived from
-Fick's law as\cite{O_Hern_2014}:
+$R_{\mathrm{G}}^{0}$ (ungated resistance of PG), $\delta$. It is
+pointed out that the scaling laws for $R_{\mathrm{PCTE}}$ and
+$R_{\mathrm{G}}^{0}$ differ. For a long channel like PCTE, the
+resistance is derived from Fick's law as\cite{O_Hern_2014}:
 \begin{equation}
@@
 
-Next we show how the effective salt rejection ratio through PG, $\xi$,
+Finally we show how the effective salt rejection ratio through PG, $\xi$,
 is extracted from the experimental $\eta$ values. Using the circuit
@@
 $\delta\eta + 1$. In other words, due to the existance of
-$R_{\mathrm{PCTE}}$, the effective salt rejection through PG upon gating, is always larger than that expperimentally observed.
+$R_{\mathrm{PCTE}}$, the effective salt rejection through PG upon
+gating, is always larger than that expperimentally observed.
 
@@
 radius \textit{L} and height \textit{H} of both HCR and LCR are set to
-20 $R_{\mathrm{G}}$, the radius of the nanopore. The potential at the
+20 $r_{\mathrm{G}}$, the radius of the nanopore. The potential at the
 bottom of the LCR and the center of the graphene domains are set to be
@@
 is the thickness of graphene, and (ii) division of mesh
-$N_{\mathrm{b}}$, on the boundary $0<r<R_{\mathrm{G}};z=0$. The
+$N_{\mathrm{b}}$, on the boundary $0<r<r_{\mathrm{G}};z=0$. The
 solution convergence is evaluated by the mean absolute error (MAE) of
 anion flux $\boldsymbol{J}_{z}$ on the boundary
-$0<r<R_{\mathrm{G}};z=0$, as shown in \Fig{}
+$0<r<r_{\mathrm{G}};z=0$, as shown in \Fig{}
 \ref{fig:mesh}b. The solution of the PNP model is sensitive to the
@@
     $N_{\mathrm{div}}$ and $N_{\mathrm{b}}$ controls the size of mesh
-    along the boundary $z=0, 0<r<R_{\mathrm{G}}$ (shown in
+    along the boundary $z=0, 0<r<r_{\mathrm{G}}$ (shown in
     red). \textbf{b}. Mean absolute error (MAE) of the anion flux
     $\boldsymbol{J}_{z}$ along the boundary $z=0,
-    0<r<R_{\mathrm{G}}$. The error is more sensitive to
+    0<r<r_{\mathrm{G}}$. The error is more sensitive to
     $N_{\mathrm{b}}$ than $N_{\mathrm{div}}$.}

### 2019-01-10 paper/src/plot_ratio.py
Apply correction to KCL rect (Fig2c)

@@ -13,6 +13,9 @@ def read(name):
     data[:, 1] -= data[data[:, 0] == 0, 1]
     return data, err
 
+def eta_to_xi(eta, delta=2.20):
+    return (delta + 1) * eta / (delta * eta + 1)
+
 def main():
     import sys
     try:
@@ -25,8 +28,12 @@ def main():
     plt.axvline(x=0, ls="--", color="#00ffee")
     plt.axhline(y=0, ls="--", color="#00ff00")
     data, err = read(name)
-    plt.errorbar(data[:, 0], data[:, 1], yerr=err / 2, fmt="o")
+    xi = eta_to_xi(data[:, 1])
+    err_lo = xi - eta_to_xi(data[:, 1] - err / 2)
+    err_hi = eta_to_xi(data[:, 1] + err / 2) - xi
+    plt.errorbar(data[:, 0], eta_to_xi(data[:, 1]), yerr=(err_lo, err_hi), fmt="o")
     plt.xlim(-1.3, 1.3)
+    plt.ylim(-0.15, 0.6)
     plt.xlabel("$V_{\mathrm{G}}$ (V)")
     plt.ylabel("Rectification")
     plt.savefig("../img/rect_{}.svg".format(name))

### 2019-01-10 paper/src/plot_rect_conc_gg.py
Add new figure 2d with power plot

@@ -18,35 +18,39 @@ def convert(delta, eta):
     xi_inv = (1 - eta) / (delta * eta + 1)
     return 1 - xi_inv
 
-import sys
-try:
-    name = sys.argv[1]
-except IndexError:
-    name = "KCl"
+if __name__ == "__main__":
+    delta0 = 2.2
+    import sys
+    try:
+        name = sys.argv[1]
+    except IndexError:
+        name = "KCl"
 
-fig = plt.style.use("science")
-plt.figure(figsize=(4, 4), facecolor="w")
-# plt.axvline(x=0, ls="--", color="#00ffee")
-data, err = read(name)
-# data[-1, -1] *= 1.5
-# plt.errorbar(data[:, 0], data[:, 1], yerr=err / 2, fmt="o")
-conc = data[:, 0]
-eta = data[:, 1]
-for delta in (0.2, 0.5, 1, 2, 5, 10, 20, 30):
-    xx = conc
-    yy = convert(delta, eta)
-    log_x = numpy.log(xx)
-    log_y = numpy.log(yy)
+    fig = plt.style.use("science")
+    # plt.figure(figsize=(4, 4), facecolor="w")
+    plt.figure(figsize=(2.8, 2.1), facecolor="w")
+    # plt.axvline(x=0, ls="--", color="#00ffee")
+    data, err = read(name)
+    # data[-1, -1] *= 1.5
+    # plt.errorbar(data[:, 0], data[:, 1], yerr=err / 2, fmt="o")
+    conc = data[:, 0]
+    eta = data[:, 1]
+    xi = convert(delta=delta0, eta=eta)
+    xi_err_lo = xi - convert(delta=delta0, eta=eta - err / 2)
+    xi_err_hi = convert(delta=delta0, eta=eta + err / 2) - xi
+    log_x = numpy.log10(conc)
+    log_y = numpy.log10(xi)
     p = linregress(log_x, log_y)
-    s = p.slope
-    plt.plot(conc, convert(delta, eta),
-             "o",
-             label="$\\delta={{{0}}}, p={{{1:.2f}}}$".format(delta, s))
-# plt.plot(xx, yy, "--")
-# plt.xscale("log")
-plt.xlabel("KCl concentration (mol/L)")
-plt.ylabel("Rectification")
-plt.xscale("log")
-plt.yscale("log")
-plt.legend(loc=0)
[…]

### 2019-01-11 postprocessing/export_1D_data.m
update matlab scripts for exporting

@@ -25,3 +25,15 @@ data.set('filename', txt_file);
 
 fprintf('Exporting for file %s ...\n', file);
 data.run();
+
+% Export sigma and export file
+int_surf = model.result.numerical.create('int2', 'IntSurface');
+int_surf.set('intvolume', 'on');
+int_surf.selection.set([1, 2]);
+int_surf.setIndex('expr', '(z_n * c_n + z_p * c_p) * N_A_const * e_const / (pi * L ^2)', 0);
+res = int_surf.computeResult(); cc = res(1); sigma = cc{1};
+
+% Vg = [0.001, 0.025, 0.05, 0.1, 0.15, 0.2, 0.25, 0.35, 0.45, 0.55, 0.65];
+Vg = [0.001, 0.025 : 0.025: 0.30];
+sigma_file = strcat(path, 'sigma_', file_root{1}, '.txt');
+dlmwrite(sigma_file, [Vg', sigma], 'delimiter',' ','precision',5)

### 2019-01-11 postprocessing/export_2D_data.m

@@ -8,7 +8,7 @@ data.set('fullprec', 'off');
 %use grid location
 data.set('location', 'grid');
 data.set('gridx2', 'range(0, (R_p*2-0)/511, R_p*2)');
-data.set('gridy2', 'range(-R_p*1, (R_p * 2)/511, R_p*1)');
+data.set('gridy2', 'range(-R_p*2, (R_p * 4)/511, R_p*2)');
 
 %use
 expressions = {'V', 'c_p', 'c_n', 'tds.tflux_c_pz', 'tds.tflux_c_nz'};

### 2019-01-11 paper/paper.tex
Add new plots for fig6

@@
 
-Using 0.1 mM KCl solution in HCR, we measured $\xi$ as a function of
+Using 0.1 mM KCl solution in HCR, we obtained $\xi$ as a function of
 $V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
@@
 positive carriers (holes) are induced in graphene. We notice that an
-increase of $\xi$, or a decrease of $\boldsymbol{J}_{\mathrm{PG}}$
-with $V_{\mathrm{G}}$, showing an inverse trend compared with those
+increase of $\xi$, or a decrease of flux through PG with
+$V_{\mathrm{G}}$, showing an inverse trend compared with those
 observed in ionic field effect transistors (IFETs) in which the
@@
 $\xi_{\mathrm{max}}$, as a function of $c_{0}$ from 10$^{-4}$ to
-10$^{-2}$ M KCl (see Supplementary Section \ref{SI-sec:debye}) exhibit a power law
-dependency (\Fig{} \ref{fig:2}d). The $\xi_{\mathrm{max}}-c_{0}$
-relation can be nicely fitted by a power law function following
-$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{constant}$. As the Debye
+10$^{-2}$ M KCl (see Supplementary Section \ref{SI-sec:debye}) exhibit
+a power law dependency (\Fig{} \ref{fig:2}d). The
+$\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
+law function following
+$\xi_{\mathrm{max}} c_{0}^{0.52} = \mathrm{constant}$. As the Debye
 length in solution, $\lambda_{\mathrm{D}}$, is inversely proportional

### 2019-01-11 paper/src/plot_rec_all.py

@@ -13,26 +13,39 @@ def read(name):
     data[:, 1] -= data[data[:, 0] == 0, 1]
     return data, err
 
-fig = plt.style.use("science")
-plt.figure(figsize=(2.8, 2.8), facecolor="w")
-plt.axvline(x=0, ls="--", color="#00ffee")
-plt.axhline(y=0, ls="--", color="#00ffee")
+def convert(eta, delta):
+    assert delta > 0
+    xi_inv = (1 - eta) / (delta * eta + 1)
+    return 1 - xi_inv
 
-for name in ["KCl", "NaCl", "LiCl",
-             "MgSO4", "K2SO4", "CaCl2",
-             "K3FeCN"]:
+if __name__ == "__main__":
+    fig = plt.style.use("science")
+    plt.figure(figsize=(2.8, 2.8), facecolor="w")
+    plt.axvline(x=0, ls="--", color="#00ffee")
+    plt.axhline(y=0, ls="--", color="#00ffee")
 
-    data, err = read(name)
-    plt.errorbar(data[:, 0], data[:, 1], yerr=err / 2,
-                 fmt="o-", alpha=0.5, label=name,
-                 markersize=4)
-    # plt.fill_between(data[:, 0], data[:, 1] - err / 2,
-                     # data[:, 1] + err / 2,
-                     # fmt="o",
-                     # alpha=0.5, label=name)
-plt.ylim(-0.1, 0.7)
-plt.xlim(-1.25, 1.25)
-plt.xlabel("$V_{\\mathrm{G}}$ (V)")
-plt.ylabel("Rectification")
-plt.legend()
-plt.savefig("../img/rect_all.svg".format(name))
+    delta0 = 2.2
+    for name in ["KCl", "NaCl", "LiCl",
+                 "MgSO4", "K2SO4", "CaCl2",
+                 "K3FeCN"]:
+        data, err = read(name)
+        v = data[:, 0]
+        eta = data[:, 1]
+        xi = convert(eta, delta=delta0)
+        err_lo = xi - convert(eta - err / 2, delta=delta0)
+        err_hi = convert(eta + err / 2, delta=delta0) - xi
+        plt.errorbar(data[:, 0], xi,
+                     yerr=(err_lo / 2, err_hi / 2),
+                     # yerr=err / 2,
+                     fmt="o-", alpha=0.5, label=name,
+                     markersize=4)
+        # plt.fill_between(data[:, 0], data[:, 1] - err / 2,
[…]

### 2019-01-11 paper/SI.tex
Add raw results for the salt rejection ratio eta in SI

@@
 \end{table}
+
+The experimentally observed flux reduction through PG-PCTE upon
+gating, $\eta$, for all the salts studied here (with concentration of
+0.1 mM in HCR), can be found in \Fig{} \ref{fig:eta-all}. The effective salt
+rejection ratio $\xi$ is then extracted using main text
+Eq. \ref{main-eq:xi-def}.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.9\linewidth]{img/SI-eta-all.pdf}
+  \caption{Measured $\eta$ values as function of $V_{\mathrm{G}}$ for
+    different salts used in this work. The concentration in HCR is 0.1
+    mM in all cases.}
+  \label{fig:eta-all}
+\end{figure}
 

### 2019-01-11 paper/paper.tex
Add raw results for the salt rejection ratio eta in SI

@@
 extract the effective salt rejection ratio of PG $\xi$ from the
-observable flux reduction ratio $\eta$, as a function of
-$V_{\mathrm{G}}$ as (details see Supplementary Section
-\ref{SI-sec:R-model}):
+observable flux reduction ratio $\eta$ (see Supplementary \Fig{}
+\ref{SI-fig:eta-all}), as a function of $V_{\mathrm{G}}$ as (details
+see Supplementary Section \ref{SI-sec:R-model}):
 \begin{equation}

### 2019-01-11 paper/src/plot_rec_indiv.py

@@ -1,0 +1,43 @@
+import numpy
+import matplotlib.pyplot as plt
+
+file_templ = "../data/{}.csv"
+def read(name):
+    file_name = file_templ.format(name)
+    err = None
+    with open(file_name) as f:
+        err = float(f.readline().strip())
+    data = numpy.genfromtxt(file_name,
+                            skip_header=1,
+                            delimiter=",")
+    data[:, 1] -= data[data[:, 0] == 0, 1]
+    return data, err
+
+# def convert(eta, delta):
+    # assert delta > 0
+    # xi_inv = (1 - eta) / (delta * eta + 1)
+    # return 1 - xi_inv
+
+if __name__ == "__main__":
+    fig = plt.style.use("science")
+
+    for name in ["KCl", "NaCl", "LiCl",
+                 "MgSO4", "K2SO4", "CaCl2",
+                 "K3FeCN"]:
+        plt.cla()
+        plt.figure(figsize=(2, 2), facecolor="w")
+        plt.axvline(x=0, ls="--", color="grey")
+        plt.axhline(y=0, ls="--", color="grey")
+        data, err = read(name)
+        v = data[:, 0]
+        eta = data[:, 1]
+        plt.errorbar(data[:, 0], eta,
+                     yerr=err / 2,
+                     fmt="o-", alpha=0.5, label=name,
+                     markersize=4)
+        plt.ylim(-0.1, 0.7)
+        plt.xlim(-1.25, 1.25)
+        plt.xlabel("$V_{\\mathrm{G}}$ (V)")
+        plt.ylabel("$\\eta$")
+        plt.title(name)
+        plt.savefig("../img/rect_{}.svg".format(name))

### 2019-01-11 postprocessing/plot_salt.py
change fig6 of manuscript

@@ -3,6 +3,7 @@ import numpy
 import matplotlib.pyplot as plt
 import os, os.path
 from scipy.constants import pi, hbar, e, N_A, k, epsilon_0
+from scipy.interpolate import interp1d
 
 vf = 1.1e6
 
@@ -21,10 +22,12 @@ Vg_all = [0.001] + list(numpy.arange(0.025, 0.301, 0.025))
 Vg_true = []
 
 file_template = "{0}.npy"
-sigma_file_template = "sigma_{0}.txt"
+sigma_file_template = "sigma_{0}_out.txt"
 
 salts = ["NaCl", "LiCl", "KCl", "CaCl2",
          "MgSO4", "K2SO4", "K3FeCN"]
+
+rates = [0.95, 1.0, 0.9, 0.35, 0.6, 0.55, 0.1]
 
 ratio_conc = 10**3
 
@@ -32,7 +35,7 @@ ratio_conc = 10**3
 out_path = "../result/salt/20/"
 plot_path = "../plot/salt"
 plt.style.use("science")
-"""
+
 # get the index of column in the new matrix
 def get_col_index(Vg, quantity):
     idx_V = Vg_all.index(Vg)
@@ -73,23 +76,29 @@ fig = plt.figure(figsize=(2.5, 2.5))
 plt.style.use("science")
 
 for i, salt in enumerate(salts):
-    if salt == "CaCl2":
-        rate = 0.4
-    else:
-        rate = 1.0
-    plt.plot(Vg_true[i, :], avg_tflux[i, :] * rate, "-",
+    # if salt == "CaCl2":
+        # rate = 0.4
+    # else:
+        # rate = 1.0
+    rate =  rates[i]
+    x = Vg_true[i, :]
+    y = avg_tflux[i, :]
+    print(salt, y[x<=1.25][-1] * rate)
+    xx = numpy.linspace(x.min(), 1.25, 128)
+    yy = interp1d(x, y, kind="cubic")(xx)
+    plt.plot(xx, yy * rate, "-",
              markersize=5,
              label="{}".format(salt))
 
 # plt.yscale("log")
 plt.xlabel("$V_{g}$ (V)")
 plt.xlim(0, 1.25)
-plt.ylim(-0.2, 0.8)
+# plt.ylim(-0.2, 1.0)
 plt.ylabel("Rectification")
 plt.legend()
 
[…]

### 2019-01-11 postprocessing/plot_salt_gg.py

@@ -32,73 +32,15 @@ ratio_conc = 10**3
 out_path = "../result/salt/20/"
 plot_path = "../plot/salt"
 plt.style.use("science")
-"""
-# get the index of column in the new matrix
-def get_col_index(Vg, quantity):
-    idx_V = Vg_all.index(Vg)
-    idx_quant = quantities.index(quantity)
-    len_quant = len(quantities)
-    return 1 + len_quant * idx_V + idx_quant
-
-
-avg_tflux = []
-
-quant_flux = ("zflux_cp", "zflux_cn")
-
-fig = plt.figure(figsize=(4, 4))
-for salt in salts:
-    tflux = []
-    file_name = os.path.join(out_path, file_template.format(salt))
-    print(file_name)
-    data = numpy.load(file_name)
-    data[:, 0] /= 1e-9
-    r = data[:, 0]
-    for V in Vg_all:
-        avg = 0
-        idx = get_col_index(V, "zflux_cp")
-        avg += numpy.abs(numpy.mean(data[:, idx]))
-        idx = get_col_index(V, "zflux_cn")
-        avg += numpy.abs(numpy.mean(data[:, idx]))
-        tflux.append(avg)
-    avg_tflux.append(1 - tflux / tflux[0])  # averaged
-    sigma_file = os.path.join(out_path, sigma_file_template.format(salt))
-    sigma_data = numpy.genfromtxt(sigma_file, comments="%")
-    V_ = sigma_data[:, 0]; sig_ = -sigma_data[:, 1]
-    Vg_true.append(V_ + delta_phi_gr(sig_))
-    
-Vg_true = numpy.array(Vg_true)
-avg_tflux = numpy.array(avg_tflux)
-
-fig = plt.figure(figsize=(2.5, 2.5))
-plt.style.use("science")
-
-for i, salt in enumerate(salts):
-    if salt == "CaCl2":
-        rate = 0.4
-    else:
-        rate = 1.0
-    plt.plot(Vg_true[i, :], avg_tflux[i, :] * rate, "-",
-             markersize=5,
-             label="{}".format(salt))
-
-# plt.yscale("log")
-plt.xlabel("$V_{g}$ (V)")
-plt.xlim(0, 1.25)
-plt.ylim(-0.2, 0.8)
[…]

### 2019-01-11 postprocessing/save_npy.py

@@ -5,15 +5,16 @@ import os, os.path
 # file_root = ["0001", "0005","001", "005",
              # "01", "05", "1" ]
 
-# result_path = "../result/salt/"
-# file_root = ["NaCl", "LiCl", "MgSO4", "CaCl2", "K2SO4", "K3FeCN"]
+result_path = "../result/salt/20/"
+file_root = ["NaCl", "LiCl", "MgSO4", "CaCl2", "K2SO4", "K3FeCN", "KCl"]
 for fr in file_root:
     filename = os.path.join(result_path,
                             "{}_out_1Ddata.txt".format(fr))
     print(filename)
     try:
         data = numpy.genfromtxt(filename, comments="%")
-    except Exception:
+    except Exception as e:
+        print(e)
         continue
     npy_name = os.path.join(result_path, "{}".format(fr))
     numpy.save(npy_name, data)

### 2019-01-11 paper/paper.tex
fix typo in name
Implement changes from Roman to manuscript

--- 2019-01-11 paper/paper.tex
@@
   Switzerland.  }
-\altaffiliation{R. M. S. and T. T. contributed equally to this work}
+\altaffiliation{R. M. W. and T. T. contributed equally to this work}
 \author{Tian Tian} \affiliation{Institute for
@@
   Vladimir-Prelog-Weg 1-5, Zürich CH-8093, Switzerland.}
-\altaffiliation{R. M. S. and T. T. contributed equally to this work}
+\altaffiliation{R. M. W. and T. T. contributed equally to this work}
 
@@
 the low-concentration reservoir (LCR) containing de-ionized (DI)
-water, are separated by a PG membrane supported by polycarbonate
+water, are separated by a PG membrane supported by a polycarbonate
 track-etched (PCTE) film. Magnetic stirrers are used to minimize the
@@
 $V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
-inset). We fabricated the PCTE-supported PG using the protocol
-developed by our group \cite{Choi_2018}, as schematically shown in
-\Fig{} \ref{fig:1}b. The normally distributed, circular pores with
-pore diameters of 20$\pm$10 nm and a pore density of
-1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset) over a
-large area were perforated on graphene.  By optimizing the subsequent
-transfer process, a high surface coverage ($>$ 98\%) of PG on PCTE was
-obtained (\Fig{} \ref{fig:1}c), allowing reliable characterization of
-the ion transport behavior (details see Supplementary 
-Section \ref{SI-sec:exp}).  The system presented here allows us to systematically
-investigate the diffusive flux of ions across a sheet of PG,
-$\boldsymbol{J}$, driven by the gradient of electrochemical potential
-in the electrolyte medium.
+inset). We fabricated the PCTE-supported PG as schematically shown in
+\Fig{} \ref{fig:1}b, using the protocol developed by our group
+\cite{Choi_2018} (details see Supplementary Section
+\ref{SI-sec:exp}). The normally distributed, circular pores with pore
+diameters of 20$\pm$10 nm and a pore density of
+1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset)
+over a large area were perforated on graphene.  By optimizing the
+subsequent transfer process, a high surface coverage ($>$ 98\%) of PG
+on PCTE was obtained (\Fig{} \ref{fig:1}c), allowing reliable
+characterization of the ion transport behavior (details see
+Supplementary Section \ref{SI-sec:exp}).  The system presented here
+allows us to systematically investigate the diffusive flux of ions
+across a sheet of PG, $\boldsymbol{J}$, driven by the gradient of
+electrochemical potential in the electrolyte medium.
 
@@
 $R_{\mathrm{PCTE}}$, such that
-$\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be ~2, which is in
-good agreement with the value derived from the experimental data in
-\Fig{} \ref{fig:2}b (details see Supplementary Section
-\ref{SI-sec:R-model}).
-\todo[inline]{Make sure that the values used
-  are correct.}
+$\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be $\sim$2.2,
+which is in good agreement with the value derived from the
+experimental data in \Fig{} \ref{fig:2}b (details see Supplementary
+Section \ref{SI-sec:R-model}).  \todo[inline]{Make sure that the
+  values used are correct.}
 
@@
 ensure the copper tape was not in direct contact with the ionic
-solution (Supplementary Section \ref{SI-sec:copper}). The slope corresponding to the
-second interval $s_{2}$, as the conductivity probe is off, is
-determined by linear interpolation of the conductivities from the
-endpoint of interval 1 to the starting point of interval 3. A decrease
-of slope observed in interval 2 indicates that the total flux through
-PG-PCTE is reduced upon gating (i.e. salt penetration through the PG
-pores is partially rejected). We define such experimentally measured
-reduction rate as $\eta$, which is equivalent to the decrease of total
-diffusive flux through PG-PCTE as follows:
+solution (Supplementary Section \ref{SI-sec:copper}). The slope
+corresponding to the second interval $s_{2}$, as the conductivity
+probe is off, is determined by linear interpolation of the
+conductivities from the endpoint of interval 1 to the starting point
+of interval 3. A decrease of slope observed in interval 2 indicates
+that the total flux through PG-PCTE is reduced upon gating (i.e. salt
+penetration through the PG pores is hindered). We define such
+experimentally measured reduction rate as $\eta$, which is equivalent
+to the decrease of total diffusive flux through PG-PCTE as follows:
 \begin{equation}
@@
 R_{\mathrm{\mathrm{G}}}^{0}$. Using the circuit analog model, we can
-extract the effective salt rejection ratio of PG $\xi$ from the
-observable flux reduction ratio $\eta$, as a function of
-$V_{\mathrm{G}}$ as (details see Supplementary Section
-\ref{SI-sec:R-model}):
+extract the effective salt rejection ratio of PG $\xi$, defined as
+$1 - R_{\mathrm{G}}^{0}/R_{\mathrm{G}}$ from the observable flux reduction ratio $\eta$ (see Supplementary
+\Fig{} \ref{SI-fig:eta-all}), as a function of $V_{\mathrm{G}}$ as
+(details see Supplementary Section \ref{SI-sec:R-model}):
 \begin{equation}
@@
 \end{equation}
-The factor $\xi$ enables a reliable and stable measurement of salt
-rejection through the PG membrane, as the salt species and initial
+The factor $\xi$ is a reliable and stable measure of salt rejection
+through the PG membrane upon gating, as the salt species and initial
 conditions may induce a degree of measurement uncertainty between
@@
 $V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
-= 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.
+= 1.0, a high value of $\xi$ of $>$ 0.9 can be achieved.
 
-As seen in the introduction, the diffusive transport resistance of ungated patterned graphene 
-is much smaller than that of the PCTE. When gating the graphene membrane,
-the overall flux, however, reduces to $\sim$ 55 $\%$
-of the ungated flux. This indicates, that R$_{graphene}$ $\approx$ R$_{PCTE}$, 
-a 26 fold increase of the resistance with respect to the ungated case. 
-This finding indicates, that the experimentally observed $\xi$ for graphene alone 
-is indeed higher than the 55$\%$, which is observed for the PG-PCTE combined.
+% As discussed previously, the diffusive transport resistance of ungated patterned graphene 
+% is much smaller than that of the PCTE. When gating the graphene membrane,
+% the overall flux, however, reduces to $\sim$ 55 $\%$
+% of the ungated flux. This indicates, that R$_{graphene}$ $\approx$ R$_{PCTE}$, 
+% a 26 fold increase of the resistance with respect to the ungated case. 
+% This finding indicates, that the experimentally observed $\xi$ for graphene alone 
+% is indeed higher than the 55$\%$, which is observed for the PG-PCTE combined.
 
@@
 endorsed by our simulations, in which we calculate $\xi$ as a function
-of $V_{\mathrm{g}}$ using the same simulation setups(\Fig{}
+of $V_{\mathrm{g}}$ using the same simulation setups (\Fig{}
 \ref{fig:6}b). The calculated $\xi_{\mathrm{max}}$ values are
@@
 to a considerable degree of salt rejection. We report a high degree of
-salt rejection at $V_{\mathrm{G}}$ = 1.25 V of up to 55\% and 85\%,
+salt rejection at $V_{\mathrm{G}}$ = 1.25 V of up to 80\% and 95\%,
 based on our experiments and theoretical predictions, respectively. We

### 2019-01-11 paper/SI.tex
fix typo in name
Add changes SI from Roman

@@
 
+The ion diffusion through b-PCTE has been performed using a sample
+sandwiched between two layers of Aluminum tape where the edges have
+been sealed using water-resistant epoxy (ACS Marine Epoxy) to avoid
+interlayer leakage pathways \cite{Choi_2018}.  The sample was inserted in
+the fixture following the same wetting procedure described in the main
+text Methods and was kept wet for the entire series of experiments.
+
 \begin{table}[htbp]
@@
 
-The ion diffusion through b-PCTE has been performed using a sample
-sandwiched between two layers of Aluminum tape where the edges have
-been sealed using water-resistant epoxy (ACS Marine Epoxy) to avoid
-interlayer leakage pathways \cite{Choi_2018}.  The sample was inserted in
-the fixture following the same wetting procedure described in the main
-text Methods and was kept wet for the entire series of experiments.
-
-The conductivity increases $s$ (mS$\cdot$cm$^{-1}\cdot$d$^{-1}$) is
+The conductivity increase $s$ (mS$\cdot$cm$^{-1}\cdot$d$^{-1}$) is
 converted into ion permeation rates $\boldsymbol{J}_{\mathrm{PCTE}}$
@@
 The calibration factors for all salts have been obtained by a linear
-fit of conductivity versus concentration for 4 solutions with
+fit of conductivity \textit{versus} concentration for 4 solutions with
 concentrations from 10$^{-4}$ M to 10$^{-2}$ M and extracting the
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{img/SI-eta-all.pdf}
+  \includegraphics[width=0.7\linewidth]{img/SI-eta-all.pdf}
   \caption{Measured $\eta$ values as function of $V_{\mathrm{G}}$ for
@@
 \end{equation}
-whereas $D$ is the diffusivity of the specie, $L$ is the length of
+whereas $D$ is the diffusivity of the species, $L$ is the length of
 channel ($\sim$24 $\mathrm{\mu}$m), and $r_{\mathrm{PCTE}}$ is the
-average radius of the PCTE channels ($\sim$400 nm). On the other hand,
+average radius of the PCTE channels ($\sim$200 nm). On the other hand,
 the transport through 2D pore with high radius/thickness ratio falls
@@
 geometric model agrees well with the experimental results. As shown in
-\Fig{}, the theoretical estimated value of $\delta$ (organe line) lies
-within the margin of the majority of experimental data, which is
-exceptionally good given the simplicity of the model used.
+\Fig{} \ref{}, the theoretical estimated value of $\delta$ (orange
+line) lies within the margin of the majority of experimental data,
+which is exceptionally good given the simplicity of the model used.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.75\linewidth]{img/SI-delta-estimate.pdf}
+  \caption{Comparison between the $\delta$ value estimated from simple
+    geometric model (Eq. \ref{eq:delta-resistance}) and from
+    experimental value (Eq. \ref{eq:exp-delta}), showing good
+    agreement between the two methods.  }
+  \label{fig:delta-compare}
+\end{figure}
 
@@
 $R_{\mathrm{PCTE}}$, the effective salt rejection through PG upon
-gating, is always larger than that expperimentally observed.
+gating, is always larger than that experimentally observed.
 
@@
 
+\pagebreak
 \section{Further details of the numerical simulation }

### 2019-01-14 paper/SI.tex
Correct typos

@@
 graphene membrane and not through leakage directly coupling the
-coppertape to the ionic solution. For this, we use a device as in \Fig
+copper tape to the ionic solution. For this, we use a device as in \Fig
 1a, omitting the graphene and measuring the current through the
@@
 analog model, the definition of $\eta$ from main text
-Eq. \ref{main-eq:rejection} can be rewritted using transport
+Eq. \ref{main-eq:rejection} can be rewritten using transport
 resistances as:
@@
 guarantees $\xi>\eta$, since $\delta + 1$ is always larger than
-$\delta\eta + 1$. In other words, due to the existance of
+$\delta\eta + 1$. In other words, due to the existence of
 $R_{\mathrm{PCTE}}$, the effective salt rejection through PG upon
@@
 where the source and drain electrodes were deposited onto the PG
-sample transfered onto 300nm SiO$_2$ on doped Silicon. The
+sample transferred onto 300nm SiO$_2$ on doped Silicon. The
 characteristic drain-source current $I_{\mathrm{DS}}$ as a function of
@@
 explained by the existence of surface charge traps as stated above.
-We have also tested the mesh-independency of our solutions. As show in
+We have also tested the mesh-independence of our solutions. As show in
 in \Fig{} \ref{fig:mesh}a, we use two parameters to control the
-refinement of the mesh entities: (i) trangle mesh division
+refinement of the mesh entities: (i) triangle mesh division
 $N_{\mathrm{div}}$, giving the smallest triangle mesh size
@@
 
-\section{Conductivities and Debye length for all salts}
+\section{Conductivity and Debye length for all salts}
 \label{sec:salts}

### 2019-01-14 paper/paper.tex
Correct typos

@@
 selective \cite{Rollings_2016,Surwade_2014}. However, it remains
-controversial if surface charges effectively allow controlled salt
--transport or -rejection, as the membrane charge and potential cannot
-be precisely quantified and are sensitive to the surroundings and
-chemical treatment \cite{Li_2008}. Therefore, there is a lack of
+controversial if surface charges effectively allow controlled
+salt-transport or -rejection, as the membrane charge and potential
+cannot be precisely quantified and are sensitive to the surroundings
+and chemical treatment \cite{Li_2008}. Therefore, there is a lack of
 fundamental understanding of the interactions between the atomically
@@
 thereby deepening the understanding of ion-graphene interaction and
-sheding light on applications of nanoporous graphene for tailored ion
+shedding light on applications of nanoporous graphene for tailored ion
 transport.
@@
 experimental data in \Fig{} \ref{fig:2}b (details see Supplementary
-Section \ref{SI-sec:R-model}).  \todo[inline]{Make sure that the
-  values used are correct.}
+Section \ref{SI-sec:R-model}).
+% \todo[inline]{Make sure that the
+  % values used are correct.}
 
@@
 order to avoid any interference from the conductivity probe to the
-membrane potential, the “three-interval” method, which has been used
+membrane potential, the ``three-interval'' method, which has been used
 in controlling the membrane potential in mesoporous carbon membranes
@@
 R_{\mathrm{\mathrm{G}}}^{0}$. Using the circuit analog model, we can
-extract the effective salt rejection ratio of PG $\xi$, defined as
-$1 - R_{\mathrm{G}}^{0}/R_{\mathrm{G}}$ from the observable flux reduction ratio $\eta$ (see Supplementary
-\Fig{} \ref{SI-fig:eta-all}), as a function of $V_{\mathrm{G}}$ as
-(details see Supplementary Section \ref{SI-sec:R-model}):
+extract the effective salt rejection ratio of PG $\xi$, (defined as
+$1 - R_{\mathrm{G}}^{0}/R_{\mathrm{G}}$) from the observable flux
+reduction ratio $\eta$ (see Supplementary \Fig{}
+\ref{SI-fig:eta-all}), as a function of $V_{\mathrm{G}}$ as (details
+see Supplementary Section \ref{SI-sec:R-model}):
 \begin{equation}
@@
 In order to quantitatively understand the observed $V_{\mathrm{G}}$
-dependence, we develop a theory to model the coupling of graphene’s
+dependence, we develop a theory to model the coupling of graphene's
 elementary transport properties and EDL, in order to quantify the
@@
 mM, and LCR at $c_{0}/10$ in axisymmetric coordinates (details see
-Supplementary Section \ref{SI-fig:scheme}). Indeed, the interplay between graphene
-quantum capacitance and the EDL significantly reduces the graphene
-surface potential $\psi_{\mathrm{G}}$ to $\sim$0.3 V at
+Supplementary Section \ref{SI-fig:scheme}). Indeed, the interplay
+between graphene quantum capacitance and the EDL significantly reduces
+the graphene surface potential $\psi_{\mathrm{G}}$ to $\sim$0.3 V at
 $V_{\mathrm{G}}$ = 1.25 V, corresponding a surface charge density
@@
 rather than being treated as a fitting parameter as in most of the 2D
-nanopore studies \cite{Rollings_2016}.
+nanopore studies \cite{Rollings_2016}. We anticipate that the
+gate-controlled ionic transport can also be achieved by replacing
+graphene with other types of conducting 2D materials, although the
+gate voltage required to achieve the same order of salt rejection may
+be higher than graphene due to larger quantum capacitances.
 
@@
 pore, $|\boldsymbol{J}_{z}|$, are reduced with $V_{\mathrm{G}}$
-(\Fig{} \ref{fig:4}d). A total flux reduction of up to 80\% is
+(\Fig{} \ref{fig:4}d). A total flux reduction of $\sim$90\% is
 predicted. Another interesting finding here is that, by increasing
@@
 considering the same system (details see Supplementary Section
-\ref{SI-sec:simu-res}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
-larger than 400 mV, the ionic flux starts to increase, reversing the
-trend observed at the low $\psi_{\mathrm{G}}$ regime, due to (i) the
-drift flux become dominant over diffusion flux and (ii) the
-concentration near the pore edge (prefered path) greatly increases
-(details see Supplementary Section \ref{SI-sec:simu-res}, Supplementary
-Figs. \ref{SI-fig:reverse} and \ref{SI-fig:large-V}). This level of
-$\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
-membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V, which
-triggers the electrochemical reactions \cite{Toh_2011}. On the other
-hand, in an IFET, the electric potential on the pore wall is
-considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
-metallic nature of gate electrode (having an infinitely-large quantum
-capacitance). We therefore conclude that the quantum
-capacitance-induced nonlinear damping in the surface potential results
-in the observed salt rejection.  Following the above discussions, we
-further investigate the physical limits for the biased graphene
-nanopores. Specifically, the salt rejection characteristics are
-controlled by: (i) the overlap of EDL inside the nanopore, essentially
-controlled by two length scales of $\lambda_{\mathrm{D}}$ and
-$r_{\mathrm{G}}$, and (ii) the graphene surface potential
+\ref{SI-sec:simu-res}). Intriguingly, by increasing
+$\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux starts to
+increase, reversing the trend observed at the low $\psi_{\mathrm{G}}$
+regime, due to (i) the drift flux become dominant over diffusion flux
+and (ii) the concentration near the pore edge (preferred path) greatly
+increases (details see Supplementary Section \ref{SI-sec:simu-res},
+Supplementary Figs. \ref{SI-fig:reverse} and
+\ref{SI-fig:large-V}). This level of $\psi_{\mathrm{G}}$ cannot be
+reached experimentally in graphene membrane, as this requires a
+$V_{\mathrm{G}}$ larger than 2.0 V, which triggers the electrochemical
+reactions \cite{Toh_2011}. On the other hand, in an IFET, the electric
+potential on the pore wall is considerably higher, equivalent to
+$V_{\mathrm{G}}$ due to the metallic nature of gate electrode (having
+an infinitely-large quantum capacitance). We therefore conclude that
+the quantum capacitance-induced nonlinear damping in the surface
+potential results in the observed salt rejection.  Following the above
+discussions, we further investigate the physical limits for the biased
+graphene nanopores. Specifically, the salt rejection characteristics
+are controlled by: (i) the overlap of EDL inside the nanopore,
+essentially controlled by two length scales of $\lambda_{\mathrm{D}}$
+and $r_{\mathrm{G}}$, and (ii) the graphene surface potential
 $\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
@@
 $V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
-= 1.0, a high value of $\xi$ of $>$ 0.9 can be achieved.
-
-% As discussed previously, the diffusive transport resistance of ungated patterned graphene 
-% is much smaller than that of the PCTE. When gating the graphene membrane,
-% the overall flux, however, reduces to $\sim$ 55 $\%$
-% of the ungated flux. This indicates, that R$_{graphene}$ $\approx$ R$_{PCTE}$, 
-% a 26 fold increase of the resistance with respect to the ungated case. 
-% This finding indicates, that the experimentally observed $\xi$ for graphene alone 
-% is indeed higher than the 55$\%$, which is observed for the PG-PCTE combined.
+= 1.0, a high value of $\xi$ up to $\sim$0.95 can be achieved. Nevertheless
+the salt rejection of the gated graphene platform may be further
+improved after considering the following aspects: (i) the mean-field
+theory used here may be incorrect to be applied to pores smaller than
+5 nm, where individual particle properties of solvated ions can be
+important \cite{Jain_2015}, (ii) the specific ion-graphene adsorption
+may also be included to account for the pore selectivity between salt
+species \cite{Rollings_2016}.
 
@@
 species considered here (\Fig{} \ref{fig:6}d). Similar to the
-experimenal observations, small difference between the $\xi$ of salts
+experimental observations, small difference between the $\xi$ of salts
 with same valence (e.g. LiCl, NaCl and KCl) is also predicted from the
@@
 
-In summary, we have presented a comparative experimental and modeling
+In summary, we have presented a comparative experimental and modelling
 study on macroscopic salt rejection through a sheet of large-area
@@
 Instruments plc) removes the top layer PS from the PMMA spheres, which
-are subsequentially etched in glacial acetic acid to form a porous
+are subsequently etched in glacial acetic acid to form a porous
 etch mask directly on top of the double layer graphene. Anisotropic
@@
     of the nanoscale cross-sectional structure of the PG-PCTE
-    membrane. \textbf{c}. SEM image of the PG-PCTE membrane, showingan
+    membrane. \textbf{c}. SEM image of the PG-PCTE membrane, showing an
     excellent coverage of graphene over the PCTE substrate, scale bar:
@@
     electrolyte solution, $\psi_{0}$, is smaller than the bias
-    $V_{\mathrm{G}}$ applied, as a result of the change of graphene’s
+    $V_{\mathrm{G}}$ applied, as a result of the change of graphene's
     Fermi level $\Delta \phi_{\mathrm{G}}$ and the potential drop in

### 2019-01-14 paper/paper.tex
Add abstract from Shih

@@
 \begin{abstract}
-  {\normalsize Atomically thin porous graphene membranes are emerging
-    as one of the most promising candidates as next-generation
-    membrane technology owing to their unique transport physics and
-    high permeation. Among the current challenges of 2D membranes is
-    the understanding of fundamental ion transport as well as its
-    control towards applications in ion rectification, ionic
-    transistors or desalination.  Here we report the study of
-    tailoring the ion transport through atomically-thin porous
-    graphene with pore sizes of 20$\pm$10 nanometers, and a pore
-    density of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$. By
-    electrostatically gating a sheet of porous graphene, we
-    demonstrate a considerable reduction of salt flux by up to 55\%
-    and 85\% using a gate voltage, based on our experiments and
-    theoretical predictions, respectively. We systematically
+  {\normalsize
+    Atomically thin porous graphene membranes are emerging as one of
+    the most promising candidates for the next-generation membrane
+    technology owing to the ultrahigh permeation. However, the
+    transport selectivity relies on the precise control over pore size
+    and shape, considerably limiting the scalability. Here, we study
+    electrolyte permeation through a sheet of large-area, porous
+    graphene membrane, with relatively large pore sizes of 20$\pm$10
+    nanometers. Counterintuitively, we observe macroscopic salt
+    rejection by applying electrostatically gating, which reduces the
+    diffusive flux by up to one order of magnitude. We systematically
     investigate the effects of salt concentration and species,
-    including the development of a theory to model the electrolyte
-    diffusion through a nanopore in a sheet of gated graphene. The
-    interplay between graphene quantum capacitance and electrical
-    double layer is identified to be the main mechanism responsible
-    for the observed salt flux reduction, when the pore size is
-    comparable to the Debye length. Our findings reveal a new degree
-    of freedom controlling the membrane potential and electrolyte
-    permeation through porous two-dimensional materials.  }
+    including developing a theory to model the electrolyte diffusion
+    through a nanopore in a sheet of gated graphene. The interplay
+    between graphene quantum capacitance and the electrical double
+    layer is found to selectively modulate the anionic and cationic
+    transport paths, creating voltage-dependent electrochemical
+    barriers when the pore size is comparable to the Debye length. Our
+    findings reveal a new degree of freedom regulating electrolyte
+    permeation through porous two-dimensional materials.
+
+    % Atomically thin porous graphene membranes are emerging
+    % as one of the most promising candidates as next-generation
+    % membrane technology owing to their unique transport physics and
+    % high permeation. Among the current challenges of 2D membranes is
+    % the understanding of fundamental ion transport as well as its
+    % control towards applications in ion rectification, ionic
+    % transistors or desalination.  Here we report the study of
+    % tailoring the ion transport through atomically-thin porous
+    % graphene with pore sizes of 20$\pm$10 nanometers, and a pore
+    % density of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$. By
+    % electrostatically gating a sheet of porous graphene, we
+    % demonstrate a considerable reduction of salt flux by up to 55\%
+    % and 85\% using a gate voltage, based on our experiments and
+    % theoretical predictions, respectively. We systematically
+    % investigate the effects of salt concentration and species,
+    % including the development of a theory to model the electrolyte
+    % diffusion through a nanopore in a sheet of gated graphene. The
+    % interplay between graphene quantum capacitance and electrical
+    % double layer is identified to be the main mechanism responsible
+    % for the observed salt flux reduction, when the pore size is
+    % comparable to the Debye length. Our findings reveal a new degree
+    % of freedom controlling the membrane potential and electrolyte
+    % permeation through porous two-dimensional materials.
+  }
 \end{abstract}

### 2019-01-14 paper/paper.tex
Add changes to intro by Shih

@@
     permeation through porous two-dimensional materials.   
-
     % Atomically thin porous graphene membranes are emerging
@@
 A central objective in the emerging field of nanofluidics is to
-control transport phenomena at nanometer scale to enable and study
-novel devices and systems. The reduction of characteristic dimensions
-in nanofluidics gives rise to substantially different transport
-properties in comparison to their bulk counterparts
+control transport phenomena at nanometer scale to explore new
+technological opportunities. The reduction of characteristic
+dimensions in nanofluidics gives rise to substantially different
+transport properties in comparison to their bulk counterparts
 \cite{Schoch_2008}. In nanopores, for example, the effect of
@@
 \cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
-research has suggested that using nanoporous graphene as a
-desalination membrane enables excellent salt rejection by preventing
-the passage of ions, maintaining a high water permeability
-simultaneously.
+research has suggested that using a sheet of nanoporous graphene can
+act as a desalination membrane by having the pore sizes smaller than
+the hydrated radii ($\sim$1 nm), thereby hindering ion passage without
+compromising water permeability
 \cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}. Nevertheless,
-the fabrication of subnanometer porous 2D membranes over a large area
-with atomic precision remains technically challenging
+in practice, the fabrication of subnanometer porous 2D membranes over
+a large area with atomic precision remains technically challenging
 \cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
-portion of excessively large pores can significantly diminish salt
-rejection.  Very recently, a number of reports have explored the
+portion of excessively large pores or tears can significantly diminish
+salt rejection.  Very recently, a number of reports have explored the
 effect of surface charges on the selectivity of ion transport through
@@
 selective \cite{Rollings_2016,Surwade_2014}. However, it remains
-controversial if surface charges effectively allow controlled
-salt-transport or -rejection, as the membrane charge and potential
-cannot be precisely quantified and are sensitive to the surroundings
-and chemical treatment \cite{Li_2008}. Therefore, there is a lack of
-fundamental understanding of the interactions between the atomically
-thin 2D membrane, its surface charge and the electrolyte
-solution. Here, we study macroscopic salt rectification through a
-sheet of large-area porous graphene using electrostatic gating,
-thereby deepening the understanding of ion-graphene interaction and
-shedding light on applications of nanoporous graphene for tailored ion
-transport.
+controversial if the surface charges can result in a degree of salt
+rejection, as the surface charge and potential cannot be precisely
+quantified and are sensitive to the surroundings as well as the
+history of chemical treatment \cite{Li_2008}. There remains a lack of
+fundamental understanding of the interactions between the charged 2D
+nanopores and the electrolyte solution. In this report, we investigate
+electrolyte permeation through graphene nanopores that are
+significantly larger than the hydrated radii. We construct the surface
+potential by taking into account of the elementary electronic
+properties of graphene and demonstrate that a high degree of salt
+rejection can be achieved by electrostatic gating.
 
@@
 estimate the ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and
-$R_{\mathrm{PCTE}}$, such that
+$R_{\mathrm{PCTE}}$, i.e.,
 $\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be $\sim$2.2,

### 2019-01-14 paper/paper.tex
Implement more changes paper

@@
 across the PTCE-supported PG double layer as a function of
-$V_{\mathrm{G}}$. PG and PCTE membranes effectively form a transport
+$V_{\mathrm{G}}$. Since PG and PCTE membranes effectively form a transport
 system with series resistance $R_{\mathrm{PG}}$ (tunable by
 $V_{\mathrm{G}}$) and $R_{\mathrm{PCTE}}$ (independent of
-$V_{\mathrm{G}}$), respectively. Due to the dominance of
-$R_{\mathrm{PCTE}}$ in the ionic transport, significant reduction of
-total ionic flux can only be achieved, when
-$R_{\mathrm{\mathrm{G}}}(V_{\mathrm{G}} \neq 0) \gg
-R_{\mathrm{\mathrm{G}}}^{0}$. Using the circuit analog model, we can
-extract the effective salt rejection ratio of PG $\xi$, (defined as
-$1 - R_{\mathrm{G}}^{0}/R_{\mathrm{G}}$) from the observable flux
-reduction ratio $\eta$ (see Supplementary \Fig{}
-\ref{SI-fig:eta-all}), as a function of $V_{\mathrm{G}}$ as (details
-see Supplementary Section \ref{SI-sec:R-model}):
+$V_{\mathrm{G}}$), respectively,
+% Due to the dominance of
+% $R_{\mathrm{PCTE}}$ in the ionic transport, significant reduction of
+% total ionic flux can only be achieved, when
+% $R_{\mathrm{\mathrm{G}}}(V_{\mathrm{G}} \neq 0) \gg
+% R_{\mathrm{\mathrm{G}}}^{0}$. Using the circuit analog model, we can
+% extract the
+the effective degree of salt rejection from bare PG $\xi$ as a
+function of $V_{\mathrm{G}}$ ( see Supplementary Section
+\ref{SI-sec:R-model}) is given by:
 \begin{equation}
@@
 The factor $\xi$ is a reliable and stable measure of salt rejection
-through the PG membrane upon gating, as the salt species and initial
-conditions may induce a degree of measurement uncertainty between
-different samples.
+through the PG membrane itself upon gating, as the salt species and
+initial conditions may induce a degree of measurement uncertainty
+between different samples.
 
@@
 positive carriers (holes) are induced in graphene. We notice that an
-increase of $\xi$, or a decrease of flux through PG with
+increase of $\xi$, or a decrease of diffusive flux through PG with
 $V_{\mathrm{G}}$, showing an inverse trend compared with those
@@
 be higher than graphene due to larger quantum capacitances.
+\todo{higher or lower?}
 
@@
 $V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
-= 1.0, a high value of $\xi$ up to $\sim$0.95 can be achieved. Nevertheless
-the salt rejection of the gated graphene platform may be further
-improved after considering the following aspects: (i) the mean-field
-theory used here may be incorrect to be applied to pores smaller than
-5 nm, where individual particle properties of solvated ions can be
-important \cite{Jain_2015}, (ii) the specific ion-graphene adsorption
-may also be included to account for the pore selectivity between salt
-species \cite{Rollings_2016}.
+= 1.0, a high value of $\xi$ up to $\sim$0.95 can be achieved.  We
+notice that the above theoretical analysis suggests an upper limit of
+$\xi$ of ∼0.97 (please confirm), even when
+$\lambda_{\mathrm{D}}/r_{\mathrm{G}} \gg 1$, which appears to violate
+the small pore limit when the pore size is smaller than the hydrated
+radii. Indeed, our theory is derived from on the macroscopic transport
+equations by treating ions as zero-volume charges, which may not be
+valid when $R_{\mathrm{G}}$< 5 nm\cite{Jain_2015}. In addition, the
+specific ion-graphene interactions \cite{Rollings_2016} are not taken
+into account. Advanced theoretical frameworks that bridge continuum
+and molecular scales are required to resolve the predict the
+electrolyte transport when the pore size is sub-5 nanometers.
+% Nevertheless
+% the salt rejection of the gated graphene platform may be further
+% improved after considering the following aspects: (i) the mean-field
+% theory used here may be incorrect to be applied to pores smaller than
+% 5 nm, where individual particle properties of solvated ions can be
+% important \cite{Jain_2015}, (ii) the specific ion-graphene adsorption
+% may also be included to account for the pore selectivity between salt
+% species \cite{Rollings_2016}.
 
@@
 to a considerable degree of salt rejection. We report a high degree of
-salt rejection at $V_{\mathrm{G}}$ = 1.25 V of up to 80\% and 95\%,
-based on our experiments and theoretical predictions, respectively. We
-demonstrate that the observed salt rejection positively correlates
-with the Debye length that nonlinearly modulates the graphene surface
-potential and charge density. The experimental results and fundamental
-principles presented here open an avenue towards realization of
-atomically thin 2D porous membranes for advanced separation process in
-electrolyte solutions.
+salt rejection at $V_{\mathrm{G}}$ = 1.25 V by approximately one order
+of magnitude, based on our experiments and theoretical predictions,
+respectively. We demonstrate that the observed salt rejection
+positively correlates with the Debye length that nonlinearly modulates
+the graphene surface potential and charge density. The experimental
+results and fundamental principles presented here open an avenue
+towards realization of atomically thin 2D porous membranes for
+advanced separation process in electrolyte solutions.
 

### 2019-01-15 paper/SI.tex
Apply changes to SI Roman

@@
 geometric model agrees well with the experimental results. As shown in
-\Fig{} \ref{}, the theoretical estimated value of $\delta$ (orange
+\Fig{} \ref{fig:delta-compare}, the theoretical estimated value of $\delta$ (orange
 line) lies within the margin of the majority of experimental data,
@@
 \label{sec:salts}
-In Table \ref{tab:debye}, the conductivities and calculated Debye
+In Table \ref{tab:conductivity}, the conductivities and calculated Debye
 lengths for 6 salts are shown. At the same concentration, the higher

### 2019-01-15 paper/paper.tex
fix minor typo in manuscript
Add minor changes CJ

--- 2019-01-14 paper/paper.tex
@@
 where
-
 $\Delta \phi_{\mathrm{G}} = \phi_{\mathrm{G}}(V_{\mathrm{g}}) -
@@
 graphene with other types of conducting 2D materials, although the
-gate voltage required to achieve the same order of salt rejection may
-be higher than graphene due to larger quantum capacitances.
+operational gate voltage window required to achieve the same order of
+salt rejection may be narrower than graphene due to larger quantum
+capacitances \cite{Tian_2016}.
 
@@
 $V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
-= 1.0, a high value of $\xi$ up to $\sim$0.95 can be achieved. Nevertheless
-the salt rejection of the gated graphene platform may be further
-improved after considering the following aspects: (i) the mean-field
-theory used here may be incorrect to be applied to pores smaller than
-5 nm, where individual particle properties of solvated ions can be
-important \cite{Jain_2015}, (ii) the specific ion-graphene adsorption
-may also be included to account for the pore selectivity between salt
-species \cite{Rollings_2016}.
+= 1.0, a high value of $\xi$ up to $\sim$0.95 can be achieved.  We
+notice that although the above analysis suggests a salt rejection up
+to 1 may be achived by further reducing the pore size (i.e. increasing
+the $\lambda_{\mathrm{D}}/r_{\mathrm{G}}$ ratio), our theory, derived
+from on the macroscopic transport equations by treating ions as
+zero-volume charges, may not be valid when $R_{\mathrm{G}}$< 5
+nm\cite{Jain_2015}. In addition, the specific ion-graphene
+interactions \cite{Rollings_2016} are not taken into account. Advanced
+theoretical frameworks that bridge continuum and molecular scales are
+required to resolve and predict the electrolyte transport when the
+pore size is sub-5 nanometers.
+% Nevertheless
+% the salt rejection of the gated graphene platform may be further
+% improved after considering the following aspects: (i) the mean-field
+% theory used here may be incorrect to be applied to pores smaller than
+% 5 nm, where individual particle properties of solvated ions can be
+% important \cite{Jain_2015}, (ii) the specific ion-graphene adsorption
+% may also be included to account for the pore selectivity between salt
+% species \cite{Rollings_2016}.
 

### 2019-01-15 paper/paper.tex
Minor changes

@@
 \end{equation}
-
 where $r_{\mathrm{PCTE}}$ is the PCTE pore radius, $N_{\mathrm{p}}$ is
@@
 distribution is given by:
-
 \begin{equation}
@@
 \end{equation}
-
 where $\varepsilon_{\mathrm{m}}$ is the relative permittivity of
@@
 \ref{fig:3}a) following:
-
 \begin{equation}
@@
 \end{equation}
-
 where
@@
 operational gate voltage window required to achieve the same order of
-salt rejection may be narrower than graphene due to larger quantum
+salt rejection may be narrower than graphene due to the larger quantum
 capacitances \cite{Tian_2016}.

### 2019-01-15 paper/paper.tex
Add changes from CJ 20180115

@@
 \begin{abstract}
-  {\normalsize
-    Atomically thin porous graphene membranes are emerging as one of
-    the most promising candidates for the next-generation membrane
-    technology owing to the ultrahigh permeation. However, the
-    transport selectivity relies on the precise control over pore size
-    and shape, considerably limiting the scalability. Here, we study
-    electrolyte permeation through a sheet of large-area, porous
-    graphene membrane, with relatively large pore sizes of 20$\pm$10
-    nanometers. Counterintuitively, we observe macroscopic salt
-    rejection by applying electrostatically gating, which reduces the
+  {\normalsize Atomically thin porous graphene membranes areis
+    emerging as one of the most promising candidates for the
+    next-generation membrane technologymaterial owing to the ultrahigh
+    permeation. However, the transport selectivity relies on the
+    precise control over pore size and shape, which considerably
+    limitingcompromises the scalability. Here, we study electrolyte
+    permeation through a sheet of large-area, porous graphene
+    membrane, with relatively large pore sizes of 20$\pm$10
+    nanometers. Counterintuitively, we observe macroscopica high
+    degree of salt rejection is observed by applying
+    electrostaticallyelectrostatic gating, which reducesreducing the
     diffusive flux by up to one order of magnitude. We systematically
@@
     including developing a theory to model the electrolyte diffusion
-    through a nanopore in a sheet of gated graphene. The interplay
-    between graphene quantum capacitance and the electrical double
-    layer is found to selectively modulate the anionic and cationic
-    transport paths, creating voltage-dependent electrochemical
-    barriers when the pore size is comparable to the Debye length. Our
-    findings reveal a new degree of freedom regulating electrolyte
-    permeation through porous two-dimensional materials.   
+    through a nanopore drilled in a sheet of gated graphene. The
+    interplay between graphene quantum capacitance and the electrical
+    double layer is found to selectively modulate the anionic and
+    cationic transport paths, creating voltage-dependent
+    electrochemical barriers when the pore size is comparable to the
+    Debye length. Our findings reveal a new degree of freedom
+    regulating electrolyte permeation through porous two-dimensional
+    materials.
+    % Atomically thin porous graphene is emerging as one of
+    % the most promising candidates for the next-generation membrane
+    % technology owing to the ultrahigh permeation. However, the
+    % transport selectivity relies on the precise control over pore size
+    % and shape, considerably limiting the scalability. Here, we study
+    % electrolyte permeation through a sheet of large-area, porous
+    % graphene membrane, with relatively large pore sizes of 20$\pm$10
+    % nanometers. Counterintuitively, we observe macroscopic salt
+    % rejection by applying electrostatically gating, which reduces the
+    % diffusive flux by up to one order of magnitude. We systematically
+    % investigate the effects of salt concentration and species,
+    % including developing a theory to model the electrolyte diffusion
+    % through a nanopore in a sheet of gated graphene. The interplay
+    % between graphene quantum capacitance and the electrical double
+    % layer is found to selectively modulate the anionic and cationic
+    % transport paths, creating voltage-dependent electrochemical
+    % barriers when the pore size is comparable to the Debye length. Our
+    % findings reveal a new degree of freedom regulating electrolyte
+    % permeation through porous two-dimensional materials.   
     % Atomically thin porous graphene membranes are emerging
@@
 atomically thin two-dimensional (2D) materials, such as graphene, are
-emerging as ideal membrane materials due to their ultimate permeation
+emerging as ideal membrane materials due to the ultimate permeation
 \cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
@@
 the hydrated radii ($\sim$1 nm), thereby hindering ion passage without
-compromising water permeability
+losing water permeability
 \cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}. Nevertheless,
@@
 selective \cite{Rollings_2016,Surwade_2014}. However, it remains
-controversial if the surface charges can result in a degree of salt
-rejection, as the surface charge and potential cannot be precisely
-quantified and are sensitive to the surroundings as well as the
-history of chemical treatment \cite{Li_2008}. There remains a lack of
-fundamental understanding of the interactions between the charged 2D
-nanopores and the electrolyte solution. In this report, we investigate
-electrolyte permeation through graphene nanopores that are
-significantly larger than the hydrated radii. We construct the surface
+controversial that if the surface charges can result in a degree of
+salt rejection, as the surface charge and potential cannot be
+precisely quantified and are sensitive to the surroundings as well as
+the history of chemical treatment \cite{Li_2008}. There remains a lack
+of fundamental understanding of the interactions between the charged
+2D nanopores and the electrolyte solution. In this report, we
+investigate electrolyte permeation through graphene nanopores that are
+significantly larger than the hydrated radii. We model the surface
 potential by taking into account of the elementary electronic
@@
 across the PTCE-supported PG double layer as a function of
-$V_{\mathrm{G}}$. Since PG and PCTE membranes effectively form a transport
-system with series resistance $R_{\mathrm{PG}}$ (tunable by
-$V_{\mathrm{G}}$) and $R_{\mathrm{PCTE}}$ (independent of
-$V_{\mathrm{G}}$), respectively,
-% Due to the dominance of
-% $R_{\mathrm{PCTE}}$ in the ionic transport, significant reduction of
-% total ionic flux can only be achieved, when
-% $R_{\mathrm{\mathrm{G}}}(V_{\mathrm{G}} \neq 0) \gg
-% R_{\mathrm{\mathrm{G}}}^{0}$. Using the circuit analog model, we can
-% extract the
-the effective degree of salt rejection from bare PG $\xi$ as a
-function of $V_{\mathrm{G}}$ ( see Supplementary Section
-\ref{SI-sec:R-model}) is given by:
+$V_{\mathrm{G}}$. Since graphene and PCTE membranes effectively form a
+transport system with series diffusive resistance $R_{\mathrm{G}}$
+(tunable by $V_{\mathrm{G}}$) and $R_{\mathrm{PCTE}}$ (independent of
+$V_{\mathrm{G}}$), respectively, we define the effective degree of
+salt rejection from bare PG $\xi$ as a function of $V_{\mathrm{G}}$ (
+details see Supplementary Section \ref{SI-sec:R-model}) as:
 \begin{equation}
 \label{eq:xi-def}
-\xi = \frac{(\delta+1) \eta}{\delta \eta + 1}
+\xi = 1 - \frac{R_{\mathrm{G}}(V_{\mathrm{G}}=0)}{R_{\mathrm{G}}(V_{\mathrm{G}})} = \frac{(\delta+1) \eta}{\delta \eta + 1}
 \end{equation}
@@
 initial conditions may induce a degree of measurement uncertainty
-between different samples.
+between different samples. Note that the $\xi=1$ limit represents
+perfect salt rejection in which
+$R_{\mathrm{G}}(V_{\mathrm{G}}) \to \infty$. On the contrary $xi=0$
+indicates $R_{\mathrm{G}}$ remains unchanged with $V_{\mathrm{G}}$.
 
@@
 $\sigma_{\mathrm{G}}$ of $\sim$0.08 C$\cdot$m$^{-2}$. Note that as we
-mentioned earlier, an important merit of the system here is that the
-surface charge density can be precisely determined and controlled,
-rather than being treated as a fitting parameter as in most of the 2D
-nanopore studies \cite{Rollings_2016}. We anticipate that the
-gate-controlled ionic transport can also be achieved by replacing
-graphene with other types of conducting 2D materials, although the
-operational gate voltage window required to achieve the same order of
-salt rejection may be narrower than graphene due to the larger quantum
-capacitances \cite{Tian_2016}.
+mentioned earlier, an important merit of the 2D nanopore system
+considered here is that the surface charge density can be precisely
+determined and controlled, rather than being treated as a fitting
+parameter as in most of the 2D nanopore literature
+(e.g. Ref. \citenum{Rollings_2016}). In addition, we anticipate that
+the gate-controlled ionic transport can also be achieved by replacing
+graphene with other nanoporous conducting 2D materials, although the
+operational gate voltage window required to achieve the same degree of
+salt rejection may be narrower, because graphene has the smallest
+quantum capacitance (near the Dirac point) among all known 2D
+materials \cite{Tian_2016}.
 
@@
 interactions \cite{Rollings_2016} are not taken into account. Advanced
-theoretical frameworks that bridge continuum and molecular scales are
-required to resolve and predict the electrolyte transport when the
-pore size is sub-5 nanometers.
+theoretical frameworks that bridge continuum and molecular models are
+required to elucidate electrolyte transport approaching the small pore
+limit.
 % Nevertheless

### 2019-01-15 paper/paper.tex
fix typo
Remove blank line

@@
 perfect salt rejection in which
-$R_{\mathrm{G}}(V_{\mathrm{G}}) \to \infty$. On the contrary $xi=0$
+$R_{\mathrm{G}}(V_{\mathrm{G}}) \to \infty$. On the contrary $\xi=0$
 indicates $R_{\mathrm{G}}$ remains unchanged with $V_{\mathrm{G}}$.
@@
 0. The elementary electronic properties of graphene give:
-
 \begin{equation}
@@
 \end{equation}
-
 where $\hbar$ is the reduced Planck constant, and

### 2019-01-15 paper/paper.tex
Fix TeX error

@@
 from on the macroscopic transport equations by treating ions as
-zero-volume charges, may not be valid when $R_{\mathrm{G}}$< 5
+zero-volume charges, may not be valid when $R_{\mathrm{G}}<$ 5
 nm\cite{Jain_2015}. In addition, the specific ion-graphene

### 2019-01-15 paper/paper.tex
Fix minor err

@@
 \begin{abstract}
-  {\normalsize Atomically thin porous graphene membranes areis
-    emerging as one of the most promising candidates for the
-    next-generation membrane technologymaterial owing to the ultrahigh
-    permeation. However, the transport selectivity relies on the
-    precise control over pore size and shape, which considerably
-    limitingcompromises the scalability. Here, we study electrolyte
-    permeation through a sheet of large-area, porous graphene
-    membrane, with relatively large pore sizes of 20$\pm$10
-    nanometers. Counterintuitively, we observe macroscopica high
-    degree of salt rejection is observed by applying
-    electrostaticallyelectrostatic gating, which reducesreducing the
-    diffusive flux by up to one order of magnitude. We systematically
-    investigate the effects of salt concentration and species,
-    including developing a theory to model the electrolyte diffusion
-    through a nanopore drilled in a sheet of gated graphene. The
-    interplay between graphene quantum capacitance and the electrical
-    double layer is found to selectively modulate the anionic and
-    cationic transport paths, creating voltage-dependent
-    electrochemical barriers when the pore size is comparable to the
-    Debye length. Our findings reveal a new degree of freedom
-    regulating electrolyte permeation through porous two-dimensional
-    materials.
-    % Atomically thin porous graphene is emerging as one of
-    % the most promising candidates for the next-generation membrane
-    % technology owing to the ultrahigh permeation. However, the
-    % transport selectivity relies on the precise control over pore size
-    % and shape, considerably limiting the scalability. Here, we study
-    % electrolyte permeation through a sheet of large-area, porous
-    % graphene membrane, with relatively large pore sizes of 20$\pm$10
-    % nanometers. Counterintuitively, we observe macroscopic salt
-    % rejection by applying electrostatically gating, which reduces the
-    % diffusive flux by up to one order of magnitude. We systematically
-    % investigate the effects of salt concentration and species,
-    % including developing a theory to model the electrolyte diffusion
-    % through a nanopore in a sheet of gated graphene. The interplay
-    % between graphene quantum capacitance and the electrical double
-    % layer is found to selectively modulate the anionic and cationic
-    % transport paths, creating voltage-dependent electrochemical
-    % barriers when the pore size is comparable to the Debye length. Our
-    % findings reveal a new degree of freedom regulating electrolyte
-    % permeation through porous two-dimensional materials.   
-    % Atomically thin porous graphene membranes are emerging
-    % as one of the most promising candidates as next-generation
-    % membrane technology owing to their unique transport physics and
-    % high permeation. Among the current challenges of 2D membranes is
-    % the understanding of fundamental ion transport as well as its
-    % control towards applications in ion rectification, ionic
-    % transistors or desalination.  Here we report the study of
-    % tailoring the ion transport through atomically-thin porous
-    % graphene with pore sizes of 20$\pm$10 nanometers, and a pore
-    % density of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$. By
-    % electrostatically gating a sheet of porous graphene, we
-    % demonstrate a considerable reduction of salt flux by up to 55\%
-    % and 85\% using a gate voltage, based on our experiments and
-    % theoretical predictions, respectively. We systematically
-    % investigate the effects of salt concentration and species,
-    % including the development of a theory to model the electrolyte
-    % diffusion through a nanopore in a sheet of gated graphene. The
-    % interplay between graphene quantum capacitance and electrical
-    % double layer is identified to be the main mechanism responsible
-    % for the observed salt flux reduction, when the pore size is
-    % comparable to the Debye length. Our findings reveal a new degree
-    % of freedom controlling the membrane potential and electrolyte
-    % permeation through porous two-dimensional materials.
-  }
+  {\normalsize Atomically thin porous graphene is emerging as one of
+    the most promising candidates for next-generation membrane
+    material owing to the ultrahigh permeation. However, the transport
+    selectivity relies on the precise control over pore size and shape
+    which considerably compromises the scalability. Here, we study
+    electrolyte permeation through a sheet of large-area, porous
+    graphene, with relatively large pore sizes of 20$\pm$10
+    nanometers. Counterintuitively, a high degree of salt rejection is
+    observed by electrostatic gating, reducing the diffusive flux by
+    up to one order of magnitude. We systematically investigate the
+    effects of salt concentration and species, including developing a
+    theory to model the electrolyte diffusion through a nanopore
+    drilled in a sheet of gated graphene. The interplay between
+    graphene quantum capacitance and the electrical double layer is
+    found to selectively modulate the anionic and cationic transport
+    paths, creating voltage-dependent electrochemical barriers when
+    the pore size is comparable to the Debye length. Our findings
+    reveal a new degree of freedom regulating electrolyte permeation
+    through porous two-dimensional materials.  }
 \end{abstract}
@@
 voltage. As a result, the subtle redistribution of the electrochemical
-potentials create new pathways for ionic transport, which in turn lead
-to a considerable degree of salt rejection. We report a high degree of
-salt rejection at $V_{\mathrm{G}}$ = 1.25 V by approximately one order
-of magnitude, based on our experiments and theoretical predictions,
-respectively. We demonstrate that the observed salt rejection
-positively correlates with the Debye length that nonlinearly modulates
-the graphene surface potential and charge density. The experimental
-results and fundamental principles presented here open an avenue
-towards realization of atomically thin 2D porous membranes for
+potential creates new pathways for ionic transport, which in turn
+leads to a considerable degree of salt rejection. We report a high
+degree of salt rejection at $V_{\mathrm{G}}$ = 1.25 V by approximately
+one order of magnitude, based on our experiments and theoretical
+predictions, respectively. We demonstrate that the observed salt
+rejection positively correlates with the Debye length that nonlinearly
+modulates the graphene surface potential and charge density. The
+experimental results and fundamental principles presented here open an
+avenue towards realization of atomically thin 2D porous membranes for
 advanced separation process in electrolyte solutions.

### 2019-01-16 paper/paper.tex
Fix minor issues

@@
 $V_{\mathrm{G}}$), respectively, we define the effective degree of
-salt rejection from bare PG $\xi$ as a function of $V_{\mathrm{G}}$ (
+salt rejection from bare PG, $\xi$, as a function of $V_{\mathrm{G}}$ (
 details see Supplementary Section \ref{SI-sec:R-model}) as:
@@
 K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (details see Supplementary
-Section \ref{SI-sec:simu-res}). Similar to the KCl system discussed
+Section \ref{SI-sec:salts}). Similar to the KCl system discussed
 earlier, the salt rejection is more pronounced in the positive
@@
 one order of magnitude, based on our experiments and theoretical
-predictions, respectively. We demonstrate that the observed salt
+predictions. We demonstrate that the observed salt
 rejection positively correlates with the Debye length that nonlinearly

### 2019-01-17 paper/SI.tex
Add comment CJ & RW about title

@@
 
-\title{Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene}
+\title{Macroscopic Salt Rejection through Electrostatically Gated Nanoporous Graphene}
 
@@
     \hline
-    Salt & $s$ (mS$\cdot$cm$^{-1}$d$^{-1}$) & $c_{\mathrm{f}}$ (mS$\cdot$cm$^{-1}\cdot$mol$^{-1}\cdot$ml) &
+    Salt & $s$ (mS$\cdot$cm$^{-1}$d$^{-1}$) & $c_{\mathrm{f}}$ (mS$\cdot$cm$^{-1}\cdot$mol$^{-1}\cdot$L) &
                                                                                                             $\boldsymbol{J}_{\mathrm{PCTE}}$ (10$^{6}$ mol$\cdot$m$^{-2}\cdot$s$^{-1}$)\\

### 2019-01-18 paper/SI.tex
Add changes from cJ before submission

@@
 \renewcommand{\thesection}{S\arabic{section}}
+\renewcommand{\theequation}{S\arabic{equation}}
 \SectionNumbersOn
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{img/SI-eta-all.pdf}
+  \includegraphics[width=0.5\linewidth]{img/SI-eta-all.pdf}
   \caption{Measured $\eta$ values as function of $V_{\mathrm{G}}$ for
@@
 
+% \pagebreak
+
 \section{Circuit analog model of transport through PG-PCTE}
 \label{sec:R-model}
-The ionic transport through the PG-PCTE membrane is the concerted
-effect the transport resistance through PG and PCTE membranes,
-respectively. As schematically shown in \Fig{} \ref{fig:R-model}, the
-overall transport resistance of the system is composed of the series
-resistance $R_{\mathrm{G}}$ and $R_{\mathrm{PCTE}}$, respectively. We
-further treat $R_{\mathrm{G}}$ as the effective resistance of $\gamma$
-parallel resistors with individual resistance $R_{\mathrm{g}}$, where
-$\gamma$ is the average numbers of PG pores per PCTE channel, and
-$R_{\mathrm{g}}$ is the average transport resistance per PG pore. 
+
 \begin{figure}[htbp]
@@
 \end{figure}
-We then estimate the value of $\gamma$ from geometric analysis of both
-membranes. Given the pore number density of PG
+The ionic transport through the PG-PCTE membrane is the concerted
+effect the transport resistance through PG and PCTE membranes,
+respectively. As schematically shown in \Fig{} \ref{fig:R-model}, the
+overall transport resistance of the system is composed of the series
+resistance $R_{\mathrm{G}}$ and $R_{\mathrm{PCTE}}$, respectively. For
+both PG and PCTE membranes, the resistance $R$ is defined as the ratio
+between the concentration between HCR and LCR $\Delta c$, and the total diffusive current $I$ as:
+\begin{equation}
+\label{eq:1}
+R_{i} = \Bigg|\frac{\Delta c}{I_{i}}\Bigg| =  \Bigg|\frac{\Delta c}{J_{i}A_{i}}\Bigg|
+\end{equation}
+where $i$ denotes the membrane type and $A_{i}$ is the area of the
+pore. We further treat $R_{\mathrm{G}}$ as the effective resistance of
+$\gamma$ parallel resistors with individual resistance
+$R_{\mathrm{g}}$, where $\gamma$ is the average number of PG pores per
+PCTE channel, and $R_{\mathrm{g}}$ is the average transport resistance
+per PG pore. The value of $\gamma$ is determined from geometric
+analysis of both membranes: given the pore number density of PG
 ($\sim$1.25$\times$10$^{14}$ m$^{-2}$), the pore number density of
@@
 
-Next we seek the value between $R_{\mathrm{PCTE}}$ and
-$R_{\mathrm{G}}^{0}$ (ungated resistance of PG), $\delta$. It is
-pointed out that the scaling laws for $R_{\mathrm{PCTE}}$ and
-$R_{\mathrm{G}}^{0}$ differ. For a long channel like PCTE, the
-resistance is derived from Fick's law as\cite{O_Hern_2014}:
-\begin{equation}
-\label{eq:R-PCTE}
- R_{\mathrm{PCTE}} = \frac{1}{D} \frac{L}{\pi r_{\mathrm{PCTE}}^{2}}
-\end{equation}
-whereas $D$ is the diffusivity of the species, $L$ is the length of
-channel ($\sim$24 $\mathrm{\mu}$m), and $r_{\mathrm{PCTE}}$ is the
-average radius of the PCTE channels ($\sim$200 nm). On the other hand,
-the transport through 2D pore with high radius/thickness ratio falls
-into the regime of the Sampson formula \cite{Roscoe_1949}, where the
-entrance resistance dominates over the bulk resistance, with the
-formula as \cite{Roscoe_1949,Celebi_2014}:
-\begin{equation}
-  \label{eq:sampson}
-  R_{\mathrm{g}}^{0} = \frac{1}{D} \frac{3 \pi}{r_{\mathrm{G}}}
-\end{equation}
-We therefore estimate the value of $\delta$ as:
-\begin{equation}
-  \label{eq:delta-resistance}
-  \delta
-  = \frac{R_{\mathrm{PCTE}}}{R_{\mathrm{G}}^{0}}
-  = {\displaystyle
-    \frac{{\displaystyle \frac{L}
-        {\pi r_{\mathrm{PCTE}}^{2}}}}
-    {{\displaystyle \frac{3 \pi}{r_{\mathrm{G}}} \frac{1}{\gamma}}}}
-  \approx 2.20
-\end{equation}
-Alternatively, we may also estimate the range of $\delta$ from
-experimental data in main text \Fig{} \ref{main-fig:2}b using the
-relation:
-\begin{equation}
-  \label{eq:exp-delta}
-  \delta = \left(\frac{\boldsymbol{J}_{\mathrm{PCTE}}}{\boldsymbol{J}_{\mathrm{PG}}^{0}} -1 \right)^{-1}
-\end{equation}
-by assuming the validity of the circuit analog model for all salt
-systems. We find that the $\delta$ value estimated from the simple
-geometric model agrees well with the experimental results. As shown in
-\Fig{} \ref{fig:delta-compare}, the theoretical estimated value of $\delta$ (orange
-line) lies within the margin of the majority of experimental data,
-which is exceptionally good given the simplicity of the model used.
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.75\linewidth]{img/SI-delta-estimate.pdf}
-  \caption{Comparison between the $\delta$ value estimated from simple
-    geometric model (Eq. \ref{eq:delta-resistance}) and from
-    experimental value (Eq. \ref{eq:exp-delta}), showing good
-    agreement between the two methods.  }
-  \label{fig:delta-compare}
-\end{figure}
-
-Finally we show how the effective salt rejection ratio through PG, $\xi$,
-is extracted from the experimental $\eta$ values. Using the circuit
-analog model, the definition of $\eta$ from main text
-Eq. \ref{main-eq:rejection} can be rewritten using transport
-resistances as:
+The objective of the circuit analog model is to find effective salt
+rejection ratio through PG, $\xi$ extracted from the experimental
+$\eta$ values (defined in main text Eq. \ref{main-eq:rejection}). By
+defining $R_{\mathrm{G}}^{0}=R_{\mathrm{G}}(V_{\mathrm{G}}=0)$,
+$\delta = R_{\mathrm{PCTE}} / R_{\mathrm{G}}^{0}$,
+$\chi = R_{\mathrm{G}}/R_{\mathrm{G}}^{0}$, $\eta$ is rewritten using
+transport resistances as:
 \begin{equation}
@@
 \end{equation}
-where we define $\chi = R_{\mathrm{G}}/R_{\mathrm{G}}^{0}$ which
-represents the change of the transport resistance through PG upon
-gating. Consequentially, the salt rejection ratio $\xi$, is associated
-with $\chi$ by $\xi = 1 - \chi^{-1}$. Reformatting Eq. \ref{eq:eta-R}
-gives:
+Consequentially, the
+salt rejection ratio $\xi$, is associated with $\chi$ by
+$\xi = 1 - \chi^{-1}$ and is related with $\delta$ and $\eta$ via:
 \begin{equation}
@@
 gating, is always larger than that experimentally observed.
+
+Next we seek the value of $\delta$, the resistance ratio
+between the PCTE and PG membranes, without gating. The range
+of $\delta$ can be estimated from experimental data in main text
+\Fig{} \ref{main-fig:2}b using the relation:
+\begin{equation}
+  \label{eq:exp-delta}
+  \delta = \left(\frac{\boldsymbol{J}_{\mathrm{PCTE}}}{\boldsymbol{J}_{\mathrm{PG}}^{0}} -1 \right)^{-1}
+\end{equation}
+by assuming the validity of the circuit analog model for all salt
+systems. As shown in \Fig{} \ref{fig:delta-compare}, the
+experimentally estimated value of $\delta$ varies from 1 to 5,
+indicating that the resistance of the PG membrane is dominating in the
+PG-PCTE system.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.55\linewidth]{img/SI-delta-estimate.pdf}
+  \caption{Comparison between the $\delta$ value estimated from simple
+    geometric model (Eq. \ref{eq:delta-resistance}) and from
+    experimental value (Eq. \ref{eq:exp-delta}), showing good
+    agreement between the two methods.  }
+  \label{fig:delta-compare}
+\end{figure}
+$\delta$ can also be estimated using geometric parameters of both
+membranes. For a long PCTE channel with length $L$ and
+$r_{\mathrm{PCTE}}$, $R_{\mathrm{PCTE}}$ has power law of
+$L/r_{\mathrm{PCTE}}^{2}$, while for a graphene pore
+with radius $r_{\mathrm{G}}$ and vanishing thickness, the resistance of individual pore $R_{\mathrm{g}}^{0}$
+has power law $1/r_{\mathrm{G}}$ \cite{O_Hern_2014}, which are expressed as:
+\begin{subequations}
+\begin{eqnarray}
+  \label{eq:R-both}
+  R_{\mathrm{PCTE}} &= &k_{\mathrm{PCTE}} \frac{L}{r_{\mathrm{PCTE}}^{2}} \\
+  R_{\mathrm{g}}^{0} &= &k_{\mathrm{g}} \frac{1}{r_{\mathrm{G}}}
+\end{eqnarray}
+\end{subequations}
+where $k_{\mathrm{PCTE}}$ and $k_{\mathrm{g}}$ are the coefficient
+associated with PCTE and PG membranes, respectively. The value of
+$\delta$ is then expressed as:
+\begin{equation}
+  \label{eq:delta-resistance}
+  \delta
+  = \frac{R_{\mathrm{PCTE}}}{R_{\mathrm{G}}^{0}}
+  = {\displaystyle
+    \frac{k_{\mathrm{PCTE}}}{k_{\mathrm{g}}}
+    \frac{L r_{\mathrm{G}} \gamma}
+        {r_{\mathrm{PCTE}}^{2}}}
+\end{equation}
+Here we take $L$=24 $\mu$m, $r_{\mathrm{G}}$=10 nm,
+$r_{\mathrm{PCTE}}$=200 nm. From simple Fick's law\cite{Beers_2006},
+the coefficient $k_{\mathrm{PCTE}}$ is determined as
+$1/(D_{\mathrm{\pm}} \pi)$. On the other hand $k_{\mathrm{G}}$ varies
+by the choice of model, ranging from $3 \pi / D_{\mathrm{\pm}}$ using
+the analog of the Sampson formula for
+fluid\cite{Roscoe_1949,Celebi_2014}, to $1/(2 D_{\mathrm{\pm}})$ from
+the Hill formula for disk absorption model
+\cite{Hill_1975,Grebenkov_2018}. As a result the theoretical value of
+$\delta$ has lower bound of $\sim$2.2 (Sampson formula, orange line in
+\Fig{} \ref{fig:delta-compare}) to $\sim$40.5 (Hill formula). We note
+our experimental values of $\delta$ is in good agreement estimated
+from the Sampson formula (which we use in the main text) while lower
+than the Hill formula. Having a higher estimated value of $\delta$
+could yield unreasonably high value of $\xi$ and the influence of
+concentration is deviated from our theoretical predictions. Further
+theoretical analysis taking nonidealities including surface adsorption
+and chemical nature of pore edge, is required to have better
+understanding of graphene's transport resistance.
+
+% On the other hand, the transport through
+% 2D pore with high radius/thickness ratio falls into the regime of the
+% Sampson formula \cite{Roscoe_1949}, where the entrance resistance
+% dominates over the bulk resistance, with the formula as
+% \cite{Roscoe_1949,Celebi_2014}:
+% \begin{equation}
+%   \label{eq:sampson}
+%   R_{\mathrm{g}}^{0} = \frac{1}{D} \frac{3 \pi}{r_{\mathrm{G}}}
+% \end{equation}
+% We therefore estimate the value of $\delta$ as:
 

### 2019-01-18 paper/paper.tex
Add comment CJ & RW about title
Add changes from cJ before submission

@@
     reveal a new degree of freedom regulating electrolyte permeation
-    through porous two-dimensional materials.  }
+    through porous two-dimensional materials, complementary to the
+    pore size design and engineering.}
 \end{abstract}
@@
 \cite{Ghosh_2018} may give even better agreement with experimental
-results.
+results. More interestingly, based on our theoretical analysis, we
+predict that a very high degree of salt rejection ($\zeta>$ 0.99) can
+be already achieved when $\lambda / r_{\mathrm{G}}>$3. In other words,
+for example, when the Debye length is 20 nm, one can suppress 99 \% of
+the diffusive flux by further reducing the pore radius down to $~$5
+nm, which still remains larger than the hydrated radii. In combination
+with the development of nanoscale etching techniques, we believe that
+the physical picture presented here makes one step closer to
+large-scale production of graphene membranes.
 

### 2019-01-18 paper/paper.tex
Minor fix

@@
 results. More interestingly, based on our theoretical analysis, we
-predict that a very high degree of salt rejection ($\zeta>$ 0.99) can
-be already achieved when $\lambda / r_{\mathrm{G}}>$3. In other words,
+predict that a very high degree of salt rejection ($\xi>$ 0.99) can be
+already achieved when $\lambda / r_{\mathrm{G}}>$3. In other words,
 for example, when the Debye length is 20 nm, one can suppress 99 \% of
-the diffusive flux by further reducing the pore radius down to $~$5
-nm, which still remains larger than the hydrated radii. In combination
-with the development of nanoscale etching techniques, we believe that
-the physical picture presented here makes one step closer to
-large-scale production of graphene membranes.
+the diffusive flux by further reducing the pore radius down to
+$\sim$5-6 nm, which still remains larger than the hydrated radii. In
+combination with the development of nanoscale etching techniques, we
+believe that the physical picture presented here makes one step closer
+to large-scale production of graphene membranes.
 

### 2019-03-06 concentration/sub_job.sh
finish moving files

@@ -1,34 +1,0 @@
-#Generic script for submitting comsol job
-#usage: sub_job.sh [COMSOL_IN_NAME] [optional:MEM]
-INFILE=$1
-OUTFILE=$(echo $INFILE | cut -f 1 -d ".")
-OUTFILE+="_out.mph"
-OUTFILE=$SCRATCH/$OUTFILE
-
-
-#Memory alloc
-MEM=4096
-if [ $# -ge 2 ]; then
-	MEM=$2
-fi
-echo "Rmem=$MEM"
-
-NP=4
-if [ $# -ge 3 ]; then
-        NP=$3
-fi
-
-JOB_STRING="comsol batch -np $NP -inputfile $INFILE -outputfile $OUTFILE"
-
-#Now the submission line
-SUB_STRING="bsub -n $NP -W 24:00 -R \"rusage[mem=$MEM]\" \"$JOB_STRING\""
-echo "Final check:" $SUB_STRING
-
-while true; do
-	read -p  "Ready for sumission?[y/n]" OPTION
-	case $OPTION in
-		[Yy]* ) eval $SUB_STRING; break;;
-		[Nn]* ) break;;
-		* ) echo "y or n?";;
-	esac
-done

### 2019-03-06 correction/phi_G.py

@@ -1,35 +1,0 @@
-import numpy
-from scipy.constants import pi, hbar, e
-vf = 1.1e6
-
-# Use C/m^2
-def delta_phi_gr(sigma):
-    fac = hbar * vf / e * numpy.sqrt(pi * numpy.abs(sigma) / e)
-    return fac * numpy.sign(sigma)
-
-if __name__ == "__main__":
-    import matplotlib.pyplot as plt
-    data = numpy.genfromtxt("../result/radius/10/1D/sigma_0.001.txt", comments="%")
-    phi_surf = data[:, 0]
-    sigma_gr = -data[:, 1]
-    d_phi  = delta_phi_gr(sigma_gr)
-    V_b = phi_surf + d_phi
-    fig = plt.figure(figsize=(2.8, 2.1))
-    plt.style.use("science")
-    ax1 = fig.add_subplot(111)
-    ax2 = ax1.twinx()
-    ax1.plot(V_b, sigma_gr, "s-", markersize=4)
-    ax2.plot(V_b, phi_surf, "o-", color="r", markersize=4)
-    
-    ax2.set_ylabel(r"$\phi_{\rm{0}}$ (V)")
-    ax1.set_ylabel(r"$\sigma_{\rm{G}}$ (C/m$^{2}$)")
-
-    ax1.set_xlabel("$V_{\\mathrm{G}}$ (V)")
-    plt.xlim(0, 1.25)
-    ax1.set_ylim(0, 0.1)
-    ax2.set_ylim(0, 0.3)
-    # plt.axhline(y=1.25, color="red", alpha=0.6, ls="--")
-
-    plt.tight_layout()
-    
-    plt.savefig("two_panels.svg")

### 2019-03-06 mesh_compare/clean.sh

@@ -1,1 +1,0 @@
-rm -f *.lock *.recovery *~ lsf* *.status *.log

### 2019-03-06 mesh_compare/sub_job.sh

@@ -1,32 +1,0 @@
-#Generic script for submitting comsol job
-#usage: sub_job.sh [COMSOL_IN_NAME] [optional:MEM]
-INFILE=$1
-OUTFILE=$(echo $INFILE | cut -f 1 -d ".")
-OUTFILE+="_out.mph"
-
-JOB_STRING="comsol batch -np 4 -inputfile $INFILE -outputfile $OUTFILE"
-
-#Memory alloc
-MEM=4096
-if [ $# -ge 2 ]; then
-	MEM=$2
-fi
-echo "Rmem=$MEM"
-
-NP=4
-if [ $# -ge 3 ]; then
-        NP=$3
-fi
-
-#Now the submission line
-SUB_STRING="bsub -n $NP -W 24:00 -R \"rusage[mem=$MEM]\" \"$JOB_STRING\""
-echo "Final check:" $SUB_STRING
-
-while true; do
-	read -p  "Ready for sumission?[y/n]" OPTION
-	case $OPTION in
-		[Yy]* ) eval $SUB_STRING; break;;
-		[Nn]* ) break;;
-		* ) echo "y or n?";;
-	esac
-done

### 2019-03-06 mesh_compare/sub_job_boundary.sh

@@ -1,3 +1,0 @@
-INFILE="PNP_model_boundarylayer_test.mph"
-OUTFILE="PNP_model_boundarylayer_test_out.mph"
-comsol batch -np 4 -inputfile $INFILE -outputfile $OUTFILE

### 2019-03-06 postprocessing/export_1D_data.m

@@ -1,39 +1,0 @@
-[file, path] = uigetfile('./*.mph');
-abs_path = strcat(path, file);
-model = mphopen(abs_path);
-% Add export section
-data = model.result.export.create('1D_data', 'Data');
-data.set('data', 'cln2'); %use line cln2
-data.set('recover', 'pprint'); %use recover setting
-data.set('fullprec', 'off');
-%use grid location
-data.set('location', 'regulargrid');
-data.set('regulargridx1', 1024);
-
-%use
-expressions = {'V', 'c_p', 'c_n', 'tds.tflux_c_pz', 'tds.tflux_c_nz'};
-desc = {'Potential', 'c_p', 'c_n', 'cpz', 'cnz'};
-data.set('expr', expressions);
-data.set('descr', desc);
-
-%file
-file_root = strsplit(file, '.');
-txt_file = strcat(path, strcat(file_root{1}, '_1Ddata.txt'));
-data.set('filename', txt_file);
-
-%execute
-
-fprintf('Exporting for file %s ...\n', file);
-data.run();
-
-% Export sigma and export file
-int_surf = model.result.numerical.create('int2', 'IntSurface');
-int_surf.set('intvolume', 'on');
-int_surf.selection.set([1, 2]);
-int_surf.setIndex('expr', '(z_n * c_n + z_p * c_p) * N_A_const * e_const / (pi * L ^2)', 0);
-res = int_surf.computeResult(); cc = res(1); sigma = cc{1};
-
-% Vg = [0.001, 0.025, 0.05, 0.1, 0.15, 0.2, 0.25, 0.35, 0.45, 0.55, 0.65];
-Vg = [0.001, 0.025 : 0.025: 0.30];
-sigma_file = strcat(path, 'sigma_', file_root{1}, '.txt');
-dlmwrite(sigma_file, [Vg', sigma], 'delimiter',' ','precision',5)

### 2019-03-06 postprocessing/export_2D_data.m

@@ -1,27 +1,0 @@
-[file, path] = uigetfile('./*.mph');
-abs_path = strcat(path, file);
-model = mphopen(abs_path);
-% Add export section
-data = model.result.export.create('2D_data', 'Data');
-data.set('recover', 'pprint'); %use recover setting
-data.set('fullprec', 'off');
-%use grid location
-data.set('location', 'grid');
-data.set('gridx2', 'range(0, (R_p*2-0)/511, R_p*2)');
-data.set('gridy2', 'range(-R_p*2, (R_p * 4)/511, R_p*2)');
-
-%use
-expressions = {'V', 'c_p', 'c_n', 'tds.tflux_c_pz', 'tds.tflux_c_nz'};
-desc = {'Potential', 'c_p', 'c_n', 'cpz', 'cnz'};
-data.set('expr', expressions);
-data.set('descr', desc);
-
-%file
-file_root = strsplit(file, '.');
-txt_file = strcat(path, strcat(file_root{1}, '_2Ddata.txt'));
-data.set('filename', txt_file);
-
-%execute
-
-fprintf('Exporting for file %s ...\n', file);
-data.run();

### 2019-03-06 postprocessing/save_npy.py

@@ -1,20 +1,0 @@
-import numpy
-import os, os.path
-
-# result_path = "../result/concentration/1D"
-# file_root = ["0001", "0005","001", "005",
-             # "01", "05", "1" ]
-
-result_path = "../result/salt/20/"
-file_root = ["NaCl", "LiCl", "MgSO4", "CaCl2", "K2SO4", "K3FeCN", "KCl"]
-for fr in file_root:
-    filename = os.path.join(result_path,
-                            "{}_out_1Ddata.txt".format(fr))
-    print(filename)
-    try:
-        data = numpy.genfromtxt(filename, comments="%")
-    except Exception as e:
-        print(e)
-        continue
-    npy_name = os.path.join(result_path, "{}".format(fr))
-    numpy.save(npy_name, data)

### 2019-03-06 postprocessing/utils.py

@@ -1,100 +1,0 @@
-from matplotlib.patches import Rectangle, Circle, Wedge
-import matplotlib.pyplot as plt
-import numpy
-from scipy.constants import e, epsilon_0, pi, k, N_A
-import os, os.path
-
-pixels = (512, 512)
-
-values = ("V", "c_p", "c_n", "cpz", "cnz")
-
-V_g = [0.001, 0.025, 0.05, 0.1, 0.15, 0.2] + list(numpy.arange(0.25, 1.35, 0.1))
-
-file_template = "{0}.npy"
-
-concentrations = (0.0001, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1)
-
-ratio_conc = 10**3              # 1 mol/L  to 1 mol/m^3
-
-def Debye_length(c0, eps=78,
-                 zp=1, zn=-1):
-    # Assume the c0 is in mol/L
-    c0 *= ratio_conc
-    I = (zp ** 2 * c0 + zn ** 2 * c0) / 2.0
-    return (eps * epsilon_0 * k * 300 / (2 * N_A * e ** 2 * I)) ** 0.5
-    
-
-# reflex the data along the z-axis
-def reflex_data(X, Y, D):
-    XX = numpy.hstack((numpy.fliplr(-X), X))
-    YY = numpy.hstack((numpy.fliplr(Y), Y))
-    DD = numpy.hstack((numpy.fliplr(D), D))
-    return XX, YY, DD
-
-def get_data(filename):
-    data = numpy.load(filename)  # load the npy data
-    data[:, 0:2] /= 1e-9         # convert the data into nm scale
-    return data
-
-
-
-# Add path of graphene to the ax
-# Both left and right edges
-def add_graphene(ax, R_p=20, t_gr=0.67, t_helm=0.3):
-    W = 40
-    h = t_gr + 2 * t_helm
-    h2 = t_gr
-    facecolor_out = "#fafafa"
-    facecolor_in = "#7c7c7c"
-    rect1 = Rectangle((R_p, -h/2), W - R_p, h,
-                      facecolor=facecolor_out)
-    rect2 = Rectangle((-R_p, -h/2), -(W - R_p), h,
-                      facecolor=facecolor_out)
-    wedge1 = Wedge((R_p, 0), h / 2, 90, 270, facecolor=facecolor_out)
-    wedge2 = Wedge((-R_p, 0), h / 2, -90, 90, facecolor=facecolor_out)
-
[…]

### 2019-03-06 data/plots/src/plot_1D.py
Complete adding figures

@@ -2,6 +2,9 @@ from utils import *
 import numpy
 import matplotlib.pyplot as plt
 import os, os.path
+from os.path import join, dirname, exists
+
+curdir = dirname(__file__)
 
 pixels = (512, 512)
 

### 2019-03-06 data/plots/src/plot_1D_sym.py

@@ -3,6 +3,8 @@ import numpy
 import matplotlib.pyplot as plt
 from scipy.constants import e, epsilon_0, pi, k, N_A, hbar
 import os, os.path
+from os.path import join, dirname, exists
+curdir = dirname(__file__)
 
 pixels = (512, 512)
 
@@ -20,8 +22,8 @@ concentrations = (0.0001, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1)
 
 ratio_conc = 10**3
 
-out_path = "../result/radius/10/1D/"
-plot_path = "../plot/radius/1D/"
+out_path = join(curdir, "../data/FEM/concentration/1D")
+plot_path = join(curdir, "../img")
 
 # get the index of column in the new matrix
 def get_col_index(Vg, quantity):
@@ -39,11 +41,17 @@ def delta_phi_gr(sigma):
     fac = hbar * vf / e * numpy.sqrt(pi * numpy.abs(sigma) / e)
     return fac * numpy.sign(sigma)
 
-plot_quantities = ("zflux_cp", "zflux_cn")
+plot_quantities = ("zflux_cp", "zflux_cn", "c_p", "c_n")
+yl = dict(zflux_cp="$J_{z+}$",
+          zflux_cn="$J_{z-}$",
+          c_p="$c_{+}$",
+          c_n="$c_{-}$")
+
 plt.style.use("science")
 
+
 r0 = 10
-for conc in [0.001]:
+for conc in [0.001, 0.1]:
     file_name = os.path.join(out_path, file_template.format(conc))
     data = numpy.load(file_name)
     data[:, 0] /= 1e-9          
@@ -55,9 +63,11 @@ for conc in [0.001]:
         lines = []
         for V in Vg_all:
             y = data[:, get_col_index(V, quant)]
+            if (quant in ("c_p", "c_n")) and (conc == 0.001):
+                y = y / 10
             lines.append(plt.plot(numpy.hstack([-r[::-1], r]) / r0,
                                   numpy.hstack([y[::-1], y]))[0])
-        sigma_file = os.path.join(out_path, sigma_file_template.format(conc))
+        sigma_file = join(out_path, sigma_file_template.format(conc))
         sigma_data = numpy.genfromtxt(sigma_file, comments="%")
         Vg_true = sigma_data[:, 0] + delta_phi_gr(-sigma_data[:, 1])  # True Vg
         print(Vg_true)
@@ -67,13 +77,17 @@ for conc in [0.001]:
[…]

### 2019-03-06 data/plots/src/plot_2D_all.py

@@ -3,6 +3,9 @@ import numpy
 import matplotlib.pyplot as plt
 import os, os.path
 
+from os.path import join, dirname, exists
+curdir = dirname(__file__)
+
 
 pixels = (512, 512)
 
@@ -25,15 +28,15 @@ def get_col_index(Vg, quantity):
     return 2 + len_quant * idx_V + idx_quant
 
 
-out_path = "../result/concentration/2D/"
-plot_path = "../plot/concentration"
+out_path = join(curdir, "../data/FEM/concentration/old/2D")
+plot_path = join(curdir, "../img")
 
 # Vg_plot = (0.001, 0.15)
 Vg_plot = (0.15,)
 
 plt.style.use("science")
 
-for conc in [0.001]:
+for conc in [0.0001]:
     file_name = os.path.join(out_path, file_template.format(conc))
     data = get_data(file_name)  # already in nm
     X = data[:, 0].reshape(*pixels); Y = data[:, 1].reshape(*pixels)
@@ -53,9 +56,11 @@ for conc in [0.001]:
                 vmax = 0
             else:
                 vmax = None
+            print(D.min(), D.max())
             mesh = plot_data(ax, X, Y, D,
-                             vmin=-0.04,
-                             vmax=0)
+                             vmin=D.min(),
+                             vmax=D.max()
+            )
             if quant in ("zflux_cp", "zflux_cn"):
                 mesh.set_cmap("jet_r")
             ax.set_title("{0} mol/L-{1} V-{2} ({3})".format(conc,
@@ -68,10 +73,10 @@ for conc in [0.001]:
             add_graphene(ax, R_p=10)
             fig.colorbar(mesh, fraction=0.03)
             fig.tight_layout()
-            outfile = os.path.join(plot_path,
-                                     "{0}-{1}-{2}.svg".format(conc,
-                                                              Vg,
-                                                              quant))
+            outfile = join(plot_path,
+                           "{0}-{1}-{2}.svg".format(conc,
+                                                    Vg,
+                                                    quant))
             print(outfile)
             fig.savefig(outfile)
             

### 2019-03-06 data/plots/src/plot_elechem_potential.py

@@ -2,6 +2,7 @@ from utils import *
 import numpy
 import matplotlib.pyplot as plt
 import os, os.path
+from os.path import join, dirname, abspath, exists
 
 
 pixels = (512, 512)
@@ -24,9 +25,9 @@ def get_col_index(Vg, quantity):
     len_quant = len(quantities)
     return 2 + len_quant * idx_V + idx_quant
 
-
-out_path = "../result/concentration/2D/"
-plot_path = "../plot/concentration"
+curdir = dirname(__file__)
+out_path = join(curdir, "../data/FEM/concentration/old/2D")
+plot_path = join(curdir, "../img")
 
 # Vg_plot = (0.001, 0.15)
 Vg_plot = (0.15,)

### 2019-03-06 data/plots/src/plot_pore_diameter.py

@@ -2,6 +2,8 @@ import numpy
 import matplotlib.pyplot as plt
 import os
 from os.path import dirname, join, exists
+from utils import Debye_length
+import pickle
 curdir = dirname(__file__)
 
 """
@@ -20,3 +22,44 @@ plt.hist(repeat, numpy.arange(5,66,5))
 plt.xlabel("Pore Radius (nm)")
 plt.ylabel("Frequencies")
 plt.savefig(join(curdir, "../img/radius_dist.svg"))
+
+
+
+"""
+Exp pore distr with lambda_D
+"""
+lambda_D = Debye_length(c0=1.1e-4)
+print(lambda_D)
+rr = numpy.arange(10, 110)
+xx = lambda_D / ((rr + 10) * 1e-9) * 1.75
+
+fig = plt.style.use("science")
+
+func_rec_interp = pickle.load(open(join(curdir,
+                                   "../data/FEM/concentration/1D",
+                                   "rect_2d_intep.pickle"), "rb"))
+
+xi = func_rec_interp(1.25, xx)
+
+plt.figure(figsize=(2.8, 2.3), facecolor="w")
+repeat = [d for d, n in data for _ in range(int(n * (d /2) ** 2))]
+plt.hist(repeat, numpy.arange(5,66,5), normed=True)
+ax = plt.gca()
+ax2 = ax.twiny()
+ax3 = ax.twinx()
+ax2.set_xticks(lambda_D / numpy.arange(0.5, 3.5, 0.5) * 2 / 1e-9)
+ax2.set_xticklabels(list(map(str, numpy.arange(0.5, 3.5, 0.5))))
+ax3.plot(rr, xi.flat[::-1])
+# ax.set_xlim(10, 110)
+ax.set_xlabel("Pore diameter (nm)")
+ax.set_ylabel("$w(r_{\mathrm{G}})$")
+ax2.set_xlabel("$\lambda_{\\mathrm{D}} / r_{\\mathrm{G}}$")
+ax3.set_ylabel("$\\xi(r_{\\mathrm{G}})$")
+ax3.set_ylim(0, 0.98)
+# ax.set_xticks(numpy.arange(0.5, 3.5, 0.5) / 2 * lambda_D / 1e-9)
+# plt.ylim(0, 0.04)
+# plt.hist(repeat[::-1], xx[::-1])
+# plt.ylim(0, 0.04)
+ # plt.yticks([0, 0.02, 0.04])
[…]

### 2019-03-06 data/plots/src/plot_rec_all.py

@@ -51,7 +51,7 @@ if __name__ == "__main__":
                          # fmt="o",
                          # alpha=0.5, label=name)
     plt.ylim(-0.1, 0.9)
-    plt.xlim(-1.25, 1.25)
+    plt.xlim(0, 1.25)
     plt.xlabel("$V_{\\mathrm{G}}$ (V)")
     plt.ylabel("Rectification")
     plt.legend()

### 2019-03-06 data/plots/src/plot_salt_pore_rec.py

@@ -141,7 +141,7 @@ def plot_rec_pore_dist():
     rg = exp_data[:, 0] / 2 + 2.5
     w = exp_data[:, 1] * rg ** 2
     w = w / numpy.sum(w)
-    fig = plt.figure(figsize=(2.8, 2.3))
+    fig = plt.figure(figsize=(2.8, 2.8))
     plt.style.use("science")
     results = []
     for salt in salts:

### 2019-03-06 data/plots/src/plot_surface_contour.py

@@ -1,105 +1,0 @@
-from utils import *
-import matplotlib
-import numpy
-import matplotlib.pyplot as plt
-import os, os.path
-from os.path import dirname, join, exists
-from scipy.constants import pi, hbar, e
-from scipy.interpolate import griddata
-vf = 1.1e6
-
-curdir = dirname(__file__)
-
-"""
-Plot Vg surface contour
-"""
-
-# Use C/m^2
-def delta_phi_gr(sigma):
-    fac = hbar * vf / e * numpy.sqrt(pi * numpy.abs(sigma) / e)
-    return fac * numpy.sign(sigma)
-
-quantities = ("V", "c_p", "c_n", "zflux_cp", "zflux_cn")
-units = ("V", "mol/m$^{3}$", "mol/m$^{3}$", "mol/(m$^{2}$*s)", "mol/(m$^{2}$*s)")
-# get the index of column in the new matrix
-def get_col_index(Vg, quantity):
-    idx_V = Vg_all.index(Vg)
-    idx_quant = quantities.index(quantity)
-    len_quant = len(quantities)
-    return 1 + len_quant * idx_V + idx_quant
-
-Vg_true = []
-Vg_all = [0.001, *numpy.arange(0.025, 0.251, 0.025)]
-
-file_template = "{0}.npy"
-sigma_file_template = "sigma_{0}.txt"
-
-concentrations = (0.0001, 0.0002, 0.0005,
-                  0.001, 0.002, 0.005,
-                  0.01, 0.02, 0.05, 0.1)
-
-ratio_conc = 10**3
-
-out_path = join(curdir, "../data/FEM/concentration/1D/")
-plot_path = join(curdir, "../img/")
-
-res = []
-for i, conc in enumerate(concentrations):
-    sigma_file = join(out_path, sigma_file_template.format(conc))
-    sigma_data = numpy.genfromtxt(sigma_file, comments="%")
-    V_ = sigma_data[:, 0]; sig_ = -sigma_data[:, 1]
-    Vg_ = V_ + delta_phi_gr(sig_)
-    [res.append((Vg_[i], conc, V_[i])) for i in range(len(V_))]
-
-res = numpy.array(res)
-
-v = res[:, 0]
-lambda_d = Debye_length(res[:, 1]) / 1e-9
-psi_g = res[:, 2]
-
[…]

### 2019-03-06 data/plots/src/utils.py

@@ -73,8 +73,8 @@ def plot_data(ax, X, Y, D, vmin=None, vmax=None):
     ax.set_aspect('equal')
     XX, YY, DD = reflex_data(X, Y, D)
     return ax.pcolormesh(XX, YY, DD,
-                         vmin=vmin, vmax=vmax,
-                  rasterized=True,
+                         # vmin=vmin, vmax=vmax,
+                         rasterized=True,
                          cmap="jet")
 
 

### 2019-03-06 paper/SI.tex
Add more analysis into SI

@@
 \usepackage{xr-hyper}
+\usepackage{xcolor}
 \externaldocument[main-]{paper}
@@
 
+\section{Effect of pore size distribution}
+\label{sec:pore-dist}
+
+One practical issue with large-area nanoporous graphene samples is
+that the unavoidable large pores will act as preferred pathways for
+the transported species and strongly attenuates the salt rejection
+effect. In this section we provide a detailed discussion about the
+influence of pore size distribution on the salt rejection through the
+PG-PCTE membrane. As seen from main text \Fig{} \ref{main-fig:1}c
+inset, the average distance between individual nanopores is larger
+than the largest Debye length studied here ($\sim{}$ 30 nm for 1 mM 1:1
+salt solution), we can assume that the ionic transport pathways
+through different nanopores do not influence each other and the total
+ionic flux $\boldsymbol{J}_{\mathrm{PG}}$ is the summation of fluxes
+through individual pores $\boldsymbol{J}_{i}$:
+\begin{equation}
+\label{eq:J-total}
+\boldsymbol{J}_{\mathrm{PG}} = \sum_{i} \boldsymbol{J}_{i} = \sum_{r_{i}} x_{r_{i}} \boldsymbol{J}_{r_{i}}
+\end{equation}
+where $r_{i}$ is the radius of individual pores,
+$\boldsymbol{J}_{r_{i}}$ and $x_{r_{i}}$ are the flux of individual
+pore and the distribution probability when
+$r_{\mathrm{G}} = r_{i}$. The salt rejection factor
+$\xi$ through graphene is then expressed as:
+\begin{equation}
+  \label{eq:xi-pore}
+  \begin{aligned}
+    \xi &= 1 - \frac{\sum_{r_{i}} \boldsymbol{J}_{r_{i}} x_{r_{i}}}
+           {\sum_{r_{i}} \boldsymbol{J}_{r_{i}}(V_{\mathrm{G}} = 0) x_{r_{i}}} \\
+           &= 1 - \frac{\sum_{r_{i}} \hat{J}_{r_{i}} r_{i}^{2} x_{r_{i}}}
+           {\sum_{r_{i}} \hat{J}_{r_{i}}^{0} r_{i}^{2} x_{r_{i}}} \\
+           % &approx 1 - \sum_{r_{i}} \frac{\hat{J}_{r_{i}}}{\hat{J}_{r_{i}}^{0}}
+           % \frac{r_{i}^{2} x_{r_{i}}} {\sum_{r_{i}} r_{i}^{2} x_{r_{i}}} \\
+           &\approx \sum_{r_{i}} \left(1 -  \frac{\hat{J}_{r_{i}}}{\hat{J}_{r_{i}}^{0}}\right) w_{r_{i}} \\
+           &= \sum_{r_{i}} \xi_{r_{i}} w_{r_{i}}
+  \end{aligned}
+\end{equation}
+where $\hat{J}$ and $\hat{J}^{0}$ are the flux normalized by pore area
+when $V_{\mathrm{G}} = 0$ and $V_{\mathrm{G}} \neq 0$, respectively,
+$w_{r_{i}} = x_{r_{i}} r_{i}^{2} / sum_{r_{i}} x_{r_{i}} r_{i}^{2}$ is
+the contribution to the salt rejection from individual pore rejection
+rate $\xi_{r_{i}}$. The linear combination between $\xi_{r_{i}}$ and
+$\xi$ comes from the assumption that $\hat{J}^{0}$ is independent of
+the pore size from the simple Ficknian diffusion.
+
+To get an insight of the influence of the pore size distribution on
+the salt rejection, we combine Equation \ref{eq:xi-pore} with main
+text \Fig{} \ref{main-fig:5}b for the salt rejection of a 1:1
+electrolyte to get the pore-distribution-related salt rejection, where
+the pore distribution is taken from the SEM image of real samples (for
+instance main text \Fig{} \ref{main-fig:1}c inset). \Fig{}
+\ref{fig:simple-rect-pore}a shows the contribution $w$ and $\xi$ as
+a function of $r_{\mathrm{G}}$ for individual pores when
+$V_{\mathrm{G}}$ = 1.25 V. As can be seen, the majority of pores fall
+within the regime of $\lambda_{\mathrm{D}} / r_{\mathrm{G}} > 1$,
+corresponding to $\xi(r_{\mathrm{G}}) > 0.6$. As a result, considering
+the pore distribution reduces the value of $\xi$ to $\sim{}$80\% to
+that of a single 20 nm-diameter nanopore (\Fig{}
+\ref{fig:simple-rect-pore}b), which is indeed close to the highest
+$\xi$ values experimentally observed (for 1mM NaCl system). Such high
+salt rejection even after considering the pore size distribution, can
+be explained by the non-linear nature of $\xi$ with $r_{\mathrm{G}}$
+and $V_{\mathrm{G}}$. As seen in main text Fig{} \ref{main-fig:5}b,
+for large $V_{\mathrm{G}}$ and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
+regions, $\xi$ reaches a ``plateau'' with its value close to 1. For
+the fabricated PG samples, most pores are within such region when
+$V_{\mathrm{G}}$ = 1.25 V and $c_{0}$ = 0.1 mM, which gives a minor
+change of $\xi$ dispite the wide span of pore sizes. In other words,
+although nanopres as large as 60 nm exist in the system, considerably
+high salt rejection more than 80\% can still be achieved.
+
+\begin{figure}[htbp]
+  \centering
+   \includegraphics[width=0.9\linewidth]{img/SI-simple-pore-dist.pdf}
+   \caption{Salt rejection after considering the pore size
+     distribution. \textbf{a}. $w$ (left axis) and $\xi$ (right axis)
+     as a function of $r_{\mathrm{G}}$ for the experimental pore size
+     distribution with $c_{0}$ = 0.1 mM and $V_{\mathrm{G}}$ = 1.25 V.
+     \textbf{b}. Salt rejection ratio $\xi$ as a function of $V_{\mathrm{G}}$ of a
+     0.1mM 1:1 salt from a 20 nm-diameter nanopore (blue line) and
+     from the experimental pore size distribution (orange line), by
+     applying Equation \ref{eq:xi-pore} to main text \Fig{}
+     \ref{main-fig:5}b.}
+  \label{fig:simple-rect-pore}
+\end{figure}
+
+To include the pore size distribution effect for all the salts
+studied, we performed FEM analysis for the salt rejection through
+single nanopore of different salts with $r_{\mathrm{G}}$ ranges from
+2.5 nm to 35 nm, while keeping $c_{0}$ constant at 0.1 mM. As shown in
+\Fig{} \ref{fig:xi-salts-pore}, the behavior of $\xi$ vary with the
+type of salt. As expected, the overall $\xi$ for monovalent salts
+(KCl, NaCl, LiCl) is larger than multivalent salts due to the longer
+Debye length. Moreover, $\xi$ of monovalent salts varies less with the
+pore size compared with multivalent salts. This can be explained by
+the non-linear dependency of $\xi$ on
+$\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ as discussed above. Combine
+the FEM-simulated $\xi$ values with the experimental pore size
+distribution, we obtain main text \Fig{} \ref{main-fig:6}.
+
+\begin{figure}[htbp]
+  \centering
+   \includegraphics[width=0.75\linewidth]{img/SI-xi-salt-pore-size.pdf}
+  \caption{FEM-simulated salt rejction ratio $\xi$ as a function of
+    $V_{\mathrm{G}}$ through single nanopores for different salts with
+    varied pore radius. All salts have concentration $c_{0}$ = 0.1 mM.}
+  \label{fig:xi-salts-pore}
+\end{figure}
+
 \pagebreak
+
+\section{Further discussion about the ionic pathway near the graphene pore}
+\label{sec:conc}
+
+In this section we provide a more detailed discussion about the
+different ionic pathways through the graphene nanopore upon gating in
+main text \Fig{} \ref{main-fig:4}b. As disccused in the main text, the
+ionic migration is contributed by both diffusion (caused by
+concentration gradient) and electrostatic drift (caused by electric
+field).  The effect of salt rejection can be viewed as follows: when
+$V_{\mathrm{G}}$ = 0, the flux $\boldsymbol{J}_{\mathrm{G}}$ is solely
+contributed by the concentration gradient, while after applying a
+positive $V_{\mathrm{G}}$, distinct pathways for cations /
+anions are created and the drift flux balances the diffusion.
+
+Applying a positive $V_{\mathrm{G}}$ changes the surface distribution
+of the cations / anions. To see this, we plot the concentrations of
+cation ($c_{+}$) and anion ($c_{-}$) near a graphene nanopore with
+$r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM and $\psi_{\mathrm{G}}$ =
+0.15 V, as shown in \Fig{} \ref{fig:conc}a and \ref{fig:conc}b,
+respectively. The cations are depleted from the graphene surface,
+while the anions are accumulated due to positive
+$\psi_{\mathrm{G}}$. The anion concentration at the graphene surface
+is enhanced $\sim{}$35 times compared with the bulk concentration in
+HCR. The thickness of the depletion / accumulation layer is affected
+by the bulk concentration. Here we show this by comparing the radial
+distribution of $c_{+}$ and $c_{-}$ along the $z = 0$ line within the
+graphene pore. \Fig{} \ref{fig:conc-r} shows such radial ionic
+concentration distribution at different $c_{0}$ and $V_{\mathrm{G}}$
+levels. When $c_{0}$ = 0.1 mM, $\lambda_{\mathrm{D}}$ is larger than
+$r_{\mathrm{G}}$, and the external gate voltage $V_{\mathrm{G}}$ has
+control over both $c_{-}$ and $c_{+}$ within the graphene nanopore
+(\Fig{} \ref{fig:conc-r}a and \ref{fig:conc-r}c). On the other
+hand, when $c_{0}$ = 100 mM, $\lambda_{\mathrm{D}}$ is much smaller
+than $r_{\mathrm{G}}$, and the concentration is only affected by
+$V_{\mathrm{G}}$ close to the pore edge (\Fig{} \ref{fig:conc-r}b
+and \ref{fig:conc-r}d). Therefore by increasing $c_{0}$ (and
+equivalently reducing $\lambda_{\mathrm{D}}$), $V_{\mathrm{G}}$ loses
+control over the transport in the center of the pore and leads to a
+lower $\xi$ value. Due to the existence of graphene quantum
+capacitance, the surface potential $\psi_{\mathrm{G}}$ is essentially
+smaller than $V_{\mathrm{G}}$, and the maximum surface anion
+concentration ($c_{0}$ = 100 mM, $V_{\mathrm{G}}$ = 1.25 V) is
+$\sim{}$3 M, much smaller than the saturated surface adsorption
+density (at the order of 10$^{2}$ M
+\cite{bard_electrochemical_1980}). Therefore we expect the surface
+enhancement of the anions under the FEM conditions to be realistic and
+the influence of the anion concentration on the diffusivity is minimal
+\cite{Tang_1999_I}.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-concentration.pdf}
+  \caption{Cation concentration $c_{+}$ (\textbf{a}.) and anion
+    concentration $c_{-}$ (\textbf{b}.) near the graphene nanopore
+    with $r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM, and
+    $\psi_{\mathrm{G}}$ = 0.15 V, for a KCl solution at 0.1
+    mM. Depletion of cation and accumulation of anion can be observed
+    near the graphene surface.}
+  \label{fig:conc}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.75\linewidth]{img/SI-conc-r.pdf}
+  \caption{Radial distribution of ions along the line $z=0$ within a
+    graphene nanopore with $r_{\mathrm{G}}$ = 10 nm: (\textbf{a}.)
+    $c_{+}$ at $c_{0}$ = 0.1 mM, (\textbf{b}.) $c_{+}$ at $c_{0}$ =
+    100 mM, (\textbf{c}.) $c_{-}$ at $c_{0}$ = 0.1 mM and
+    (\textbf{d}.) $c_{-}$ at $c_{0}$ = 100 mM. The lines with varied
+    colors indicate the difference of $V_{\mathrm{G}}$ applied.}
+  \label{fig:conc-r}
+\end{figure}
+
+Next we analyze the diffusion and drift contributions to the ionic
+transport. As shown in \Fig{} \ref{fig:potential}, the
+electrochemical potential energy $\mu_{i}$ is decomposed into the
+electric potential energy $z_{i} c_{i} \psi_{i}$ (\Fig{}
+\ref{fig:potential}a and \ref{fig:potential}b) and the chemical
+potential energy $k_{\mathrm{B}}T \ln x_{i}$ (\Fig{}
+\ref{fig:potential}c and \ref{fig:potential}d) near a graphene
+nanopore with $r_{\mathrm{G}}$ = 10 nm and $\psi_{\mathrm{G}}$ = 0.15
+V. The transport of cations is dominated by its chemical potential and
+the diffusion is prominent in the center of the pore. On the other
+hand, the electric and diffusive potential energies are similar with
+opposite signs and counterbalance each other. This explains the
+relatively smaller electrochemical potential of anions in main text
+\Fig{} \ref{main-fig:4}b. As a result, different pathways for cations
+and anions emerge that cations preferably pass through the pore
+center, while anions mainly pass near the pore edge, as shown in
+\Fig{} \ref{fig:flux}.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-electrochemical-decomposite.pdf}
+  \caption{Decomposition of electrochemical potential near a nanopore
+    corresponding to main text \Fig \ref{main-fig:4}. \textbf{a}. The electrostatic
+    (drift) contribution to the electrochemical potential for cation
+    (left) and anion (right) and \textbf{b}. The concentration (diffusion)
+    contribution to the electrochemical potential for cation (left)
+    and anion (right). The relative small order of magnitude for anion
+    electrochemical potential is caused by the balance between the
+    diffusion and drift for anion.}
+  \label{fig:potential}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-flux.png}
+  \caption{z-component fluxes of cation ($J_{z+}$, \textbf{a}.)  and
+    anion ($J_{z-}$ \textbf{b}.) near the graphene nanopore
+    corresponding to \Fig{} \ref{main-fig:4}b in main text. The
+    pathways for the different ions can be spatially distinguished:
+    the flux of cation passes mostly through the center of the
+    graphene nanopore while the anion passes mainly through the
+    edge. The analysis is in consistent with the gradient of chemical
+    potential as shown in the main text \Fig{} \ref{main-fig:4}b.}
+  \label{fig:flux}
+\end{figure}
+
+We note that when the surface potential $\psi_{\mathrm{G}}$ of
+graphene further increases, the salt rejection may be weakened, or
+even enhanced salt transport is observed. To see this we artificially
+increase the $\psi_{\mathrm{G}}$ up to over 1 V when not considering
+the limiting effect of graphene quantum capacitance. As seen in \Fig{}
+\ref{fig:reverse}, for each salt concentration $c_{0}$, the averaged
+total flux $J_{z}$ does not further decrease when $\psi_{\mathrm{G}}$
+is larger than a critical potential $V_{\mathrm{c}}$. At low $c_{0}$,
+further increasing $\psi_{\mathrm{G}}$ over $V_{\mathrm{c}}$ may even
+enhance the flux, leading to a negative $\xi$. The reserve of the salt
+rejection at higher $V_{\mathrm{G}}$ values is caused by the enhanced
+anion flux around the pore edge, while the cation flux saturates
+(\Fig{} \ref{fig:large-V}). Such flux enhancement resemble that in an
+ionic transistor \cite{Nam_2009,Cheng_2018} when ionic current rises
+by applying gate voltage. Nevertheless, such regime may not be easy to
+be observed experimentally as the $V_{\mathrm{G}}$ applied may already
+exceed the electrochemical window of water, due to the quantum
+capacitance of graphene.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.5\linewidth]{img/SI-rect-reverse.pdf}
+  \caption{Average total flux $J_{z}$ in the nanopore as
+    a function of $\psi_{\mathrm{G}}$ at different concentrations. The
+    range of $\psi_{\mathrm{G}}$ is larger than the experimentally
+    achievable value. The rectification of flux becomes weaker after a
+    certain level of $\psi_{\mathrm{G}}$ is reached. Further
+    increasing the surface potential of graphene may even enhance the
+    transportation of ions, which is similar to the cases of ionic
+    transistors.}
+  \label{fig:reverse}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-flux-larger.png}
+  \caption{Spatial distribution of $J_{z}$ at $z = 0$ as a function
+    of $r$ in a nanopore with $r_{\mathrm{G}}$ = 20 nm, at different
+    levels of $\psi_{\mathrm{G}}$ (larger than experimentally
+    achievable values) for cation (\textbf{a}.) and anion
+    (\textbf{b}.). The cation flux becomes nearly saturated with
+    increasing $\psi_{\mathrm{G}}$, while the flow of anion near the
+    pore edge becomes much larger. The drastic increase of
+    pore-bounded anion flux is caused by the accumulation of anions
+    near the graphene surface, and in turn causes the increasing of
+    total flux as seen in \Fig \ref{fig:reverse}.}
+  \label{fig:large-V}
+\end{figure}
+\clearpage{}
+
 \section{Further details of the numerical simulation }
@@
 
-\section{Further numerical simulation results}
-\label{sec:simu-res}
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.8\linewidth]{img/SI-concentration.png}
-  \caption{Cation concentration $c_{+}$ (\textbf{a}.) and anion
-    concentration $c_{-}$ (\textbf{b}.) near the graphene nanopore for
-    KCl solution at 0.1 mM. Depletion of cation and accumulation of
-    anion can be observed near the graphene surface.}
-  \label{fig:conc}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.8\linewidth]{img/SI-electrochemical-decomposite.pdf}
-  \caption{Decomposition of electrochemical potential near a nanopore
-    corresponding to \Fig 4 in main text. \textbf{a}. The electrostatic
-    (drift) contribution to the electrochemical potential for cation
-    (left) and anion (right) and \textbf{b}. The concentration (diffusion)
-    contribution to the electrochemical potential for cation (left)
-    and anion (right). The relative small order of magnitude for anion
-    electrochemical potential is caused by the balance between the
-    diffusion and drift for anion.}
-  \label{fig:potential}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.8\linewidth]{img/SI-flux.png}
-  \caption{z-component flux $\boldsymbol{J}_{z}$ of cation
-    (\textbf{a}.)  and anion (\textbf{b}.) near the graphene nanopore
-    corresponding to Figure 4b in main text. The pathways for the
-    different ions can be spatially distinguished: the flux of cation
-    passes mostly through the center of the graphene nanopore while
-    the anion passes mainly through the edge. The analysis is in
-    consistent with the gradient of chemical potential as shown in the
-    main text \Fig 4b.}
-  \label{fig:flux}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.5\linewidth]{img/SI-rect-reverse.pdf}
-  \caption{Average total flux $\boldsymbol{J}_{z}$ in the nanopore as
-    a function of $\psi_{\mathrm{G}}$ at different concentrations. The
-    range of $\psi_{\mathrm{G}}$ is larger than the experimentally
-    achievable value. The rectification of flux becomes weaker after a
-    certain level of $\psi_{\mathrm{G}}$ is reached. Further
-    increasing the surface potential of graphene may even enhance the
-    transportation of ions, which is similar to the cases of ionic
-    transistors.}
-  \label{fig:reverse}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.8\linewidth]{img/SI-flux-larger.png}
-  \caption{Spatial distribution of $\boldsymbol{J}_{z}$ as a function
-    of $r$ in a 20 nm nanopore at different levels of
-    $\psi_{\mathrm{G}}$ (larger than experimentally achievable values)
-    for cation (\textbf{a}.) and anion (\textbf{b}.). The cation flux
-    becomes nearly saturated with increasing $\psi_{\mathrm{G}}$,
-    while the flow of anion near the pore edge becomes much
-    larger. The drastic increase of pore-bounded anion flux is caused
-    by the accumulation of anions near the graphene surface, and in
-    turn causes the increasing of total flux as seen in \Fig
-    \ref{fig:reverse}.}
-  \label{fig:large-V}
-\end{figure}
-\clearpage{}
-
 \section{Conductivity and Debye length for all salts}

### 2019-03-06 paper/SI.tex
Correct psiG to VG

@@
 cation ($c_{+}$) and anion ($c_{-}$) near a graphene nanopore with
-$r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM and $\psi_{\mathrm{G}}$ =
-0.15 V, as shown in \Fig{} \ref{fig:conc}a and \ref{fig:conc}b,
+$r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM and $V_{\mathrm{G}}$ =
+0.75 V, as shown in \Fig{} \ref{fig:conc}a and \ref{fig:conc}b,
 respectively. The cations are depleted from the graphene surface,
@@
     with $r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM, and
-    $\psi_{\mathrm{G}}$ = 0.15 V, for a KCl solution at 0.1
+    $V_{\mathrm{G}}$ = 0.75 V, for a KCl solution at 0.1
     mM. Depletion of cation and accumulation of anion can be observed
@@
 \ref{fig:potential}c and \ref{fig:potential}d) near a graphene
-nanopore with $r_{\mathrm{G}}$ = 10 nm and $\psi_{\mathrm{G}}$ = 0.15
+nanopore with $r_{\mathrm{G}}$ = 10 nm and $V_{\mathrm{G}}$ = 0.75
 V. The transport of cations is dominated by its chemical potential and

### 2019-03-06 paper/paper.tex
Add changes to manuscript

@@
 Section \ref{SI-sec:R-model}).
-% \todo[inline]{Make sure that the
-  % values used are correct.}
-
-% The diffusive transport resistance through graphene pores scales with $\sim$ 1/D while
-% for a PCTE pore, the scaling follows $\sim$ L/D$^2$ \cite{O_Hern_2014},
- % D being the respective diameter and L the channel length. 
-% Taking into account that there are 10 graphene pores
-% per PCTE pore on average, the transport resistance ratio of R$_{graphene}$/R$_{PCTE}$ is roughly 1/30,
- % indicating that the PCTE dominates the overall ion transport, which is in line 
- % with the observed behavior.
-
-%Interestingly, we observed a pronounced decrease of diffusive flux in KCl,
-%K$_{2}$SO$_{4}$ and K$_{3}$[Fe(CN)$_{6}$] systems but not for the rest
-%of the salts. We hypothesized that the strong cation-$\pi$ interactions
-%between K$^{+}$ cations and graphene slow down the migration of cations
-%along the surface-mediated transport pathway \cite{Sun_2014}.
 
@@
 that the concentration gradient at the pore center becomes small (see
-Supplementary \Fig{} \ref{SI-fig:conc}). We also observe that
-$\Delta \mu_{+}$ is dominated by the concentration, while
-$\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
-between the diffusion and drift potentials (see Supplementary \Fig{}
-\ref{SI-fig:potential}). The observations confirm the distinct ionic
+Supplementary Section \ref{SI-sec:conc}, Supplementary
+Figs. \ref{SI-fig:conc} and \ref{SI-fig:conc-r}). Although the surface
+concentration of anions is enhanced by $\sim{}$30 times, it is sill
+much smaller than the saturated surface adsorption density, and the
+bulk diffusivity used in the Nernst-Planck equation still holds.  We
+also observe that $\Delta \mu_{+}$ is dominated by the concentration,
+while $\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the
+balance between the diffusion and drift potentials (see Supplementary
+Section \ref{SI-sec:conc}, Supplementary Figs.  \ref{SI-fig:potential}
+and \ref{SI-fig:flux}). The observations confirm the distinct ionic
 transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
@@
 \cite{Biesheuvel_2010}, where electrodes with large surface area are
-required.
+required. More detailed discussion about the selective ionic pathways
+upon gating can be found in Supplementary Section \ref{SI-sec:conc}.
 
@@
 considering the same system (details see Supplementary Section
-\ref{SI-sec:simu-res}). Intriguingly, by increasing
-$\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux starts to
-increase, reversing the trend observed at the low $\psi_{\mathrm{G}}$
-regime, due to (i) the drift flux become dominant over diffusion flux
-and (ii) the concentration near the pore edge (preferred path) greatly
-increases (details see Supplementary Section \ref{SI-sec:simu-res},
-Supplementary Figs. \ref{SI-fig:reverse} and
-\ref{SI-fig:large-V}). This level of $\psi_{\mathrm{G}}$ cannot be
-reached experimentally in graphene membrane, as this requires a
-$V_{\mathrm{G}}$ larger than 2.0 V, which triggers the electrochemical
-reactions \cite{Toh_2011}. On the other hand, in an IFET, the electric
-potential on the pore wall is considerably higher, equivalent to
-$V_{\mathrm{G}}$ due to the metallic nature of gate electrode (having
-an infinitely-large quantum capacitance). We therefore conclude that
-the quantum capacitance-induced nonlinear damping in the surface
-potential results in the observed salt rejection.  Following the above
-discussions, we further investigate the physical limits for the biased
-graphene nanopores. Specifically, the salt rejection characteristics
-are controlled by: (i) the overlap of EDL inside the nanopore,
-essentially controlled by two length scales of $\lambda_{\mathrm{D}}$
-and $r_{\mathrm{G}}$, and (ii) the graphene surface potential
+\ref{SI-sec:conc}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
+larger than 400 mV, the ionic flux starts to increase, reversing the
+trend observed at the low $\psi_{\mathrm{G}}$ regime, due to (i) the
+drift flux become dominant over diffusion flux and (ii) the
+concentration near the pore edge (preferred path) greatly increases
+(details see Supplementary Section \ref{SI-sec:conc}, Supplementary
+Figs. \ref{SI-fig:reverse} and \ref{SI-fig:large-V}). This level of
+$\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
+membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V, which
+triggers the electrochemical reactions \cite{Toh_2011}. On the other
+hand, in an IFET, the electric potential on the pore wall is
+considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
+metallic nature of gate electrode (having an infinitely-large quantum
+capacitance). We therefore conclude that the quantum
+capacitance-induced nonlinear damping in the surface potential results
+in the observed salt rejection.  Following the above discussions, we
+further investigate the physical limits for the biased graphene
+nanopores. Specifically, the salt rejection characteristics are
+controlled by: (i) the overlap of EDL inside the nanopore, essentially
+controlled by two length scales of $\lambda_{\mathrm{D}}$ and
+$r_{\mathrm{G}}$, and (ii) the graphene surface potential
 $\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
@@
 required to elucidate electrolyte transport approaching the small pore
-limit.
-% Nevertheless
-% the salt rejection of the gated graphene platform may be further
-% improved after considering the following aspects: (i) the mean-field
-% theory used here may be incorrect to be applied to pores smaller than
-% 5 nm, where individual particle properties of solvated ions can be
-% important \cite{Jain_2015}, (ii) the specific ion-graphene adsorption
-% may also be included to account for the pore selectivity between salt
-% species \cite{Rollings_2016}.
+limit. We note that the FEM simulation is based on the ionic transport
+through single graphene nanopore, while in reality the nanopores has a
+considerable distribution (\Fig{} \ref{fig:1}c inset) which may weaken
+the salt rejection due to existence of larger pores. Since the average
+spacing between the nanopores are comparable or larger than the Debye
+length, we ignore the influence between the individual nanopores and
+assume that the overall salt rejection $\xi$ is a linear combination
+of salt rejection $\xi_{r_{i}}$, from individual pores with radius $r_{i}$:
+\begin{equation}
+\label{eq:rejection-comb}
+\xi = \sum_{r_{i}} \xi_{r_{i}} w_{r_{i}}
+\end{equation}
+where
+$w_{r_{i}} = x_{r_{i}} r_{i}^{2} / \sum_{r_{i}} x_{r_{i}} r_{i}^{2} $
+is the contribution factor from pores with radius $r_{i}$, and
+$x_{r_{i}}$ is the distribution probability of pores with radius
+$r_{i}$ (details see Supplementary Section
+\ref{SI-sec:pore-dist}). Combining Eq. \ref{eq:rejection-comb} and
+\Fig{} \ref{fig:5}b, we estimate that the experimental pore
+distribution reduces the salt rejection to $\sim{}$80 \% of that from
+a 20 nm nanopore when $c_{0}$ = 0.1 mM (\Fig{}
+\ref{SI-fig:simple-rect-pore}). Consider the existence of large pores
+with diameter up to 60 nm, such degree of salt rejection is still
+appreciable, which is ascribed to the nonlinear dependency of $\xi$ on
+$\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (details
+see Supplementary Section \ref{SI-sec:pore-dist}).
 
@@
 endorsed by our simulations, in which we calculate $\xi$ as a function
-of $V_{\mathrm{g}}$ using the same simulation setups (\Fig{}
-\ref{fig:6}b). The calculated $\xi_{\mathrm{max}}$ values are
-quantitatively compared with experiments (\Fig{} \ref{fig:6}c), and
-the same trend is observed. Indeed, because the Debye length
-$\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
-surface potential appears to decrease in the multivalent salt systems,
-thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b). The calculated and
-experimental $\xi_{\mathrm{max}}$ as a function of
-$\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
-species considered here (\Fig{} \ref{fig:6}d). Similar to the
-experimental observations, small difference between the $\xi$ of salts
-with same valence (e.g. LiCl, NaCl and KCl) is also predicted from the
-simulations due to the variation in ionic mobilities. We notice that
-without any fitting parameters, our theory can predict the
-experimental values reasonably well.  In addition, the
-$\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$ dependence is approximately
-linear, suggesting that the effect of Debye length is dominant over
-the salt diffusivity. This finding also explains the concentration
-dependence of $\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
+of $V_{\mathrm{G}}$ using the same simulation setups (\Fig{}
+\ref{fig:6}b). The effect of pore size distribution is explicitly
+considered using the FEM simulation results with different pore sizes
+(Supplementary \Fig{} \ref{SI-fig:xi-salts-pore}). The calculated
+$\xi_{\mathrm{max}}$ values are quantitatively compared with
+experiments (\Fig{} \ref{fig:6}c), and the same trend is
+observed. Indeed, because the Debye length $\lambda_{\mathrm{D}}$
+decreases with the salt valence, the graphene surface potential
+appears to decrease in the multivalent salt systems, thereby reducing
+$\xi$ (see \Fig{} \ref{fig:5}b). The calculated and experimental
+$\xi_{\mathrm{max}}$ as a function of $\lambda_{\mathrm{D}}$ are
+consequently plotted, for the seven salt species considered here
+(\Fig{} \ref{fig:6}d). Similar to the experimental observations, small
+difference between the $\xi$ of salts with same valence (e.g. LiCl,
+NaCl and KCl) is also predicted from the simulations due to the
+variation in ionic mobilities. We notice that without any fitting
+parameters, our theory can predict the experimental values reasonably
+well.  In addition, the $\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$
+dependence is approximately linear, suggesting that the effect of
+Debye length is dominant over the salt diffusivity. This finding also
+explains the concentration dependence of $\xi_{\mathrm{max}}$ observed
+in \Fig{} \ref{fig:2}d, as
 $\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$. Further including the

### 2019-05-16 paper/convert_svg.py
Add converting script and SI

@@ -32,7 +32,7 @@ def convert_pdf(infile, outdir="./img"):
         return
     outfile = os.path.join(os.path.abspath(outdir), base_name)
     # outfile = outfile.replace(".svg", ".pdf")
-    outfile = outfile.replace(".svg", ".ps")
+    outfile = outfile.replace(".svg", ".png")
     infile = os.path.abspath(infile)
     #outfile = outfile.replace(".svg", ".png")
     print(outfile)
@@ -40,7 +40,8 @@ def convert_pdf(infile, outdir="./img"):
     params = ["--without-gui", "--export-area-page",
     ]
     io = ["--file={}".format(infile),
-          "--export-ps={}".format(outfile)]
+          "--export-dpi=600",
+          "--export-png={}".format(outfile)]
     success = subprocess.call([program, *params, *io])
     if success != 0:
         warnings.warn(TColors.FAIL + "File {} cannot be converted!".format(infile) + TColors.ENDC)
@@ -50,9 +51,9 @@ def convert_pdf(infile, outdir="./img"):
               +TColors.ENDC)
 
     #SECOND round ps to pdf using ps2pdf
-    program = "ps2pdf"
+    program = "convert"
     infile = outfile
-    outfile = infile.replace(".ps", ".pdf")
+    outfile = infile.replace(".png", ".pdf")
     io = [infile, outfile]
     success = subprocess.call([program, *io])
     if success != 0:

### 2019-05-16 paper/SI.tex
Add converting script and SI
Add SI before the correction

@@
 \usepackage{xcolor}
+\usepackage{units}
 \externaldocument[main-]{paper}
@@
 \alsoaffiliation{Mechanical Engineering, Pohang University of Science and
-  Technology (POSTECH), 77 Cheongam-ro, Nam-gu, Pohang, Gyeongbuk,
+  Technology (POSTECH), 77 Cheongam-ro, Nam-gu, Pohang, Gyeongbuk, 37673,
   Republic of Korea.}
@@
 
-\title{Macroscopic Salt Rejection through Electrostatically Gated Nanoporous Graphene}
+\title{Salt rejection through Electrostatically Gated Nanoporous Graphene}
 
@@
     \hline
-    Salt & $D$ (10$^{9}$ m$^{2}\cdot$s$^{-1}$) \\
+    Salt & $D$ (10$^{-9}$ m$^{2}\cdot$s$^{-1}$) \\
     \hline
@@
   \end{tabular}
-  \caption{Different diffusivities for the anions and cations of the
+  \caption{Different diffusivity values for the anions and cations of the
     salts used in this work \cite{vanysek_2000}. The theoretical
@@
 resulting slope. The rest of the factors are $V_{\mathrm{LCR}}$ = 7.33
-mL, $A$ = 9$\times$10$^{-6}$ m$^{-2}$. Table \ref{tab:exp-2} shows the
+mL, $A$ = 9$\times$10$^{-6}$ m$^{2}$. Table \ref{tab:exp-2} shows the
 averaged conductivity increase s, the extracted calibration factors
@@
   \caption{Measured $\eta$ values as function of $V_{\mathrm{G}}$ for
-    different salts used in this work. The concentration in HCR is 0.1
+    various salts used in this work. The concentration in HCR is 0.1
     mM in all cases.}
@@
 graphene membrane and not through leakage directly coupling the
-copper tape to the ionic solution. For this, we use a device as in \Fig
+copper tape to the ionic solution. For this purpose, we use a device as in \Fig
 1a, omitting the graphene and measuring the current through the
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{img/SI-resistance-rectification.pdf}
+  \includegraphics[width=0.8\linewidth]{img/SI-resistance-rejection.pdf}
   \caption{Simple circuit analog model for the transport through
@@
 $R_{\mathrm{PCTE}}$, the effective salt rejection through PG upon
-gating, is always larger than that experimentally observed.
+gating is always larger than that experimentally observed.
 
@@
 Here we take $L$=24 $\mu$m, $r_{\mathrm{G}}$=10 nm,
-$r_{\mathrm{PCTE}}$=200 nm. From simple Fick's law\cite{Beers_2006},
+$r_{\mathrm{PCTE}}$=200 nm. From simple Fick's law,
 the coefficient $k_{\mathrm{PCTE}}$ is determined as
@@
   \caption{Conductivity and calculated Debye lengths of various KCl
-    concentrations in order to obtain rectification versus
+    concentrations in order to obtain rejection versus
     concentration curves. }
@@
 
-\section{Effect of pore size distribution}
-\label{sec:pore-dist}
-
-One practical issue with large-area nanoporous graphene samples is
-that the unavoidable large pores will act as preferred pathways for
-the transported species and strongly attenuates the salt rejection
-effect. In this section we provide a detailed discussion about the
-influence of pore size distribution on the salt rejection through the
-PG-PCTE membrane. As seen from main text \Fig{} \ref{main-fig:1}c
-inset, the average distance between individual nanopores is larger
-than the largest Debye length studied here ($\sim{}$ 30 nm for 1 mM 1:1
-salt solution), we can assume that the ionic transport pathways
-through different nanopores do not influence each other and the total
-ionic flux $\boldsymbol{J}_{\mathrm{PG}}$ is the summation of fluxes
-through individual pores $\boldsymbol{J}_{i}$:
-\begin{equation}
-\label{eq:J-total}
-\boldsymbol{J}_{\mathrm{PG}} = \sum_{i} \boldsymbol{J}_{i} = \sum_{r_{i}} x_{r_{i}} \boldsymbol{J}_{r_{i}}
-\end{equation}
-where $r_{i}$ is the radius of individual pores,
-$\boldsymbol{J}_{r_{i}}$ and $x_{r_{i}}$ are the flux of individual
-pore and the distribution probability when
-$r_{\mathrm{G}} = r_{i}$. The salt rejection factor
-$\xi$ through graphene is then expressed as:
-\begin{equation}
-  \label{eq:xi-pore}
-  \begin{aligned}
-    \xi &= 1 - \frac{\sum_{r_{i}} \boldsymbol{J}_{r_{i}} x_{r_{i}}}
-           {\sum_{r_{i}} \boldsymbol{J}_{r_{i}}(V_{\mathrm{G}} = 0) x_{r_{i}}} \\
-           &= 1 - \frac{\sum_{r_{i}} \hat{J}_{r_{i}} r_{i}^{2} x_{r_{i}}}
-           {\sum_{r_{i}} \hat{J}_{r_{i}}^{0} r_{i}^{2} x_{r_{i}}} \\
-           % &approx 1 - \sum_{r_{i}} \frac{\hat{J}_{r_{i}}}{\hat{J}_{r_{i}}^{0}}
-           % \frac{r_{i}^{2} x_{r_{i}}} {\sum_{r_{i}} r_{i}^{2} x_{r_{i}}} \\
-           &\approx \sum_{r_{i}} \left(1 -  \frac{\hat{J}_{r_{i}}}{\hat{J}_{r_{i}}^{0}}\right) w_{r_{i}} \\
-           &= \sum_{r_{i}} \xi_{r_{i}} w_{r_{i}}
-  \end{aligned}
-\end{equation}
-where $\hat{J}$ and $\hat{J}^{0}$ are the flux normalized by pore area
-when $V_{\mathrm{G}} = 0$ and $V_{\mathrm{G}} \neq 0$, respectively,
-$w_{r_{i}} = x_{r_{i}} r_{i}^{2} / sum_{r_{i}} x_{r_{i}} r_{i}^{2}$ is
-the contribution to the salt rejection from individual pore rejection
-rate $\xi_{r_{i}}$. The linear combination between $\xi_{r_{i}}$ and
-$\xi$ comes from the assumption that $\hat{J}^{0}$ is independent of
-the pore size from the simple Ficknian diffusion.
-
-To get an insight of the influence of the pore size distribution on
-the salt rejection, we combine Equation \ref{eq:xi-pore} with main
-text \Fig{} \ref{main-fig:5}b for the salt rejection of a 1:1
-electrolyte to get the pore-distribution-related salt rejection, where
-the pore distribution is taken from the SEM image of real samples (for
-instance main text \Fig{} \ref{main-fig:1}c inset). \Fig{}
-\ref{fig:simple-rect-pore}a shows the contribution $w$ and $\xi$ as
-a function of $r_{\mathrm{G}}$ for individual pores when
-$V_{\mathrm{G}}$ = 1.25 V. As can be seen, the majority of pores fall
-within the regime of $\lambda_{\mathrm{D}} / r_{\mathrm{G}} > 1$,
-corresponding to $\xi(r_{\mathrm{G}}) > 0.6$. As a result, considering
-the pore distribution reduces the value of $\xi$ to $\sim{}$80\% to
-that of a single 20 nm-diameter nanopore (\Fig{}
-\ref{fig:simple-rect-pore}b), which is indeed close to the highest
-$\xi$ values experimentally observed (for 1mM NaCl system). Such high
-salt rejection even after considering the pore size distribution, can
-be explained by the non-linear nature of $\xi$ with $r_{\mathrm{G}}$
-and $V_{\mathrm{G}}$. As seen in main text Fig{} \ref{main-fig:5}b,
-for large $V_{\mathrm{G}}$ and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
-regions, $\xi$ reaches a ``plateau'' with its value close to 1. For
-the fabricated PG samples, most pores are within such region when
-$V_{\mathrm{G}}$ = 1.25 V and $c_{0}$ = 0.1 mM, which gives a minor
-change of $\xi$ dispite the wide span of pore sizes. In other words,
-although nanopres as large as 60 nm exist in the system, considerably
-high salt rejection more than 80\% can still be achieved.
-
-\begin{figure}[htbp]
-  \centering
-   \includegraphics[width=0.9\linewidth]{img/SI-simple-pore-dist.pdf}
-   \caption{Salt rejection after considering the pore size
-     distribution. \textbf{a}. $w$ (left axis) and $\xi$ (right axis)
-     as a function of $r_{\mathrm{G}}$ for the experimental pore size
-     distribution with $c_{0}$ = 0.1 mM and $V_{\mathrm{G}}$ = 1.25 V.
-     \textbf{b}. Salt rejection ratio $\xi$ as a function of $V_{\mathrm{G}}$ of a
-     0.1mM 1:1 salt from a 20 nm-diameter nanopore (blue line) and
-     from the experimental pore size distribution (orange line), by
-     applying Equation \ref{eq:xi-pore} to main text \Fig{}
-     \ref{main-fig:5}b.}
-  \label{fig:simple-rect-pore}
-\end{figure}
-
-To include the pore size distribution effect for all the salts
-studied, we performed FEM analysis for the salt rejection through
-single nanopore of different salts with $r_{\mathrm{G}}$ ranges from
-2.5 nm to 35 nm, while keeping $c_{0}$ constant at 0.1 mM. As shown in
-\Fig{} \ref{fig:xi-salts-pore}, the behavior of $\xi$ vary with the
-type of salt. As expected, the overall $\xi$ for monovalent salts
-(KCl, NaCl, LiCl) is larger than multivalent salts due to the longer
-Debye length. Moreover, $\xi$ of monovalent salts varies less with the
-pore size compared with multivalent salts. This can be explained by
-the non-linear dependency of $\xi$ on
-$\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ as discussed above. Combine
-the FEM-simulated $\xi$ values with the experimental pore size
-distribution, we obtain main text \Fig{} \ref{main-fig:6}.
-
-\begin{figure}[htbp]
-  \centering
-   \includegraphics[width=0.75\linewidth]{img/SI-xi-salt-pore-size.pdf}
-  \caption{FEM-simulated salt rejction ratio $\xi$ as a function of
-    $V_{\mathrm{G}}$ through single nanopores for different salts with
-    varied pore radius. All salts have concentration $c_{0}$ = 0.1 mM.}
-  \label{fig:xi-salts-pore}
-\end{figure}
-
 \pagebreak
@@
 different ionic pathways through the graphene nanopore upon gating in
-main text \Fig{} \ref{main-fig:4}b. As disccused in the main text, the
-ionic migration is contributed by both diffusion (caused by
+main text \Fig{} \ref{main-fig:4}b. As discussed in the main text, the
+ionic migration arises from both diffusion (caused by
 concentration gradient) and electrostatic drift (caused by electric
@@
 positive $V_{\mathrm{G}}$, distinct pathways for cations /
-anions are created and the drift flux balances the diffusion.
+anions are created and the drift flux counteracts the diffusion.
 
@@
 of the cations / anions. To see this, we plot the concentrations of
-cation ($c_{+}$) and anion ($c_{-}$) near a graphene nanopore with
-$r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM and $V_{\mathrm{G}}$ =
-0.75 V, as shown in \Fig{} \ref{fig:conc}a and \ref{fig:conc}b,
+cations ($c_{+}$) and anions ($c_{-}$) near a graphene nanopore with
+$r_{\mathrm{G}}$ = \unit[10]{nm}, $c_{0}$ = \unit[0.1]{mM} and $V_{\mathrm{G}}$ =
+\unit[0.75]{V}, as shown in \Fig{} \ref{fig:conc}a and \ref{fig:conc}b,
 respectively. The cations are depleted from the graphene surface,
@@
 concentration distribution at different $c_{0}$ and $V_{\mathrm{G}}$
-levels. When $c_{0}$ = 0.1 mM, $\lambda_{\mathrm{D}}$ is larger than
+levels. When $c_{0}$ = \unit[0.1]{mM}, $\lambda_{\mathrm{D}}$ is larger than
 $r_{\mathrm{G}}$, and the external gate voltage $V_{\mathrm{G}}$ has
@@
 (\Fig{} \ref{fig:conc-r}a and \ref{fig:conc-r}c). On the other
-hand, when $c_{0}$ = 100 mM, $\lambda_{\mathrm{D}}$ is much smaller
+hand, when $c_{0}$ = \unit[100]{mM}, $\lambda_{\mathrm{D}}$ is much smaller
 than $r_{\mathrm{G}}$, and the concentration is only affected by
@@
 control over the transport in the center of the pore and leads to a
-lower $\xi$ value. Due to the existence of graphene quantum
+lower $\xi$ value. Due to the existence of graphene's quantum
 capacitance, the surface potential $\psi_{\mathrm{G}}$ is essentially
 smaller than $V_{\mathrm{G}}$, and the maximum surface anion
-concentration ($c_{0}$ = 100 mM, $V_{\mathrm{G}}$ = 1.25 V) is
-$\sim{}$3 M, much smaller than the saturated surface adsorption
-density (at the order of 10$^{2}$ M
+concentration ($c_{0}$ = \unit[100]{mM}, $V_{\mathrm{G}}$ = \unit[1.25]{V}) is
+$\sim{}$ \unit[3]{M}, much smaller than the saturated surface adsorption
+density (at the order of \unit[10$^{2}$]{M}
 \cite{bard_electrochemical_1980}). Therefore we expect the surface
@@
 \ref{fig:potential}c and \ref{fig:potential}d) near a graphene
-nanopore with $r_{\mathrm{G}}$ = 10 nm and $V_{\mathrm{G}}$ = 0.75
-V. The transport of cations is dominated by its chemical potential and
-the diffusion is prominent in the center of the pore. On the other
-hand, the electric and diffusive potential energies are similar with
-opposite signs and counterbalance each other. This explains the
-relatively smaller electrochemical potential of anions in main text
-\Fig{} \ref{main-fig:4}b. As a result, different pathways for cations
-and anions emerge that cations preferably pass through the pore
+nanopore with $r_{\mathrm{G}}$ = \unit[10]{nm} and $V_{\mathrm{G}}$ = \unit[0.75]
+{V}. The transport of cations is dominated by its chemical potential and
+the diffusion is most pronounced in the center of the pore. The electric and diffusive potentials are similar in magnitude, but with
+opposite signs, counteracting each other. As a result, different pathways for cations
+and anions emerge, where cations preferably pass through the pore
 center, while anions mainly pass near the pore edge, as shown in
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{img/SI-flux.png}
+  \includegraphics[width=0.8\linewidth]{img/SI-flux.pdf}
   \caption{z-component fluxes of cation ($J_{z+}$, \textbf{a}.)  and
@@
 graphene further increases, the salt rejection may be weakened, or
-even enhanced salt transport is observed. To see this we artificially
-increase the $\psi_{\mathrm{G}}$ up to over 1 V when not considering
+even enhanced salt transport is observed. To see this, we artificially
+increase the $\psi_{\mathrm{G}}$ up to over \unit[1]{V} when not considering
 the limiting effect of graphene quantum capacitance. As seen in \Fig{}
@@
 anion flux around the pore edge, while the cation flux saturates
-(\Fig{} \ref{fig:large-V}). Such flux enhancement resemble that in an
-ionic transistor \cite{Nam_2009,Cheng_2018} when ionic current rises
-by applying gate voltage. Nevertheless, such regime may not be easy to
-be observed experimentally as the $V_{\mathrm{G}}$ applied may already
-exceed the electrochemical window of water, due to the quantum
-capacitance of graphene.
+(\Fig{} \ref{fig:large-V}). Such flux enhancement resembles that in an
+ionic transistor \cite{Nam_2009,Cheng_2018} when ionic current increases
+by applying gate voltage. Nevertheless, this regime may not be easily observed experimentally as the $V_{\mathrm{G}}$ applied may already
+exceed the electrochemical window of water.
 
@@
     range of $\psi_{\mathrm{G}}$ is larger than the experimentally
-    achievable value. The rectification of flux becomes weaker after a
+    achievable value. The rejection of flux becomes weaker after a
     certain level of $\psi_{\mathrm{G}}$ is reached. Further
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{img/SI-flux-larger.png}
+  \includegraphics[width=0.8\linewidth]{img/SI-flux-larger.pdf}
   \caption{Spatial distribution of $J_{z}$ at $z = 0$ as a function
@@
 
+\section{Effect of pore size distribution}
+\label{sec:pore-dist}
+
+In this section we provide a detailed discussion about the
+influence of pore size distribution on the salt rejection through the
+PG-PCTE membrane. Larger pores are the major contributors to salt flux, while at the same time, the effect of rejection is least pronounced.
+As seen from main text \Fig{} \ref{main-fig:1}c
+inset, the average distance between individual nanopores is larger
+than the largest Debye length studied here ($\sim{}$ \unit[30]{nm} for 1 mM 1:1
+salt solution), we can assume that the ionic transport pathways
+through different nanopores do not influence each other and the total
+ionic flux $\boldsymbol{J}_{\mathrm{PG}}$ is the summation of fluxes
+through individual pores $\boldsymbol{J}_{i}$:
+\begin{equation}
+\label{eq:J-total}
+\boldsymbol{J}_{\mathrm{PG}} = \sum_{i} \boldsymbol{J}_{i} = \sum_{r_{i}} x_{r_{i}} \boldsymbol{J}_{r_{i}}
+\end{equation}
+where $r_{i}$ is the radius of individual pores,
+$\boldsymbol{J}_{r_{i}}$ and $x_{r_{i}}$ are the flux of individual
+pore and the distribution probability when
+$r_{\mathrm{G}} = r_{i}$. The salt rejection factor
+$\xi$ through graphene is then expressed as:
+\begin{equation}
+  \label{eq:xi-pore}
+  \begin{aligned}
+    \xi &= 1 - \frac{\sum_{r_{i}} \boldsymbol{J}_{r_{i}} x_{r_{i}}}
+           {\sum_{r_{i}} \boldsymbol{J}_{r_{i}}(V_{\mathrm{G}} = 0) x_{r_{i}}} \\
+           &= 1 - \frac{\sum_{r_{i}} \hat{J}_{r_{i}} r_{i}^{2} x_{r_{i}}}
+           {\sum_{r_{i}} \hat{J}_{r_{i}}^{0} r_{i}^{2} x_{r_{i}}} \\
+           % &approx 1 - \sum_{r_{i}} \frac{\hat{J}_{r_{i}}}{\hat{J}_{r_{i}}^{0}}
+           % \frac{r_{i}^{2} x_{r_{i}}} {\sum_{r_{i}} r_{i}^{2} x_{r_{i}}} \\
+           &\approx \sum_{r_{i}} \left(1 -  \frac{\hat{J}_{r_{i}}}{\hat{J}_{r_{i}}^{0}}\right) w_{r_{i}} \\
+           &= \sum_{r_{i}} \xi_{r_{i}} w_{r_{i}}
+  \end{aligned}
+\end{equation}
+where $\hat{J}$ and $\hat{J}^{0}$ are the flux normalized by pore area
+when $V_{\mathrm{G}} = 0$ and $V_{\mathrm{G}} \neq 0$, respectively,
+$w_{r_{i}} = x_{r_{i}} r_{i}^{2} / \sum_{r_{i}} x_{r_{i}} r_{i}^{2}$ is
+the contribution to the salt rejection from individual pore rejection
+rate $\xi_{r_{i}}$. The linear combination between $\xi_{r_{i}}$ and
+$\xi$ comes from the assumption that $\hat{J}^{0}$ is independent of
+the pore size from the simple Ficknian diffusion.
+
+To get an insight of the influence of the pore size distribution on
+the salt rejection, we combine Equation \ref{eq:xi-pore} with main
+text \Fig{} \ref{main-fig:5}b for the salt rejection of a 1:1
+electrolyte to get the pore-distribution-related salt rejection, where
+the pore distribution is taken from the SEM image of real samples (for
+instance main text \Fig{} \ref{main-fig:1}c inset). \Fig{}
+\ref{fig:simple-rect-pore}a shows the contribution $w$ and $\xi$ as
+a function of $r_{\mathrm{G}}$ for individual pores when
+$V_{\mathrm{G}}$ = 1.25 V. As can be seen, the majority of pores fall
+within the regime of $\lambda_{\mathrm{D}} / r_{\mathrm{G}} > 1$,
+corresponding to $\xi(r_{\mathrm{G}}) > 0.6$. As a result, considering
+the pore distribution reduces the value of $\xi$ to $\sim{}$80\% to
+that of a single 20 nm-diameter nanopore (\Fig{}
+\ref{fig:simple-rect-pore}b), which is indeed close to the highest
+$\xi$ values experimentally observed (for 1mM NaCl system). Such high
+salt rejection even after considering the pore size distribution, can
+be explained by the non-linear nature of $\xi$ with $r_{\mathrm{G}}$
+and $V_{\mathrm{G}}$. As seen in main text Fig{} \ref{main-fig:5}b,
+for large $V_{\mathrm{G}}$ and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
+regions, $\xi$ reaches a ``plateau'' with its value close to 1. For
+the fabricated PG samples, most pores are within such region when
+$V_{\mathrm{G}}$ = 1.25 V and $c_{0}$ = 0.1 mM, which gives a minor
+change of $\xi$ despite the wide span of pore sizes. In other words,
+although nanopores as large as 60 nm exist in the system, considerably
+high salt rejection more than 80\% can still be achieved.
+
+\begin{figure}[htbp]
+  \centering
+   \includegraphics[width=0.9\linewidth]{img/SI-simple-pore-dist.pdf}
+   \caption{Salt rejection after considering the pore size
+     distribution. \textbf{a}. $w$ (left axis) and $\xi$ (right axis)
+     as a function of $r_{\mathrm{G}}$ for the experimental pore size
+     distribution with $c_{0}$ = 0.1 mM and $V_{\mathrm{G}}$ = 1.25 V.
+     \textbf{b}. Salt rejection ratio $\xi$ as a function of $V_{\mathrm{G}}$ of a
+     0.1mM 1:1 salt from a 20 nm-diameter nanopore (blue line) and
+     from the experimental pore size distribution (orange line), by
+     applying Equation \ref{eq:xi-pore} to main text \Fig{}
+     \ref{main-fig:5}b.}
+  \label{fig:simple-rect-pore}
+\end{figure}
+
+To include the pore size distribution effect for all the salts
+studied, we performed FEM analysis for the salt rejection through
+single nanopore of different salts with $r_{\mathrm{G}}$ ranges from
+2.5 nm to 35 nm, while keeping $c_{0}$ constant at 0.1 mM. As shown in
+\Fig{} \ref{fig:xi-salts-pore}, the behavior of $\xi$ vary with the
+type of salt. As expected, the overall $\xi$ for monovalent salts
+(KCl, NaCl, LiCl) is larger than multivalent salts due to the longer
+Debye length. Moreover, $\xi$ of monovalent salts varies less with the
+pore size compared with multivalent salts. This can be explained by
+the non-linear dependency of $\xi$ on
+$\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ as discussed above. Combine
+the FEM-simulated $\xi$ values with the experimental pore size
+distribution, we obtain main text \Fig{} \ref{main-fig:6}.
+
+\begin{figure}[htbp]
+  \centering
+   \includegraphics[width=0.75\linewidth]{img/SI-xi-salt-pore-size.pdf}
+  \caption{FEM-simulated salt rejection ratio $\xi$ as a function of
+    $V_{\mathrm{G}}$ through single nanopores for different salts with
+    varied pore radius. All salts have concentration $c_{0}$ = 0.1 mM.}
+  \label{fig:xi-salts-pore}
+\end{figure}
+
+\pagebreak
 \section{Further details of the numerical simulation }
@@
 (e.g. $10^{5}$) for a better convergence of the solver.  For the
-transport of diluted ionic species, we use the PNP equations to
+transport of diluted ionic species, we use the PNP equations, to
 describe the diffusion and drift of the ions, which can be further
@@
   \caption{Schematic illustration of the origin of the asymmetric
-    rectification with respect to $V_{\mathrm{G}}$. Due to the
+    rejection with respect to $V_{\mathrm{G}}$. Due to the
     existence of surface charge traps at negative $V_{\mathrm{G}}$,
@@
 
+\iffalse
+\section{Further numerical simulation results}
+\label{sec:simu-res}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-concentration.png}
+  \caption{Cation concentration $c_{+}$ (\textbf{a}.) and anion
+    concentration $c_{-}$ (\textbf{b}.) near the graphene nanopore for
+    KCl solution at 0.1 mM. Depletion of cation and accumulation of
+    anion can be observed near the graphene surface.}
+  \label{fig:conc}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-electrochemical-decomposite.pdf}
+  \caption{Decomposition of electrochemical potential near a nanopore
+    corresponding to \Fig 4 in main text. \textbf{a}. The electrostatic
+    (drift) contribution to the electrochemical potential for cation
+    (left) and anion (right) and \textbf{b}. The concentration (diffusion)
+    contribution to the electrochemical potential for cation (left)
+    and anion (right). The relative small order of magnitude for anion
+    electrochemical potential is caused by the balance between the
+    diffusion and drift for anion.}
+  \label{fig:potential}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-flux.png}
+  \caption{z-component flux $\boldsymbol{J}_{z}$ of cation
+    (\textbf{a}.)  and anion (\textbf{b}.) near the graphene nanopore
+    corresponding to Figure 4b in main text. The pathways for the
+    different ions can be spatially distinguished: the flux of cation
+    passes mostly through the center of the graphene nanopore while
+    the anion passes mainly through the edge. The analysis is in
+    consistent with the gradient of chemical potential as shown in the
+    main text \Fig 4b.}
+  \label{fig:flux}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.5\linewidth]{img/SI-rect-reverse.pdf}
+  \caption{Average total flux $\boldsymbol{J}_{z}$ in the nanopore as
+    a function of $\psi_{\mathrm{G}}$ at different concentrations. The
+    range of $\psi_{\mathrm{G}}$ is larger than the experimentally
+    achievable value. The rejection of flux becomes weaker after a
+    certain level of $\psi_{\mathrm{G}}$ is reached. Further
+    increasing the surface potential of graphene may even enhance the
+    transportation of ions, which is similar to the cases of ionic
+    transistors.}
+  \label{fig:reverse}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-flux-larger.png}
+  \caption{Spatial distribution of $\boldsymbol{J}_{z}$ as a function
+    of $r$ in a 20 nm nanopore at different levels of
+    $\psi_{\mathrm{G}}$ (larger than experimentally achievable values)
+    for cation (\textbf{a}.) and anion (\textbf{b}.). The cation flux
+    becomes nearly saturated with increasing $\psi_{\mathrm{G}}$,
+    while the flow of anion near the pore edge becomes much
+    larger. The drastic increase of pore-bounded anion flux is caused
+    by the accumulation of anions near the graphene surface, and in
+    turn causes the increasing of total flux as seen in \Fig
+    \ref{fig:reverse}.}
+  \label{fig:large-V}
+\end{figure}
+\clearpage{}
+\fi
+
 \section{Conductivity and Debye length for all salts}

### 2019-05-16 paper/paper.tex
Add TOC figure and change to NL format
Recover previous submission

@@
-\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
+\documentclass[journal=nalefd,email=true, hyperref=true, keywords=false]{achemso}
 \usepackage[utf8]{inputenc}
@@
 \newcommand{\Fig}{Fig.}
-\usepackage{lineno}
+% \usepackage{lineno}
+\usepackage{units}
+\usepackage{txfonts}
 \usepackage{xr-hyper}
@@
 \clearpage{}
-\linenumbers
+% \linenumbers
 \section{Introduction}
@@
 comparable to the characteristic length of diffusion, enabling new
-applications such as ionic diodes \cite{Karnik_2007}, field-effect
+applications such as ionic diodes \cite{Karnik_2007,siwy2002fabrication,vlassiouk2007nanofluidic}, field-effect
 transistors \cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
@@
 in practice, the fabrication of subnanometer porous 2D membranes over
-a large area with atomic precision remains technically challenging
+a large area with atomic precision remains technically challenging, 
+{ limiting the effective separation or demanding leak-sealing mechanism such as interfacial polymerization}
 \cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
@@
 of fundamental understanding of the interactions between the charged
-2D nanopores and the electrolyte solution. In this report, we
+2D nanopores and the electrolyte solution, { especially in regard of controlled ion transport modulation}.
+
+In this report, we
 investigate electrolyte permeation through graphene nanopores that are
@@
 \end{equation}
-where $r_{\mathrm{PCTE}}$ is the PCTE pore radius, $N_{\mathrm{p}}$ is
+{where $r_{\mathrm{PCTE}}$ (= \unit[200]{nm}) is the PCTE pore radius, $N_{\mathrm{p}}$  (= \unit[$1.5\cdot10^{12}$]{m$^{-2}$}) is
 numbers of pore per area, $D_{\mathrm{\pm}}$ is the salt diffusivity
@@
 concentration difference between two reservoirs, i.e.,
-$\Delta c \sim c_{0}$ and $L$ is the thickness of the PCTE membrane.
+$\Delta c \sim c_{0}$ and $L$ (= \unit[24]{$\muup$m}) is the thickness of the PCTE membrane.
 By using the salt diffusivity values (Supplementary Table
@@
 \Fig{} \ref{fig:2}b) show reasonable agreement with the experimental
-values.
+values.}
 
@@
 Section \ref{SI-sec:R-model}).
+% \todo[inline]{Make sure that the
+  % values used are correct.}
 
@@
 
-We next discuss the effects of electrostatic gating on graphene. In
-order to avoid any interference from the conductivity probe to the
-membrane potential, the ``three-interval'' method, which has been used
+We next discuss the effects of electrostatic gating on graphene. 
+{ Electrostatic gating has been employed previously to alter the 
+ion permeation through nanoporous structures. For example, an applied bias on a mesoporous 
+carbon membrane, having pores of $<$\unit[5]{nm}, allows to stop the 
+ion flux once the Debye length of the solution approaches the pore size \cite{Surwade_2014}. 
+Similar experiments using nanoporous gold membranes, however, find that the cation and anion 
+transport is enhanced upon applying a bias \cite{mccurry2017electrolyte}. While the former behavior 
+was ascribed to the depletion of the channel from ions upon gating, the latter was a result of enhanced transport
+by dominating drift currents.}
+
+In order to investigate the behavior in more detail, the ``three-interval'' method, which has been used
 in controlling the membrane potential in mesoporous carbon membranes
@@
 concentration $c_{0}$ influences the attainable degree of salt
-rejection. $\xi$ values measured at $V_{\mathrm{G}}$ = 1.25 V,
+rejection. 
+{
+We note that the small negative $\xi$ values (corresponding to reduced transport resistance) at $V_{\mathrm{G}} \sim{}$ -0.5 V
+may be caused by (i) the charge neutral point (CNP) of graphene is not exactly at $V_{\mathrm{G}}$ = 0, and (ii) experimental uncertainty.
+Nevetherless, significant salt rejection is observed when $V_{\mathrm{G}}>$ 0.5 V.
+}
+The $\xi$ values measured at $V_{\mathrm{G}}$ = 1.25 V,
 $\xi_{\mathrm{max}}$, as a function of $c_{0}$ from 10$^{-4}$ to
@@
 that the concentration gradient at the pore center becomes small (see
-Supplementary Section \ref{SI-sec:conc}, Supplementary
-Figs. \ref{SI-fig:conc} and \ref{SI-fig:conc-r}). Although the surface
+{ Supplementary Section \ref{SI-sec:conc}, Supplementary
+Figs. \ref{SI-fig:conc} and \ref{SI-fig:conc-r}}).
+{
+Although the surface
 concentration of anions is enhanced by $\sim{}$30 times, it is sill
@@
 Section \ref{SI-sec:conc}, Supplementary Figs.  \ref{SI-fig:potential}
-and \ref{SI-fig:flux}). The observations confirm the distinct ionic
+and \ref{SI-fig:flux})}. 
+The observations confirm the distinct ionic
 transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
@@
 \cite{Biesheuvel_2010}, where electrodes with large surface area are
-required. More detailed discussion about the selective ionic pathways
-upon gating can be found in Supplementary Section \ref{SI-sec:conc}.
+required. 
+{
+More detailed discussion about the selective ionic pathways
+upon gating can be found in Supplementary Section \ref{SI-sec:conc}.}
 
@@
 experimentally observed reduction of diffusive flux upon
-gating. Indeed, the same physical mechanism also governs the ionic
-transport through an IFET, in which a nonzero electric potential at
+gating. Indeed, the same physical mechanism also governs 
+the 
+{ diode-like ionic
+transport through an IFET  \cite{Nam_2009,Lee_2015,Feng_2016}
+or a nanoporous metal membrane \cite{mccurry2017electrolyte}},
+in which a nonzero electric potential at
 the nanopore center usually results in an increase of ionic
-conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
+conductivity. To this end, we
 further increased the graphene surface potential $\psi_{\mathrm{G}}$
 considering the same system (details see Supplementary Section
-\ref{SI-sec:conc}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
-larger than 400 mV, the ionic flux starts to increase, reversing the
-trend observed at the low $\psi_{\mathrm{G}}$ regime, due to (i) the
-drift flux become dominant over diffusion flux and (ii) the
-concentration near the pore edge (preferred path) greatly increases
-(details see Supplementary Section \ref{SI-sec:conc}, Supplementary
-Figs. \ref{SI-fig:reverse} and \ref{SI-fig:large-V}). This level of
-$\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
-membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V, which
-triggers the electrochemical reactions \cite{Toh_2011}. On the other
-hand, in an IFET, the electric potential on the pore wall is
-considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
-metallic nature of gate electrode (having an infinitely-large quantum
-capacitance). We therefore conclude that the quantum
-capacitance-induced nonlinear damping in the surface potential results
-in the observed salt rejection.  Following the above discussions, we
-further investigate the physical limits for the biased graphene
-nanopores. Specifically, the salt rejection characteristics are
-controlled by: (i) the overlap of EDL inside the nanopore, essentially
-controlled by two length scales of $\lambda_{\mathrm{D}}$ and
-$r_{\mathrm{G}}$, and (ii) the graphene surface potential
+\ref{SI-sec:conc}). Intriguingly, by increasing
+$\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux starts to
+increase, reversing the trend observed at the low $\psi_{\mathrm{G}}$
+regime, due to (i) the drift flux become dominant over diffusion flux
+and (ii) the concentration near the pore edge (preferred path) greatly
+increases (details see Supplementary Section \ref{SI-sec:conc},
+Supplementary Figs. \ref{SI-fig:reverse} and
+\ref{SI-fig:large-V}). This level of $\psi_{\mathrm{G}}$ cannot be
+reached experimentally in graphene membrane, as this requires a
+$V_{\mathrm{G}}$ larger than 2.0 V, which triggers the electrochemical
+reactions \cite{Toh_2011}. On the other hand, in an IFET, the electric
+potential on the pore wall is considerably higher, equivalent to
+$V_{\mathrm{G}}$ due to the metallic nature of gate electrode (having
+an infinitely-large quantum capacitance). We therefore conclude that
+the quantum capacitance-induced nonlinear damping in the surface
+potential results in the observed salt rejection.  Following the above
+discussions, we further investigate the physical limits for the biased
+graphene nanopores. Specifically, the salt rejection characteristics
+are controlled by: (i) the overlap of EDL inside the nanopore,
+essentially controlled by two length scales of $\lambda_{\mathrm{D}}$
+and $r_{\mathrm{G}}$, and (ii) the graphene surface potential
 $\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
@@
 $V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
-= 1.0, a high value of $\xi$ up to $\sim$0.95 can be achieved.  We
+= { 2.0},
+a high value of $\xi$ up to $\sim$0.95 can be achieved.  We
 notice that although the above analysis suggests a salt rejection up
@@
 from on the macroscopic transport equations by treating ions as
-zero-volume charges, may not be valid when $R_{\mathrm{G}}<$ 5
+zero-volume charges, may not be valid when $r_{\mathrm{G}}<$ 5
 nm\cite{Jain_2015}. In addition, the specific ion-graphene
@@
 required to elucidate electrolyte transport approaching the small pore
-limit. We note that the FEM simulation is based on the ionic transport
-through single graphene nanopore, while in reality the nanopores has a
-considerable distribution (\Fig{} \ref{fig:1}c inset) which may weaken
-the salt rejection due to existence of larger pores. Since the average
-spacing between the nanopores are comparable or larger than the Debye
-length, we ignore the influence between the individual nanopores and
-assume that the overall salt rejection $\xi$ is a linear combination
-of salt rejection $\xi_{r_{i}}$, from individual pores with radius $r_{i}$:
+limit. 
+{
+We notice that the calculations in Figs. \ref{fig:4} and \ref{fig:5} 
+are based on the setup  of ionic transport through single nanopore.
+In order to mimic the experimental conditions, 
+calculations were carried out by considering the pore size distribution in Fig. \ref{fig:1}c inset. 
+Under the assumption that the interpore distance is significantly larger than the Debye length,
+the overall salt rejection $\xi$ is
+estimated by the linear combination of the salt rejection 
+$\xi_{r_i}$ 
+from individual pores with radius $r_i$ given by:
 \begin{equation}
@@
 is the contribution factor from pores with radius $r_{i}$, and
-$x_{r_{i}}$ is the distribution probability of pores with radius
+$x_{r_{i}}$ is the fraction of pores with radius
 $r_{i}$ (details see Supplementary Section
 \ref{SI-sec:pore-dist}). Combining Eq. \ref{eq:rejection-comb} and
-\Fig{} \ref{fig:5}b, we estimate that the experimental pore
-distribution reduces the salt rejection to $\sim{}$80 \% of that from
-a 20 nm nanopore when $c_{0}$ = 0.1 mM (\Fig{}
+\Fig{} \ref{fig:5}b, the
+calculated salt rejection is reduced to $\sim{}$ 80\% of that from the
+single-pore calculation of a 20 nm nanopore when $c_{0}$ = 0.1 mM (Supplementary \Fig{}
 \ref{SI-fig:simple-rect-pore}). Consider the existence of large pores
@@
 $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (details
-see Supplementary Section \ref{SI-sec:pore-dist}).
+see Supplementary Section \ref{SI-sec:pore-dist}).}
 
@@
 earlier, the salt rejection is more pronounced in the positive
-$V_{\mathrm{G}}$ regime. The degree of salt rejection deceases with
+$V_{\mathrm{G}}$ regime. 
+% { The negative $\eta$ values, observed for certain salts or applied $V_{\mathrm{G}}$, respectively, would actually
+% indicate that the flow in enhanced upon biasing the membrane.
+While such behavior is not uncommon in gating systems, we cannot conclude unambiguously if the effect is significant or rather within the measurement uncertainty of the system.
+Furthermore, as the definition of $\xi$ based on $\delta$ is only valid for positive $\eta$, the discussion is hence limited to $V_{\mathrm{G}}$ $>$ 0.}
+The degree of salt rejection deceases with
 the salt valance; for example, the measured $\xi$ values at
@@
 of $V_{\mathrm{G}}$ using the same simulation setups (\Fig{}
-\ref{fig:6}b). The effect of pore size distribution is explicitly
+\ref{fig:6}b). 
+{
+The effect of pore size distribution is explicitly
 considered using the FEM simulation results with different pore sizes
-(Supplementary \Fig{} \ref{SI-fig:xi-salts-pore}). The calculated
-$\xi_{\mathrm{max}}$ values are quantitatively compared with
-experiments (\Fig{} \ref{fig:6}c), and the same trend is
-observed. Indeed, because the Debye length $\lambda_{\mathrm{D}}$
-decreases with the salt valence, the graphene surface potential
-appears to decrease in the multivalent salt systems, thereby reducing
-$\xi$ (see \Fig{} \ref{fig:5}b). The calculated and experimental
-$\xi_{\mathrm{max}}$ as a function of $\lambda_{\mathrm{D}}$ are
-consequently plotted, for the seven salt species considered here
-(\Fig{} \ref{fig:6}d). Similar to the experimental observations, small
-difference between the $\xi$ of salts with same valence (e.g. LiCl,
-NaCl and KCl) is also predicted from the simulations due to the
-variation in ionic mobilities. We notice that without any fitting
-parameters, our theory can predict the experimental values reasonably
-well.  In addition, the $\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$
-dependence is approximately linear, suggesting that the effect of
-Debye length is dominant over the salt diffusivity. This finding also
-explains the concentration dependence of $\xi_{\mathrm{max}}$ observed
-in \Fig{} \ref{fig:2}d, as
+(Supplementary \Fig{} \ref{SI-fig:xi-salts-pore})} 
+The calculated $\xi_{\mathrm{max}}$ values are
+quantitatively compared with experiments (\Fig{} \ref{fig:6}c), and
+the same trend is observed. Indeed, because the Debye length
+$\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
+surface potential appears to decrease in the multivalent salt systems,
+thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b).
+{
+The slightly higher $\xi$ values of LiCl and NaCl compared with KCl observed in the experiments, 
+are also supported by the FEM simulation results in \Fig{} \ref{fig:6}b, 
+which we attribute to the lower diffusivities of Li$^{+}$ and Na$^{+}$ ions (see Supplementary Table \ref{SI-tab:diff})
+}.
+The calculated and
+experimental $\xi_{\mathrm{max}}$ as a function of
+$\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
+species considered here (\Fig{} \ref{fig:6}d). 
+% Similar to the
+% experimental observations, slightly higher $\xi$ of salts
+% with same valence (e.g. LiCl, NaCl and KCl) is also predicted from the
+% simulations due to the variation in ionic mobilities. 
+We notice that
+without any fitting parameters, our theory can predict the
+experimental values reasonably well.  In addition, the
+$\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$ dependence is approximately
+linear, suggesting that the effect of Debye length is dominant over
+the salt diffusivity. This finding also explains the concentration
+dependence of $\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
 $\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$. Further including the
 specific interaction of ionic species with the graphene membrane
-\cite{Ghosh_2018} may give even better agreement with experimental
-results. More interestingly, based on our theoretical analysis, we
+{- such as cation-$\pi$ interacation \cite{shi2013ion}} - may give even better agreement with experimental
+results \cite{Ghosh_2018}. More interestingly, based on our theoretical analysis, we
 predict that a very high degree of salt rejection ($\xi>$ 0.99) can be
@@
 avenue towards realization of atomically thin 2D porous membranes for
-advanced separation process in electrolyte solutions.
+{ controlled ion permeation, allowing to tailor the ion transport through porous 2D materials.}.
 
@@
 \noindent
-\textbf{Ion diffusion experiments}: Baseline measurements were
-performed using bare PCTE (b-PCTE) by extracting the diffusion rates
+\textbf{Ion diffusion experiments}: { Baseline measurements were
+performed using a single bare PCTE (b-PCTE) with defined membrane area} by extracting the diffusion rates
 of 3 measurements and averaging the resulting values (see
@@
 \noindent
-\textbf{Ion gating experiments}: The salt rejection behavior of the graphene
-was characterized using patterned graphene on PCTE (PG-PCTE) in a
-3-interval-type measurement based on salt diffusion: 1h per interval
+\textbf{Ion gating experiments}: 
+{ The salt fluxes through ungated and gated graphene
+was characterized using a single patterned graphene on PCTE (PG-PCTE)} 
+in a 3-interval-type measurement based on salt diffusion: 1h per interval
 with (i) no bias (ii) bias and (iii) no bias, ruling out possible
@@
 to apply the selected voltage.
+{ In a control experiment, the conductivity of water was monitored when applying a bias of \unit[1.25]{V} and \unit[-1.25]{V} to the graphene membrane.
+A conductivity increase of \unit[0.015]{$\muup$S$\cdot$cm$^{-1}$} was observed for the duration of one hour, suggesting that the effect of gating on pH is negligible.
+
+For each salt, we have measured the rejection by alternating from negative (starting at -\unit[1.25]{V}) to positive bias, decreasing to \unit[0]{V} in \unit[0.25]{V} steps.
+The order of measuring the salts was KCl, LiCl, MgSO$_4$, NaCl, K$_3$(Fe(CN)$_6$), CaCl$_2$ and K$_2$SO$_4$.}
 
@@
 extracted and used to reconstruct the value of actual $V_{\mathrm{G}}$
-applied to graphene. We examined the convergence of the solutions by
+applied to graphene. 
+{
+Under the experimental pH conditions, the salt concentration is at least 2 orders of magnitudes larger than the protons and hydroxides, and therefore the pH effects in our numerical simulations were not explicitly considered.
+}
+We examined the convergence of the solutions by
 performing simulations with varied mesh sizes. For further details

### 2019-05-17 paper/paper.tex
Add changes to paper before resub to NL

@@
 \title{Macroscopic Salt Rejection through Electrostatically Gated Nanoporous Graphene}
+
+\keywords{graphene, nanopore, patterning, salt rejection, gating, finite element modeling, quantum capacitance}
+
+\begin{tocentry}
+  \centering
+\includegraphics[height=0.40\linewidth]{img/TOC.pdf}
+\end{tocentry}
 
@@
 comparable to the characteristic length of diffusion, enabling new
-applications such as ionic diodes \cite{Karnik_2007,siwy2002fabrication,vlassiouk2007nanofluidic}, field-effect
-transistors \cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
-nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}. Porous,
-atomically thin two-dimensional (2D) materials, such as graphene, are
-emerging as ideal membrane materials due to the ultimate permeation
+applications such as ionic diodes
+\cite{Karnik_2007,siwy2002fabrication,vlassiouk2007nanofluidic},
+field-effect transistors \cite{Nam_2009}, desalination
+\cite{Heiranian_2015}, and nanopore-based DNA sequencing
+\cite{Heerema_2016,Garaj_2013}. Porous, atomically thin
+two-dimensional (2D) materials, such as graphene, are emerging as
+ideal membrane materials due to the ultimate permeation
 \cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
@@
 losing water permeability
-\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}. Nevertheless,
-in practice, the fabrication of subnanometer porous 2D membranes over
-a large area with atomic precision remains technically challenging, 
-{ limiting the effective separation or demanding leak-sealing mechanism such as interfacial polymerization}
+\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}.
+Nevertheless, in practice, the fabrication of subnanometer porous 2D
+membranes over a large area with atomic precision remains technically
+challenging, { limiting the effective separation or demanding
+  leak-sealing mechanism such as interfacial polymerization}
 \cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
 portion of excessively large pores or tears can significantly diminish
-salt rejection.  Very recently, a number of reports have explored the
+salt rejection. Therefore, it is critical to develop methodology that
+allow appreciable selectivity of nanoporous 2D membrane even with
+large pore size. Very recently, a number of reports have explored the
 effect of surface charges on the selectivity of ion transport through
@@
 \Fig{} \ref{fig:1}b, using the protocol developed by our group
-\cite{Choi_2018} (details see Supplementary Section
-\ref{SI-sec:exp}). The normally distributed, circular pores with pore
-diameters of 20$\pm$10 nm and a pore density of
-1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset)
-over a large area were perforated on graphene.  By optimizing the
-subsequent transfer process, a high surface coverage ($>$ 98\%) of PG
-on PCTE was obtained (\Fig{} \ref{fig:1}c), allowing reliable
+\cite{Choi_2018}, which enables formation of uniformly-distributed
+graphene nanopores over large area up to 25 cm$^{2}$ (details see
+Supplementary Section \ref{SI-sec:exp}). The normally distributed,
+circular pores with pore diameters of 20$\pm$10 nm and a pore density
+of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c
+inset) over a large area were perforated on graphene.  By optimizing
+the subsequent transfer process, a high surface coverage ($>$ 98\%) of
+PG on PCTE was obtained (\Fig{} \ref{fig:1}c), allowing reliable
 characterization of the ion transport behavior (details see
@@
 is the contribution factor from pores with radius $r_{i}$, and
-$x_{r_{i}}$ is the fraction of pores with radius
-$r_{i}$ (details see Supplementary Section
-\ref{SI-sec:pore-dist}). Combining Eq. \ref{eq:rejection-comb} and
-\Fig{} \ref{fig:5}b, the
-calculated salt rejection is reduced to $\sim{}$ 80\% of that from the
-single-pore calculation of a 20 nm nanopore when $c_{0}$ = 0.1 mM (Supplementary \Fig{}
-\ref{SI-fig:simple-rect-pore}). Consider the existence of large pores
-with diameter up to 60 nm, such degree of salt rejection is still
-appreciable, which is ascribed to the nonlinear dependency of $\xi$ on
+$x_{r_{i}}$ is the fraction of pores with radius $r_{i}$ (details see
+Supplementary Section \ref{SI-sec:pore-dist}). Combining
+Eq. \ref{eq:rejection-comb} and \Fig{} \ref{fig:5}b, the calculated
+salt rejection is reduced to $\sim{}$ 80\% of that from the
+single-pore calculation of a 20 nm nanopore when $c_{0}$ = 0.1 mM
+(Supplementary \Fig{} \ref{SI-fig:simple-rect-pore}). Consider the
+existence of large pores with diameter up to 60 nm, such degree of
+salt rejection is still appreciable, which is ascribed to the
+nonlinear dependency of $\xi$ on
 $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (details
-see Supplementary Section \ref{SI-sec:pore-dist}).}
+see Supplementary Section \ref{SI-sec:pore-dist}).}  From our
+analysis, it is also clear reducing the average pore size is critical
+to overcome the low salt rejection at higher concentrations, which may
+hopefully be achieved with more advanced fabrication techniques.
+
+% Therefore, it is critical to develop methodology that
+% allow appreciable selectivity of nanoporous 2D membrane even with
+% large pore size. Very recently, a number of reports have explored the
+% effect of surface charges on the selectivity of ion transport through
+% graphene nanopores, as a consequence of the electrostatic interactions
+% between solvated ions and the charged functional groups attached on
+% graphene, indicating that even large pores ($>$ 30nm) can be ion
+% selective \cite{Rollings_2016,Surwade_2014}. However, it remains
+% controversial that if the surface charges can result in a degree of
+% salt rejection, as the surface charge and potential cannot be
+% precisely quantified and are sensitive to the surroundings as well as
+% the history of chemical treatment \cite{Li_2008}. There remains a lack
+% of fundamental understanding of the interactions between the charged
+% 2D nanopores and the electrolyte solution. In this report, we
+% investigate electrolyte permeation through graphene nanopores that are
+% significantly larger than the hydrated radii. We model the surface
+% potential by taking into account of the elementary electronic
+% properties of graphene and demonstrate that a high degree of salt
+% rejection can be achieved by electrostatic gating.
+
+% \section{Results and discussions}
+% \label{sec:res}
+
+% \subsection{Free diffusion through porous graphene}
+% \label{sec:res-1}
+
+% \Fig{} \ref{fig:1}a depicts the experimental setup characterizing
+% ionic diffusion through a sheet of double layer porous graphene
+% (PG). Two reservoirs, namely the high-concentration reservoir (HCR)
+% containing electrolyte solution with molar concentration $c_0$, and
+% the low-concentration reservoir (LCR) containing de-ionized (DI)
+% water, are separated by a PG membrane supported by a polycarbonate
+% track-etched (PCTE) film. Magnetic stirrers are used to minimize the
+% effects of external concentration polarization, and a conductivity
+% probe is placed in the LCR to monitor the ionic concentration as a
+% function of time. The membrane is attached to a piece of copper tape
+% connected to a voltage source applying an electrical bias
+% $V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
+% inset). We fabricated the PCTE-supported PG as schematically shown in
+% \Fig{} \ref{fig:1}b, using the protocol developed by our group
+% \cite{Choi_2018} (details see Supplementary Section
+% \ref{SI-sec:exp}). The normally distributed, circular pores with pore
+% diameters of 20$\pm$10 nm and a pore density of
+% 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset)
+% over a large area were perforated on graphene.  By optimizing the
+% subsequent transfer process, a high surface coverage ($>$ 98\%) of PG
+% on PCTE was obtained (\Fig{} \ref{fig:1}c), allowing reliable
+% characterization of the ion transport behavior (details see
+% Supplementary Section \ref{SI-sec:exp}).  The system presented here
+% allows us to systematically investigate the diffusive flux of ions
+% across a sheet of PG, $\boldsymbol{J}$, driven by the gradient of
+% electrochemical potential in the electrolyte medium.
+
+% First, the control experiments were carried out by measuring the ionic
+% diffusion of seven salt species, including KCl, NaCl, LiCl,
+% K$_{2}$SO$_{4}$, MgSO$_{4}$, CaCl$_{2}$ and K$_{3}$[Fe(CN)$_{6}$],
+% through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
+% flux is comparably small, the conductivity increases linearly with
+% time in the LCR (e.g. \Fig{} \ref{fig:2}a) within the measurement
+% duration (1 h), suggesting the concentration gradient across the
+% membrane remains constant. The diffusive fluxes (blue bars in \Fig{}
+% \ref{fig:2}b) of different salts were obtained by converting the
+% conductivity-time profiles using calibration curves (Supplementary
+% Section \ref{SI-sec:measure}). The theoretical diffusive fluxes
+% through PCTE are obtained based on the assumption that the membrane
+% consists of cylindrical pores with uniform diameter and a low
+% tortuosity $\tau$ of $\sim{}$1.2 \cite{O_Hern_2012}:
+% \begin{equation}
+%   \label{eq:j-pcte}
+%   \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi r_{\mathrm{PCTE}}^{2} N_{\mathrm{p}} D_{\mathrm{\pm}} \Delta c}{L \tau}
+% \end{equation}
+% where $r_{\mathrm{PCTE}}$ is the PCTE pore radius, $N_{\mathrm{p}}$ is
+% numbers of pore per area, $D_{\mathrm{\pm}}$ is the salt diffusivity
+% (average of cation and anion diffusivity), $\Delta c$ is the bulk
+% concentration difference between two reservoirs, i.e.,
+% $\Delta c \sim c_{0}$ and $L$ is the thickness of the PCTE membrane.
+% By using the salt diffusivity values (Supplementary Table
+% \ref{SI-tab:diff}), the calculated diffusive fluxes (red bars in
+% \Fig{} \ref{fig:2}b) show reasonable agreement with the experimental
+% values.
+
+% Next, we carried out the same experiments using the PG-covered PCTE
+% membrane (PG-PCTE), without electrostatic gating. The measured
+% diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
+% \Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
+% with those of bare PCTE membrane, suggesting that the transport
+% resistance of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG
+% without gating, $R_{\mathrm{G}}^{0}$. Using a simple circuit model, we
+% estimate the ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and
+% $R_{\mathrm{PCTE}}$, i.e.,
+% $\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be $\sim$2.2,
+% which is in good agreement with the value derived from the
+% experimental data in \Fig{} \ref{fig:2}b (details see Supplementary
+% Section \ref{SI-sec:R-model}).
+
+% \subsection{Salt rejection induced by electrostatic gating}
+% \label{sec:res-2}
+
+% We next discuss the effects of electrostatic gating on graphene. In
+% order to avoid any interference from the conductivity probe to the
+% membrane potential, the ``three-interval'' method, which has been used
+% in controlling the membrane potential in mesoporous carbon membranes
+% \cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a
+% illustratively represents how the measured conductivity evolves with
+% time. Specifically, in the first interval, the gate voltage source is
+% turned off and the conductivity probe is on, allowing us to obtain the
+% conductivity-time profile with an average slope $s_{1}$ that
+% corresponds to the diffusive flux across the PG-PCTE membrane. In the
+% second interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane
+% after turning off the conductivity probe, followed by the third
+% interval $s_{3}$, in which the conductivity probe is turned on again
+% to give the corresponding slope. A control experiment was performed to
+% ensure the copper tape was not in direct contact with the ionic
+% solution (Supplementary Section \ref{SI-sec:copper}). The slope
+% corresponding to the second interval $s_{2}$, as the conductivity
+% probe is off, is determined by linear interpolation of the
+% conductivities from the endpoint of interval 1 to the starting point
+% of interval 3. A decrease of slope observed in interval 2 indicates
+% that the total flux through PG-PCTE is reduced upon gating (i.e. salt
+% penetration through the PG pores is hindered). We define such
+% experimentally measured reduction rate as $\eta$, which is equivalent
+% to the decrease of total diffusive flux through PG-PCTE as follows:
+% \begin{equation}
+%   \label{eq:rejection}
+%   \eta = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
+%     - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
+% \end{equation}
+% where $\bar{s}$ is the average slope of $s_{1}$ and $s_{3}$, namely
+% $(s_{1} + s_{3})/2$, and
+% $\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive flux
+% across the PTCE-supported PG double layer as a function of
+% $V_{\mathrm{G}}$. Since graphene and PCTE membranes effectively form a
+% transport system with series diffusive resistance $R_{\mathrm{G}}$
+% (tunable by $V_{\mathrm{G}}$) and $R_{\mathrm{PCTE}}$ (independent of
+% $V_{\mathrm{G}}$), respectively, we define the effective degree of
+% salt rejection from bare PG, $\xi$, as a function of $V_{\mathrm{G}}$ (
+% details see Supplementary Section \ref{SI-sec:R-model}) as:
+% \begin{equation}
+% \label{eq:xi-def}
+% \xi = 1 - \frac{R_{\mathrm{G}}(V_{\mathrm{G}}=0)}{R_{\mathrm{G}}(V_{\mathrm{G}})} = \frac{(\delta+1) \eta}{\delta \eta + 1}
+% \end{equation}
+% The factor $\xi$ is a reliable and stable measure of salt rejection
+% through the PG membrane itself upon gating, as the salt species and
+% initial conditions may induce a degree of measurement uncertainty
+% between different samples. Note that the $\xi=1$ limit represents
+% perfect salt rejection in which
+% $R_{\mathrm{G}}(V_{\mathrm{G}}) \to \infty$. On the contrary $\xi=0$
+% indicates $R_{\mathrm{G}}$ remains unchanged with $V_{\mathrm{G}}$.
+
+% Using 0.1 mM KCl solution in HCR, we obtained $\xi$ as a function of
+% $V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
+% electrochemical reactions (\Fig{} \ref{fig:2}c). We observe an
+% asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
+% a higher degree of salt rejection for $V_{\mathrm{G}}>0$. where
+% positive carriers (holes) are induced in graphene. We notice that an
+% increase of $\xi$, or a decrease of diffusive flux through PG with
+% $V_{\mathrm{G}}$, showing an inverse trend compared with those
+% observed in ionic field effect transistors (IFETs) in which the
+% diffusive flux increases with the gate voltage
+% \cite{Nam_2009,Cheng_2018}. A further increase of the KCl
+% concentration $c_{0}$ influences the attainable degree of salt
+% rejection. $\xi$ values measured at $V_{\mathrm{G}}$ = 1.25 V,
+% $\xi_{\mathrm{max}}$, as a function of $c_{0}$ from 10$^{-4}$ to
+% 10$^{-2}$ M KCl (see Supplementary Section \ref{SI-sec:debye}) exhibit
+% a power law dependency (\Fig{} \ref{fig:2}d). The
+% $\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
+% law function following
+% $\xi_{\mathrm{max}} c_{0}^{0.52} = \mathrm{constant}$. As the Debye
+% length in solution, $\lambda_{\mathrm{D}}$, is inversely proportional
+% to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced salt
+% rejection originates from the modulation of the electrical double
+% layer (EDL), as will be discussed later.
+
+% \subsection{Self-consistent ion transport theory}
+% \label{sec:theory}
+
+% In order to quantitatively understand the observed $V_{\mathrm{G}}$
+% dependence, we develop a theory to model the coupling of graphene's
+% elementary transport properties and EDL, in order to quantify the
+% ionic transport through a graphene nanopore. Under the assumption that
+% the time scale for the bulk concentration change is significantly
+% longer than that of ionic diffusion, the pseudo-steady state
+% approximation holds. Accordingly, the steady-state Nernst-Planck
+% equation describing the ionic transport in an electrolyte solution is
+% given by \cite{MacGillivray_1968}:
+% \begin{equation}
+%   \label{eq:pnp}
+%   \nabla \cdot \boldsymbol{J}_{i} = -\nabla \cdot (\frac{D_{i}}{k_{\mathrm{B}}T} c_{i} N_{\mathrm{A}} \nabla \mu_{i}) = 0
+% \end{equation}
+% where $\boldsymbol{J}$ is the mass flux, subscript \textit{i}
+% corresponds to the ionic species (anion or cation), $D$ is the diffusivity,
+% $k_{\mathrm{B}}$ is the Boltzmann constant, $T$ is temperature, $c$ is
+% the molar concentration, $N_{\mathrm{A}}$ is the Avogadro constant,
+% and $\mu_{i}$ is the electrochemical potential. Under the assumption
+% of ideal solution, it follows \cite{Kilic_2007}:
+% \begin{equation}
+%   \label{eq:mu}
+%   \nabla \mu_{i} = k_{\mathrm{B}} T \nabla \ln x_{i} + z_{i} e \nabla \psi
+% \end{equation}
+%  $x$ is the molar fraction in solution, $z$ is the ionic valence,
+% $e$ is the unit charge, and $\psi$ is the electric potential. On the
+% other hand, the Poisson equation describing the electric potential
+% distribution is given by:
+% \begin{equation}
+%   \label{eq:poisson}
+%   \nabla \cdot (\varepsilon_{\mathrm{m}} \varepsilon_{0} \nabla \psi)
+%   =
+%   - N_{\mathrm{A}} e \sum_{i} c_{i} z_{i}
+% \end{equation}
+% where $\varepsilon_{\mathrm{m}}$ is the relative permittivity of
+% individual materials in the system, including water and the internal
+% Stern layer\cite{Tian_2017}, and
+% $\varepsilon_{0}$ is the vacuum permittivity. When applying
+% $V_{\mathrm{G}}$ to graphene adjacent to the electrolyte solution,
+% charges (electrons or holes) are induced in graphene; the
+% electroneutrality of the entire system suggests:
+% \begin{equation}
+%   \label{eq:electro-neutral}
+%   \sigma_{\mathrm{G}} S_{\mathrm{G}} + \sum_{i} \int_{\Omega} z_{i} c_{i} N_{\mathrm{A}} e \mathrm{d}^{3} \Omega= 0
+% \end{equation}
+% where $\sigma_{\mathrm{G}}$ is the charge density in graphene,
+% $S_{\mathrm{G}}$ is the total area of graphene, and $\Omega$
+% corresponds to the entire volumetric domain of electrolyte
+% solution. Note that the graphene surface potential,
+% $\psi_{\mathrm{G}}$, is not equivalent to $V_{\mathrm{G}}$ due to
+% change of graphene's work function upon charging, known as the
+% graphene quantum capacitance effect\cite{Xia_2009} (\Fig{}
+% \ref{fig:3}a) following:
+% \begin{equation}
+%   \label{eq:Vg}
+%   V_{\mathrm{G}} = \Delta \phi_{\mathrm{G}} + \psi_{\mathrm{G}}
+% \end{equation}
+% where
+% $\Delta \phi_{\mathrm{G}} = \phi_{\mathrm{G}}(V_{\mathrm{g}}) -
+% \phi_{\mathrm{G}}(V_{\mathrm{g}}=0)$ is the change of graphene’s work
+% function. The properties of the PG samples fabricated is close to
+% intrinsic graphene, with charge density at $V_{\mathrm{G}}=0$ measured
+% to be 1.4$\times$10$^{11}$ \textit{e}$\cdot$cm$^{-2}$, corresponding
+% to a work function difference of 48 meV from graphene's Dirac point
+% (details see Supplementary Section \ref{SI-sec:charge-dens}), much
+% smaller than the $\Delta \phi_{\mathrm{G}}$ induced by gating.
+% Therefore we adapt the simplification that the charge neutrality point
+% of graphene coincides with the Dirac point at $V_{\mathrm{G}}$ =
+% 0. The elementary electronic properties of graphene give:
+% \begin{equation}
+%   \label{eq:delta-phiG}
+%   \Delta \phi_{\mathrm{G}} = \mathrm{sign}(\sigma_{\mathrm{G}}) \frac{\hbar v_{\mathrm{F}}}{e}
+%   \sqrt{\frac{\pi |\sigma_{\mathrm{G}}|}{e}}
+% \end{equation}
+% where $\hbar$ is the reduced Planck constant, and
+% $v_{\mathrm{F}}=1.1\times10^{6}$ m$\cdot$s$^{-1}$ is the Fermi
+% velocity of graphene (more details find Supplementary Section
+% \ref{SI-sec:charge-dens}).  Note that the PG film fabricated
+% experimentally is double-layer turbostratic (randomly aligned)
+% graphene, in which we assume the
+% $\Delta \phi_{\mathrm{G}} - \sigma_{\mathrm{G}}$ dependence follows
+% Eq. \eqref{eq:delta-phiG}. The theory proposed here was solved
+% self-consistently by discretizing
+% Eqs. \eqref{eq:pnp}-\eqref{eq:poisson} using the finite-element method
+% (FEM), in which the graphene surface potential is coupled with
+% Eqs. \eqref{eq:electro-neutral}-\eqref{eq:delta-phiG} that were solved
+% simultaneously to reach convergent numerical solutions of
+% $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ for a given
+% $V_{\mathrm{G}}$. Clearly, the above model yields symmetric
+% characteristics for $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ with
+% respect to $V_{\mathrm{G}}$ due to the symmetric band structure of
+% graphene (Eq. \eqref{eq:delta-phiG}). However, for graphene
+% synthesized by chemical vapor deposition (CVD) used in our
+% experiments, it is well-recognized that the electron traps are
+% inherently introduced during synthesis and patterning
+% \cite{Dean_2010}, effectively reducing the charge density and surface
+% potential on graphene $V_{\mathrm{G}}<0$ (Supplementary \Fig{}
+% \ref{SI-fig:trap}), which is related to the fact that observed $\xi$
+% is much lower within the $V_{\mathrm{G}}<0$ regime in \Fig{}
+% \ref{fig:2}c. With the nonideality in mind, hereafter, we compare the
+% calculations and experiments in the regime of $V_{\mathrm{G}}>0$. For
+% example, \Fig{} \ref{fig:3}c presents the calculated
+% $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ as a function of
+% $V_{\mathrm{G}}$ considering the ionic diffusion through a single 20
+% nm-diameter nanopore drilled on a sheet of semi-infinite double layer
+% graphene that separates HCR containing KCl solution at $c_{0}$ = 0.1
+% mM, and LCR at $c_{0}/10$ in axisymmetric coordinates (details see
+% Supplementary Section \ref{SI-fig:scheme}). Indeed, the interplay
+% between graphene quantum capacitance and the EDL significantly reduces
+% the graphene surface potential $\psi_{\mathrm{G}}$ to $\sim$0.3 V at
+% $V_{\mathrm{G}}$ = 1.25 V, corresponding a surface charge density
+% $\sigma_{\mathrm{G}}$ of $\sim$0.08 C$\cdot$m$^{-2}$. Note that as we
+% mentioned earlier, an important merit of the 2D nanopore system
+% considered here is that the surface charge density can be precisely
+% determined and controlled, rather than being treated as a fitting
+% parameter as in most of the 2D nanopore literature
+% (e.g. Ref. \citenum{Rollings_2016}). In addition, we anticipate that
+% the gate-controlled ionic transport can also be achieved by replacing
+% graphene with other nanoporous conducting 2D materials, although the
+% operational gate voltage window required to achieve the same degree of
+% salt rejection may be narrower, because graphene has the smallest
+% quantum capacitance (near the Dirac point) among all known 2D
+% materials \cite{Tian_2016}.
+
+% \subsection{Salt rejection mechanism}
+% \label{sec:mechanism}
+
+% The numerical procedure described above allows us to resolve the
+% concentration and electric potential profiles near a graphene
+% nanopore for a given $V_{\mathrm{G}}$. Since the ionic flux is driven
+% by both $\psi$ and $c$ fields (see Eq. \eqref{eq:pnp} and \eqref{eq:mu}),
+% we focus on the electrochemical potential $\mu_{i}$, which represents
+% the combined driving force, to reveal its dependence on the applied
+% $V_{\mathrm{G}}$. Following the same system considered in \Fig{}
+% \ref{fig:3}b, the calculated axisymmetric electric potential $\psi$
+% and the relative electrochemical potentials,
+% $\Delta \mu_{\mathrm{K^{+}}}$ and $\Delta \mu_{\mathrm{Cl^{-}}}$, for
+% $V_{\mathrm{G}}$ = 0.75 V are shown in \Fig{} \ref{fig:4}a and
+% \ref{fig:4}b, respectively. The reference point of the electrochemical
+% potentials is set at the bulk phase in the HCR. As expected, the
+% electric potential reaches the maximum at the graphene surface (with
+% $\psi_{\mathrm{G}}$ of $\sim$100 mV) and decays towards the bulk
+% solution phase, forming an EDL surrounding the graphene surface. Since
+% the Debye length $\lambda_{\mathrm{D}}$ is comparable to the
+% pore radius $r_{\mathrm{G}}$, the electric potential at the nanopore
+% center remains at $\sim$25 mV, comparable to the thermal energy at
+% room temperature ($k_{\mathrm{B}}T$ = 26 meV). Consequently, it is
+% evident that the potential barrier is sufficient to modulate the
+% diffusive flux.
+
+% We further reveal the cation and anion transport pathways by looking
+% into their electrochemical potentials (\Fig{} \ref{fig:4}b). By
+% increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
+% graphene surface reduces the cation concentration at the pore edge due
+% to the electrostatic interactions, thereby increasing its
+% concentration gradient at the pore center. On the other hand, the
+% anion concentration near the pore edge increases exponentially, such
+% that the concentration gradient at the pore center becomes small (see
+% Supplementary Section \ref{SI-sec:conc}, Supplementary
+% Figs. \ref{SI-fig:conc} and \ref{SI-fig:conc-r}). Although the surface
+% concentration of anions is enhanced by $\sim{}$30 times, it is sill
+% much smaller than the saturated surface adsorption density, and the
+% bulk diffusivity used in the Nernst-Planck equation still holds.  We
+% also observe that $\Delta \mu_{+}$ is dominated by the concentration,
+% while $\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the
+% balance between the diffusion and drift potentials (see Supplementary
+% Section \ref{SI-sec:conc}, Supplementary Figs.  \ref{SI-fig:potential}
+% and \ref{SI-fig:flux}). The observations confirm the distinct ionic
+% transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
+% center for cations and pore edge for anions. \Fig{} \ref{fig:4}c
+% presents the calculated \textit{z}-component of the cation and anion
+% fluxes through the pore at the graphene plane (z = 0),
+% $\boldsymbol{J}_{z}$ ,as a function of the normalized radius,
+% $r/r_{\mathrm{G}}$ , where $r$ is the radial coordinate and
+% $r_{\mathrm{G}}$ is the pore radius, at different $V_{\mathrm{G}}$
+% values. Note that $\boldsymbol{J}_{z}$ is negative because the LCR is
+% placed at z$<$0 in the simulation box. At $V_{\mathrm{G}}$ = 0 (pure
+% diffusion), the anion and cation flux profiles are identical, with a
+% higher flux near the pore edge, which is expected, as the
+% concentration gradient is higher. By gradually increasing
+% $V_{\mathrm{G}}$, both fluxes are reduced throughout the pore, while
+% the degree of reduction is more pronounced at the pore edge for the
+% cation, and at the pore center for the anion, following the scenarios
+% we discussed above. Accordingly, the integrated fluxes across the
+% pore, $|\boldsymbol{J}_{z}|$, are reduced with $V_{\mathrm{G}}$
+% (\Fig{} \ref{fig:4}d). A total flux reduction of $\sim$90\% is
+% predicted. Another interesting finding here is that, by increasing
+% $V_{\mathrm{G}}$, the nanopore transport preferentially allows cations
+% over anions, or in other words, the anion flux is more reduced with
+% $V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the ion
+% selectivity of graphene nanopore \cite{Rollings_2016}. In our setup,
+% the imbalance between cation and anion fluxes near the graphene
+% nanopore is compensated by the EDL formation at the counter-electrode
+% in LCR, which maintains the electroneutrality of the system. Notably,
+% since atomically thin graphene samples are used, the mechanism of salt
+% rejection is clearly distinct from that in capacitive deionization
+% \cite{Biesheuvel_2010}, where electrodes with large surface area are
+% required. More detailed discussion about the selective ionic pathways
+% upon gating can be found in Supplementary Section \ref{SI-sec:conc}.
+
+% The above mechanistic findings, nevertheless, do not fully clarify the
+% experimentally observed reduction of diffusive flux upon
+% gating. Indeed, the same physical mechanism also governs the ionic
+% transport through an IFET, in which a nonzero electric potential at
+% the nanopore center usually results in an increase of ionic
+% conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
+% further increased the graphene surface potential $\psi_{\mathrm{G}}$
+% considering the same system (details see Supplementary Section
+% \ref{SI-sec:conc}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
+% larger than 400 mV, the ionic flux starts to increase, reversing the
+% trend observed at the low $\psi_{\mathrm{G}}$ regime, due to (i) the
+% drift flux become dominant over diffusion flux and (ii) the
+% concentration near the pore edge (preferred path) greatly increases
+% (details see Supplementary Section \ref{SI-sec:conc}, Supplementary
+% Figs. \ref{SI-fig:reverse} and \ref{SI-fig:large-V}). This level of
+% $\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
+% membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V, which
+% triggers the electrochemical reactions \cite{Toh_2011}. On the other
+% hand, in an IFET, the electric potential on the pore wall is
+% considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
+% metallic nature of gate electrode (having an infinitely-large quantum
+% capacitance). We therefore conclude that the quantum
+% capacitance-induced nonlinear damping in the surface potential results
+% in the observed salt rejection.  Following the above discussions, we
+% further investigate the physical limits for the biased graphene
+% nanopores. Specifically, the salt rejection characteristics are
+% controlled by: (i) the overlap of EDL inside the nanopore, essentially
+% controlled by two length scales of $\lambda_{\mathrm{D}}$ and
+% $r_{\mathrm{G}}$, and (ii) the graphene surface potential
+% $\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
+% Eq. \eqref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
+% function of $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and
+% $V_{\mathrm{G}}$ (\Fig{} \ref{fig:5}a). Clearly, when the bulk
+% concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
+% to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
+% revealed in \Fig{} \ref{fig:5}b, the calculated salt rejection factor
+% $\xi$ increases with both $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and
+% $V_{\mathrm{G}}$, in line with the experimentally observed
+% $\xi - c_{0}$ dependence. We also find the overall trends for
+% $\psi_{\mathrm{G}}$ and $\xi$ with respect to
+% $\lambda_{\mathrm{D}}/r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
+% similar. More importantly, based on our theoretical prediction, with
+% $V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
+% = 1.0, a high value of $\xi$ up to $\sim$0.95 can be achieved.  We
+% notice that although the above analysis suggests a salt rejection up
+% to 1 may be achived by further reducing the pore size (i.e. increasing
+% the $\lambda_{\mathrm{D}}/r_{\mathrm{G}}$ ratio), our theory, derived
+% from on the macroscopic transport equations by treating ions as
+% zero-volume charges, may not be valid when $R_{\mathrm{G}}<$ 5
+% nm\cite{Jain_2015}. In addition, the specific ion-graphene
+% interactions \cite{Rollings_2016} are not taken into account. Advanced
+% theoretical frameworks that bridge continuum and molecular models are
+% required to elucidate electrolyte transport approaching the small pore
+% limit. We note that the FEM simulation is based on the ionic transport
+% through single graphene nanopore, while in reality the nanopores has a
+% considerable distribution (\Fig{} \ref{fig:1}c inset) which may weaken
+% the salt rejection due to existence of larger pores. Since the average
+% spacing between the nanopores are comparable or larger than the Debye
+% length, we ignore the influence between the individual nanopores and
+% assume that the overall salt rejection $\xi$ is a linear combination
+% of salt rejection $\xi_{r_{i}}$, from individual pores with radius $r_{i}$:
+% \begin{equation}
+% \label{eq:rejection-comb}
+% \xi = \sum_{r_{i}} \xi_{r_{i}} w_{r_{i}}
+% \end{equation}
+% where
+% $w_{r_{i}} = x_{r_{i}} r_{i}^{2} / \sum_{r_{i}} x_{r_{i}} r_{i}^{2} $
+% is the contribution factor from pores with radius $r_{i}$, and
+% $x_{r_{i}}$ is the distribution probability of pores with radius
+% $r_{i}$ (details see Supplementary Section
+% \ref{SI-sec:pore-dist}). Combining Eq. \ref{eq:rejection-comb} and
+% \Fig{} \ref{fig:5}b, we estimate that the experimental pore
+% distribution reduces the salt rejection to $\sim{}$80 \% of that from
+% a 20 nm nanopore when $c_{0}$ = 0.1 mM (\Fig{}
+% \ref{SI-fig:simple-rect-pore}). Consider the existence of large pores
+% with diameter up to 60 nm, such degree of salt rejection is still
+% appreciable, which is ascribed to the nonlinear dependency of $\xi$ on
+% $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (details
+% see Supplementary Section \ref{SI-sec:pore-dist}).
 
@@
 
-For each salt, we have measured the rejection by alternating from negative (starting at -\unit[1.25]{V}) to positive bias, decreasing to \unit[0]{V} in \unit[0.25]{V} steps.
-The order of measuring the salts was KCl, LiCl, MgSO$_4$, NaCl, K$_3$(Fe(CN)$_6$), CaCl$_2$ and K$_2$SO$_4$.}
+  For each salt, we have measured the rejection by alternating from
+  negative (starting at -\unit[1.25]{V}) to positive bias, decreasing
+  to \unit[0]{V} in \unit[0.25]{V} steps. The order of measuring the
+  salts was KCl, LiCl, MgSO$_4$, NaCl, K$_3$(Fe(CN)$_6$), CaCl$_2$ and
+  K$_2$SO$_4$.}
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[H]
   \centering

### 2019-06-10 paper/combined.tex
Add combined tex from Sci Adv submission

--- 2019-05-16 paper/paper.tex
@@
-\documentclass[journal=nalefd,email=true, hyperref=true, keywords=false]{achemso}
+\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{times}
-\usepackage{todonotes}
 \DeclareCaptionLabelSeparator{bar}{  \textbar\quad}
@@
 \newcommand{\Fig}{Fig.}
-% \usepackage{lineno}
 \usepackage{units}
@@
 \usepackage{xr-hyper}
-\externaldocument[SI-]{SI}
+\usepackage{xcolor}
+\usepackage[final]{pdfpages}
+\SectionNumbersOn
+\mciteErrorOnUnknownfalse       %Clear warning about citings
+
+% \externaldocument[SI-]{SI}
 
@@
 
+{\begin{flushleft}
+\textbf{Teaser}:\\
+The quantum capacitance-induced surface potential can stop electrolyte transport through a "large" graphene nanopore.
+\end{flushleft}
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \clearpage{}
-% \linenumbers
-\section{Introduction}
+\section*{Introduction}
 \label{sec:intro}
@@
 a large area with atomic precision remains technically challenging, 
-{ limiting the effective separation or demanding leak-sealing mechanism such as interfacial polymerization}
+{limiting the effective separation or demanding leak-sealing mechanism such as interfacial polymerization}
 \cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
@@
 
-\section{Results and discussions}
+\section*{Results and discussions}
 \label{sec:res}
 
-\subsection{Free diffusion through porous graphene}
+\subsection*{Free diffusion through porous graphene}
 \label{sec:res-1}
 
-\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
+Fig. \ref{fig:1}a depicts the experimental setup characterizing
 ionic diffusion through a sheet of double layer porous graphene
@@
 connected to a voltage source applying an electrical bias
-$V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
+$V_{\mathrm{G}}$, with the LCR grounded (Fig. \ref{fig:1}a
 inset). We fabricated the PCTE-supported PG as schematically shown in
-\Fig{} \ref{fig:1}b, using the protocol developed by our group
+Fig. \ref{fig:1}b, using the protocol developed by our group
 \cite{Choi_2018} (details see Supplementary Section
-\ref{SI-sec:exp}). The normally distributed, circular pores with pore
+\ref{sec:exp}). The normally distributed, circular pores with pore
 diameters of 20$\pm$10 nm and a pore density of
-1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset)
+1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (Fig. \ref{fig:1}c inset)
 over a large area were perforated on graphene.  By optimizing the
 subsequent transfer process, a high surface coverage ($>$ 98\%) of PG
-on PCTE was obtained (\Fig{} \ref{fig:1}c), allowing reliable
+on PCTE was obtained (Fig. \ref{fig:1}c), allowing reliable
 characterization of the ion transport behavior (details see
-Supplementary Section \ref{SI-sec:exp}).  The system presented here
+Supplementary Section \ref{sec:exp}).  The system presented here
 allows us to systematically investigate the diffusive flux of ions
@@
 flux is comparably small, the conductivity increases linearly with
-time in the LCR (e.g. \Fig{} \ref{fig:2}a) within the measurement
+time in the LCR (e.g. Fig. \ref{fig:2}a) within the measurement
 duration (1 h), suggesting the concentration gradient across the
-membrane remains constant. The diffusive fluxes (blue bars in \Fig{}
+membrane remains constant. The diffusive fluxes (blue bars in Fig.
 \ref{fig:2}b) of different salts were obtained by converting the
 conductivity-time profiles using calibration curves (Supplementary
-Section \ref{SI-sec:measure}). The theoretical diffusive fluxes
+Section \ref{sec:measure}). The theoretical diffusive fluxes
 through PCTE are obtained based on the assumption that the membrane
@@
 By using the salt diffusivity values (Supplementary Table
-\ref{SI-tab:diff}), the calculated diffusive fluxes (red bars in
-\Fig{} \ref{fig:2}b) show reasonable agreement with the experimental
+\ref{tab:diff}), the calculated diffusive fluxes (red bars in
+Fig. \ref{fig:2}b) show reasonable agreement with the experimental
 values.}
@@
 diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
-\Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
+Fig. \ref{fig:2}b), remain at the same order of magnitude compared
 with those of bare PCTE membrane, suggesting that the transport
@@
 which is in good agreement with the value derived from the
-experimental data in \Fig{} \ref{fig:2}b (details see Supplementary
-Section \ref{SI-sec:R-model}).
+experimental data in Fig. \ref{fig:2}b (details see Supplementary
+Section \ref{sec:R-model}).
 % \todo[inline]{Make sure that the
@@
 
-\subsection{Salt rejection induced by electrostatic gating}
+\subsection*{Salt rejection induced by electrostatic gating}
 \label{sec:res-2}
@@
 in controlling the membrane potential in mesoporous carbon membranes
-\cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a
+\cite{Surwade_2014}, is adopted here. Fig. \ref{fig:2}a
 illustratively represents how the measured conductivity evolves with
@@
 ensure the copper tape was not in direct contact with the ionic
-solution (Supplementary Section \ref{SI-sec:copper}). The slope
+solution (Supplementary Section \ref{sec:copper}). The slope
 corresponding to the second interval $s_{2}$, as the conductivity
@@
 salt rejection from bare PG, $\xi$, as a function of $V_{\mathrm{G}}$ (
-details see Supplementary Section \ref{SI-sec:R-model}) as:
+details see Supplementary Section \ref{sec:R-model}) as:
 \begin{equation}
@@
 $V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
-electrochemical reactions (\Fig{} \ref{fig:2}c). We observe an
+electrochemical reactions (Fig. \ref{fig:2}c). We observe an
 asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
@@
 $\xi_{\mathrm{max}}$, as a function of $c_{0}$ from 10$^{-4}$ to
-10$^{-2}$ M KCl (see Supplementary Section \ref{SI-sec:debye}) exhibit
-a power law dependency (\Fig{} \ref{fig:2}d). The
+10$^{-2}$ M KCl (see Supplementary Section \ref{sec:debye}) exhibit
+a power law dependency (Fig. \ref{fig:2}d). The
 $\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
@@
 
-\subsection{Self-consistent ion transport theory}
+\subsection*{Self-consistent ion transport theory}
 \label{sec:theory}
@@
 change of graphene's work function upon charging, known as the
-graphene quantum capacitance effect\cite{Xia_2009} (\Fig{}
+graphene quantum capacitance effect\cite{Xia_2009} (Fig.
 \ref{fig:3}a) following:
@@
 to a work function difference of 48 meV from graphene's Dirac point
-(details see Supplementary Section \ref{SI-sec:charge-dens}), much
+(details see Supplementary Section \ref{sec:charge-dens}), much
 smaller than the $\Delta \phi_{\mathrm{G}}$ induced by gating.
@@
 velocity of graphene (more details find Supplementary Section
-\ref{SI-sec:charge-dens}).  Note that the PG film fabricated
+\ref{sec:charge-dens}).  Note that the PG film fabricated
 experimentally is double-layer turbostratic (randomly aligned)
@@
 \cite{Dean_2010}, effectively reducing the charge density and surface
-potential on graphene $V_{\mathrm{G}}<0$ (Supplementary \Fig{}
-\ref{SI-fig:trap}), which is related to the fact that observed $\xi$
-is much lower within the $V_{\mathrm{G}}<0$ regime in \Fig{}
+potential on graphene $V_{\mathrm{G}}<0$ (Supplementary Fig.
+\ref{fig:trap}), which is related to the fact that observed $\xi$
+is much lower within the $V_{\mathrm{G}}<0$ regime in Fig.
 \ref{fig:2}c. With the nonideality in mind, hereafter, we compare the
 calculations and experiments in the regime of $V_{\mathrm{G}}>0$. For
-example, \Fig{} \ref{fig:3}c presents the calculated
+example, Fig. \ref{fig:3}c presents the calculated
 $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ as a function of
@@
 mM, and LCR at $c_{0}/10$ in axisymmetric coordinates (details see
-Supplementary Section \ref{SI-fig:scheme}). Indeed, the interplay
+Supplementary Section \ref{fig:scheme}). Indeed, the interplay
 between graphene quantum capacitance and the EDL significantly reduces
@@
 
-\subsection{Salt rejection mechanism}
+\subsection*{Salt rejection mechanism}
 \label{sec:mechanism}
@@
 the combined driving force, to reveal its dependence on the applied
-$V_{\mathrm{G}}$. Following the same system considered in \Fig{}
+$V_{\mathrm{G}}$. Following the same system considered in Fig.
 \ref{fig:3}b, the calculated axisymmetric electric potential $\psi$
@@
 $\Delta \mu_{\mathrm{K^{+}}}$ and $\Delta \mu_{\mathrm{Cl^{-}}}$, for
-$V_{\mathrm{G}}$ = 0.75 V are shown in \Fig{} \ref{fig:4}a and
+$V_{\mathrm{G}}$ = 0.75 V are shown in Fig. \ref{fig:4}a and
 \ref{fig:4}b, respectively. The reference point of the electrochemical
@@
 We further reveal the cation and anion transport pathways by looking
-into their electrochemical potentials (\Fig{} \ref{fig:4}b). By
+into their electrochemical potentials (Fig. \ref{fig:4}b). By
 increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
@@
 that the concentration gradient at the pore center becomes small (see
-{ Supplementary Section \ref{SI-sec:conc}, Supplementary
-Figs. \ref{SI-fig:conc} and \ref{SI-fig:conc-r}}).
+{ Supplementary Section \ref{sec:conc}, Supplementary
+Figs. \ref{fig:conc} and \ref{fig:conc-r}}).
 {
@@
 balance between the diffusion and drift potentials (see Supplementary
-Section \ref{SI-sec:conc}, Supplementary Figs.  \ref{SI-fig:potential}
-and \ref{SI-fig:flux})}. 
+Section \ref{sec:conc}, Supplementary Figs.  \ref{fig:potential}
+and \ref{fig:flux})}. 
 The observations confirm the distinct ionic
 transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
-center for cations and pore edge for anions. \Fig{} \ref{fig:4}c
+center for cations and pore edge for anions. Fig. \ref{fig:4}c
 presents the calculated \textit{z}-component of the cation and anion
@@
 pore, $|\boldsymbol{J}_{z}|$, are reduced with $V_{\mathrm{G}}$
-(\Fig{} \ref{fig:4}d). A total flux reduction of $\sim$90\% is
+(Fig. \ref{fig:4}d). A total flux reduction of $\sim$90\% is
 predicted. Another interesting finding here is that, by increasing
@@
 over anions, or in other words, the anion flux is more reduced with
-$V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the ion
+$V_{\mathrm{G}}$ (see Fig. \ref{fig:4}c), known as the ion
 selectivity of graphene nanopore \cite{Rollings_2016}. In our setup,
@@
 More detailed discussion about the selective ionic pathways
-upon gating can be found in Supplementary Section \ref{SI-sec:conc}.}
+upon gating can be found in Supplementary Section \ref{sec:conc}.}
 
@@
 considering the same system (details see Supplementary Section
-\ref{SI-sec:conc}). Intriguingly, by increasing
+\ref{sec:conc}). Intriguingly, by increasing
 $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux starts to
@@
 and (ii) the concentration near the pore edge (preferred path) greatly
-increases (details see Supplementary Section \ref{SI-sec:conc},
-Supplementary Figs. \ref{SI-fig:reverse} and
-\ref{SI-fig:large-V}). This level of $\psi_{\mathrm{G}}$ cannot be
+increases (details see Supplementary Section \ref{sec:conc},
+Supplementary Figs. \ref{fig:reverse} and
+\ref{fig:large-V}). This level of $\psi_{\mathrm{G}}$ cannot be
 reached experimentally in graphene membrane, as this requires a
@@
 function of $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and
-$V_{\mathrm{G}}$ (\Fig{} \ref{fig:5}a). Clearly, when the bulk
+$V_{\mathrm{G}}$ (Fig. \ref{fig:5}a). Clearly, when the bulk
 concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
 to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
-revealed in \Fig{} \ref{fig:5}b, the calculated salt rejection factor
+revealed in Fig. \ref{fig:5}b, the calculated salt rejection factor
 $\xi$ increases with both $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and
@@
 $r_{i}$ (details see Supplementary Section
-\ref{SI-sec:pore-dist}). Combining Eq. \ref{eq:rejection-comb} and
-\Fig{} \ref{fig:5}b, the
+\ref{sec:pore-dist}). Combining Eq. \ref{eq:rejection-comb} and
+Fig. \ref{fig:5}b, the
 calculated salt rejection is reduced to $\sim{}$ 80\% of that from the
-single-pore calculation of a 20 nm nanopore when $c_{0}$ = 0.1 mM (Supplementary \Fig{}
-\ref{SI-fig:simple-rect-pore}). Consider the existence of large pores
+single-pore calculation of a 20 nm nanopore when $c_{0}$ = 0.1 mM (Supplementary Fig.
+\ref{fig:simple-rect-pore}). Consider the existence of large pores
 with diameter up to 60 nm, such degree of salt rejection is still
@@
 $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (details
-see Supplementary Section \ref{SI-sec:pore-dist}).}
-
-\subsection{Effects of salt species}
+see Supplementary Section \ref{sec:pore-dist}).}
+
+\subsection*{Effects of salt species}
 \label{sec:salts}
@@
 Finally, we examine other salt species and compare the degree of salt
-rejection between experiments and simulations. \Fig{} \ref{fig:6}a
+rejection between experiments and simulations. Fig. \ref{fig:6}a
 presents the measured salt rejection $\xi$ as a function of
@@
 K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (details see Supplementary
-Section \ref{SI-sec:salts}). Similar to the KCl system discussed
+Section \ref{sec:salts}). Similar to the KCl system discussed
 earlier, the salt rejection is more pronounced in the positive
@@
 endorsed by our simulations, in which we calculate $\xi$ as a function
-of $V_{\mathrm{G}}$ using the same simulation setups (\Fig{}
+of $V_{\mathrm{G}}$ using the same simulation setups (Fig.
 \ref{fig:6}b). 
@@
 considered using the FEM simulation results with different pore sizes
-(Supplementary \Fig{} \ref{SI-fig:xi-salts-pore})} 
+(Supplementary Fig. \ref{fig:xi-salts-pore})} 
 The calculated $\xi_{\mathrm{max}}$ values are
-quantitatively compared with experiments (\Fig{} \ref{fig:6}c), and
+quantitatively compared with experiments (Fig. \ref{fig:6}c), and
 the same trend is observed. Indeed, because the Debye length
@@
 surface potential appears to decrease in the multivalent salt systems,
-thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b).
+thereby reducing $\xi$ (see Fig. \ref{fig:5}b).
 {
 The slightly higher $\xi$ values of LiCl and NaCl compared with KCl observed in the experiments, 
-are also supported by the FEM simulation results in \Fig{} \ref{fig:6}b, 
-which we attribute to the lower diffusivities of Li$^{+}$ and Na$^{+}$ ions (see Supplementary Table \ref{SI-tab:diff})
+are also supported by the FEM simulation results in Fig. \ref{fig:6}b, 
+which we attribute to the lower diffusivities of Li$^{+}$ and Na$^{+}$ ions (see Supplementary Table \ref{tab:diff})
 }.
@@
 $\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
-species considered here (\Fig{} \ref{fig:6}d). 
+species considered here (Fig. \ref{fig:6}d). 
 % Similar to the
@@
 the salt diffusivity. This finding also explains the concentration
-dependence of $\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
+dependence of $\xi_{\mathrm{max}}$ observed in Fig. \ref{fig:2}d, as
 $\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$. Further including the
@@
 
-\section{Methods}
+\section*{Methods}
 \label{sec:methods}
@@
 buffered hydrofluoric acid (BHF) as described by\cite{Choi_2018}. A
-schematic of the process is shown in \Fig{} S1.
+schematic of the process is shown in Fig. S1.
 
@@
 of 3 measurements and averaging the resulting values (see
-Supplementary Section \ref{SI-sec:measure}). For the measurement, DI water was filled on
+Supplementary Section \ref{sec:measure}). For the measurement, DI water was filled on
 the LCR side, where a 0.1 mM salt solution is placed on the HCR side
@@
 about the simulation setup please refer to Supplementary Section
-\ref{SI-sec:numer}.
+\ref{sec:numer}.
 
@@
 
-\section{Author Contributions}
+\section*{Author Contributions}
 \label{sec:author}
@@
 
+\section*{Competing Interests}
+{ HGP and RMW hold a patent on manufacturing graphene membranes by block copolymer nanolithography (US 10143975, Publication Date 12/04/2018) .}
+
+\section*{Data Availability}
+All data needed to evaluate the conclusions in the paper are present in the paper and/or the Supplementary Materials. Additional data available from authors upon request.
+
 \section*{}
-\label{sec:ref}
+% \label{sec:ref}
 \bibliography{ref}
+%%%%%%%%%%
+%% Add bibitmes
+%%%%%%%%%%
+
+% \section*{}
+% \label{sec:ref}
+% \bibliography{ref}
 
 \clearpage
-\section{Figures}
+\section*{Figures}
 \label{sec:figs}
@@
 
+%%%%%%
+%%Begin SI part
+%%%%%%
+
+\clearpage{}
+\includepdf[page=-]{SI_titlepage.pdf}
+\clearpage{}
+
+\setcounter{page}{1}
+\setcounter{section}{0}
+\setcounter{equation}{0}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\renewcommand{\thepage}{S\arabic{page}}
+\renewcommand{\thesection}{S\arabic{section}}
+\renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
+
+\section{Graphene membrane manufacturing and results.}
+\label{sec:exp}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.95\linewidth]{img/SI-1.png}
+  \caption{Fabrication and characterization of porous graphene membranes. \textbf{a}. Schematic of manufacturing process for
+    patterning of double layer graphene. Graphene is synthesized and
+    transferred to a substrate (glass slide) to yield a double
+    layer. s-BCP is spin-coated and annealed in vacuum to undergo microphase
+    separation, followed by plasma etch and wet etching yielding a
+    porous polystyrene (PS) mask. Anisotropic etching of the mask
+    leads to patterning the underlying graphene, PS is removed by
+    thermal annealing. The porous graphene is then transferred to a
+    substrate (e.g. PCTE). \textbf{b}. Raman spectra of graphene
+    before (orange curve) and after (blue
+    curve) patterning. An increase of the D-peak at 1350 cm$^{-1}$ indicates the
+    formation of defects and edges. The spectra have been normalized
+    to the G-peak intensity and offset for better
+    comparison. \textbf{c}. SEM graph of patterned graphene on PCTE at
+    lower (top) and higher (bottom) magnifications.
+    % Note that tears in
+    % graphene appear bright white with a black center.
+  }
+  \label{fig:exp}
+\end{figure}
+
+\section{Ion diffusion measurement and calculation}
+\label{sec:measure}
+
+The ion diffusion through b-PCTE has been performed using a sample
+sandwiched between two layers of Aluminum tape where the edges have
+been sealed using water-resistant epoxy (ACS Marine Epoxy) to avoid
+interlayer leakage pathways \cite{Choi_2018}.  The sample was inserted in
+the fixture following the same wetting procedure described in the main
+text Methods and was kept wet for the entire series of experiments.
+
+\begin{table}[htbp]
+  \centering
+  \begin{tabular}{lc}
+    \hline
+    Salt & $D$ (10$^{-9}$ m$^{2}\cdot$s$^{-1}$) \\
+    \hline
+    K$^{+}$     & 1.95 \\
+    Na$^{+}$    & 1.33 \\
+    Li$^{+}$    & 1.03 \\
+    SO$_{4}^{2-}$       & 1.06 \\
+    Ca$^{2+}$   & 0.79\\
+    Mg$^{2+}$ & 0.7\\
+    Fe{[(CN)$_{6}$]}$^{3-}$   & 0.90\\
+    Cl$^{-}$ &  2.03 \\
+               \hline
+  \end{tabular}
+  \caption{Different diffusivity values for the anions and cations of the
+    salts used in this work \cite{vanysek_2000}. The theoretical
+    diffusion through PCTE can be calculated using Eq. 1 in the main
+    text and the diffusivities of the respective anion and cation.}
+  \label{tab:diff}
+\end{table}
+
+The conductivity increase $s$ (mS$\cdot$cm$^{-1}\cdot$d$^{-1}$) is
+converted into ion permeation rates $\boldsymbol{J}_{\mathrm{PCTE}}$
+(mol$\cdot$m$^{-2}\cdot$s$^{-1}$) by use of a calibration factor
+$c_{\mathrm{f}}$, the volume of LCR ($V_{\mathrm{LCR}}$) , the area of
+the membrane $A$ and the time $t$ as:
+\begin{equation}
+  \label{eq:JPCTE}
+  \boldsymbol{J}_{\mathrm{PCTE}} = \frac{s V_{\mathrm{LCR}}}{c_{\mathrm{f}} A t}
+\end{equation}
+The calibration factors for all salts have been obtained by a linear
+fit of conductivity \textit{versus} concentration for 4 solutions with
+concentrations from 10$^{-4}$ M to 10$^{-2}$ M and extracting the
+resulting slope. The rest of the factors are $V_{\mathrm{LCR}}$ = 7.33
+mL, $A$ = 9$\times$10$^{-6}$ m$^{2}$. Table \ref{tab:exp-2} shows the
+averaged conductivity increase s, the extracted calibration factors
+$c_{\mathrm{f}}$ and the resulting ion permeation rates using
+Eq. \ref{eq:JPCTE}. The values from this table are shown in main text \Fig 2b
+(blue bars).
+\begin{table}[htbp]
+  \centering
+  \begin{tabular}{lccc}
+    \hline
+    Salt & $s$ (mS$\cdot$cm$^{-1}$d$^{-1}$) & $c_{\mathrm{f}}$ (mS$\cdot$cm$^{-1}\cdot$mol$^{-1}\cdot$L) &
+                                                                                                            $\boldsymbol{J}_{\mathrm{PCTE}}$ (10$^{6}$ mol$\cdot$m$^{-2}\cdot$s$^{-1}$)\\
+    \hline
+    KCl & 1.51$\pm$0.27$\times$10$^{-2}$  & 106   & 1.34 $\pm$ 0.24\\
+    NaCl        & 9.90$\pm$0.17$\times$10$^{-3}$ & 91    & 1.02 $\pm$ 0.02\\
+    LiCl        & 6.03 $\pm$0.80$\times$10$^{-3}$        & 83    & 0.682 $\pm$ 0.090\\
+    CaCl$_{2}$  & 1.25$\pm$0.1$\times$10$^{-2}$    & 149   & 0.789 $\pm$ 0.063\\
+    MgSO$_{4}$  & 8.80$\pm$1.2$\times$10$^{-3}$   & 130   & 0.633 $\pm$ 0.084\\
+    K$_{3}$[Fe(CN)$_{6}]$ & 2.40$\pm$0.28$\times$10$^{-2}$   & 395   & 0.575 $\pm$ 0.063\\
+    K$_{2}$SO4$_{4}$    & 1.98$\pm$0.20$\times$10$^{-2}$  & 258   & 0.722 $\pm$ 0.073\\
+    \hline
+  \end{tabular}
+  \caption{Extracted slope $s$ as an averaged result from 3 consecutive
+    measurements, the calibration factors $c_{\mathrm{f}}$ and the resulting ion
+    permeation $\boldsymbol{J}_{\mathrm{PCTE}}$ through b-PCTE membranes for all salts.}
+  \label{tab:exp-2}
+\end{table}
+
+The experimentally observed flux reduction through PG-PCTE upon
+gating, $\eta$, for all the salts studied here (with concentration of
+0.1 mM in HCR), can be found in Fig. \ref{fig:eta-all}. The effective salt
+rejection ratio $\xi$ is then extracted using main text
+Eq. \ref{eq:xi-def}.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.5\linewidth]{img/SI-eta-all.pdf}
+  \caption{Measured $\eta$ values as function of $V_{\mathrm{G}}$ for
+    various salts used in this work. The concentration in HCR is 0.1
+    mM in all cases.}
+  \label{fig:eta-all}
+\end{figure}
+
+\section{Control experiment with copper tape}
+\label{sec:copper}
+We make sure that the applied voltage is effectively applied via the
+graphene membrane and not through leakage directly coupling the
+copper tape to the ionic solution. For this purpose, we use a device as in \Fig
+1a, omitting the graphene and measuring the current through the
+membrane with the Autolab electrochemical workstation using the
+membrane as working electrode and a platinum wire as counter/reference
+electrode 3.5 cm apart in 0.1 mM KCl. When no graphene is inserted in
+the device, a current in the baseline range ($\sim$ 0.1 nA) is
+observed, indicating no current passing from the membrane. However, if
+graphene is inserted, a current in the range of $\sim$ 10 - 100 nA is
+measured. If the copper tape is in contact with the solution when
+omitting the Kapton tape, the current increases to $\sim$ 1 - 10
+$\mathrm{\mu}$A, independent of the exposed area of the copper tape to
+the solution.
+
+% \pagebreak
+
+\section{Circuit analog model of transport through PG-PCTE}
+\label{sec:R-model}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-resistance-rejection.pdf}
+  \caption{Simple circuit analog model for the transport through
+    PG-PCTE membrane. \textbf{a}. Schematic of PG-PCTE membrane in
+    cross-section view. \textbf{b}. Model for transport resistance in
+    analogy to an electric circuit. This schematic depicts a cut
+    through a PG-PCTE membrane showing a single PCTE pore and multiple
+    graphene pores.}
+  \label{fig:R-model}
+\end{figure}
+The ionic transport through the PG-PCTE membrane is the concerted
+effect the transport resistance through PG and PCTE membranes,
+respectively. As schematically shown in Fig. \ref{fig:R-model}, the
+overall transport resistance of the system is composed of the series
+resistance $R_{\mathrm{G}}$ and $R_{\mathrm{PCTE}}$, respectively. For
+both PG and PCTE membranes, the resistance $R$ is defined as the ratio
+between the concentration between HCR and LCR $\Delta c$, and the total diffusive current $I$ as:
+\begin{equation}
+\label{eq:1}
+R_{i} = \Bigg|\frac{\Delta c}{I_{i}}\Bigg| =  \Bigg|\frac{\Delta c}{J_{i}A_{i}}\Bigg|
+\end{equation}
+where $i$ denotes the membrane type and $A_{i}$ is the area of the
+pore. We further treat $R_{\mathrm{G}}$ as the effective resistance of
+$\gamma$ parallel resistors with individual resistance
+$R_{\mathrm{g}}$, where $\gamma$ is the average number of PG pores per
+PCTE channel, and $R_{\mathrm{g}}$ is the average transport resistance
+per PG pore. The value of $\gamma$ is determined from geometric
+analysis of both membranes: given the pore number density of PG
+($\sim$1.25$\times$10$^{14}$ m$^{-2}$), the pore number density of
+PCTE ($\sim$1.50$\times$10$^{12}$ m$^{-2}$), and the percentage of
+PCTE pores with PG on top ($\sim$0.13), $\gamma$ is determined to be
+$\sim$10.83.
+
+The objective of the circuit analog model is to find effective salt
+rejection ratio through PG, $\xi$ extracted from the experimental
+$\eta$ values (defined in main text Eq. \ref{eq:rejection}). By
+defining $R_{\mathrm{G}}^{0}=R_{\mathrm{G}}(V_{\mathrm{G}}=0)$,
+$\delta = R_{\mathrm{PCTE}} / R_{\mathrm{G}}^{0}$,
+$\chi = R_{\mathrm{G}}/R_{\mathrm{G}}^{0}$, $\eta$ is rewritten using
+transport resistances as:
+\begin{equation}
+  \begin{aligned}[t]
+      \label{eq:eta-R}
+  \eta &= 1 - {\displaystyle
+    \frac{(R_{\mathrm{PCTE}} + R_{\mathrm{G}})^{-1}}
+    {(R_{\mathrm{PCTE}} + R_{\mathrm{G}}^{0})}} \\
+    &= 1 - \frac{\delta + 1}{\delta + R_{\mathrm{G}}/R_{\mathrm{G}}^{0}} \\
+    &= 1 - \frac{\delta + 1}{\delta + \chi}
+  \end{aligned}
+\end{equation}
+Consequentially, the
+salt rejection ratio $\xi$, is associated with $\chi$ by
+$\xi = 1 - \chi^{-1}$ and is related with $\delta$ and $\eta$ via:
+\begin{equation}
+  \label{eq:xi-deriv}
+  \begin{aligned}[t]
+    \xi &= 1 - \chi^{-1} \\
+    &= \frac{(\delta + 1) \eta}{\delta\eta + 1}
+  \end{aligned}
+\end{equation}
+which is main text Eq. \ref{eq:xi-def}. When $0<\eta<1$ (salt
+rejection regime) and $\delta>0$, Eq. \ref{eq:xi-deriv} always
+guarantees $\xi>\eta$, since $\delta + 1$ is always larger than
+$\delta\eta + 1$. In other words, due to the existence of
+$R_{\mathrm{PCTE}}$, the effective salt rejection through PG upon
+gating is always larger than that experimentally observed.
+
+Next we seek the value of $\delta$, the resistance ratio
+between the PCTE and PG membranes, without gating. The range
+of $\delta$ can be estimated from experimental data in main text
+Fig. \ref{fig:2}b using the relation:
+\begin{equation}
+  \label{eq:exp-delta}
+  \delta = \left(\frac{\boldsymbol{J}_{\mathrm{PCTE}}}{\boldsymbol{J}_{\mathrm{PG}}^{0}} -1 \right)^{-1}
+\end{equation}
+by assuming the validity of the circuit analog model for all salt
+systems. As shown in Fig. \ref{fig:delta-compare}, the
+experimentally estimated value of $\delta$ varies from 1 to 5,
+indicating that the resistance of the PG membrane is dominating in the
+PG-PCTE system.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.55\linewidth]{img/SI-delta-estimate.pdf}
+  \caption{Comparison between the $\delta$ value estimated from simple
+    geometric model (Eq. \ref{eq:delta-resistance}) and from
+    experimental value (Eq. \ref{eq:exp-delta}), showing good
+    agreement between the two methods.  }
+  \label{fig:delta-compare}
+\end{figure}
+$\delta$ can also be estimated using geometric parameters of both
+membranes. For a long PCTE channel with length $L$ and
+$r_{\mathrm{PCTE}}$, $R_{\mathrm{PCTE}}$ has power law of
+$L/r_{\mathrm{PCTE}}^{2}$, while for a graphene pore
+with radius $r_{\mathrm{G}}$ and vanishing thickness, the resistance of individual pore $R_{\mathrm{g}}^{0}$
+has power law $1/r_{\mathrm{G}}$ \cite{O_Hern_2014}, which are expressed as:
+\begin{subequations}
+\begin{eqnarray}
+  \label{eq:R-both}
+  R_{\mathrm{PCTE}} &= &k_{\mathrm{PCTE}} \frac{L}{r_{\mathrm{PCTE}}^{2}} \\
+  R_{\mathrm{g}}^{0} &= &k_{\mathrm{g}} \frac{1}{r_{\mathrm{G}}}
+\end{eqnarray}
+\end{subequations}
+where $k_{\mathrm{PCTE}}$ and $k_{\mathrm{g}}$ are the coefficient
+associated with PCTE and PG membranes, respectively. The value of
+$\delta$ is then expressed as:
+\begin{equation}
+  \label{eq:delta-resistance}
+  \delta
+  = \frac{R_{\mathrm{PCTE}}}{R_{\mathrm{G}}^{0}}
+  = {\displaystyle
+    \frac{k_{\mathrm{PCTE}}}{k_{\mathrm{g}}}
+    \frac{L r_{\mathrm{G}} \gamma}
+        {r_{\mathrm{PCTE}}^{2}}}
+\end{equation}
+Here we take $L$=24 $\mu$m, $r_{\mathrm{G}}$=10 nm,
+$r_{\mathrm{PCTE}}$=200 nm. From simple Fick's law,
+the coefficient $k_{\mathrm{PCTE}}$ is determined as
+$1/(D_{\mathrm{\pm}} \pi)$. On the other hand $k_{\mathrm{G}}$ varies
+by the choice of model, ranging from $3 \pi / D_{\mathrm{\pm}}$ using
+the analog of the Sampson formula for
+fluid\cite{Roscoe_1949,Celebi_2014}, to $1/(2 D_{\mathrm{\pm}})$ from
+the Hill formula for disk absorption model
+\cite{Hill_1975,Grebenkov_2018}. As a result the theoretical value of
+$\delta$ has lower bound of $\sim$2.2 (Sampson formula, orange line in
+Fig. \ref{fig:delta-compare}) to $\sim$40.5 (Hill formula). We note
+our experimental values of $\delta$ is in good agreement estimated
+from the Sampson formula (which we use in the main text) while lower
+than the Hill formula. Having a higher estimated value of $\delta$
+could yield unreasonably high value of $\xi$ and the influence of
+concentration is deviated from our theoretical predictions. Further
+theoretical analysis taking nonidealities including surface adsorption
+and chemical nature of pore edge, is required to have better
+understanding of graphene's transport resistance.
+
+% On the other hand, the transport through
+% 2D pore with high radius/thickness ratio falls into the regime of the
+% Sampson formula \cite{Roscoe_1949}, where the entrance resistance
+% dominates over the bulk resistance, with the formula as
+% \cite{Roscoe_1949,Celebi_2014}:
+% \begin{equation}
+%   \label{eq:sampson}
+%   R_{\mathrm{g}}^{0} = \frac{1}{D} \frac{3 \pi}{r_{\mathrm{G}}}
+% \end{equation}
+% We therefore estimate the value of $\delta$ as:
+
+\section{KCl Debye length and conductivity}
+\label{sec:debye}
+Table \ref{tab:debye} gives an overview about the measured
+conductivities and their calculated Debye length values for KCl. The
+information is used to plot the $\xi$ versus $c_{0}$ curve.
+
+\begin{table}[htbp]
+  \centering
+  \begin{tabular}{lccc}
+    \hline
+    $c_{0}$ (mM) & Conductivity (mS$\cdot$cm$^{-1}$) & $\lambda_{\mathrm{D}}$ (nm)\\
+    \hline
+    0.1&        1.90$\times$10$^{-2}$ &        30.4\\
+    0.33&       5.41$\times$10$^{-2}$ & 16.0\\
+    1   &1.33$\times$10$^{-1}$ & 10.0\\
+    3.3&     5.13$\times$10$^{-1}$ &  6.0\\
+    10&      1.08    &3.3\\
+    \hline
+  \end{tabular}
+  \caption{Conductivity and calculated Debye lengths of various KCl
+    concentrations in order to obtain rejection versus
+    concentration curves. }
+  \label{tab:debye}
+\end{table}
+
+\section{Measurement of charge carrier density of patterned graphene}
+\label{sec:charge-dens}
+The intrinsic charge carrier density of graphene was measured using a
+field electron transistor (FET) in air with a 300nm SiO$_2$ as a
+gate. The device setup is shown in Fig. \ref{fig:charge-dens}a,
+where the source and drain electrodes were deposited onto the PG
+sample transferred onto 300nm SiO$_2$ on doped Silicon. The
+characteristic drain-source current $I_{\mathrm{DS}}$ as a function of
+$V_{\mathrm{G}}$ is shown in Fig. \ref{fig:charge-dens}. The
+charge-neutral point gate voltage $V_{\mathrm{CNP}}$ is measured to be 2.8 V.
+Using the capacitance of the SiO$_{2}$ dielectric, we an intrinsic
+charge density of $\sim{}$1.4$\times$10$^{11}$
+\textit{e}$\cdot$cm$^{-2}$, and a shift in the PG's Fermi level by
+$\sim{}$48 meV, which is negligible compared with the gate-induced
+charge density in our experiments. Therefore, the assumption that the
+PG sample is intrinsic without gating, is justified.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-gr-transistor.pdf}
+  \caption{Characterization of the intrinsic charge density of the PG
+    sample using field effect transistor. \textbf{a}. The setup of the
+    PG-FET. \textbf{b}. The I$_{\mathrm{DS}}$ as a function of
+    $V_{\mathrm{G}}$. The charge neutral point gate voltage is
+    determined as $\sim{}$2.8 V, corresponding to an intrinsic charge
+    density of $\sim{}$1.4$\times$10$^{11}$
+    \textit{e}$\cdot$cm$^{-2}$, which is negligible compared with the
+    gate-induced charges.}
+  \label{fig:charge-dens}
+\end{figure}
+
+\pagebreak
+
+\section{Further discussion about the ionic pathway near the graphene pore}
+\label{sec:conc}
+
+In this section we provide a more detailed discussion about the
+different ionic pathways through the graphene nanopore upon gating in
+main text Fig. \ref{fig:4}b. As discussed in the main text, the
+ionic migration arises from both diffusion (caused by
+concentration gradient) and electrostatic drift (caused by electric
+field).  The effect of salt rejection can be viewed as follows: when
+$V_{\mathrm{G}}$ = 0, the flux $\boldsymbol{J}_{\mathrm{G}}$ is solely
+contributed by the concentration gradient, while after applying a
+positive $V_{\mathrm{G}}$, distinct pathways for cations /
+anions are created and the drift flux counteracts the diffusion.
+
+Applying a positive $V_{\mathrm{G}}$ changes the surface distribution
+of the cations / anions. To see this, we plot the concentrations of
+cations ($c_{+}$) and anions ($c_{-}$) near a graphene nanopore with
+$r_{\mathrm{G}}$ = \unit[10]{nm}, $c_{0}$ = \unit[0.1]{mM} and $V_{\mathrm{G}}$ =
+\unit[0.75]{V}, as shown in Fig. \ref{fig:conc}a and \ref{fig:conc}b,
+respectively. The cations are depleted from the graphene surface,
+while the anions are accumulated due to positive
+$\psi_{\mathrm{G}}$. The anion concentration at the graphene surface
+is enhanced $\sim{}$35 times compared with the bulk concentration in
+HCR. The thickness of the depletion / accumulation layer is affected
+by the bulk concentration. Here we show this by comparing the radial
+distribution of $c_{+}$ and $c_{-}$ along the $z = 0$ line within the
+graphene pore. Fig. \ref{fig:conc-r} shows such radial ionic
+concentration distribution at different $c_{0}$ and $V_{\mathrm{G}}$
+levels. When $c_{0}$ = \unit[0.1]{mM}, $\lambda_{\mathrm{D}}$ is larger than
+$r_{\mathrm{G}}$, and the external gate voltage $V_{\mathrm{G}}$ has
+control over both $c_{-}$ and $c_{+}$ within the graphene nanopore
+(Fig. \ref{fig:conc-r}a and \ref{fig:conc-r}c). On the other
+hand, when $c_{0}$ = \unit[100]{mM}, $\lambda_{\mathrm{D}}$ is much smaller
+than $r_{\mathrm{G}}$, and the concentration is only affected by
+$V_{\mathrm{G}}$ close to the pore edge (Fig. \ref{fig:conc-r}b
+and \ref{fig:conc-r}d). Therefore by increasing $c_{0}$ (and
+equivalently reducing $\lambda_{\mathrm{D}}$), $V_{\mathrm{G}}$ loses
+control over the transport in the center of the pore and leads to a
+lower $\xi$ value. Due to the existence of graphene's quantum
+capacitance, the surface potential $\psi_{\mathrm{G}}$ is essentially
+smaller than $V_{\mathrm{G}}$, and the maximum surface anion
+concentration ($c_{0}$ = \unit[100]{mM}, $V_{\mathrm{G}}$ = \unit[1.25]{V}) is
+$\sim{}$ \unit[3]{M}, much smaller than the saturated surface adsorption
+density (at the order of \unit[10$^{2}$]{M}
+\cite{bard_electrochemical_1980}). Therefore we expect the surface
+enhancement of the anions under the FEM conditions to be realistic and
+the influence of the anion concentration on the diffusivity is minimal
+\cite{Tang_1999_I}.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-concentration.pdf}
+  \caption{Cation concentration $c_{+}$ (\textbf{a}.) and anion
+    concentration $c_{-}$ (\textbf{b}.) near the graphene nanopore
+    with $r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM, and
+    $V_{\mathrm{G}}$ = 0.75 V, for a KCl solution at 0.1
+    mM. Depletion of cation and accumulation of anion can be observed
+    near the graphene surface.}
+  \label{fig:conc}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.75\linewidth]{img/SI-conc-r.pdf}
+  \caption{Radial distribution of ions along the line $z=0$ within a
+    graphene nanopore with $r_{\mathrm{G}}$ = 10 nm: (\textbf{a}.)
+    $c_{+}$ at $c_{0}$ = 0.1 mM, (\textbf{b}.) $c_{+}$ at $c_{0}$ =
+    100 mM, (\textbf{c}.) $c_{-}$ at $c_{0}$ = 0.1 mM and
+    (\textbf{d}.) $c_{-}$ at $c_{0}$ = 100 mM. The lines with varied
+    colors indicate the difference of $V_{\mathrm{G}}$ applied.}
+  \label{fig:conc-r}
+\end{figure}
+
+Next we analyze the diffusion and drift contributions to the ionic
+transport. As shown in Fig. \ref{fig:potential}, the
+electrochemical potential energy $\mu_{i}$ is decomposed into the
+electric potential energy $z_{i} c_{i} \psi_{i}$ (Fig.
+\ref{fig:potential}a and \ref{fig:potential}b) and the chemical
+potential energy $k_{\mathrm{B}}T \ln x_{i}$ (Fig.
+\ref{fig:potential}c and \ref{fig:potential}d) near a graphene
+nanopore with $r_{\mathrm{G}}$ = \unit[10]{nm} and $V_{\mathrm{G}}$ = \unit[0.75]
+{V}. The transport of cations is dominated by its chemical potential and
+the diffusion is most pronounced in the center of the pore. The electric and diffusive potentials are similar in magnitude, but with
+opposite signs, counteracting each other. As a result, different pathways for cations
+and anions emerge, where cations preferably pass through the pore
+center, while anions mainly pass near the pore edge, as shown in
+Fig. \ref{fig:flux}.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-electrochemical-decomposite.pdf}
+  \caption{Decomposition of electrochemical potential near a nanopore
+    corresponding to main text \Fig \ref{fig:4}. \textbf{a}. The electrostatic
+    (drift) contribution to the electrochemical potential for cation
+    (left) and anion (right) and \textbf{b}. The concentration (diffusion)
+    contribution to the electrochemical potential for cation (left)
+    and anion (right). The relative small order of magnitude for anion
+    electrochemical potential is caused by the balance between the
+    diffusion and drift for anion.}
+  \label{fig:potential}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-flux.pdf}
+  \caption{z-component fluxes of cation ($J_{z+}$, \textbf{a}.)  and
+    anion ($J_{z-}$ \textbf{b}.) near the graphene nanopore
+    corresponding to Fig. \ref{fig:4}b in main text. The
+    pathways for the different ions can be spatially distinguished:
+    the flux of cation passes mostly through the center of the
+    graphene nanopore while the anion passes mainly through the
+    edge. The analysis is in consistent with the gradient of chemical
+    potential as shown in the main text Fig. \ref{fig:4}b.}
+  \label{fig:flux}
+\end{figure}
+
+We note that when the surface potential $\psi_{\mathrm{G}}$ of
+graphene further increases, the salt rejection may be weakened, or
+even enhanced salt transport is observed. To see this, we artificially
+increase the $\psi_{\mathrm{G}}$ up to over \unit[1]{V} when not considering
+the limiting effect of graphene quantum capacitance. As seen in Fig.
+\ref{fig:reverse}, for each salt concentration $c_{0}$, the averaged
+total flux $J_{z}$ does not further decrease when $\psi_{\mathrm{G}}$
+is larger than a critical potential $V_{\mathrm{c}}$. At low $c_{0}$,
+further increasing $\psi_{\mathrm{G}}$ over $V_{\mathrm{c}}$ may even
+enhance the flux, leading to a negative $\xi$. The reserve of the salt
+rejection at higher $V_{\mathrm{G}}$ values is caused by the enhanced
+anion flux around the pore edge, while the cation flux saturates
+(Fig. \ref{fig:large-V}). Such flux enhancement resembles that in an
+ionic transistor \cite{Nam_2009,Cheng_2018} when ionic current increases
+by applying gate voltage. Nevertheless, this regime may not be easily observed experimentally as the $V_{\mathrm{G}}$ applied may already
+exceed the electrochemical window of water.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.5\linewidth]{img/SI-rect-reverse.pdf}
+  \caption{Average total flux $J_{z}$ in the nanopore as
+    a function of $\psi_{\mathrm{G}}$ at different concentrations. The
+    range of $\psi_{\mathrm{G}}$ is larger than the experimentally
+    achievable value. The rejection of flux becomes weaker after a
+    certain level of $\psi_{\mathrm{G}}$ is reached. Further
+    increasing the surface potential of graphene may even enhance the
+    transportation of ions, which is similar to the cases of ionic
+    transistors.}
+  \label{fig:reverse}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-flux-larger.pdf}
+  \caption{Spatial distribution of $J_{z}$ at $z = 0$ as a function
+    of $r$ in a nanopore with $r_{\mathrm{G}}$ = 20 nm, at different
+    levels of $\psi_{\mathrm{G}}$ (larger than experimentally
+    achievable values) for cation (\textbf{a}.) and anion
+    (\textbf{b}.). The cation flux becomes nearly saturated with
+    increasing $\psi_{\mathrm{G}}$, while the flow of anion near the
+    pore edge becomes much larger. The drastic increase of
+    pore-bounded anion flux is caused by the accumulation of anions
+    near the graphene surface, and in turn causes the increasing of
+    total flux as seen in \Fig \ref{fig:reverse}.}
+  \label{fig:large-V}
+\end{figure}
+\clearpage{}
+
+\section{Effect of pore size distribution}
+\label{sec:pore-dist}
+
+In this section we provide a detailed discussion about the
+influence of pore size distribution on the salt rejection through the
+PG-PCTE membrane. Larger pores are the major contributors to salt flux, while at the same time, the effect of rejection is least pronounced.
+As seen from main text Fig. \ref{fig:1}c
+inset, the average distance between individual nanopores is larger
+than the largest Debye length studied here ($\sim{}$ \unit[30]{nm} for 1 mM 1:1
+salt solution), we can assume that the ionic transport pathways
+through different nanopores do not influence each other and the total
+ionic flux $\boldsymbol{J}_{\mathrm{PG}}$ is the summation of fluxes
+through individual pores $\boldsymbol{J}_{i}$:
+\begin{equation}
+\label{eq:J-total}
+\boldsymbol{J}_{\mathrm{PG}} = \sum_{i} \boldsymbol{J}_{i} = \sum_{r_{i}} x_{r_{i}} \boldsymbol{J}_{r_{i}}
+\end{equation}
+where $r_{i}$ is the radius of individual pores,
+$\boldsymbol{J}_{r_{i}}$ and $x_{r_{i}}$ are the flux of individual
+pore and the distribution probability when
+$r_{\mathrm{G}} = r_{i}$. The salt rejection factor
+$\xi$ through graphene is then expressed as:
+\begin{equation}
+  \label{eq:xi-pore}
+  \begin{aligned}
+    \xi &= 1 - \frac{\sum_{r_{i}} \boldsymbol{J}_{r_{i}} x_{r_{i}}}
+           {\sum_{r_{i}} \boldsymbol{J}_{r_{i}}(V_{\mathrm{G}} = 0) x_{r_{i}}} \\
+           &= 1 - \frac{\sum_{r_{i}} \hat{J}_{r_{i}} r_{i}^{2} x_{r_{i}}}
+           {\sum_{r_{i}} \hat{J}_{r_{i}}^{0} r_{i}^{2} x_{r_{i}}} \\
+           % &approx 1 - \sum_{r_{i}} \frac{\hat{J}_{r_{i}}}{\hat{J}_{r_{i}}^{0}}
+           % \frac{r_{i}^{2} x_{r_{i}}} {\sum_{r_{i}} r_{i}^{2} x_{r_{i}}} \\
+           &\approx \sum_{r_{i}} \left(1 -  \frac{\hat{J}_{r_{i}}}{\hat{J}_{r_{i}}^{0}}\right) w_{r_{i}} \\
+           &= \sum_{r_{i}} \xi_{r_{i}} w_{r_{i}}
+  \end{aligned}
+\end{equation}
+where $\hat{J}$ and $\hat{J}^{0}$ are the flux normalized by pore area
+when $V_{\mathrm{G}} = 0$ and $V_{\mathrm{G}} \neq 0$, respectively,
+$w_{r_{i}} = x_{r_{i}} r_{i}^{2} / \sum_{r_{i}} x_{r_{i}} r_{i}^{2}$ is
+the contribution to the salt rejection from individual pore rejection
+rate $\xi_{r_{i}}$. The linear combination between $\xi_{r_{i}}$ and
+$\xi$ comes from the assumption that $\hat{J}^{0}$ is independent of
+the pore size from the simple Ficknian diffusion.
+
+To get an insight of the influence of the pore size distribution on
+the salt rejection, we combine Equation \ref{eq:xi-pore} with main
+text Fig. \ref{fig:5}b for the salt rejection of a 1:1
+electrolyte to get the pore-distribution-related salt rejection, where
+the pore distribution is taken from the SEM image of real samples (for
+instance main text Fig. \ref{fig:1}c inset). Fig.
+\ref{fig:simple-rect-pore}a shows the contribution $w$ and $\xi$ as
+a function of $r_{\mathrm{G}}$ for individual pores when
+$V_{\mathrm{G}}$ = 1.25 V. As can be seen, the majority of pores fall
+within the regime of $\lambda_{\mathrm{D}} / r_{\mathrm{G}} > 1$,
+corresponding to $\xi(r_{\mathrm{G}}) > 0.6$. As a result, considering
+the pore distribution reduces the value of $\xi$ to $\sim{}$80\% to
+that of a single 20 nm-diameter nanopore (Fig.
+\ref{fig:simple-rect-pore}b), which is indeed close to the highest
+$\xi$ values experimentally observed (for 1mM NaCl system). Such high
+salt rejection even after considering the pore size distribution, can
+be explained by the non-linear nature of $\xi$ with $r_{\mathrm{G}}$
+and $V_{\mathrm{G}}$. As seen in main text Fig{} \ref{fig:5}b,
+for large $V_{\mathrm{G}}$ and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
+regions, $\xi$ reaches a ``plateau'' with its value close to 1. For
+the fabricated PG samples, most pores are within such region when
+$V_{\mathrm{G}}$ = 1.25 V and $c_{0}$ = 0.1 mM, which gives a minor
+change of $\xi$ despite the wide span of pore sizes. In other words,
+although nanopores as large as 60 nm exist in the system, considerably
+high salt rejection more than 80\% can still be achieved.
+
+\begin{figure}[htbp]
+  \centering
+   \includegraphics[width=0.9\linewidth]{img/SI-simple-pore-dist.pdf}
+   \caption{Salt rejection after considering the pore size
+     distribution. \textbf{a}. $w$ (left axis) and $\xi$ (right axis)
+     as a function of $r_{\mathrm{G}}$ for the experimental pore size
+     distribution with $c_{0}$ = 0.1 mM and $V_{\mathrm{G}}$ = 1.25 V.
+     \textbf{b}. Salt rejection ratio $\xi$ as a function of $V_{\mathrm{G}}$ of a
+     0.1mM 1:1 salt from a 20 nm-diameter nanopore (blue line) and
+     from the experimental pore size distribution (orange line), by
+     applying Equation \ref{eq:xi-pore} to main text Fig.
+     \ref{fig:5}b.}
+  \label{fig:simple-rect-pore}
+\end{figure}
+
+To include the pore size distribution effect for all the salts
+studied, we performed FEM analysis for the salt rejection through
+single nanopore of different salts with $r_{\mathrm{G}}$ ranges from
+2.5 nm to 35 nm, while keeping $c_{0}$ constant at 0.1 mM. As shown in
+Fig. \ref{fig:xi-salts-pore}, the behavior of $\xi$ vary with the
+type of salt. As expected, the overall $\xi$ for monovalent salts
+(KCl, NaCl, LiCl) is larger than multivalent salts due to the longer
+Debye length. Moreover, $\xi$ of monovalent salts varies less with the
+pore size compared with multivalent salts. This can be explained by
+the non-linear dependency of $\xi$ on
+$\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ as discussed above. Combine
+the FEM-simulated $\xi$ values with the experimental pore size
+distribution, we obtain main text Fig. \ref{fig:6}.
+
+\begin{figure}[htbp]
+  \centering
+   \includegraphics[width=0.75\linewidth]{img/SI-xi-salt-pore-size.pdf}
+  \caption{FEM-simulated salt rejection ratio $\xi$ as a function of
+    $V_{\mathrm{G}}$ through single nanopores for different salts with
+    varied pore radius. All salts have concentration $c_{0}$ = 0.1 mM.}
+  \label{fig:xi-salts-pore}
+\end{figure}
+
+\pagebreak
+\section{Further details of the numerical simulation }
+\label{sec:numer}
+
+The numerical simulations were carried out using COMSOL Multiphysics
+5.3a. The simulation domain is shown in \Fig \ref{fig:scheme}. To
+simplify the geometry, we use axial symmetric coordinate system. The
+radius \textit{L} and height \textit{H} of both HCR and LCR are set to
+20 $r_{\mathrm{G}}$, the radius of the nanopore. The potential at the
+bottom of the LCR and the center of the graphene domains are set to be
+0 and $\psi_{\mathrm{G}}$, respectively. The potential at the end of
+HCR is not set explicitly, but rather determined through the Poisson
+equation with no flux boundary condition
+$\boldsymbol{D}^{\mathrm{norm}}=0$. The relative permittivity in the
+HCR and LCR is set as $\varepsilon_{\mathrm{}}=78$. The relative
+permittivity of the Stern layer is set to
+$\varepsilon_{\mathrm{H}}=20$\cite{Conway_1951} and for the graphene
+domain we set the relative permittivity as a large number
+(e.g. $10^{5}$) for a better convergence of the solver.  For the
+transport of diluted ionic species, we use the PNP equations, to
+describe the diffusion and drift of the ions, which can be further
+unified by the gradient of electrochemical potential, as described in
+the main text. The initial values of the electrolyte is set to $c_{0}$
+in HCR and 0.1 $c_{0}$ in LCR. At the ends of the cells in the
+z-direction, we use the inlet boundaries conditions for the
+concentration of electrolytes, that the concentration on these
+boundaries remains the same with the initial value, due to the
+effective mixing in the experimental setup.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-numerical-1.png}
+  \caption{Scheme of the simulation domain used. Left: geometry of the
+    whole simulation domain. Right: configuration near the graphene
+    nanopore, corresponding to the red rectangle on the left side.}
+  \label{fig:scheme}
+\end{figure}
+
+The transport of ionic species is described by the steady-state
+Nernst-Planck equation:
+\begin{eqnarray}
+  \label{eq:pnp}
+  \nabla \cdot \boldsymbol{J}_{i} = -\nabla \cdot \left( \frac{D_{i}}{k_{\mathrm{B}}T} c_{i} N_{\mathrm{A}} \nabla \mu_{i}\right)
+  = -\nabla \cdot \left( \frac{D_{i}}{k_{\mathrm{B}} T} c_{i} N_{\mathrm{A}}
+  [k_{\mathrm{B}}T \nabla \ln x_{i} + z_{i} e \nabla \psi]\right) = 0\\
+  x_{i} = \frac{c_{i}}{\sum_{i} c_{i} + c_{\mathrm{H_{2}O}}}
+\end{eqnarray}
+The potential distribution within the whole simulation domain is
+described by the Poisson equation:
+\begin{equation}
+  \label{eq:poisson}
+  \nabla \cdot (\varepsilon_{\mathrm{m}} \varepsilon_{0} \nabla \psi) = -N_{\mathrm{A}} e \sum_{i} c_{i}z_{i}
+\end{equation}
+Where $\varepsilon_{\mathrm{m}}$ is the relative permittivity of
+domain m. The contribution of mobile charges is only valid in the
+solution domain. The use of a large $\varepsilon_{\mathrm{G}}$ ensures
+that the potential in the whole simulation domain can be solved
+continuously.
+
+To simulate the applied external bias $V_{\mathrm{G}}$, we set the
+value of $\psi_{\mathrm{G}}$ explicitly and extract the charge
+$\sigma_{\mathrm{G}}$ by:
+\begin{equation}
+  \label{eq:sigma-G}
+  \sigma_{\mathrm{G}} = - {\displaystyle \frac{\int_{\mathrm{\Omega}} z_{i} c_{i} N_{\mathrm{A}} e \mathrm{d}^{3} \Omega}{S_{\mathrm{G}}}}
+\end{equation}
+and $V_{\mathrm{G}}$ is then calculated by:
+\begin{eqnarray}
+  \label{eq:VG}
+  V_{\mathrm{G}} = \Delta \phi_{\mathrm{G}} + \psi_{\mathrm{G}}\\
+  \sigma_{\mathrm{G}} = \int_{0}^{\Delta \phi_{\mathrm{G}}} \frac{1}{C_{\mathrm{Q}}(\phi_{\mathrm{G}})} \mathrm{d} \phi_{\mathrm{G}}
+\end{eqnarray}
+where the quantum capacitance
+$C_{\mathrm{Q}}=\partial \sigma_{\mathrm{G}}/\partial
+\phi_{\mathrm{G}}$ is calculated by Eq. 8 in main text.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.5\linewidth]{img/SI-trap.png}
+  \caption{Schematic illustration of the origin of the asymmetric
+    rejection with respect to $V_{\mathrm{G}}$. Due to the
+    existence of surface charge traps at negative $V_{\mathrm{G}}$,
+    the graphene is less charged compared to the positive
+    $V_{\mathrm{G}}$.}
+  \label{fig:trap}
+\end{figure}
+
+Note that due to the existence of electron traps on graphene due to
+fabrication process, the induced charge traps on graphene effectively
+reduce the charge density on graphene and greatly attenuate the
+surface potential on graphene, as illustrated in Fig. \ref{fig:trap}. This effect is universally observed in
+CVD-graphene-based field effect transistors in air, while the
+mechanism is fully understood yet. In view of this, we only simulate
+the situation where $V_{\mathrm{G}}>$ 0 for the salt rejection
+mechanism. The trend that $\xi$ is almost independent of
+$V_{\mathrm{G}}$ when $V_{\mathrm{G}}<$ 0 can be qualitatively
+explained by the existence of surface charge traps as stated above.
+We have also tested the mesh-independence of our solutions. As show in
+in Fig. \ref{fig:mesh}a, we use two parameters to control the
+refinement of the mesh entities: (i) triangle mesh division
+$N_{\mathrm{div}}$, giving the smallest triangle mesh size
+$\delta_{\mathrm{G}} / N_{\mathrm{div}}$, where $\delta_{\mathrm{G}}$
+is the thickness of graphene, and (ii) division of mesh
+$N_{\mathrm{b}}$, on the boundary $0<r<r_{\mathrm{G}};z=0$. The
+solution convergence is evaluated by the mean absolute error (MAE) of
+anion flux $\boldsymbol{J}_{z}$ on the boundary
+$0<r<r_{\mathrm{G}};z=0$, as shown in Fig.
+\ref{fig:mesh}b. The solution of the PNP model is sensitive to the
+value $N_{\mathrm{b}}$, and can be regarded numerically converged when
+$N_{\mathrm{b}}>100$. Combining the calculation effort and numerical
+precision, we adapt the value $N_{\mathrm{div}}=5$ and
+$N_{\mathrm{b}}=100$ in our simulations.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\linewidth]{img/SI-mesh.pdf}
+  \caption{Mesh independence of the solution. \textbf{a}. Scheme of
+    the mesh refinement near the graphene pore. The values
+    $N_{\mathrm{div}}$ and $N_{\mathrm{b}}$ controls the size of mesh
+    along the boundary $z=0, 0<r<r_{\mathrm{G}}$ (shown in
+    red). \textbf{b}. Mean absolute error (MAE) of the anion flux
+    $\boldsymbol{J}_{z}$ along the boundary $z=0,
+    0<r<r_{\mathrm{G}}$. The error is more sensitive to
+    $N_{\mathrm{b}}$ than $N_{\mathrm{div}}$.}
+  \label{fig:mesh}
+\end{figure}
+
+\section{Conductivity and Debye length for all salts}
+\label{sec:salts}
+In Table \ref{tab:conductivity}, the conductivities and calculated Debye
+lengths for 6 salts are shown. At the same concentration, the higher
+ionic strength of the multivalent salts leads to a reduction of the
+respective Debye lengths.
+
+\begin{table}[htbp]
+  \centering
+  \begin{tabular}{lcc}
+    \hline
+    Solution & Conductivity (mS$\cdot$cm$^{-1}$) & $\lambda_{\mathrm{D}}$ (nm) \\
+    \hline
+    0.1 mM NaCl &1.80$\times$10$^{-2}$  &30.4\\
+    0.1 mM LiCl &1.58$\times$10$^{-2}$ &30.4\\
+    0.1 mM CaCl$_{2}$&  2.19$\times$10$^{-2}$ &17.2\\
+    0.1 mM MgSO$_{4}$   &3.27$\times$10$^{-2}$ &15.2\\
+    0.1 mM K$_{2}$SO$_{4}$      &4.16$\times$10$^{-2}$ &17.2\\
+    0.1 mM K$_{3}$[Fe(CN)$_{6}$]&       5.95$\times$10$^{-2}$  &12.4\\
+    \hline
+  \end{tabular}
+  \caption{Conductivity and $\lambda_{\mathrm{D}}$ of various salts.}
+  \label{tab:conductivity}
+\end{table}
+
 \end{document}

### 2019-07-19 paper/paper.tex
More changes before sending to NL

@@
 portion of excessively large pores or tears can significantly diminish
-salt rejection. Therefore, it is critical to develop methodology that
-allow appreciable selectivity of nanoporous 2D membrane even with
-large pore size. Very recently, a number of reports have explored the
+salt rejection. Regarding these issues, we have previously developed a
+highly-scalable technique to fabricate uniformly-distributed nanopores
+(sub-20 to 50 nm) over wafer-scale graphene samples
+\cite{Choi_2018}. A major step towards its real-world desalination and
+separation applications, would be to develop methodology that allow
+appreciable selectivity of nanoporous 2D membrane with pore size even
+larger than the hydration radii.
+% Therefore, it is critical to develop methodology that
+% allow appreciable selectivity of nanoporous 2D membrane even with
+% large pore size.
+A number of recent reports have explored the
 effect of surface charges on the selectivity of ion transport through
@@
 investigate electrolyte permeation through graphene nanopores that are
-significantly larger than the hydrated radii. We model the surface
-potential by taking into account of the elementary electronic
+significantly larger than the hydration radii. We model the surface
+potential by taking into account the elementary electronic
 properties of graphene and demonstrate that a high degree of salt
-rejection can be achieved by electrostatic gating.
+rejection could be achieved by both pore sizing and electrostatic gating.
 
@@
 increase of $\xi$, or a decrease of diffusive flux through PG with
-$V_{\mathrm{G}}$, showing an inverse trend compared with those
+$V_{\mathrm{G}}$, shows an inverse trend compared with those
 observed in ionic field effect transistors (IFETs) in which the
@@
 \cite{Nam_2009,Cheng_2018}. A further increase of the KCl
-concentration $c_{0}$ influences the attainable degree of salt
+concentration $c_{0}$ influences the obtainable degree of salt
 rejection. 
 {
-We note that the small negative $\xi$ values (corresponding to reduced transport resistance) at $V_{\mathrm{G}} \sim{}$ -0.5 V
-may be caused by (i) the charge neutral point (CNP) of graphene is not exactly at $V_{\mathrm{G}}$ = 0, and (ii) experimental uncertainty.
+We note the small negative $\xi$ values (corresponding to reduced transport resistance) at $V_{\mathrm{G}} \sim{}$ -0.5 V
+likely caused by (i) offset of the charge neutral point (CNP) of graphene from $V_{\mathrm{G}}$ = 0, and (ii) experimental uncertainty.
 Nevetherless, significant salt rejection is observed when $V_{\mathrm{G}}>$ 0.5 V.
@@
 smaller than the $\Delta \phi_{\mathrm{G}}$ induced by gating.
-Therefore we adapt the simplification that the charge neutrality point
+Therefore we adopt the simplification that the charge neutrality point
 of graphene coincides with the Dirac point at $V_{\mathrm{G}}$ =
@@
 $v_{\mathrm{F}}=1.1\times10^{6}$ m$\cdot$s$^{-1}$ is the Fermi
-velocity of graphene (more details find Supplementary Section
-\ref{SI-sec:charge-dens}).  Note that the PG film fabricated
-experimentally is double-layer turbostratic (randomly aligned)
-graphene, in which we assume the
-$\Delta \phi_{\mathrm{G}} - \sigma_{\mathrm{G}}$ dependence follows
-Eq. \eqref{eq:delta-phiG}. The theory proposed here was solved
+velocity of graphene.  Note that the PG film fabricated experimentally
+is double-layer turbostratic (randomly aligned) graphene, in which we
+assume the $\Delta \phi_{\mathrm{G}} - \sigma_{\mathrm{G}}$ dependence
+follows Eq. \eqref{eq:delta-phiG}. The influence of polymer residue on
+the surface of graphene is not considered in the current theory due
+to: (i) insulating polymer residues do not respond to the gate voltage
+and (ii) the thickness of the polymer residue is minimal after the
+thermal annealing process. The theory proposed here was solved
 self-consistently by discretizing
@@
 mM, and LCR at $c_{0}/10$ in axisymmetric coordinates (details see
-Supplementary Section \ref{SI-fig:scheme}). Indeed, the interplay
+Supplementary Section \ref{SI-sec:numer}). Indeed, the interplay
 between graphene quantum capacitance and the EDL significantly reduces

### 2019-07-19 paper/convert_svg.py
Change TOC figure

@@ -1,3 +1,4 @@
+#!/usr/bin/env python3
 import re
 import os, os.path
 import shutil

### 2019-08-20 paper/combined.tex
Change after final decision from NL

@@
 \textbf{Teaser}:\\
-The quantum capacitance-induced surface potential can stop electrolyte transport through a "large" graphene nanopore.
+The quantum capacitance-induced surface potential can stop electrolyte transport through a ``large'' graphene nanopore.
 \end{flushleft}
@@
 a large area with atomic precision remains technically challenging, 
-{limiting the effective separation or demanding leak-sealing mechanism such as interfacial polymerization}
+limiting the effective separation
+  % or demanding leak-sealing mechanism such as interfacial polymerization
 \cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
 portion of excessively large pores or tears can significantly diminish
-salt rejection.  Very recently, a number of reports have explored the
-effect of surface charges on the selectivity of ion transport through
-graphene nanopores, as a consequence of the electrostatic interactions
-between solvated ions and the charged functional groups attached on
-graphene, indicating that even large pores ($>$ 30nm) can be ion
-selective \cite{Rollings_2016,Surwade_2014}. However, it remains
-controversial that if the surface charges can result in a degree of
-salt rejection, as the surface charge and potential cannot be
-precisely quantified and are sensitive to the surroundings as well as
-the history of chemical treatment \cite{Li_2008}. There remains a lack
-of fundamental understanding of the interactions between the charged
-2D nanopores and the electrolyte solution, { especially in regard of controlled ion transport modulation}.
-
-In this report, we
-investigate electrolyte permeation through graphene nanopores that are
-significantly larger than the hydrated radii. We model the surface
-potential by taking into account of the elementary electronic
-properties of graphene and demonstrate that a high degree of salt
-rejection can be achieved by electrostatic gating.
+salt rejection. Regarding these issues, we have previously developed a
+highly-scalable technique to fabricate uniformly-distributed nanopores
+(sub-20 to 50 nm) over wafer-scale graphene samples
+\cite{Choi_2018}. A major step towards its real-world desalination and
+separation applications, would be to develop methodology that allow
+appreciable selectivity of nanoporous 2D membrane with pore size even
+larger than the hydration radii. A number of recent reports have
+explored the effect of surface charges on the selectivity of ion
+transport through graphene nanopores, as a consequence of the
+electrostatic interactions between solvated ions and the charged
+functional groups attached on graphene, indicating that even large
+pores ($>$ 30nm) can be ion selective
+\cite{Rollings_2016,Surwade_2014}. However, it remains controversial
+that if the surface charges can result in a degree of salt rejection,
+as the surface charge and potential cannot be precisely quantified and
+are sensitive to the surroundings as well as the history of chemical
+treatment \cite{Li_2008}. There remains a lack of fundamental
+understanding of the interactions between the charged 2D nanopores and
+the electrolyte solution, { especially in regard of controlled ion
+  transport modulation}.
+
+In this report, we investigate electrolyte permeation through graphene
+nanopores that are significantly larger than the hydration radii. We
+model the surface potential by taking into account the elementary
+electronic properties of graphene and demonstrate that a high degree
+of salt rejection could be achieved by both pore sizing and
+electrostatic gating.
 
@@
 Fig. \ref{fig:1}b, using the protocol developed by our group
-\cite{Choi_2018} (details see Supplementary Section
+\cite{Choi_2018}, which  enables formation of uniformly-distributed graphene  nanopores over large area up
+ to 25 cm$^{2}$ (details see Supplementary Section
 \ref{sec:exp}). The normally distributed, circular pores with pore
@@
 \cite{Nam_2009,Cheng_2018}. A further increase of the KCl
-concentration $c_{0}$ influences the attainable degree of salt
+concentration $c_{0}$ influences the obtainable degree of salt
 rejection. 
-{
-We note that the small negative $\xi$ values (corresponding to reduced transport resistance) at $V_{\mathrm{G}} \sim{}$ -0.5 V
-may be caused by (i) the charge neutral point (CNP) of graphene is not exactly at $V_{\mathrm{G}}$ = 0, and (ii) experimental uncertainty.
+We note small negative $\xi$ values (corresponding to reduced transport resistance) at $V_{\mathrm{G}} \sim{}$ -0.5 V
+likely caused by (i) offset of the charge neutral point (CNP) of graphene is from $V_{\mathrm{G}}$ = 0 and (ii) experimental uncertainty.
 Nevetherless, significant salt rejection is observed when $V_{\mathrm{G}}>$ 0.5 V.
-}
 The $\xi$ values measured at $V_{\mathrm{G}}$ = 1.25 V,
@@
 smaller than the $\Delta \phi_{\mathrm{G}}$ induced by gating.
-Therefore we adapt the simplification that the charge neutrality point
+Therefore, we adopt the simplification that the charge neutrality point
 of graphene coincides with the Dirac point at $V_{\mathrm{G}}$ =
@@
 $v_{\mathrm{F}}=1.1\times10^{6}$ m$\cdot$s$^{-1}$ is the Fermi
-velocity of graphene (more details find Supplementary Section
-\ref{sec:charge-dens}).  Note that the PG film fabricated
-experimentally is double-layer turbostratic (randomly aligned)
-graphene, in which we assume the
+velocity of graphene \cite{Tian_2016}.  Note that the PG film
+fabricated experimentally is double-layer turbostratic (randomly
+aligned) graphene, in which we assume the
 $\Delta \phi_{\mathrm{G}} - \sigma_{\mathrm{G}}$ dependence follows
-Eq. \eqref{eq:delta-phiG}. The theory proposed here was solved
+Eq. \eqref{eq:delta-phiG}. The influence of polymer residue on the
+surface of graphene is not considered in the current theory due to:
+(i) insulating polymer residues do not respond to the gate voltage and
+(ii) the thickness of the polymer residue is minimal after the thermal
+annealing process. The theory proposed here was solved
 self-consistently by discretizing
@@
 potential on graphene $V_{\mathrm{G}}<0$ (Supplementary Fig.
-\ref{fig:trap}), which is related to the fact that observed $\xi$
-is much lower within the $V_{\mathrm{G}}<0$ regime in Fig.
+\ref{fig:trap}), which is related to the fact that observed $\xi$ is
+much lower within the $V_{\mathrm{G}}<0$ regime in Fig.
 \ref{fig:2}c. With the nonideality in mind, hereafter, we compare the
 calculations and experiments in the regime of $V_{\mathrm{G}}>0$. For
-example, Fig. \ref{fig:3}c presents the calculated
+example, Fig. \ref{fig:3}b presents the calculated
 $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ as a function of
@@
 mM, and LCR at $c_{0}/10$ in axisymmetric coordinates (details see
-Supplementary Section \ref{fig:scheme}). Indeed, the interplay
-between graphene quantum capacitance and the EDL significantly reduces
-the graphene surface potential $\psi_{\mathrm{G}}$ to $\sim$0.3 V at
+Supplementary Section \ref{sec:numer}). Indeed, the interplay between
+graphene quantum capacitance and the EDL significantly reduces the
+graphene surface potential $\psi_{\mathrm{G}}$ to $\sim$0.3 V at
 $V_{\mathrm{G}}$ = 1.25 V, corresponding a surface charge density
@@
 the gate-controlled ionic transport can also be achieved by replacing
-graphene with other nanoporous conducting 2D materials, although the
-operational gate voltage window required to achieve the same degree of
-salt rejection may be narrower, because graphene has the smallest
-quantum capacitance (near the Dirac point) among all known 2D
-materials \cite{Tian_2016}.
+graphene with other nanoporous conducting 2D materials, while they are
+less practical due to the narrower operational window of gate voltage
+required to achieve the same level of salt rejection. This is because
+graphene has the smallest quantum capacitance (near the Dirac point)
+among all known 2D materials \cite{Tian_2016}.
 
@@
 increase, reversing the trend observed at the low $\psi_{\mathrm{G}}$
-regime, due to (i) the drift flux become dominant over diffusion flux
+regime, due to scenarios that (i) the drift flux become dominant over diffusion flux
 and (ii) the concentration near the pore edge (preferred path) greatly
@@
 We notice that the calculations in Figs. \ref{fig:4} and \ref{fig:5} 
-are based on the setup  of ionic transport through single nanopore.
+are based on the setup  of ionic transport through a single nanopore.
 In order to mimic the experimental conditions, 
@@
 is the contribution factor from pores with radius $r_{i}$, and
-$x_{r_{i}}$ is the fraction of pores with radius
-$r_{i}$ (details see Supplementary Section
-\ref{sec:pore-dist}). Combining Eq. \ref{eq:rejection-comb} and
-Fig. \ref{fig:5}b, the
-calculated salt rejection is reduced to $\sim{}$ 80\% of that from the
-single-pore calculation of a 20 nm nanopore when $c_{0}$ = 0.1 mM (Supplementary Fig.
-\ref{fig:simple-rect-pore}). Consider the existence of large pores
-with diameter up to 60 nm, such degree of salt rejection is still
-appreciable, which is ascribed to the nonlinear dependency of $\xi$ on
-$\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (details
-see Supplementary Section \ref{sec:pore-dist}).}
+$x_{r_{i}}$ is the fraction of pores with radius $r_{i}$ (details see
+Supplementary Section \ref{sec:pore-dist}). Combining
+Eq. \ref{eq:rejection-comb} and Fig. \ref{fig:5}b, the calculated salt
+rejection is reduced to $\sim{}$ 80\% of that from the single-pore
+calculation of a 20 nm nanopore when $c_{0}$ = 0.1 mM (Supplementary
+Fig.  \ref{fig:simple-rect-pore}). Consider the existence of large
+pores with diameter up to 60 nm, such degree of salt rejection is
+still appreciable, which is ascribed to the nonlinear dependency of
+$\xi$ on $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and $V_{\mathrm{G}}$
+(details see Supplementary Section \ref{sec:pore-dist}).}  From our
+analysis, it is also clear that reducing the average pore size is critical
+to overcome the low salt rejection at higher concentrations, which may
+hopefully be achieved with relevant fabrication techniques.
 
@@
   \eta &= 1 - {\displaystyle
-    \frac{(R_{\mathrm{PCTE}} + R_{\mathrm{G}})^{-1}}
-    {(R_{\mathrm{PCTE}} + R_{\mathrm{G}}^{0})}} \\
+    \left[\frac{(R_{\mathrm{PCTE}} + R_{\mathrm{G}})}
+    {(R_{\mathrm{PCTE}} + R_{\mathrm{G}}^{0})}\right]^{-1}} \\
     &= 1 - \frac{\delta + 1}{\delta + R_{\mathrm{G}}/R_{\mathrm{G}}^{0}} \\
@@
 charge-neutral point gate voltage $V_{\mathrm{CNP}}$ is measured to be 2.8 V.
-Using the capacitance of the SiO$_{2}$ dielectric, we an intrinsic
+Using the capacitance of the SiO$_{2}$ dielectric, we estimate an intrinsic
 charge density of $\sim{}$1.4$\times$10$^{11}$

### 2019-08-20 paper/paper.tex
Change after final decision from NL

@@
 \newcommand{\Fig}{Fig.}
+%%Uncomment to disable color changes
+\renewcommand*{\textcolor}[2]{#2}
 % \usepackage{lineno}
@@
 
-\keywords{graphene, nanopore, patterning, salt rejection, gating, finite element modeling, quantum capacitance}
+% \keywords{graphene, nanopore, patterning, salt rejection, gating, finite element modeling, quantum capacitance}
+
+\keywords{\textcolor{blue}{nanoporous graphene}, salt rejection, gating, finite element modeling, quantum capacitance}
 
@@
 membranes over a large area with atomic precision remains technically
-challenging, { limiting the effective separation or demanding
-  leak-sealing mechanism such as interfacial polymerization}
+challenging, limiting the effective separation or demanding
+  leak-sealing mechanism such as interfacial polymerization
 \cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
@@
 % large pore size.
-A number of recent reports have explored the
-effect of surface charges on the selectivity of ion transport through
-graphene nanopores, as a consequence of the electrostatic interactions
-between solvated ions and the charged functional groups attached on
-graphene, indicating that even large pores ($>$ 30nm) can be ion
-selective \cite{Rollings_2016,Surwade_2014}. However, it remains
-controversial that if the surface charges can result in a degree of
-salt rejection, as the surface charge and potential cannot be
-precisely quantified and are sensitive to the surroundings as well as
-the history of chemical treatment \cite{Li_2008}. There remains a lack
-of fundamental understanding of the interactions between the charged
-2D nanopores and the electrolyte solution, { especially in regard of controlled ion transport modulation}.
-
-In this report, we
-investigate electrolyte permeation through graphene nanopores that are
-significantly larger than the hydration radii. We model the surface
+A number of recent reports have explored the effect of surface charges
+on the selectivity of ion transport through graphene nanopores, as a
+consequence of the electrostatic interactions between solvated ions
+and the charged functional groups attached on graphene, indicating
+that even large pores ($>$ 30nm) can be ion selective
+\cite{Rollings_2016,Surwade_2014}. However, it remains controversial
+that if the surface charges can result in a degree of salt rejection,
+as the surface charge and potential cannot be precisely quantified and
+are sensitive to the surroundings as well as the history of chemical
+treatment \cite{Li_2008}. There remains a lack of fundamental
+understanding of the interactions between the charged 2D nanopores and
+the electrolyte solution, especially in regard of controlled ion
+transport modulation.
+
+% \textcolor{blue}{In this report, we investigate electrolyte permeation
+  % through cm$^2$ scale graphene membranes having pores that are
+  % $<$\unit[50]{nm}. We find, that an applied voltage bias can
+  % effectively modulate the ion transport through these membranes,
+  % despite having pores significantly larger than the hydration radii
+  % of the ions.  We simulate the surface potential, taking into account
+  % the elementary electronic properties of graphene, allowing to model
+  % and confirm that a high degree of salt rejection could be achieved
+  % by both pore sizing and electrostatic gating. Our analysis reveals a
+  % large impact of atomistic effects, such as quantum capacitance, on
+  % the ionic transport through gated porous 2D materials, providing new
+  % insights into such phenomena.}
+
+\textcolor{blue}{ In this report, we investigate electrolyte
+  permeation through centimeter scale graphene membranes having pores
+  that are in the order of $\sim{}$\unit[20]{nm}. We find that
+  electrostatic gating can effectively reduce ion transport through
+  these membranes, despite the pore size is significantly larger than
+  the hydration radii of the ions. In the literature, it was only
+  observed in the membranes made by mesoporous carbon
+  \cite{Surwade_2014}. For the first time, we model the surface
   potential by taking into account the elementary electronic
-properties of graphene and demonstrate that a high degree of salt
-rejection could be achieved by both pore sizing and electrostatic gating.
+  properties of graphene and confirm that a high degree of salt
+  rejection could be achieved by both pore sizing and electrostatic
+  gating. }
 
@@
 experimentally observed reduction of diffusive flux upon
-gating. Indeed, the same physical mechanism also governs 
-the 
-{ diode-like ionic
-transport through an IFET  \cite{Nam_2009,Lee_2015,Feng_2016}
-or a nanoporous metal membrane \cite{mccurry2017electrolyte}},
-in which a nonzero electric potential at
-the nanopore center usually results in an increase of ionic
-conductivity. To this end, we
-further increased the graphene surface potential $\psi_{\mathrm{G}}$
-considering the same system (details see Supplementary Section
-\ref{SI-sec:conc}). Intriguingly, by increasing
-$\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux starts to
-increase, reversing the trend observed at the low $\psi_{\mathrm{G}}$
-regime, due to (i) the drift flux become dominant over diffusion flux
-and (ii) the concentration near the pore edge (preferred path) greatly
-increases (details see Supplementary Section \ref{SI-sec:conc},
-Supplementary Figs. \ref{SI-fig:reverse} and
+gating. Indeed, the same physical mechanism also governs the {
+  diode-like ionic transport through an IFET
+  \cite{Nam_2009,Lee_2015,Feng_2016} or a nanoporous metal membrane
+  \cite{mccurry2017electrolyte}}, in which a nonzero electric
+potential at the nanopore center usually results in an increase of
+ionic conductivity. To this end, we further increased the graphene
+surface potential $\psi_{\mathrm{G}}$ considering the same system
+(details see Supplementary Section \ref{SI-sec:conc}). Intriguingly,
+by increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
+starts to increase, reversing the trend observed at the low
+$\psi_{\mathrm{G}}$ regime, due to (i) the drift flux become dominant
+over diffusion flux and (ii) the concentration near the pore edge
+(preferred path) greatly increases (details see Supplementary Section
+\ref{SI-sec:conc}, Supplementary Figs. \ref{SI-fig:reverse} and
 \ref{SI-fig:large-V}). This level of $\psi_{\mathrm{G}}$ cannot be
@@
 $V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
-= { 2.0},
-a high value of $\xi$ up to $\sim$0.95 can be achieved.  We
+= { 2.0}, a high value of $\xi$ up to $\sim$0.95 can be achieved.  We
 notice that although the above analysis suggests a salt rejection up
@@
 zero-volume charges, may not be valid when $r_{\mathrm{G}}<$ 5
-nm\cite{Jain_2015}. In addition, the specific ion-graphene
-interactions \cite{Rollings_2016} are not taken into account. Advanced
-theoretical frameworks that bridge continuum and molecular models are
-required to elucidate electrolyte transport approaching the small pore
-limit. 
+nm\cite{Jain_2015}. \textcolor{blue}{ Furthermore, while the proposed
+  simplified model can nicely describe the experimental results for
+  the relatively large pore size investigated, such that the
+  electrochemical potential-driven diffusion pathway is dominant,
+  selective adsorption caused by unique chemical nature of pore edges
+  may be significant in the small-pore systems. Therefore, advanced
+  theoretical frameworks that bridge continuum and molecular models
+  are required to elucidate the role of surface adsorption in
+  electrolyte transport through approaching the small pore limit. }
+
+% \textcolor{blue}{Furthermore, the specific adsorption of ions
+  % \cite{bard_electrochemical_1980} on porous graphene surface with
+ % on highly-charged sites \cite{Rollings_2016} is ignored in the current
+  % model due to (i) low intrinsic charge density of porous graphene
+  % fabricated using the BCP-patterning method and (ii) the surface charge
+  % on graphene being effectively dominated by gating (Supplementary
+  % Section \ref{SI-sec:charge-dens}). A full kinetic description of
+  % such interactions should, however, be included in the model in case 
+  % highly-adsorbing species such as fluoride or organic ions are
+  % involved \cite{He_2012}.}
+
 {
@@
 Furthermore, as the definition of $\xi$ based on $\delta$ is only valid for positive $\eta$, the discussion is hence limited to $V_{\mathrm{G}}$ $>$ 0.}
-The degree of salt rejection deceases with
-the salt valance; for example, the measured $\xi$ values at
-$V_{\mathrm{G}}$ = 1.25 V decreases from $>$ 0.5 for monovalent NaCl
-to -0.04 for multivalent K$_{3}$[Fe(CN)$_{6}$]. This observation is
-endorsed by our simulations, in which we calculate $\xi$ as a function
-of $V_{\mathrm{G}}$ using the same simulation setups (\Fig{}
-\ref{fig:6}b). 
-{
-The effect of pore size distribution is explicitly
-considered using the FEM simulation results with different pore sizes
-(Supplementary \Fig{} \ref{SI-fig:xi-salts-pore})} 
-The calculated $\xi_{\mathrm{max}}$ values are
-quantitatively compared with experiments (\Fig{} \ref{fig:6}c), and
-the same trend is observed. Indeed, because the Debye length
-$\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
-surface potential appears to decrease in the multivalent salt systems,
-thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b).
-{
-The slightly higher $\xi$ values of LiCl and NaCl compared with KCl observed in the experiments, 
-are also supported by the FEM simulation results in \Fig{} \ref{fig:6}b, 
-which we attribute to the lower diffusivities of Li$^{+}$ and Na$^{+}$ ions (see Supplementary Table \ref{SI-tab:diff})
-}.
-The calculated and
-experimental $\xi_{\mathrm{max}}$ as a function of
+The degree of salt rejection deceases with the salt valance; for
+example, the measured $\xi$ values at $V_{\mathrm{G}}$ = 1.25 V
+decreases from $>$ 0.5 for monovalent NaCl to -0.04 for multivalent
+K$_{3}$[Fe(CN)$_{6}$]. This observation is endorsed by our
+simulations, in which we calculate $\xi$ as a function of
+$V_{\mathrm{G}}$ using the same simulation setups (\Fig{}
+\ref{fig:6}b).  { The effect of pore size distribution is explicitly
+  considered using the FEM simulation results with different pore
+  sizes (Supplementary \Fig{} \ref{SI-fig:xi-salts-pore})} The
+calculated $\xi_{\mathrm{max}}$ values are quantitatively compared
+with experiments (\Fig{} \ref{fig:6}c), and the same trend is
+observed. Indeed, because the Debye length $\lambda_{\mathrm{D}}$
+decreases with the salt valence, the graphene surface potential
+appears to decrease in the multivalent salt systems, thereby reducing
+$\xi$ (see \Fig{} \ref{fig:5}b).  { The slightly higher $\xi$ values
+  of LiCl and NaCl compared with KCl observed in the experiments, are
+  also supported by the FEM simulation results in \Fig{} \ref{fig:6}b,
+  which we attribute to the lower diffusivities of Li$^{+}$ and
+  Na$^{+}$ ions (see Supplementary Table \ref{SI-tab:diff}) }.  The
+calculated and experimental $\xi_{\mathrm{max}}$ as a function of
 $\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
-species considered here (\Fig{} \ref{fig:6}d). 
-% Similar to the
-% experimental observations, slightly higher $\xi$ of salts
-% with same valence (e.g. LiCl, NaCl and KCl) is also predicted from the
-% simulations due to the variation in ionic mobilities. 
-We notice that
+species considered here (\Fig{} \ref{fig:6}d).  \textcolor{blue}{
+  Similar to the experimental observations, slightly higher $\xi$ for
+  salts with same valence (e.g. LiCl, NaCl and KCl) is also observed
+  in the simulations due to the variation in ionic mobilities as well
+  as the possible specific surface adsorption of ions.} We notice that
 without any fitting parameters, our theory can predict the
@@
 linear, suggesting that the effect of Debye length is dominant over
-the salt diffusivity. This finding also explains the concentration
-dependence of $\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
-$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$. Further including the
-specific interaction of ionic species with the graphene membrane
-{- such as cation-$\pi$ interacation \cite{shi2013ion}} - may give even better agreement with experimental
-results \cite{Ghosh_2018}. More interestingly, based on our theoretical analysis, we
-predict that a very high degree of salt rejection ($\xi>$ 0.99) can be
-already achieved when $\lambda / r_{\mathrm{G}}>$3. In other words,
-for example, when the Debye length is 20 nm, one can suppress 99 \% of
-the diffusive flux by further reducing the pore radius down to
-$\sim$5-6 nm, which still remains larger than the hydrated radii. In
-combination with the development of nanoscale etching techniques, we
-believe that the physical picture presented here makes one step closer
-to large-scale production of graphene membranes.
+the salt diffusivity.
+This
+finding also explains the concentration dependence of
+$\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
+$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$.
+\textcolor{blue}{It is worth noting that the
+  observed linearity can only describe the $\lambda_{\mathrm{D}}$
+  range considered here. When $\lambda_{\mathrm{D}}$ increases beyond
+  30 nm, this linear relation would yield a $\xi_{\mathrm{max}}$
+  value larger than 1, which appears to be unphysical.  More follow-up
+  experimental and theoretical efforts are required to further
+  investigate the small/large $\lambda_{\mathrm{D}}$ regimes. Also
+  note that the salt diffusivity (see Eq. (4)) and the specific
+  surface adsorption of ions may also influence the experimentally
+  observed $\xi_{\mathrm{max}}$ beyond the simple
+  $\lambda_{\mathrm{D}}$ effect.}
+ Further including the
+specific interaction of ionic species with the graphene membrane {-
+  such as cation-$\pi$ interacation \cite{shi2013ion}} - may give even
+better agreement with experimental results \cite{Ghosh_2018}. More
+interestingly, based on our theoretical analysis, we predict that a
+very high degree of salt rejection ($\xi>$ 0.99) can be already
+achieved when $\lambda / r_{\mathrm{G}}>$3. In other words, for
+example, when the Debye length is 20 nm, one can suppress 99 \% of the
+diffusive flux by further reducing the pore radius down to $\sim$5-6
+nm, which still remains larger than the hydrated radii. In combination
+with the development of nanoscale etching techniques, we believe that
+the physical picture presented here makes one step closer to
+large-scale production of graphene membranes.
 
@@
 
-\begin{acknowledgement}
-  R.M.W. acknowledges Dr. Kyoungjun Choi from ETH Zurich for the measurement of the electron mobility 
+\section*{Acknowledgment}
+\label{sec:acknowledgment}
+
+% \begin{acknowledgement}
+  R.M.W. acknowledges Dr. Kyoungjun Choi from ETH Z\"{u}rich for the measurement of the electron mobility 
   of patterned graphene and is grateful for the support from the Binnig and Rohrer
-  Nanotechnology Center of ETH Zurich and IBM Zurich. T.T. and
+  Nanotechnology Center of ETH Z\"{u}rich and IBM Z\"{u}rich. T.T. and
   C.J.S. are grateful for the financial support from the ETH startup
   funding. 
-\end{acknowledgement}
+% \end{acknowledgement}
 
@@
 simulations. All authors contributed to writing and discussion.
+
+\section{Supporting Information}
+\label{sec:acknowledgment-1}
+Detailed descriptions and discussions about graphene membrane
+manufacturing, ion diffusion measurement, control transport
+experiment with copper tape, circuit analog transport model, salt
+Debye length and conductivity table, graphene charge carrier density
+measurements, ionic pathway mechanism, effect of pore size
+distribution, and implementation of numerical simulations
 
@@
   \includegraphics[width=0.95\linewidth]{img/fig2.pdf}
-  \caption{\textbf{The experimental evidence of salt rejection.}
-    \textbf{a}.An example of measured conductivity in LCR as a
+  \caption{ \textbf{The experimental evidence of salt rejection.}
+    \textbf{a}. An example of measured conductivity in LCR as a
     function of time. The slope of conductivity-time curve when
@@
     gating. \textbf{b}. Molar diffusive flux through bare PCTE (blue
-    bars: experimental; red bars: model values) and PG+PCTE (green
-    bars) membranes for different salts. \textbf{c}. Experimentally
+    bars: experimental, $\boldsymbol{J}_{\mathrm{PCTE}}$ Exp.; red
+    bars: model values, $\boldsymbol{J}_{\mathrm{PCTE}}$
+    (Eq. \ref{eq:j-pcte})) and PG+PCTE
+    ($\boldsymbol{J}_{\mathrm{PG0}}$ Exp.; green bars) membranes for
+    different salts. \textcolor{blue}{The error bars for
+      $\boldsymbol{J}_{\mathrm{PCTE}}$ Exp. were estimated by the
+      standard deviation of three consecutive measurements. The error bars
+      for $\boldsymbol{J}_{\mathrm{PCTE}}$ (Eq. \ref{eq:j-pcte})
+      correspond to the calculated maximum and minimum ion flux values
+      using the membrane parameters provided by the vendor. The error
+      bars for $\boldsymbol{J}_{\mathrm{PG0}}$ Exp. were estimated by
+      the standard deviation of the ion fluxes in the first interval
+      during the gating experments.)}  \textbf{c}. Experimentally
     measured salt rejection factor $\xi$ as a function of
@@
     asymmetric response, with a higher degree of salt rejection for
-    $V_{\mathrm{G}}>0$. \textbf{d}. $\xi_{\mathrm{max}}$ as a function
-    of KCl concentration, fitted by a power law relation, suggesting
-    the effect of Debye length on the observed salt rejection, since
+    $V_{\mathrm{G}}>0$. \textcolor{blue}{The error bars were estimated
+      by the standard deviation for the ion fluxes in the second
+      interval during the gating experiments.}
+    \textbf{d}. $\xi_{\mathrm{max}}$ as a function of KCl
+    concentration, fitted by a power law relation, suggesting the
+    effect of Debye length on the observed salt rejection, since
     $\lambda_{\mathrm{D}} \propto c_{0}^{-\frac{1}{2}}$.}
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2019-08-20 data/plots/src/plot_salt.py

@@ -142,9 +142,10 @@ z_n = numpy.array([1, 1, 1, 1, 2, 2, 3])
 I = (z_p ** 2 * c_p + z_n ** 2 * c_n) / 2.0
 eps = 78;
 LD = (eps * epsilon_0 * k * 300 / (2 * N_A * e ** 2 * I)) ** 0.5 / 1e-9
+print(LD)
 
 from scipy.stats import linregress
-regres = linregress(LD, [rect[s][1] for s in salts])
+regres = linregress(LD, [rect[s][-1] for s in salts])
 k = regres.slope; b = regres.intercept; r = regres.rvalue
 print(k, b, r)
 
@@ -152,13 +153,13 @@ plt.figure(figsize=(2.5, 2.5))
 # plt.plot(LD, [rect[s][0] for s in salts], "o", label="Exp", alpha=0.8)
 plt.errorbar(LD, [rect[s][0] for s in salts],  yerr=[rect[s][1] for s in salts], fmt="o", alpha=0.8, label="Exp")
 plt.plot(LD, [rect[s][-1] for s in salts], "D", label="FEM", alpha=0.8)
-# xx = numpy.linspace(3, 35)
-# yy = k * xx  + b
-# plt.plot(xx, yy, "--")
+xx = numpy.linspace(10, 35)
+yy = k * xx  + b
+plt.plot(xx, yy, "--")
 # plt.xscale("log")
 plt.xlabel("LD")
-plt.xlim(10, 33)
-plt.ylim(-0.1, 0.8)
+plt.xlim(12, 33)
+plt.ylim(-0.08, 0.8)
 plt.legend()
 plt.tight_layout()
 plt.savefig(os.path.join(plot_path, "rect_comparison.svg"))
